### 2020-09-22 paper.tex
Update on Overleaf.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}

\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}

\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

\ifCLASSINFOpdf
\else
\fi

\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
pdftitle={Bare Demo of IEEEtran.cls for Computer Society Journals},%<!CHANGE!
pdfsubject={Typesetting},%<!CHANGE!
pdfauthor={Michael D. Shell},%<!CHANGE!
pdfkeywords={Computer Society, IEEEtran, journal, LaTeX, paper,
             template}}%<^!CHANGE!

\begin{document}

\title{Fast Influence Maximization Sketching\\ with Fusing and Vectorization }

\author{G\"{o}khan~G\"{o}kt\"{u}rk
        and~Kamer~Kaya% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G. G\"{o}kt\"{u}rk and K. Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, Istanbul, Turkey.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
}
%FIXME

\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for IEEE Computer Society Journals}

\IEEEtitleabstractindextext{%
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}}

\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEpeerreviewmaketitle

\ifCLASSOPTIONcompsoc
\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\else
\section{Introduction}
\label{sec:introduction}
\fi

Influence maximization is the problem of finding subset of $K$ vertices in a graph $G$ that has maximum reachability on some diffusion model $M$.

In addition to introducing the problem, Kempe et al.\cite{kempe2003maximizing} proved it to be NP-hard and provided a greedy Monte-Carlo approach that has a constant approximation for the optimal solution.

Many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, skim, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.

\section{Notation and Background}\label{sec:background}

We denoted $G = (V,E)$ as a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations between the agents in $V$.
The neighborhood of a vertex $u \in V$ is denoted as $\Gamma_G(v) = \{v: (u,v) \in E\}$. 
A graph $G' = (V',E')$ is a subgraph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. 
Diffusion probability on edge $(u, v) \in G$ is noted as $w_{u,v}$.
$w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(v)$   & Neighborhood of vertex $v$ in graph $G$\\
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
\hline\hline
        %$p$             & Sampling probability for edges\\
%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $B$             & Batch size, number of simultaneous simulations ran.\\
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & Sketch $j$th register for vertex $u$\\
        $\varsigma $    & Influence gained before sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after sketch build\\
        $\epsilon_g$    & Allowed global estimation error ratio\\
        $\epsilon_l$    & Allowed local estimation error\\ 
        $\epsilon_c$    & Allowed non-convergenced vertex ratio\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

Influence Maximization aims to find a seed set $S \subseteq V$ among all possible size $K$ subsets of $V$ that maximizes an {\em influence spread function} $\sigma$  when the diffusion process is initiated from $S$. Although we focus on undirected graphs, for IM, the graph can be directed or undirected depending on the initial construction. Figure~\ref{fig:xx} shows a~(Fig.~\ref{fig:ic}) and directed~(Fig.~\ref{fig:wc})
graph for which the weights on the edges are diffusion/influence probabilities.

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.45\linewidth]{ic-dif.png}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.45\linewidth]{wc-dif.png}}
    \\% IMAGES HERE
  \caption{\protect\subref{fig:ic} 
The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph obtained from the directed one by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. 
  }
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}
The influence spread function $\sigma_{G,M}(\cdot)$ computes the {\em expected} number of agents/nodes/vertices influenced~(activated) through a diffusion model $M$. For the sake of simplicity, we drop $M$ from the notation; in the rest of the text, $\sigma_{G}$ refers to $\sigma_{G,M}$. Some of the popular diffusion models for IM in the literature are {\em independent} and {\em weighted cascade}~(IC and WC),  and {\em linear threshold}~(LT)~\cite{kempe2003maximizing}.

\subsection{Sketch}\label{sec:sketch}
The count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements. Computing reachability sets of a vertex is a similar problem; cardinality of all vertices visited is calculated while traversing sample sub-graphs from the given vertex. Exact cardinality calculations requires memory proportional to the cardinality.

Reachability set of a vertex is distinct union of all connected vertices' reachability sets. Many other Influence Maximization methods exploit this property in some degree.

The methods based on Reverse reachability and Bottom-Up Traversal, utilizes this property directly to merge reachability sets of connected vertices to estimate vertices influence.
MixGreedy method goes one step further; it utilizes that all vertices in a connected component that have the same reachability set in undirected graphs. So that, for a sample graph, all reachability sets can be found in single graph traversal.

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for non-trivial graphs. 
% If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(ackermann'(\sigma))$ complexity.

Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm can estimate cardinality of distinct elements in reachability sets with constant number of registers($M$), and most importantly union of these sets can be done in constant number of operations.

Flajolet–Martin sketch only stores how rare elements are in a multi-set.Rarity of the elements are often computed by counting leading zeros in item's hash values. Items are added by storing longest leading zero count. Cardinality estimation can be done by taking 2 to the power of the stored value. Multiple registers, $M[j]$, are commonly used to reduce variance, average of longest running zeros can be used compute the cardinality and the result is divided to correction factor $\phi \approx 0.77351$ to correct hash collisions.

The merge operation for two sketches, $M_u$,$M_v$, can be performed by computing the pairwise maximum of the registers; $M[j] = max(M_u[j],M_v[j]) ~ \forall j\in(0,J]$

In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate estimated influence, we use one register per simulation, and take average of longest leading zero counts to calculate average cardinality of reachability sets. Also, in an another perspective, it is same as using register as much as MC simulation, where updates are done with same probability as influence propagation.

\subsection{SIMD}
{\em Single Instruction-Multiple Data} machines exploits data level parallelism to perform the same operation on multiple data points simultaneously. In this work, we utilized Advanced Vector Extensions (AVX2) instruction set. AVX2 works on 256-bit registers in multiple packed forms; 8x32 bit operations are used in fused sampling, where as sketch merge  performed with 32x8bit operations. This dichotomy between operations solved by processing in 32 simulations batches at a time.
Even-though, auto-vectorization is enabled, most of the operation mention are cannot by vectorized by the used compiler. As far as we know, no compiler vectorizes chain conditional move or move-mask operations. Vectorization in the implementation is done using explicit intrinsics.

% First, active edges are checked by generating random values, $P(u,v)_r$. After comparing random values with edge threshold, active edges are store in an 32bit integer as one-hot vector. Then,

For completeness, the intrinsics explicitly used in this paper are described in Table~\ref{tab:avx2-instructions}.

\begin{table}[!ht]
    \caption{AVX2 intrinsics used in the implementation.}
    \label{tab:avx2-instructions}
    \centering

    \begin{tabular}{|p{0.33\linewidth}|p{0.58\linewidth}|}
    \hline
    Intrinsic & Definition\\
    \hline
    {\tt \_mm256\_set1\_epi32} & Initializes 256-bit vector with scalar integer values. Doesn't map to any AVX instructions. \\
        % \hline
    {\tt \_mm256\_and\_si256} & Performs bitwise logical AND operation on 256-bit integer vectors. \\
            % \hline
    {\tt \_mm256\_xor\_si256} &  Performs bitwise logical XOR operation on 256-bit integer vectors.\\
            % \hline
    {\tt \_mm256\_cmpgt\_epi32} & Compares packed 8x 32-bit integers of two input vectors. \\
            % \hline
        % \hline
    {\tt \_mm256\_movemask\_ps} & Extracts the first bits of 8x 32-bit elements in a compact 8-bit format \\
            % \hline
    {\tt \_mm256\_blendv\_epi8} & Blends/selects byte elements of input vectors depending on the bits in a given mask vector.\\ 
             \hline         
    \end{tabular}
\end{table}{}

\section{Method}\label{sec:method}

\subsubsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling sub-graphs $\hat{G}$ from $G = (V, E)$ to simulate the diffusion process.  Sampling can be a dominating factor in processing; sampling may demand multiple passes on the graph, if samples are memoized, multiple times of the graph size needs to be stored.
In this work, samples are not generated explicitly. By using a hash-based, fused sampling, we eliminate the necessity of in-memory creation and storage of the sample sub-graphs.
While processing an edge, it is considered for all possible samples.
It is sampled or skipped depending on the outcome of hash based random value. The hash function used is given in equation \ref{eq:hash}
\begin{equation}
    \label{eq:hash}
    h(u,v) = \mbox{{\sc Murmur3}}(u||v)  
\end{equation}
where $||$ is the concatenation operator.

The {{\sc Murmur3}}~\cite{MurmurHash3} hash function is preferred because of its simplicity, good avalanche behavior and bias$.

For performance considerations, edge hash values were pre-computed in our work and only existing pairs were considered. The trade-off between extra memory and computation here maybe not be applicable for different architectures and faster/simpler hash functions.

Although the above-mentioned approach generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.

Multiple deterministic random values for each edge is generated by using the edge hash values and random numbers $X_r$ associated with each simulation $r$. 
Sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed as follows; First, $h(u,v)$ is XOR'ed with a uniformly randomly chosen $X_r \in_R [0, h_{max}]$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$. Formally,
\begin{equation}
    \label{eq:hash_prob}
    {\rho}(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
\end{equation}

The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations. In addition, the following control flow branch can be removed using conditional move operations. An efficient SIMD implementation of this approach will be discussed later in this section.

Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed. This property allows us to generate good enough pseudo-random values for fair sampling. To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the Cumulative Distribution Function~(CDF) of random values $P(u,v)_r$ used while sampling.

For a given graph $G = (V,E)$, the CDF of a sampling probability $x$ is computed as $\Pr\left(x \leq P(u,v)_r\right)$ for all $(u,v) \in E$ and $0 \leq r < R$. Figure~\ref{fig:prob_cdf} shows the CDFs for 12 real-life networks. The sampling probability distribution with hash-based computation is almost identical with the uniform distribution which is used to simulate the influence diffusion process.

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{cdf}
    \caption{Cumulative distribution function of hash-based sampling probabilities on various real-life networks.}
    \label{fig:prob_cdf} 
\end{figure}

%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
Since it is possible to know if the edge traversed whether is in any sample, many memory access overheads are avoided. Only down-side of hash-based fused sampling is that, all probabilities $P(u,v)_r$  should be generated for each edge traversal. Fortunately, this computations are quite fast on modern computing hardware.

\subsection{Reachability Set Cardinality Estimation}

Greedy solution to influence maximization problem requires finding a vertex that maximizes marginal influence gain at each step. Until $K$ vertices are added to the seed set this procedure is repeated. 
Finding a vertex's influence is distinct element count in all sample sub-graphs. Count-distinct sketch we mentioned in section \ref{sec:sketch} is

\begin{algorithm}
\caption{\sc{SketchFuser}($G,K,J$)}
\label{algo:newgredy}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$K$: number of seed vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
\algorithmicensure{$S$: a seed set that maximizes influence on $G$
}
\begin{algorithmic}[1]
    \State {$S \leftarrow \{\emptyset\}$}
    \For{$ v\in V$}
        \For{$ j\in J$}
            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
        \EndFor
    \EndFor
    \State $M \leftarrow Simulate(G,M,\emptyset)$
    \State $mask \leftarrow zeros(J)$
    \State $\varsigma \leftarrow 0$
    \For{$k=1\ldots K$}
        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
        \State $S \leftarrow S \cup \{s\}$
        \State $e \leftarrow estimate(merge(mask,M_s))$
        % \State $R_S \leftarrow run\_cascade(G,S,J)$
        \State {Compute seed set $S$'s Reachability set $R_S(S)$ }
        \State $\sigma_G(S) \leftarrow |R_S|/J$
        \State $\delta = \sigma - \varsigma$
        \If{$ (e - \delta) / \delta < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$}
            \State $mask \leftarrow merge(mask,M_s)$
        \Else
            \For{$ v\in V$}
                \For{$ j\in J$}
                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
                \EndFor
            \EndFor
            \State $M \leftarrow simulate(G,M,R_S)$
            \State $mask \leftarrow zeros(J) $ 
            \State $\varsigma \leftarrow \sigma $ 
        \EndIf
    \EndFor
    \State \Return $S$
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{\sc{Simulate}($G,M,J,R_S$)}
\label{algo:newgredy}
\algorithmicrequire{$G = (V,E)$: the influence graph
\\\hspace*{6.6ex}{$M$: Sketch vectors of vertices
\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations
\\\hspace*{6.7ex}$R_S$: Reachability set of the seed set
}
\\}
\algorithmicensure{$M$: Updated Sketch vectors
}
\begin{algorithmic}[1]
    \State {$L \leftarrow V$}
    \State {$L' \leftarrow {\emptyset}$}
    \While{$|L|/|V| > \epsilon_c$}
        \For{$e_{u,v} \in \Gamma(L)$} %REVERSE THIS
            \For{$j \in (0,J]$}
                \If{$P(u,v)_j < W_{u,v} \land u  \not\in R_S[j]$}
                    \State{$M_u[j]\leftarrow max(M_u[j],M_v[j])$}                
                \EndIf
            \EndFor
            \If {$M_u$ changed}
                \State $L' \cup u $
            \EndIf
        \EndFor
        \State $L \leftarrow L'$
        \State $L' \leftarrow \{\emptyset\}$
    \EndWhile
\end{algorithmic}
\end{algorithm}

\section{Evaluation}\label{sec:evaluation}

\section{Related Work}\label{sec:relatedwork}

\section{Conclusion}\label{sec:conclusion}

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\bibliographystyle{IEEEtran}
\bibliography{refs}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/gokhan.png}}]{G\"{o}khan~G\"{o}kt\"{u}rk} is a PhD candidate at the Faculty of Engineering and Natural Sciences in Sabancı University. He has received his BS and MS degrees from Sabancı University as well. He is interested in High Performance Computing, Parallel Programming, and Graph Processing.
\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Assistant Professor at the Faculty of Engineering and Natural Sciences at Sabancı University. He got his PhD from Dept. Computer Science and Engineering from Bilkent University. He worked at CERFACS, France, as a post-graduate researcher in the Parallel Algorithms Project. He then joined the Ohio State University in September 2011 as a postdoctoral researcher, and in December 2013, he became a Research Assistant Professor in the Dept. of Biomedical Informatics.
His current research interests include Parallel Programming, High Performance Computing, and Cryptography. 
    \end{IEEEbiography}

\end{document}

### 2020-09-25 paper.tex
Update on Overleaf.

@@
 \usepackage{algorithm}
+\usepackage{subfig}
 \usepackage[noend]{algpseudocode}
@@
 The neighborhood of a vertex $u \in V$ is denoted as $\Gamma_G(v) = \{v: (u,v) \in E\}$. 
-A graph $G' = (V',E')$ is a subgraph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. 
+A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. 
 Diffusion probability on edge $(u, v) \in G$ is noted as $w_{u,v}$.
@@
 %        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
+        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
         $h(u,v)$        & Hash function for edge $\{u,v\}$\\
@@
         \hline\hline
-        $B$             & Batch size, number of simultaneous simulations ran.\\
+        $B$             & Batch size\\
         $e$             & Estimated reachability set size\\
@@
   \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.45\linewidth]{ic-dif.png}}
+       \includegraphics[width=0.45\linewidth]{./images/ic-dif.png}}
   \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.45\linewidth]{wc-dif.png}}
+        \includegraphics[width=0.45\linewidth]{./images/wc-dif.png}}
     \\% IMAGES HERE
@@
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for non-trivial graphs. 
-% If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
+If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
 if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(ackermann'(\sigma))$ complexity.
 
-Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm can estimate cardinality of distinct elements in reachability sets with constant number of registers($M$), and most importantly union of these sets can be done in constant number of operations.
+Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate cardinality of distinct elements in reachability sets with constant number of registers($M$), and most importantly union of these sets can be done in constant number of operations.
 
 Flajolet–Martin sketch only stores how rare elements are in a multi-set.Rarity of the elements are often computed by counting leading zeros in item's hash values.
+The registers are initialized with zero values in begining.
 Items are added by storing longest leading zero count.
 Cardinality estimation can be done by taking 2 to the power of the stored value.
-Multiple registers, $M[j]$, are commonly used to reduce variance, average of longest running zeros can be used compute the cardinality and the result is divided to correction factor $\phi \approx 0.77351$ to correct hash collisions.
+Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
+Adding item $x$ to register $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
 
-The merge operation for two sketches, $M_u$,$M_v$, can be performed by computing the pairwise maximum of the registers; $M[j] = max(M_u[j],M_v[j]) ~ \forall j\in(0,J]$
+\begin{equation}
+    \label{eq:sketch-add}
+    M'[j] = max(M[j],clz(h_j(x)) ~ \forall j\in(0,J]
+\end{equation} where $clz$ is count leading zeros function and $J$ is number of sketch registers.
+
+The merge operation for two sketches, $M_u$,$M_v$, can be performed by computing the pairwise maximum of the registers. Formally; 
+\begin{equation}
+    \label{eq:sketch-merge}
+    M'[j] = max(M_u[j],M_v[j]) ~ \forall j\in(0,J]
+\end{equation} 
+where $M'$ is union of set and $J$ is number of sketch registers.
+
+Average of longest running zeros can be used compute the cardinality and the result is divided to correction factor $\phi \approx 0.77351$ to correct hash collisions.
+\begin{equation}
+    \label{eq:sketch-estimate}
+    e = 2^{\bar{M}}/\phi
+\end{equation} 
+where $e$ distinct cardinality and $\bar{M}$ is M's registers mean.
 
@@
 This dichotomy between operations solved by processing in 32 simulations batches at a time.
-Even-though, auto-vectorization is enabled, most of the operation mention are cannot by vectorized by the used compiler.
+Even-though, auto-vectorization is enabled, most of the operation mention are cannot be vectorized by the compiler.
 As far as we know, no compiler vectorizes chain conditional move or move-mask operations.
@@
 
-\subsubsection{Hash-based Fused Sampling}
+\subsection{Hash-based Fused Sampling}
 The probabilistic nature of cascade models requires sampling sub-graphs $\hat{G}$ from $G = (V, E)$ to simulate the diffusion process.
@@
 
-The {{\sc Murmur3}}~\cite{MurmurHash3} hash function is preferred because of its simplicity, good avalanche behavior and bias$.
+The {{\sc Murmur3}}~\cite{MurmurHash3} hash function is preferred because of its simplicity, good avalanche behavior and bias.
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{cdf}
+    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
     \caption{Cumulative distribution function of hash-based sampling probabilities on various real-life networks.}
@@
 %Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-Since it is possible to know if the edge traversed whether is in any sample, many memory access overheads are avoided.
-Only down-side of hash-based fused sampling is that, all probabilities $P(u,v)_r$  should be generated for each edge traversal.
-Fortunately, this computations are quite fast on modern computing hardware.
+Being able to generate infinitely many samples on-the-fly, allows us to avoid many memory accesses.
+The only down-side of hash-based fused sampling is that we have to generate all random values,   $P(u,v)_r$, for each edge traversal.
+Fortunately, these computations are quite fast on modern computing hardware.
 
 \subsection{Reachability Set Cardinality Estimation}
+A greedy solution to the influence maximization problem requires finding a vertex that maximizes marginal influence gain at each step until the seed set size reaches $K$.
+And, Single vertex influence estimation is the same problem as the count-distinct problem applied to all sample sub-graphs.
+So, it is possible to use Count-distinct sketches to estimate influence scores in the greedy method.
 
-Greedy solution to influence maximization problem requires finding a vertex that maximizes marginal influence gain at each step.
-Until $K$ vertices are added to the seed set this procedure is repeated.
-Finding a vertex's influence is distinct element count in all sample sub-graphs. Count-distinct sketch we mentioned in section \ref{sec:sketch} is
+We propose an influence maximization method, that utilizes the Count-distinct sketch we mentioned in section \ref{sec:sketch} to estimate averages of distinct elements in sample subgraphs for both time and space efficiency.
+Algorithm \ref{algo:main} describes the method proposed as follows;
+
+First, reachability sets of all vertices are initialized with vertices themselves.
+For all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{\hat{G}_j}(u) = \{u\}$.
+Then, we perform diffusion process on the sketch registers.
+
+The diffusion process works as follows; first, all vertices added to live vertices set $L$.
+Then, incoming edges $(u,v)$ for all live vertices are processed.
+For all simulation $u$ is live, the sketch of both sides are merged and set to $u$ registers.
+If any of the sketch-registers change, vertex $u$ added to the next iteration's live vertices set $L'$.
+After live edges are processed, if the next iteration's live vertices set is smaller than the convergence threshold $\epsilon_c$, the diffusion process concluded.
+If not, we swap $L$ and $L'$, clear $L'$, and then diffusion processed is repeated.
+
+In Greedy algorithm\cite{kempe2003maximizing} for each candidate vertex, influence diffusion computations are perform for each vertex.
+On the other hand, diffusion on sketch registers allows finding all vertices reachability set.
+All vertices influence in single step distance only computed once.
+This dynamic programming like property allows fast selection of influence maximizing candidate.
+
+After diffusion, following process is repeated until $K$ vertices are added to the seed set; For all vertex $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $mask$ and their sketch registers.
+The $mask$ used for the sketch of $R_G(S)$ and initialized with zeros.
+Vertex with maximum cardinality is selected to add to the seed set.
+Then, the actual Monte-Carlo simulations were performed to compute the reachability set of the seed set.
+Having actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
+Blocked vertices skipped in the diffusion step in coming iterations.
+Besides, the real influence score allows us to rebuild our sketch when the sketches have gone stale.
+
+The sketches are assumed as stale if the absolute error in estimated total influence score is more than global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch larger than local threshold $\epsilon_{l}$.
+Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minimal in the total score.
+If a rebuild is not required, only the last added vertex's sketch also merged with $mask$ to update $R_G(S)$.
 
@@
 \caption{\sc{SketchFuser}($G,K,J$)}
-\label{algo:newgredy}
+\label{algo:main}
 \algorithmicrequire{$G = (V,E)$: the influence graph
@@
             \EndFor
-            \State $M \leftarrow simulate(G,M,R_S)$
+            \State $M \leftarrow Simulate(G,M,R_S)$
             \State $mask \leftarrow zeros(J) $ 
@@
 
-\begin{algorithm}
+\begin{algorithm}[!ht]
 \caption{\sc{Simulate}($G,M,J,R_S$)}
-\label{algo:newgredy}
+\label{algo:diffusion-step}
 \algorithmicrequire{$G = (V,E)$: the influence graph
@@
     \EndWhile
+\end{algorithmic}
+\end{algorithm}
+\FloatBarrier
+\subsection{Vectorization and Performance considerations}
+
+Traditional two-step, sample-then-diffuse computation model stores data loosely-coupled.
+Sampled edges are stored together, diffusion related information stored afar.
+This way, SIMD operation is allowed on consecutively located edges, requiring random memory accesses for the diffusion process.
+Even if tightly coupled
+
+One of the main advantages of fused sampling is allowing similar simulation data and computations together. 
+Our implementation generates $B/4$ sample edges and runs $B$ simulations at a time. 
+The dichotomy of two batch sizes comes from SIMD width; 
+sampling probabilities are computed in 31-bit fixed-point precision, 
+whereas since we are using 64-bit hash values, sketch registers only require $\left\lceil log2(64+1) \right\rceil = 6$ bits.
+Aligned to the nearest data type they can fit, sampling probabilities utilizes 8x32-bit operators, where as sketch operations employ 32x8bit SIMD vectors.
+
+% \subsubsection{Vectorized edge processing} first loads edge hash and threshold to vector units.
+Then, we check if the edge is live in any simulations.
+8 random values generated by XOR'ing hash vector and X_r
+
+\begin{algorithm}
+    \caption{\sc{Vectorized-Merge} ({$u,v,X_r,M_u,M_v,$})}\label{alg:VecLabel}
+    \algorithmicrequire{
+    $u:$ source vertex\\
+    \hspace*{7ex}$v:$ target vertex\\
+    \hspace*{7ex}$X$: random number for simulations\\
+    \hspace*{7ex}$M_u$: sketch registers of $u$\\
+    \hspace*{7ex}$M_v$: sketch registers of $v$\\
+    \hspace*{7ex}$visited$: one-hot visited vector grouped by samples}\\
+    \algorithmicensure{$islive$: a boolean which state if $u$ is live}
+    % \hspace*{8ex}$live_v$: a boolean which state if $v$ is live
+    \begin{algorithmic}[1]
+        \State $islive \leftarrow False$
+        \For{$r \in [0,J)~|~r~mod~32 = 0$}
+            \State $hashvec \leftarrow \_mm256\_set1\_epi32(hash(u,v)$
+            \State $threshold \leftarrow \_mm256\_set1\_epi32(w_{u,v})$
+            \State $live \leftarrow 0$
+            \For{$b\in [0,32)~|~b~mod~8 = 0 $}
+                \State $prob \leftarrow \_mm256\_xor\_si256(X_{r+b\dots8},hashvec)$
+                \State $cmp \leftarrow \_mm256\_cmpgt\_epi32(threshold, prob)$
+                \State $cmpmask \leftarrow \_mm256\_movemask\_ps(cmp))$
+                \State $live\leftarrow (cmpmask<<b)~|~live $
+                \EndFor
+                \If{$live = 0$}
+                    \State continue
+                \EndIf
+                \State $live \leftarrow live~\&~\sim visited_{r\dots32}[u]$
+                \State $livebytes \leftarrow expand\_bits\_to\_bytes(live)$
+                \State $M' \leftarrow 
+                    \_mm256\_cmpgt\_epi8(M_u[r..32],M_v[r..32])$
+                \State $select \leftarrow \_mm256\_and\_si256(livebytes,M')$
+                \State $\_mm256\_blendv\_epi8(M_u[r..32],M_v[r..32])$
+                % \State $$
+                \State $islive \leftarrow islive~|~  \_mm256\_cmp\_ps(\newline
+                    \hspace*{4em}\_mm256\_setzero\_ps(), \newline
+                    \hspace*{4em}\_mm256\_castsi256\_ps(sel))$
+
+                % \State $live \leftarrow live \setminus \bigcup_{} j|u\notin R_{\hat{G}_j} $ 
+            % \EndIf
+        \EndFor
     \end{algorithmic}

### 2020-12-13 paper.tex
Update on Overleaf.

@@
 \usepackage{subfiles}
+\usepackage{url}
 \usepackage[pdftex]{graphicx}
@@
 \newcommand\ovr[1]{\overrightarrow{#1}}
-
+\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
+\usepackage{booktabs}
 \usepackage{array}
@@
 \usepackage{enumitem}
-
+%%%%%%
+% Notes: 
+% plot grouping/hue +
+% table smallcaps +
+% Time score memory center +
+% Abstract
+% Differences between infuser and us+
+% time skecth diff between us +
+% neden 0.005 +
+% active vertex colors +
+%%%%%
 \ifCLASSOPTIONcompsoc
@@
 \fi
+\newcommand\ggx[1]{\textcolor{blue}{#1}}
 
@@
 pdfsubject={Typesetting},%<!CHANGE!
-pdfauthor={Michael D. Shell},%<!CHANGE!
-pdfkeywords={Computer Society, IEEEtran, journal, LaTeX, paper,
-             template}}%<^!CHANGE!
+pdfauthor={Gokhan Gokturk, Kamer Kaya},%<!CHANGE!
+pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch}}%<^!CHANGE!
+
+\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
+\usepackage{xcolor}
+\newcommand\kktodo[1]{\textcolor{red}{#1}}
+
+\newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
+\newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
+
+\newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
+\newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
+\newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}
 
@@
 
-\title{Fast Influence Maximization Sketching\\ with Fusing and Vectorization }
+\title{Fast and Error-Adaptive Count-Distinct Sketch
+\\for Influence Maximization}
 
@@
 G\"{o}kt\"{u}rk and K.
-Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, Istanbul, Turkey.}% <-this % stops a space
+Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, TR~34956, Istanbul, Turkey.}% <-this % stops a space
 %\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
@@
 
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for IEEE Computer Society Journals}
+% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+% {Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for IEEE Computer Society Journals}
 
@@
 \begin{abstract}
-The abstract goes here.
+Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
+Due to the NP-Hardness of finding an optimal seed set, approximation methods are frequently used for IM.
+In addition to high-quality yet expensive approximation algorithms, to meet with the scale of today's networks, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature.
+As expected, the quality of the seed sets for the latter is inferior to those of the former.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and the recently proposed hash-based, fused sampling.
+To estimate the vertex set sizes influenced throughout the simulations, we use per-vertex Flajolet-Martin sketches where each sketch register corresponds to a sample sub-graph.
+During the diffusion simulations, the reach set cardinalities of a single vertex are stored in adjacent registers in memory.
+This allows the proposed algorithm to find the number of influenced vertices in a single simulation step in different simulations at once.
+In addition, thanks to its efficiency and scalability of the our the parallel implementation can rebuild the sketches after observing large estimation errors.
+Our experimental results show that the proposed method finds high-quality seed sets  while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
+In addition, it is shown to be $3.5\times$--$11.1\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
 \end{abstract}
-
 % Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Computer Society, IEEE, IEEEtran, journal, \LaTeX, paper, template.
-\end{IEEEkeywords}}
+}
 
@@
 
-Influence maximization is the problem of finding subset of $K$ vertices in a graph $G$ that has maximum reachability on some diffusion model $M$.
+The study of efficient information/influence propagation in networks becomes an important area of research with several applications from many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
+As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
+Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagates the information/influence effectively is essential.
 
-In addition to introducing the problem, Kempe et al.\cite{kempe2003maximizing} proved it to be NP-hard and provided a greedy Monte-Carlo approach that has a constant approximation for the optimal solution.
+Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability under some diffusion model $M$.
+In addition to introducing the problem, Kempe et al.~\cite{kempe2003maximizing} proved it to be NP-hard and provided a greedy Monte-Carlo approach that has a constant approximation for the optimal solution.
+This greedy approach is one of the most frequently applied algorithms for IM.
+The time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+Although they perform well in terms of seed-set quality, in consequence, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices.
+Due to this reason, many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.
 
-Many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, skim, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+% However, these simulation-based, greedy algorithms provide the best possible approximation guarantees. Therefore they are considered as the gold standard for IM.
+
+Simulating a greedy algorithm in parallel is an obvious and straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
+However, for large networks, a greedy approach with a good approximation guarantee does not come cheap even if a large number of processing units/cores are available on networks with billions of vertices and edges.
+Following similar attempts in the literature, we propose a parallel, sketch-based greedy approach that approximates the Monte-Carlo processes.
+The proposed approach does not exactly count the number of influenced vertices.
+Instead, it leverages Count-Distinct sketches.
+in this work, we apply parallelism in multiple levels; thread-level and instruction-level parallelism.
+While modern compilers employ instruction-level parallelism effectively and automatically for applications with regular memory access patterns, graph kernels are usually harder to deal with.
+The irregularity of the neighbor IDs.
+.....
+due to their irregular memory access patterns, it is not a straightforward task for graph processing kernels.
+Besides, vectorization attempts on such kernels typically fail to provide substantial speed-up in performance.
+
+In this work;
+\begin{itemize}[leftmargin=*]
+\item We propose, \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, a blazing-fast, and accurate Influence Maximization algorithm.
+The proposed scheme samples the edges as they are traversed across several simulations.
+Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
+
+\item Running concurrent simulations on per-vertex count-distinct sketches reduces the number of memory accesses.
+While traversing an edge, any number of diffusion simulations can be performed between vertices, using only a single integer (8-bit) per vertex for each simulation.
+
+That is when the simulations traverse the same edge within close time intervals, the edge is accessed only once as long as the simulation timelines allow \acro to do so.
+The suggested approach, therefore, decreases the pressure on the memory management unit.
+In relation, for the cascade model, we employ a vector compute unit, near maximum efficiency to regularize memory accesses.
+%\item In addition to instruction-level parallelism, we parallelize \acro on multi-core architectures.
+
+\item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results.
+For large graphs, due to its \ggx{race condition indifferent} nature, performance scales near linearly with the number of threads available.
+While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.
+
+% \item \acro can be around $200000\times$ faster compared to the traditional greedy approaches.
+It is usable on large graphs that have been considered as {\em too large} in the literature.
+For instance, the new algorithm runs in $2.09$, $0.08$, $0.36$ seconds on networks {\tt Amazon}, {\tt NetHEP}, {\tt NetPhy} with 16 threads where the sequential baseline takes $141.3$, $259.1$ and $1725.2$ seconds, respectively.
+In fact, with a 302,400 seconds~(3.5 days) timeout, the sequential baseline can process only the above-mentioned 3 (out of 12) real-life graphs, having 1.2M, 58.9K and 231.5K edges.
+On the other graphs, the original algorithm cannot complete the simulations within the time limit.
+However, \acro{} completes all of 12 graphs around 1200 seconds in total, where the maximum is 654 seconds for the {\tt Orkut} network having 3.1M vertices and 117.2M edges.
+
+\item We evaluate the performance, memory consumption, and influence score with a state-of-the-art influence maximization algorithms {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim}, {\sc Imm}~\cite{minutoli2019fast} in order to accurately position the performance of \acro{} in the IM literature.
+The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than state-of-the-art while still being better in comparison in terms of scores, and using a comparable amount of memory.
+
+\end{itemize}
+
+The paper is organized as follows: 
+In Section~\ref{sec:background}, we present 
+the background on IM and introduce the mathematical notation. 
+Section~\ref{sec:method} describes the proposed approach in detail.
+In Section~\ref{sec:evaluation}, a thorough performance comparison over the traditional algorithms is provided by conducting experiments on various real-world datasets and influence settings.
+Besides, a comparison with the state-of-the-art from the literature is given.
+Section~\ref{sec:relatedwork} presents a comparative overview of the existing work. Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Notation and Background}\label{sec:background}
 
-We denoted $G = (V,E)$ as a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations between the agents in $V$.
-The neighborhood of a vertex $u \in V$ is denoted as $\Gamma_G(v) = \{v: (u,v) \in E\}$. 
+Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations between the agents in $V$.
+The neighborhood of a vertex $u \in V$ is denoted as $\Gamma_{G}(v) = \{v: (u,v) \in E\}$. 
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. 
@@
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
-        $\Gamma_G(v)$   & Neighborhood of vertex $v$ in graph $G$\\
+        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
         $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
@@
         % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
-        $M_u[j]$        & Sketch $j$th register for vertex $u$\\
-        $\varsigma $    & Influence gained before sketch build\\
+        $M_u[j]$        & $j$th sketch register for vertex $u$\\
+        $\varsigma $    & Influence gained before last sketch build\\
         $\sigma $       & Influence Score\\
-        $\delta$        & Marginal Gain after sketch build\\
-        $\epsilon_g$    & Allowed global estimation error ratio\\
-        $\epsilon_l$    & Allowed local estimation error\\ 
-        $\epsilon_c$    & Allowed non-convergenced vertex ratio\\
+        $\delta$        & Marginal Gain after last sketch build\\
+        $\epsilon_{global}$    & Global estimation error threshold\\
+        $\epsilon_{local}$    & Local estimation error threshold\\ 
+        $\epsilon_{conv}$    & Non-convergenced vertex threshold\\
       %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
@@
   \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.45\linewidth]{./images/ic-dif.png}}
+       \includegraphics[width=0.50\linewidth]{images/ic.pdf}}
   \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.45\linewidth]{./images/wc-dif.png}}
+        \includegraphics[width=0.50\linewidth]{images/wc.pdf}}
     \\% IMAGES HERE
@@
 \protect\subref{fig:wc}
-The directed graph obtained from the directed one by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. 
+The directed graph was obtained from the directed one by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. 
   }
@@
 \end{figure}
-The influence spread function $\sigma_{G,M}(\cdot)$ computes the {\em expected} number of agents/nodes/vertices influenced~(activated) through a diffusion model $M$.
-For the sake of simplicity, we drop $M$ from the notation; in the rest of the text, $\sigma_{G}$ refers to $\sigma_{G,M}$.
-Some of the popular diffusion models for IM in the literature are {\em independent} and {\em weighted cascade}~(IC and WC),  and {\em linear threshold}~(LT)~\cite{kempe2003maximizing}.
 
-\subsection{Sketch}\label{sec:sketch}
+The $\sigma_{G, M}(\cdot)$ influence spread function calculates the {\em estimated} number of agents / nodes / vertices affected~(activated) through a $M$ diffusion model. 
+We eliminate $M$ from the notation for the sake of elegant simplicity; in the remainder of the text, $\sigma_{G}$ refers to $\sigma_{G, M}$.
+In the literature, {\em independent} and {\em weighted cascade}~(IC and WC), and 
+{\em linear threshold}~(LT)~\cite{kempe2003maximizing} are some of the widely recognized diffusion models for IM.
+
+\begin{itemize}[leftmargin=*]
+\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges, $(u, v)$, is 
+used during the iteration of diffusion, which has an expected probability of $w_{u, v}$, because $u$ was already influenced in the previous rounds. 
+Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
+In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
+
+\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set weights as shown in Figure~\ref{fig:wc}.
+The method, as described in ~\cite{MixGreedy}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
+of incoming edges of $v$ for introducing weight values(which in the original graph is equal to $\Gamma G(v)$).
+Therefore, if $v$ is triggered after the last round with $\ell$ neighbors, its activation probability in the new round is $1-( 1-1 / d_v)^\ell$.
+
+%$ {|E^G_{u,v}|}/{|E^G_{u}|}$ where $|E^G_{u,v}|$ is the number of parallel $\{u, v\}$ edges and $|E^G_{u}|$ is the number of $\{u, .\}$ edges, i.e., all of $u$'s edges in the undirected graph.
+
+\item{\bf Linear threshold} generalizes the cascade models and activates the $v$ vertex once the cumulative activation coming from the neighbors of $v$ exceeds the $\theta v$ threshold. 
+All the $\{u, v\}$~(or $(u, v)$ in the directed graph) edges 
+with active $u$ vertices are taken into account in the process. Vertex $v$ is activated~\cite{kempe2003maximizing} when the number of these edge weights reaches $\theta v$.  
+Therefore, the cascade models are special variants of the linear threshold model with $\theta v = 0 $.
+
+%Each edge $e=(s,v) \in E$ has a weight $w_{s,v}$.
+Each vertex $v$ has incoming edge list $Adj^{-1}(v)$ and $\sum_{s\in Adj^{-1}(v) }{w_{s,v}} \leq 1$.
+Also, each vertex $v$ has associated with a threshold $\theta_v$.
+Initially, $\theta$ is sampled uniformly, and seed set is set as activated.
+Then, until convergence is reached simulation ran to transfer $w_ij$ values from activated vertices to their neighborhoods, activating each vertex $v$ that reach $\theta_v$ value.
+Weights can be uniform i.e 0.1, 0.01, or 0.001 for all edges, as we observed in many work.
+
+\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize of previous models mentioned above.
+In the triggering model, each neighbor has a probability to influence vertex $v$.
+The diffusion process chooses a random subset of vertices called the "triggering set" to activate vertices at each instance.
+\end{itemize}
+
+The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models. 
+% Current studies focus on reducing the number of simulations run \cite{goyal2011celf++, goyal2011simpath}, sketch-based speedup methods\cite{SKIM}, and proxy methods that solve similar yet simpler problems \cite{kempe2003maximizing}.
+%FIXME too many methods, one french paper in python
+%\cite{kempe2003maximizing} 
+We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to the other models in the literature.
+%  \[ \sigma(S^*)=\argmax_{S\subseteq V \land |S| \leq k } \sigma_{G}(S) \]
+
+%is a simple diffusion model that Vertex v can be activated by any of incoming edges from activated vertices w with probability $p$.
+Given a seed set $S$ and influence probability $p$, cascade model starts from activated seed set and tries to diffuse until each of the out-going edges of active vertices are considered.
+The diffusion process considers all edges only once.
+
+\subsection{Count-Distinct Sketch}\label{sec:sketch}
 The count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
-Computing reachability sets of a vertex is a similar problem; cardinality of all vertices visited is calculated while traversing sample sub-graphs from the given vertex.
-Exact cardinality calculations requires memory proportional to the cardinality.
+Computing reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample sub-graphs from the given vertex.
+Exact cardinality calculations require memory proportional to the cardinality.
 
-Reachability set of a vertex is distinct union of all connected vertices' reachability sets. Many other Influence Maximization methods exploit this property in some degree.
+The reachability set of a vertex is a distinct union of all connected vertices' reachability sets. Many other Influence Maximization methods exploit this property to some degree.
 
-The methods based on Reverse reachability and Bottom-Up Traversal, utilizes this property directly to merge reachability sets of connected vertices to estimate vertices influence.
+The methods based on Reverse reachability and Bottom-Up Traversal utilizes this property directly to merge reachability sets of connected vertices to estimate vertices influence.
 MixGreedy method goes one step further; it utilizes that all vertices in a connected component that have the same reachability set in undirected graphs.
-So that, for a sample graph, all reachability sets can be found in single graph traversal.
+So, for a sample graph, all reachability sets can be found in a single graph traversal.
 
@@
 
-Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate cardinality of distinct elements in reachability sets with constant number of registers($M$), and most importantly union of these sets can be done in constant number of operations.
+Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($M$), and most importantly union of these sets can be done in a constant number of operations.
 
-Flajolet–Martin sketch only stores how rare elements are in a multi-set.Rarity of the elements are often computed by counting leading zeros in item's hash values.
-The registers are initialized with zero values in begining.
-Items are added by storing longest leading zero count.
+Flajolet–Martin sketch only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.
+The registers are initialized with zero values in beginning.
+Items are added by storing the longest leading zero count.
 Cardinality estimation can be done by taking 2 to the power of the stored value.
@@
     M'[j] = max(M[j],clz(h_j(x)) ~ \forall j\in(0,J]
-\end{equation} where $clz$ is count leading zeros function and $J$ is number of sketch registers.
+\end{equation} where $clz$ is count leading zeros function and $J$ is the number of sketch registers.
 
@@
 \end{equation} 
-where $e$ distinct cardinality and $\bar{M}$ is M's registers mean.
+where $e$ distinct cardinality and $\bar{M}$ is the mean of the registers.
 
@@
 
-\subsection{SIMD}
-{\em Single Instruction-Multiple Data} machines exploits data level parallelism to perform the same operation on multiple data points simultaneously.
+% \subsection{SIMD}
+% {\em Single Instruction-Multiple Data} machines exploits data level parallelism to perform the same operation on multiple data points simultaneously.
 In this work, we utilized Advanced Vector Extensions (AVX2) instruction set.
@@
 This dichotomy between operations solved by processing in 32 simulations batches at a time.
-Even-though, auto-vectorization is enabled, most of the operation mention are cannot be vectorized by the compiler.
+% Even-though, auto-vectorization is enabled, most of the operation mention are cannot be vectorized by the compiler.
 As far as we know, no compiler vectorizes chain conditional move or move-mask operations.
@@
 
-For completeness, the intrinsics explicitly used in this paper are described in Table~\ref{tab:avx2-instructions}.
+% For completeness, the intrinsics explicitly used in this paper are described in Table~\ref{tab:avx2-instructions}.
 
-\begin{table}[!ht]
-    \caption{AVX2 intrinsics used in the implementation.}
-    \label{tab:avx2-instructions}
-    \centering
+% \begin{table}[!ht]
+%     \caption{AVX2 intrinsics used in the implementation.}
+%     \label{tab:avx2-instructions}
+%     \centering
 
-    \begin{tabular}{|p{0.33\linewidth}|p{0.58\linewidth}|}
-    \hline
-    Intrinsic & Definition\\
-    \hline
-    {\tt \_mm256\_set1\_epi32} & Initializes 256-bit vector with scalar integer values. Doesn't map to any AVX instructions. \\
+%     \begin{tabular}{|p{0.33\linewidth}|p{0.58\linewidth}|}
 %     \hline
-    {\tt \_mm256\_and\_si256} & Performs bitwise logical AND operation on 256-bit integer vectors. \\
+%     Intrinsic & Definition\\
 %     \hline
-    {\tt \_mm256\_xor\_si256} &  Performs bitwise logical XOR operation on 256-bit integer vectors.\\
+%     {\tt \_mm256\_set1\_epi32} & Initializes 256-bit vector with scalar integer values. Doesn't map to any AVX instructions. \\
+%         % \hline
+%     {\tt \_mm256\_and\_si256} & Performs bitwise logical AND operation on 256-bit integer vectors. \\
+%             % \hline
+%     {\tt \_mm256\_xor\_si256} &  Performs bitwise logical XOR operation on 256-bit integer vectors.\\
+%             % \hline
+%     {\tt \_mm256\_cmpgt\_epi32} & Compares packed 8x32-bit integers of two input vectors.\\
+%     {\tt \_mm256\_max\_epi8} & Compares packed 32x8-bit integers of two input vectors and returns element-wise maximums. \\
+%             % \hline
+%         % \hline
+%     {\tt \_mm256\_movemask\_ps} & Extracts the first bits of 8x 32-bit elements in a compact 8-bit format \\
+%             % \hline
+%     {\tt \_mm256\_blendv\_epi8} & Blends/selects byte elements of input vectors depending on the bits in a given mask vector.\\ 
 %              \hline         
-    {\tt \_mm256\_cmpgt\_epi32} & Compares packed 8x 32-bit integers of two input vectors. \\
-            % \hline
-        % \hline
-    {\tt \_mm256\_movemask\_ps} & Extracts the first bits of 8x 32-bit elements in a compact 8-bit format \\
-            % \hline
-    {\tt \_mm256\_blendv\_epi8} & Blends/selects byte elements of input vectors depending on the bits in a given mask vector.\\ 
-             \hline         
-    \end{tabular}
-\end{table}{}
+%     \end{tabular}
+% \end{table}{}
 
@@
 Sampling can be a dominating factor in processing; sampling may demand multiple passes on the graph, if samples are memoized, multiple times of the graph size needs to be stored.
-In this work, samples are not generated explicitly. By using a hash-based, fused sampling, we eliminate the necessity of in-memory creation and storage of the sample sub-graphs.
+In this work, we borrow hash-based fused sampling from {\sc InFuseR}\cite{infuser}.
+By using a hash-based fused sampling, we eliminate the necessity of in-memory creation and storage of the sample sub-graphs.
 While processing an edge, it is considered for all possible samples.
-It is sampled or skipped depending on the outcome of hash based random value. The hash function used is given in equation \ref{eq:hash}
+It is sampled or skipped depending on the outcome of the hash-based random value. The hash function used is given in equation \ref{eq:hash}.
 \begin{equation}
     \label{eq:hash}
-    h(u,v) = \mbox{{\sc Murmur3}}(u||v)  
+    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
 \end{equation}
@@
 
-The {{\sc Murmur3}}~\cite{MurmurHash3} hash function is preferred because of its simplicity, good avalanche behavior and bias.
+We have tried a few other hash algorithms as well; Ideally, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with maximum bias $0.5\%$\rev{\cite{MurmurHash3Performance}}.
 
 For performance considerations, edge hash values were pre-computed in our work and only existing pairs were considered.
-The trade-off between extra memory and computation here maybe not be applicable for different architectures and faster/simpler hash functions.
+The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
 
 Although the above-mentioned approach generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
+
+\begin{figure}[!ht] 
+    \centering
+    %\subfloat[\label{fig:toy}]{%
+    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
+    \subfloat[\label{fig:sims}]{%
+        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
+    } 
+    \subfloat[\label{fig:fused}]{%
+     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
+  \caption{
+  %\protect\subref{fig:toy} The toy graph 
+  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
+  \protect\subref{fig:fused} The simulations are performed in a way to be fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
+  }
+  \label{fig:traversal} 
+\end{figure}
 
@@
     \label{eq:hash_prob}
-    {\rho}(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
+    P(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
 \end{equation}
@@
 One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations.
-In addition, the following control flow branch can be removed using conditional move operations.
-An efficient SIMD implementation of this approach will be discussed later in this section.
-
+Also, the following control flow branch can be removed using conditional move operations.
+An efficient implementation of this approach will be discussed later in this section.
+\begin{figure}[!ht] 
+    \centering
+    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
+    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
+    \label{fig:prob-cdf} 
+\end{figure}
 Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed.
 This property allows us to generate good enough pseudo-random values for fair sampling.
-To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the Cumulative Distribution Function~(CDF) of random values $P(u,v)_r$ used while sampling.
+To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.
 
-For a given graph $G = (V,E)$, the CDF of a sampling probability $x$ is computed as $\Pr\left(x \leq P(u,v)_r\right)$ for all $(u,v) \in E$ and $0 \leq r < R$.
-Figure~\ref{fig:prob_cdf} shows the CDFs for 12 real-life networks.
-The sampling probability distribution with hash-based computation is almost identical with the uniform distribution which is used to simulate the influence diffusion process.
+% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
+Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks.
+The sampling probability distribution with hash-based computation is almost identical to the uniform distribution with very small bias.
 
@@
     \centering
-    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
-    \caption{Cumulative distribution function of hash-based sampling probabilities on various real-life networks.}
-    \label{fig:prob_cdf} 
+    \includegraphics[width=1\linewidth]{./images/bias.pdf}
+    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.}
+    \label{fig:prob-bias} 
 \end{figure}
@@
 
-The diffusion process works as follows; first, all vertices added to live vertices set $L$.
+Second, the diffusion process is performed between vertex sketches.
+All vertices added to live vertices set $L$.
 Then, incoming edges $(u,v)$ for all live vertices are processed.
 For all simulation $u$ is live, the sketch of both sides are merged and set to $u$ registers.
-If any of the sketch-registers change, vertex $u$ added to the next iteration's live vertices set $L'$.
+If any of the sketch-registers change, vertex $u$ is added to the next iteration's live vertices set $L'$.
 After live edges are processed, if the next iteration's live vertices set is smaller than the convergence threshold $\epsilon_c$, the diffusion process concluded.
@@
 
-In Greedy algorithm\cite{kempe2003maximizing} for each candidate vertex, influence diffusion computations are perform for each vertex.
+In Greedy algorithm\cite{kempe2003maximizing} for each candidate vertex, influence diffusion computations are performed for each vertex.
 On the other hand, diffusion on sketch registers allows finding all vertices reachability set.
-All vertices influence in single step distance only computed once.
+All vertices influence in a single-step distance only computed once.
 This dynamic programming like property allows fast selection of influence maximizing candidate.
+Only iterations as much as the diameter of sample graphs are required to converge the sketches.
 
-After diffusion, following process is repeated until $K$ vertices are added to the seed set; For all vertex $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $mask$ and their sketch registers.
+After diffusion, the following process is repeated until $K$ vertices are added to the seed set; For all vertex, $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $mask$ and their sketch registers.
 The $mask$ used for the sketch of $R_G(S)$ and initialized with zeros.
@@
 Blocked vertices skipped in the diffusion step in coming iterations.
-Besides, the real influence score allows us to rebuild our sketch when the sketches have gone stale.
+Besides, the real influence score allows us to know when to rebuild our sketch when the sketches have gone stale.
 
-The sketches are assumed as stale if the absolute error in estimated total influence score is more than global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch larger than local threshold $\epsilon_{l}$.
-Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minimal in the total score.
-If a rebuild is not required, only the last added vertex's sketch also merged with $mask$ to update $R_G(S)$.
+\subsection{Error-Adaptive Sketch Rebuilding}
+
+Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
+After adding vertices to the seed set, \acro perform Monte-Carlo simulations to estimate the reachability of the latent seed set.
+The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch larger than local threshold $\epsilon_{l}$.
+Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, and considered blocked in their respective simulations while rebuilding the sketches.
+Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score.
+If a rebuild is not required, only the last added vertex's sketch is also merged with $mask$ to update $R_G(S)$.
+
+This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.
+Other methods mentioned in this paper, doesn't report time spend on calculating the influence scores, whereas our method includes the time since it is crucial for keeping sketches in high quality.
+
+\begin{figure*}[!ht]
+\begin{center}
+\includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
+\caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
+% For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
+For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
+Since the first register of vertex 1 is bigger, we only update the second register.
+Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register.
+Notice that, we are moving registers in reverse, from target to source of the edges.
+We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
+(d) All vertices have registers converged, there are no live vertices.
+}\label{fig:hf-processing}
+\end{center}
+\end{figure*}
 
 \begin{algorithm}
-\caption{\sc{SketchFuser}($G,K,J$)}
+\caption{\sc{\acro}($G,K,J$)}
 \label{algo:main}
@@
     \State {$S \leftarrow \{\emptyset\}$}
-    \For{$ v\in V$}
+    \For{$ v\in V$} {\bf in parallel}
         \For{$ j\in J$}
@@
     \EndFor
-    \State $M \leftarrow Simulate(G,M,\emptyset)$
+    \State $M \leftarrow simulate(G,M,\emptyset)$
     \State $mask \leftarrow zeros(J)$
@@
         \Else
-            \For{$ v\in V$}
+            \For{$ v\in V$} {\bf in parallel}
                 \For{$ j\in J$}
@@
             \EndFor
-            \State $M \leftarrow Simulate(G,M,R_S)$
+            \State $M \leftarrow simulate(G,M,R_S)$
             \State $mask \leftarrow zeros(J) $ 
@@
     \While{$|L|/|V| > \epsilon_c$}
-        \For{$e_{u,v} \in \Gamma(L)$} %REVERSE THIS
+        \For{$u \in \Gamma(L)$} {\bf in parallel} \label{ln:inner_start} %REVERSE THIS
+        \For{$e_{u,v} \in A(u) $}
             \For{$j \in (0,J]$}
-                \If{$P(u,v)_j < W_{u,v} \land u  \not\in R_S[j]$}
-                    \State{$M_u[j]\leftarrow max(M_u[j],M_v[j])$}                
+                \If{$P(u,v)_j < w_{u,v} \land u  \not\in R_S[j]$} \label{ln:early_exit}
+                    \State{$M_u[j]\leftarrow max(M_u[j],M_v[j])$}\label{ln:update}         
                 \EndIf
@@
             \If {$M_u$ changed}
-                \State $L' \cup u $
+                \State $L' \leftarrow L' \cup u $ \label{ln:inner_end}
             \EndIf
+        \EndFor
         \EndFor
@@
     \EndWhile
+    \State \Return $M$
 \end{algorithmic}
 \end{algorithm}
-\FloatBarrier
-\subsection{Vectorization and Performance considerations}
 
+\subsection{Regularization and Performance considerations}
 Traditional two-step, sample-then-diffuse computation model stores data loosely-coupled.
@@
 This way, SIMD operation is allowed on consecutively located edges, requiring random memory accesses for the diffusion process.
-Even if tightly coupled
+Even if samples or diffusion information stored closely, without fusing random access overhead is still there and much memory is wasted.
 
 One of the main advantages of fused sampling is allowing similar simulation data and computations together.
-Our implementation generates $B/4$ sample edges and runs $B$ simulations at a time. 
-The dichotomy of two batch sizes comes from SIMD width; 
-sampling probabilities are computed in 31-bit fixed-point precision, 
-whereas since we are using 64-bit hash values, sketch registers only require $\left\lceil log2(64+1) \right\rceil = 6$ bits.
-Aligned to the nearest data type they can fit, sampling probabilities utilizes 8x32-bit operators, where as sketch operations employ 32x8bit SIMD vectors.
+For processing samples for an edge in algorithm \ref{algo:diffusion-step}~(lines~\ref{ln:inner_start}--\ref{ln:inner_end}).
 
-% \subsubsection{Vectorized edge processing} first loads edge hash and threshold to vector units.
-Then, we check if the edge is live in any simulations.
-8 random values generated by XOR'ing hash vector and X_r
+ All memory registers from different simulations are stored together for each vertex, this allows the use of vectorized computation hardware.
+Random number generation, sampling, and merging sketches are all vectorizable operations when coupled together.
+Vectorization also reduces branching on overall computation; When vectorized, many comparison operations are done without branching.
 
-\begin{algorithm}
-    \caption{\sc{Vectorized-Merge} ({$u,v,X_r,M_u,M_v,$})}\label{alg:VecLabel}
-    \algorithmicrequire{
-    $u:$ source vertex\\
-    \hspace*{7ex}$v:$ target vertex\\
-    \hspace*{7ex}$X$: random number for simulations\\
-    \hspace*{7ex}$M_u$: sketch registers of $u$\\
-    \hspace*{7ex}$M_v$: sketch registers of $v$\\
-    \hspace*{7ex}$visited$: one-hot visited vector grouped by samples}\\
-    \algorithmicensure{$islive$: a boolean which state if $u$ is live}
-    % \hspace*{8ex}$live_v$: a boolean which state if $v$ is live
-    \begin{algorithmic}[1]
-        \State $islive \leftarrow False$
-        \For{$r \in [0,J)~|~r~mod~32 = 0$}
-            \State $hashvec \leftarrow \_mm256\_set1\_epi32(hash(u,v)$
-            \State $threshold \leftarrow \_mm256\_set1\_epi32(w_{u,v})$
-            \State $live \leftarrow 0$
-            \For{$b\in [0,32)~|~b~mod~8 = 0 $}
-                \State $prob \leftarrow \_mm256\_xor\_si256(X_{r+b\dots8},hashvec)$
-                \State $cmp \leftarrow \_mm256\_cmpgt\_epi32(threshold, prob)$
-                \State $cmpmask \leftarrow \_mm256\_movemask\_ps(cmp))$
-                \State $live\leftarrow (cmpmask<<b)~|~live $
-                \EndFor
-                \If{$live = 0$}
-                    \State continue
-                \EndIf
-                \State $live \leftarrow live~\&~\sim visited_{r\dots32}[u]$
-                \State $livebytes \leftarrow expand\_bits\_to\_bytes(live)$
-                \State $M' \leftarrow 
-                    \_mm256\_cmpgt\_epi8(M_u[r..32],M_v[r..32])$
-                \State $select \leftarrow \_mm256\_and\_si256(livebytes,M')$
-                \State $\_mm256\_blendv\_epi8(M_u[r..32],M_v[r..32])$
-                % \State $$
-                \State $islive \leftarrow islive~|~  \_mm256\_cmp\_ps(\newline
-                    \hspace*{4em}\_mm256\_setzero\_ps(), \newline
-                    \hspace*{4em}\_mm256\_castsi256\_ps(sel))$
+We allow a single easy to predict branch after sample edges are generated to exit early without merging the registers.
+In our experiments, sorting random values $X_r$ significantly increases performance by clustering similar simulations together.
+Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non-taken edges are sampled together.
+Up to 20\% performance can be gained by early exit at line \ref{ln:early_exit} using sorted random values.
 
-                % \State $live \leftarrow live \setminus \bigcup_{} j|u\notin R_{\hat{G}_j} $ 
+% Our implementation generates $B/4$ sample edges and runs $B$ simulations at a time. The dichotomy of two batch sizes comes from SIMD width; 
+% sampling probabilities are computed in 31-bit fixed-point precision, 
+% whereas since we are using 64-bit hash values, sketch registers only require $\left\lceil log2(64+1) \right\rceil = 6$ bits.
+Aligned to the nearest data type they can fit, sampling probabilities utilizes 8x32-bit operators, whereas sketch operations employ 32x8bit SIMD vectors.
+
+% ~works in batches.
+Each batch sized $B=8$ processed by follows; first, edge hash and threshold are loaded to vector units.
+The live sample vector, which is stored as 32-bit unsigned integer is initialized with zero.
+Then, liveness information is inferred by generating random numbers and comparing them to the edge activation threshold.
+Random number generation is done by XOR'ing simulation randoms between $X_{r}$ to $X_{r+b}$ and edge hash.
+Resulting random numbers are considered as fixed-point numbers and compared with the edge threshold $W_{u,v}$ which is also stored as a fixed-point number.
+After, 8x 32-bit aligned results are converted to compact 8-bit representation by extracting the first bits using the move mask operator.
+Finally, the result is appended to the live sample vector.
+Since the live sample vector is a one-hot 32-bit integer, if it is zero, the edge is blocked in all samples and we can skip merging sketch registers.
+
+% {\bf Regularization.} %FIXme
+
+% {\bf Vectorized Sketch Merge} can work with larger batch size, due to smaller item size.
+Before the merge, bitwise-AND is performed on live sample vector bits and the inverse of the visited set of source vertex $u$ to find samples where $u$ is not visited.
+Live sample vector expanded to 32x8bit vector, all 1 bits converted to 255, and 0 bits are converted to 0 bytes in AVX2 vector.
+
+% After expansion, Registers of source and target vertex, $M_u$ and $M_v$, are compared to get element-wise maximums.
+Then, only live samples were selected from the maximum vector by blending live sample byte vector.
+Finally, $M_u$ is compared against its previous value to check whether source vertex $u$ will be added to the next iteration's live vertices set.
+
+% \begin{algorithm}
+%     \caption{\sc{Vectorized-Merge} ({$u,v,X_r,M_u,M_v,$})}\label{algo:vector-merge}
+%     \algorithmicrequire{
+%     $u:$ source vertex\\
+%     \hspace*{7ex}$v:$ target vertex\\
+%     \hspace*{7ex}$X$: random number for simulations\\
+%     \hspace*{7ex}$M_u$: sketch registers of $u$\\
+%     \hspace*{7ex}$M_v$: sketch registers of $v$\\
+%     \hspace*{7ex}$visited$: one-hot visited vector grouped by samples}\\
+%     \algorithmicensure{$islive$: a boolean which state if $u$ is live}
+%     % \hspace*{8ex}$live_v$: a boolean which state if $v$ is live
+%     \begin{algorithmic}[1]
+%         \State $islive \leftarrow False$
+%         \For{$r \in [0,32,64,\dots,J)$}
+%             \State $hashvec \leftarrow \_mm256\_set1\_epi32(hash(u,v)$
+%             \State $threshold \leftarrow \_mm256\_set1\_epi32(w_{u,v})$
+%             \State $live \leftarrow 0$
+%             \For{$b\in [0,8,16,24]$}
+%                 \State $prob \leftarrow \_mm256\_xor\_si256(X_{r+b\dots8},hashvec)$
+%                 \State $cmp \leftarrow \_mm256\_cmpgt\_epi32(threshold, prob)$
+%                 \State $cmpmask \leftarrow \_mm256\_movemask\_ps(cmp))$
+%                 \State $live\leftarrow (cmpmask<<b)~|~live $
+%                 \EndFor
+%                 \If{$live = 0$}
+%                     \State continue
 %                 \EndIf
-        \EndFor
-    \end{algorithmic}
-    \end{algorithm}
+%                 \State $live \leftarrow live~\&~\sim visited_{u}[r..32]$
+%                 \State $livebytes \leftarrow expand\_bits\_to\_bytes(live)$
+%                 % \State $M' \leftarrow 
+%                 %     \_mm256\_cmpgt\_epi8(M_u[r..32],M_v[r..32])$
+%                 % \State $select \leftarrow \_mm256\_and\_si256(livebytes,M')$
+%                 % \State $M_u \leftarrow \_mm256\_blendv\_epi8(M_u[r..32],M_v[r..32])$
+%                 % % \State $$
+%                 % \State $islive \leftarrow islive~|~  \_mm256\_cmp\_ps(\newline
+%                 %     \hspace*{4em}\_mm256\_setzero\_ps(), \newline
+%                 %     \hspace*{4em}\_mm256\_castsi256\_ps(sel))$
+
+%                 \State $max \leftarrow 
+%                     \_mm256\_max\_epi8(M_u[r..32],~M_v[r..32])$
+%                 \State $temp \leftarrow M_u[r..32] $
+%                 \State $M_u[r..32] \leftarrow \_mm256\_blendv\_epi8(\newline  
+%                 \hspace*{4em}M_u[r..32],~max,~livebytes)$
+%                 % \State $$
+%                 \State $islive \leftarrow islive~|~\_mm256\_cmp\_ps(M_u[r..32],~temp)$
+
+%                 % \State $live \leftarrow live \setminus \bigcup_{} j|u\notin R_{\hat{G}_j} $ 
+%             % \EndIf
+%         \EndFor
+%     \end{algorithmic}
+%     \end{algorithm}
+
+\subsection{Implementation Details}
+The Compressed Sparse Row~(CSR) graph data the structure used by all the algorithms. 
+In CSR, an array, $index$, holds the starting indices of each neighboring vertex, while another vector, $adj$, holds consecutive neighbors of each vertex. 
+To enter the neighbors of vertex $i$ we first visit $index[i]$ and $index[i+1]$ 
+to find the data's start and end positions, then search from $adj[index[i]]$ to $adj[index[i+1]]$.
 
 \section{Evaluation}\label{sec:evaluation}
+We performed the experiments on a server with {\tt Intel Xeon Gold 6140}, running at 2.3 Ghz and 250 GB memory.
+All of the 18 cores are allowed in the experiments.
+The Operating System on the server was {\tt Ubuntu 16.04 LTS} with 5.4.0-48 kernel.
+The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.2.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
+Multi-thread parallelization was achieved with {\tt OpenMP} pragmas.
+{\tt AVX2} instructions are utilized by handcrafted code with vector intrinsics.
+
+\begin{table}[!ht]
+\caption{Properties of networks used in the experiments}\label{tab:NetProps}
+\centering
+\scalebox{0.95}{
+\begin{tabular}{ll||r|r|r|r}
+& & No. of           & No. of    & Avg.  &  Avg.  \\
+&Dataset & Vertices          & Edges     &    Weight         &  Degree               \\
+\hline
+\multirow{6}{*}{\rotatebox[origin=c]{90}{Undirected}}& {\tt Amazon} & 262,113 & 1,234,878 & 1.00 & 4.71 \\
+&{\tt DBLP} & 317,081 & 1,049,867 & 1.00 & 3.31 \\
+&{\tt NetHEP} & 15,235 & 58,892 & 1.83 & 3.87 \\
+&{\tt NetPhy} & 37,151 & 231,508 & 1.28 & 6.23 \\
+&{\tt Orkut} & 3,072,441 & 117,185,083 & 1.00 & 38.14 \\
+&{\tt Youtube} & 1,134,891 & 2,987,625 & 1.00 & 2.63 \\
+
+\hline
+\multirow{6}{*}{\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838 & 1.00 & 6.71 \\
+&{\tt LiveJournal} & 4,847,571 & 68,993,773 & 1.00 & 14.23 \\
+&{\tt Pokec} & 1,632,803 & 30,622,564 & 1.00 & 18.75 \\
+&{\tt Slashdot0811} & 77,360 & 905,468 & 1.00 & 11.70 \\
+&{\tt Slashdot0902} & 82,168 & 948,464 & 1.00 & 11.54 \\
+&{\tt Twitter} & 81,306 & 2,420,766 & 1.37 & 29.77 
+\end{tabular}
+}
+\end{table}
+\subsection{Experiment Settings}
+
+We performed experiments on twelve graphs~(six undirected, six directed) are used in the experiments. For relevancy, datasets that are frequently used for Influence Maximization are selected.
+
+The datasets are {\tt Amazon} co-purchase network~\cite{snapnets}, {\tt DBLP} co-laboration network~\cite{snapnets}, {\tt Epinions} consumer review trust network, {\tt LiveJournal}~\cite{snapnets}, {\tt NetHEP} citation network~\cite{MixGreedy}, {\tt NetPhy} citation network~\cite{MixGreedy}, {\tt Orkut}~\cite{snapnets}, {\tt Pokec} Slovakian poker game site friend network~\cite{snapnets}, {\tt Slashdot} friend-foe networks~(08-11, 09-11)~\cite{snapnets}, {\tt Twitter} list co-occurence network~\cite{snapnets}, and {\tt Youtube} friendship network~\cite{snapnets}.
+The properties of these datasets are given in Table~\ref{tab:NetProps}.
+
+The properties of these datasets are given in Table~\ref{tab:NetProps}.
+
+Three diffusion settings are simulated for a comprehensive experimental evaluation; for each network, we use 
+\begin{enumerate}
+    \item constant edge weights $w = 0.005$,
+    \item constant edge weights $w = 0.01$~(as in~\cite{kempe2003maximizing} and~\cite{MixGreedy}),
+    \item constant edge weights $w = 0.1$~(as in~\cite{kempe2003maximizing}),
+    % \item weighted cascade edge weights $w_{u,v} = 1/|\Gamma(v)|$.
+\end{enumerate}
+
+We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; Due to nature of diffusion algorithm, \acro traverses vertices even if they are blocked.
+Also, for each live vertex \acro generates sample edges for all simulations regardless.
+Small $w$ values increases overhead operations we mentioned.
+Other two experiment settings are used to emulate experiments of Kempe et al.~\cite{kempe2003maximizing}
+
+\subsection{Performance Metrics}
+
+In this paper, the algorithms are evaluated on execution time, influence score, and maximum resident memory use. In computing, these three are
+often traded off to each other; In the extreme, it is trivial to select random vertices as seed set or compute reachability sets of every possible seed set combination.
+
+The observed execution times and memory consumption of different algorithms are comparable when the algorithms run on the same computer.
+In this paper, the execution time measured is always the wall time reported by the programs. 
+All methods we benchmarked leave out the time spend on reading files and pre-processing.
+To be fair in evaluating our method, we only left out the time to spend on reading files, and respected authors' measurement schemes in other methods.
+In all benchmarks, we allowed methods to fully utilize all available CPU cores, except {\sc Tim+} which is a single-threaded software.
+Memory use we reported is Resident Set Size(RSS) and measured using GNU Time software.
+
+Although, because the algorithms can use various methods to measure the impact score, the reported influence scores may be deceptive. 
+Due to reason, we implemented an oracle with a very simple, sample-than-diffuse algorithm without any optimization mentioned.
+The random oracle values are generated by the 32-bit Mersenne Twister pseudo-random generator with a state size of 19937 bits {\tt mt19937} from {\tt C++ standard library}.
+All influence scores in this paper are reported with the independent oracle.
+
+\subsection{Algorithms evaluated in the experiments}
+
+We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, and {\sc Imm}.
+
+First, Two-phased Influence Maximization({\sc Tim+})~\cite{tim},TIM consists of two phases, Parameter Estimation and Node Selection. The first phase computes a lower-bound
+of the maximum expected to spread among all size-k node sets,
+and then uses the lower-bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from
+G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
+
+Second, Sketch-based Influence Maximization({\sc Skim})~\cite{cohen2014sketch} constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-thread parallelization in some degree.
+
+Third, Minutoli et al.'s {\sc Imm}~\cite{minutoli2019fast}. 
+{\sc Imm} is a fast algorithm that efficiently produces accurate seed sets. 
+The {\sc Imm}  algorithm\cite{tang2015influence} is an approximation method that improves the Reverse Influence Sampling(RIS)\cite{borgs2014maximizing} algorithm By eliminating the need for the threshold to be used.
+
+The influence of all vertices is generalized on a small set of sample graphs that is sampled from reachability sets of few vertices.
+Experimentations are done with $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined hyper-parameter controlling the approximation boundaries.
+
+Finally, our method \acro employs both Monte-Carlo simulations and count-distinct sketches for estimating reachability set cardinalities.
+Even-though, \acro is blazing-fast and accurate for limited $K$, we exploit the performance of the method to improve results by rebuilding sketches after removing residual influence networks.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table*} %TABLE 5+7
+    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.005$.
+Influence scores are given relative to \acro{}.
+}
+    \label{tab:timings005}
+    \centering
+    \scalebox{0.96}{
+
+\begin{tabular}{l|rrrr|rrrr|rrrr}
+\toprule
+{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
+Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+Dataset      &            &         &        &       &            &         &         &         &            &       &      &      \\
+\midrule
+{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041x &  1.000x &  0.562x &       0.17 & 21.62 & 0.90 & 6.78 \\
+{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068x &  1.027x &  1.036x &       0.27 & 31.24 & 0.95 & 3.12 \\
+{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026x &  1.001x &  0.939x &       0.06 &  0.78 & 0.07 & 1.04 \\
+{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010x &  0.995x &  0.957x &       3.97 & 27.43 & 2.78 & 2.00 \\
+{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065x &  0.993x &  0.871x &       0.01 &  0.80 & 0.04 & 0.33 \\
+{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042x &  0.999x &  0.777x &       0.03 &  2.01 & 0.08 & 0.16 \\
+{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997x &  1.001x &       5.19 &     - & 7.81 & 1.77 \\
+{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032x &  1.027x &  0.925x &       1.57 & 10.16 & 1.40 & 1.74 \\
+{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015x &  0.983x &  0.942x &       0.06 &  0.76 & 0.09 & 0.13 \\
+{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022x &  0.998x &  0.953x &       0.06 &  0.71 & 0.08 & 0.14 \\
+{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006x &  0.990x &  0.942x &       0.09 &  2.02 & 0.12 & 0.15 \\
+{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025x &  1.013x &  1.000x &       0.73 &  3.96 & 0.48 & 1.39 \\
+\bottomrule
+Geo. Mean wrt.&1.00x&28.19x&1.69x&3.46x&1.00x&1.03x&1.00x&0.90x&1.00x&22.75x&1.65x&3.58x \\ \acro
+\end{tabular}
+
+    }
+    \end{table*}
+
+    \begin{table*} %TABLE 5+7
+    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.01$.
+Influence scores are given relative to \acro{}.
+}
+    \label{tab:timings01}
+    \centering
+    \scalebox{0.93}{
+
+% \begin{tabular}{lrrrrrrrrrrrr}
+% \toprule
+% {} & \multicolumn{4}{l}{Time} & \multicolumn{4}{l}{Score} & \multicolumn{4}{l}{Memory} \\
+% Method & HyperFuser &    TIM+ &     IMM &   SKIM & HyperFuser &    TIM+ &     IMM &    SKIM & HyperFuser &  TIM+ &   IMM & SKIM \\
+\begin{tabular}{l|rrrr|rrrr|rrrr}
+\toprule
+{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
+Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+
+Dataset      &            &         &         &        &            &         &         &         &            &       &       &      \\
+\midrule
+{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037x &  1.024x &  0.390x &       0.17 & 18.11 &  0.55 & 6.40 \\
+{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043x &  1.005x &  0.997x &       0.27 & 11.92 &  0.52 & 2.05 \\
+{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006x &  0.983x &  0.984x &       0.06 &  1.95 &  0.10 & 0.68 \\
+{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996x &  0.993x &       3.97 &     - &  6.64 & 1.45 \\
+{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036x &  0.997x &  0.826x &       0.01 &  0.60 &  0.03 & 0.31 \\
+{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010x &  0.985x &  0.732x &       0.03 &  0.67 &  0.05 & 0.12 \\
+{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000x &  1.000x &       5.19 &     - & 20.13 & 3.43 \\
+{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004x &  0.996x &  0.988x &       1.57 & 39.98 &  2.09 & 0.78 \\
+{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003x &  0.984x &  0.976x &       0.06 &  2.01 &  0.10 & 0.08 \\
+{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008x &  0.992x &  0.980x &       0.06 &  2.42 &  0.11 & 0.08 \\
+{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004x &  0.992x &  0.978x &       0.09 &  4.91 &  0.23 & 0.09 \\
+{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009x &  0.994x &  1.006x &       0.73 &  7.10 &  0.48 & 1.73 \\
+\bottomrule
+Geo. Mean wrt.&1.00x&100.14x&5.45x&3.58x&1.00x&1.02x&1.00x&0.88x&1.00x&36.26x&1.91x&2.82x \\ \acro
+\end{tabular}
+
+    }
+    \end{table*}
+    \begin{table*} %TABLE 5+7
+    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.1$.
+Influence scores are given relative to \acro{}.
+}
+    \label{tab:timings1}
+    \centering
+    \scalebox{0.90}{
+
+\begin{tabular}{l|rrrr|rrrr|rrrr}
+\toprule
+{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
+Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+Dataset      &            &         &         &        &            &         &         &         &            &        &       &      \\
+\midrule
+{\tt Amazon}       &       0.69 &  133.22 &    1.98 &  23.62 &    11797.0 &  1.006x &  0.990x &  0.815x &       0.17 &   5.49 &  0.23 & 2.59 \\
+{\tt DBLP }         &       0.54 & 1368.83 &   14.54 &   6.30 &    48549.9 &  1.001x &  0.995x &  1.001x &       0.27 &  35.19 &  1.06 & 0.65 \\
+{\tt Epinions }     &       0.26 &  439.33 &    5.46 &   9.42 &    18409.9 &  1.000x &  0.998x &  0.997x &       0.06 &  12.17 &  0.39 & 1.18 \\
+{\tt LiveJournal }  &      10.10 &       - & 1071.30 &  65.73 &  2134726.0 &       - &  1.000x &  1.000x &       3.97 &      - & 65.49 & 1.40 \\
+{\tt NetHEP }       &       0.10 &   14.18 &    0.33 &   0.61 &     2461.7 &  1.002x &  0.975x &  0.899x &       0.01 &   1.02 &  0.04 & 0.10 \\
+{\tt NetPhy }       &       0.16 &  107.52 &    1.53 &   0.34 &     8339.5 &  1.007x &  0.994x &  0.975x &       0.03 &   3.84 &  0.13 & 0.03 \\
+{\tt Orkut }        &      16.55 &       - & 1964.83 & 446.92 &  2692366.5 &       - &  1.000x &  1.000x &       5.19 &      - & 71.94 & 9.68 \\
+{\tt Pokec }        &       4.90 &       - &  514.79 &  31.80 &  1034859.8 &       - &  1.000x &  1.000x &       1.57 &      - & 26.46 & 0.98 \\
+{\tt Slashdot0811 } &       0.21 &  677.49 &    7.34 &   2.44 &    25871.8 &  1.000x &  1.000x &  0.999x &       0.06 &  19.10 &  0.59 & 0.25 \\
+{\tt Slashdot0902 } &       0.23 &  695.12 &    7.99 &   2.35 &    27519.5 &  1.000x &  1.000x &  0.999x &       0.06 &  18.45 &  0.66 & 0.24 \\
+{\tt Twitter }      &       0.33 & 1897.50 &   16.09 &   1.62 &    55327.3 &  1.000x &  0.998x &  0.998x &       0.09 &  34.56 &  1.04 & 0.05 \\
+{\tt Youtube }      &       1.12 & 7158.56 &   60.59 &  30.57 &   171392.9 &  1.000x &  0.999x &  1.001x &       0.73 & 139.12 &  4.19 & 2.88 \\
+\bottomrule
+Geo. Mean wrt.&1.00x&1449.41x&27.87x&11.06x&1.00x&1.00x&1.00x&0.97x&1.00x&163.77x&7.14x&2.63x \\ \acro
+\end{tabular}
+
+    }
+    \end{table*}
+
+ \begin{figure}[!h] 
+     \centering
+     \includegraphics[width=1\linewidth]{images/speedup-imm}
+   \centering \caption{Speed-up obtained by \acro{} over {\sc Imm}($\epsilon\myeq 0.5$) using $\tau=18$ threads.
+     \label{fig:vs-imm}} 
+ \end{figure}
+
+ \begin{figure}[!h] 
+     \centering
+     \includegraphics[width=1\linewidth]{images/speedup-skim}
+   \centering \caption{Speed-up obtained by \acro{}($J=256$) over {\sc Skim}($r\myeq 64,l\myeq 64$) using $\tau=18$ threads.
+     \label{fig:vs-skim}} 
+ \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{figure*}[htbp] 
+%     \centering
+%     \includegraphics[width=1\linewidth]{images/threads}
+%     \centering\caption{Speed-up obtained by \acro{} over {\sc Imm}($\epsilon\myeq 0.13$).
+%   \label{fig:scaling} }  
+% \end{figure*}
+
+\subsection{Scalability with multi-threaded parallelism}
+
+\begin{figure*}[!ht] 
+    \centering
+    \includegraphics[width=\linewidth]{images/threads.pdf}
+   \centering \caption{\acro scaling with multiple threads on some of largest datasets in the benchmarks.
+     \label{fig:scaling}} 
+\end{figure*}
+
+In our implementation, the parallel processing of live vertices  (as source) is necessary to reduce the number of visited edges.
+However, since a (target) vertex can be being processed at the same time, the update operation at line~\ref {ln:update} of this {\em pull-based} approach can be seen as a potential source of race conditions.
+But, since iterations are performed until convergence, \ggx{the results are sound within our assumptions}.
+On the other hand, the performance may suffer due to false sharing.
+Figure~\ref{fig:scaling} shows the speedup values obtained via {\tt OpenMP} parallelization.
+
+Even though {\em pull-based} diffusion approach we employed in this work gives us superior performance in most of the benchmarks, it is possible to implement \acro using other approaches; E.g.
+{\em queue-based} approach is similarly feasible and may improve performance by only processing live vertices.
+The pull-based diffusion method is chosen due to its simplicity and scalability to a large number of threads/compute units.
+
+\subsection{Comparing \acro with State-of-art}
+All algorithms mentioned in this paper, estimates influence maximizing seed sets, that are good enough but not optimal.
+For that reason, we compare both the performance and quality of the results.
+In addition to this trade-off, the parameters of the experimented methods are hard to compare directly.
+It is infeasible to find exactly the corresponding parameter between any two methods in this setting.
+For that reason, we have used parameters that authors of the methods used in their papers.
+We performed experiments using following parameters; {\sc Tim+} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$).
+
+One of the drawbacks of \acro is that we do not have direct control over the approximation factor whereas other methods we compare against some form of an approximation control parameter.
+\acro can only control approximation quality indirectly by tuning the number of Monte-Carlo simulations $J$, and to some degree with estimation/convergence thresholds.
+For \acro, we used $J=256$ registers which is comparable in terms of quality of other methods.
+And, for performance we used global estimation error threshold $\epsilon_{global}=0.01$, local estimation error threshold $\epsilon=0.3$, and set non-converged vertices ratio as $\epsilon_{conv}=0.02$.
+The threshold values are chosen by observations and intuition, simple grid search over threshold most likely would give superior performance but we opt-to leave parameter selection to future work.
+
+For small $w=0.005$ and small graphs such as NetHep, NetPhy, or Amazon; we can see {\sc Tim+}  has ($4\sim 6\%$) better results, whereas {\sc Skim}  has much ($- 13\sim 44\%$) worse results than \acro in terms of quality.
+While \acro having a hard time to catch edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim+} won't suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
+On the performance side, \acro is superior to other methods, Amazon dataset only takes 1.3 seconds including Monte-Carlo influence oracle computations.
+{\sc Skim} and {\sc Imm} take 63.73 and 124.38 seconds.
+For 4\% quality improvement, {\sc Imm} is $\sim$100 slower than \acro.
+For small improvements in quality, we can always double the number of registers/simulations $J=256$ to $512$, which would approximately double the wall time.
+For the same $w=0.005$ and larger graphs such as {\tt LiveJournal} and {\tt Orkut}, the quality gap narrows {\sc Skim}  only $5\%$ behind, and {\sc Tim+} is marginally better.
+The performance gap also narrows between \acro and {\sc Skim}, \acro only $30\%$ faster in small $w$.
+In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, \ggx{could not finish {\tt Orkut}; crashing after consuming all memory available}.
+\ggx{On larger} $w=0.1$, \acro is much faster than all other methods and still providing high-quality results.
+While all methods are struggling with problem size, \acro is converging results much faster, even faster than previous experiment settings.
+Also, memory consumption stays the same for all experimental settings, much smaller than other methods.
 
@@
 
-\section{Conclusion}\label{sec:conclusion}
+Although they can be inferior in terms of influence score, recent IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}. 
+% However, in this work, we show that \acro{}, which is a conventional algorithm, can be orders of magnitude faster than {\sc MixGreedy} while keeping the quality of the seed vertices the same. 
+Techniques such as using GPUs, sketches for finding set intersections, reverse sampling to estimate influence from a small subset of vertices, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time~\cite{leskovec2009community, borgs2014maximizing, minutoli2019fast, cohen2014sketch, IPA, IMGPU, curipples}.
+
+\acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling and vertex parallel diffusion algorithm.
+{\sc InFuseR} computes influence by memoizing connected-components for all vertices and only works on {\em undirected} datasets.
+Also, employs CELF optimizations to reduce candidate seed set cardinality computations.
+Whereas, \acro can process both directed and undirected graphs, and uses sampled Flajolet–Martin sketches to both estimate cardinalities and choose candidates.
+
+Sketch-based influence maximization improves theoretical efficiency against simulation-based methods.
+The sketch-based approach pre-computes sketches for evaluating the influence spread instead of running simulations repetitively.
+One of the interesting methods for sketch-based influence maximization is {\sc Skim} ~\cite{cohen2014sketch} by Cohen~et~al.
+It constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-core, multi-CPU parallelization.
+
+Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al runs a proxy model and prunes paths with probabilities less than a given threshold.
+IPA uses {\tt OpenMP} to work on independent paths in parallel.
+The approach only keeps a dense but small part of the network and scalable on only sparse networks.
+Liu~et~al.
+proposed IMGPU~\cite{IMGPU}, an IM  estimation method by utilizing a bottom-up traversal algorithm.
+It performs a single Monte-Carlo simulation on many GPU threads to find the reachability of the seed set.
+It is $5.1\times$ faster than {\sc MixGreedy} on a CPU.
+The GPU implementation is up to $60\times$ faster with an average speedup of  $24.8\times$.
+
+Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS) which samples a fraction of all random reverse reachable sets.
+Then it computes a set of $K$ seeds that covers the maximum number of those.
+The number of samples is calculated concerning the number of visited vertices.
+The algorithm has an approximation guarantee of $(1-1/e-\epsilon)$.
+Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast}.
+Recently, the authors extended the algorithm to work on GPUs~\cite{curipples}.
+
+Two-phased Influence Maximization({\sc Tim+} )\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
+The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets, and then uses the lower-bound to derive a parameter $\theta$.
+In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
+
+Cohen\cite{cohen2015all} presented the Historic Inverse Probability (HIP) estimators.
+When applied to the All Distance Sketches, HIP outperforms in estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for approximate distinct counting on data streams.
+In this work, we preferred Flajolet-Martin\cite{flajolet1985probabilistic} sketches for simplicity and performance.
+In future work, other estimators such as HIP can improve to improve \acro.
+
+Kumar and Calders\cite{kumar2017information} proposed Time Constrained Information
+Cascade Model and an influence maximization algorithm that works on the model using versioned HyperLogLog sketches.
+The algorithm performs the influence reachability sets for all vertices in an interaction graph performing a single pass over the data.
+Sketches build for each time window to estimate active edges where as \acro builds sketches for each vertex to estimate cumulative influence of the latent seed set.
+\acro also utilizes fused sampling and error adaptive rebuilding of sketches.
+
+\section{Conclusion \ggx{and Future Work}}\label{sec:conclusion}
+
+In conclusion, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and error-adaptive rebuilding.
+We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple CPU cores.
+In addition, we present performance comparison with state-of-the-art IM algorithms on real-world datasets.
+With the proposed method, \acro{} can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.
+
+In the future, we would like to extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges.
+The main issue with \acro on such computation scheme is the broadcast of sketch registers; when vertices are partitioned to different computation units, resulting sketch updates should be communicated to all partitions.
+To overcome the issue, graph pre-processing and speculative diffusion strategies can reduce communication bottlenecks.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-12-18 paper.tex
Update on Overleaf.

@@
 % active vertex colors +
+
+% GRID PARAM SEARCH
+% Performance comparison vs others (why slowed down?)
+% Error-Adaptive rebuilding sat
 %%%%%
@@
 
-Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($M$), and most importantly union of these sets can be done in a constant number of operations.
+Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($J$), and most importantly union of these sets can be done in a constant number of operations.
 
@@
 Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
-Adding item $x$ to register $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
+Adding item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
 
@@
 
-The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
+% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
 The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
@@
 Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
-After adding vertices to the seed set, \acro perform Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch larger than local threshold $\epsilon_{l}$.
+After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
+The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch is larger than local threshold $\epsilon_{l}$.
 Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, and considered blocked in their respective simulations while rebuilding the sketches.

### 2021-01-09 paper.tex
Grammer fixes

@@
 This allows the proposed algorithm to find the number of influenced vertices in a single simulation step in different simulations at once.
-In addition, thanks to its efficiency and scalability of the our the parallel implementation can rebuild the sketches after observing large estimation errors.
+In addition, thanks to its efficiency and scalability of our parallel implementation can rebuild the sketches after observing large estimation errors.
 Our experimental results show that the proposed method finds high-quality seed sets  while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
@@
 \end{abstract}
-% Note that keywords are not normally used for peerreview papers.
+% Note that keywords are not normally used for peer review papers.
 }
@@
 %is a simple diffusion model that Vertex v can be activated by any of incoming edges from activated vertices w with probability $p$.
-Given a seed set $S$ and influence probability $p$, cascade model starts from activated seed set and tries to diffuse until each of the out-going edges of active vertices are considered.
+Given a seed set $S$ and influence probability $p$, the cascade model starts from the activated seed set and tries to diffuse until each of the out-going edges of active vertices are considered.
 The diffusion process considers all edges only once.
@@
 
-Flajolet–Martin sketch only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.
+Flajolet–Martin algorithm only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.
 The registers are initialized with zero values in beginning.
@@
 
-In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate estimated influence, we use one register per simulation, and take average of longest leading zero counts to calculate average cardinality of reachability sets.
-Also, in an another perspective, it is same as using register as much as MC simulation, where updates are done with same probability as influence propagation.
-
-% \subsection{SIMD}
-% {\em Single Instruction-Multiple Data} machines exploits data level parallelism to perform the same operation on multiple data points simultaneously.
-In this work, we utilized Advanced Vector Extensions (AVX2) instruction set.
-AVX2 works on 256-bit registers in multiple packed forms; 8x32 bit operations are used in fused sampling, where as sketch merge  performed with 32x8bit operations.
-This dichotomy between operations solved by processing in 32 simulations batches at a time.
-% Even-though, auto-vectorization is enabled, most of the operation mention are cannot be vectorized by the compiler.
-As far as we know, no compiler vectorizes chain conditional move or move-mask operations.
-Vectorization in the implementation is done using explicit intrinsics.
-
-% First, active edges are checked by generating random values, $P(u,v)_r$. After comparing random values with edge threshold, active edges are store in an 32bit integer as one-hot vector. Then,
-
-% For completeness, the intrinsics explicitly used in this paper are described in Table~\ref{tab:avx2-instructions}.
-
-% \begin{table}[!ht]
-%     \caption{AVX2 intrinsics used in the implementation.}
-%     \label{tab:avx2-instructions}
-%     \centering
-
-%     \begin{tabular}{|p{0.33\linewidth}|p{0.58\linewidth}|}
-%     \hline
-%     Intrinsic & Definition\\
-%     \hline
-%     {\tt \_mm256\_set1\_epi32} & Initializes 256-bit vector with scalar integer values. Doesn't map to any AVX instructions. \\
-%         % \hline
-%     {\tt \_mm256\_and\_si256} & Performs bitwise logical AND operation on 256-bit integer vectors. \\
-%             % \hline
-%     {\tt \_mm256\_xor\_si256} &  Performs bitwise logical XOR operation on 256-bit integer vectors.\\
-%             % \hline
-%     {\tt \_mm256\_cmpgt\_epi32} & Compares packed 8x32-bit integers of two input vectors.\\
-%     {\tt \_mm256\_max\_epi8} & Compares packed 32x8-bit integers of two input vectors and returns element-wise maximums. \\
-%             % \hline
-%         % \hline
-%     {\tt \_mm256\_movemask\_ps} & Extracts the first bits of 8x 32-bit elements in a compact 8-bit format \\
-%             % \hline
-%     {\tt \_mm256\_blendv\_epi8} & Blends/selects byte elements of input vectors depending on the bits in a given mask vector.\\ 
-%              \hline         
-%     \end{tabular}
-% \end{table}{}
+In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate estimated influence, we use one register per simulation, and take the average of longest leading zero counts to calculate the average cardinality of reachability sets.
+Merge operations are performed if and only if there is an edge between the respective simulation.
 
@@
 
-We have tried a few other hash algorithms as well; Ideally, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with maximum bias $0.5\%$\rev{\cite{MurmurHash3Performance}}.
+We have tried a few other hash algorithms as well; Ideally, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with maximum bias $0.5 \% $\cite{MurmurHash3Performance}.
 
@@
 % For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
-Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks.
-The sampling probability distribution with hash-based computation is almost identical to the uniform distribution with very small bias.
+Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. The sampling probability distribution with hash-based computation is almost identical to the uniform distribution with small bias.
 
@@
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, and the marginal gain estimation error after the last sketch is larger than local threshold $\epsilon_{l}$.
-Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, and considered blocked in their respective simulations while rebuilding the sketches.
+The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
+and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$. 
+Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, 
+and considered blocked in their respective simulations while rebuilding the sketches. 
 Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
@@
 
-This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.
-Other methods mentioned in this paper, doesn't report time spend on calculating the influence scores, whereas our method includes the time since it is crucial for keeping sketches in high quality.
+This approach allows us to keep sketches high quality even after many vertices are added to the seed set, 
+but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.
+
+Other methods mentioned in this paper, doesn't report time spend on calculating the influence scores, 
+whereas our method includes the time since it is crucial for keeping sketches in high quality.
 
@@
 Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non-taken edges are sampled together.
-Up to 20\% performance can be gained by early exit at line \ref{ln:early_exit} using sorted random values.
-
-% Our implementation generates $B/4$ sample edges and runs $B$ simulations at a time. The dichotomy of two batch sizes comes from SIMD width; 
-% sampling probabilities are computed in 31-bit fixed-point precision, 
-% whereas since we are using 64-bit hash values, sketch registers only require $\left\lceil log2(64+1) \right\rceil = 6$ bits.
-Aligned to the nearest data type they can fit, sampling probabilities utilizes 8x32-bit operators, whereas sketch operations employ 32x8bit SIMD vectors.
-
-% ~works in batches.
-Each batch sized $B=8$ processed by follows; first, edge hash and threshold are loaded to vector units.
-The live sample vector, which is stored as 32-bit unsigned integer is initialized with zero.
-Then, liveness information is inferred by generating random numbers and comparing them to the edge activation threshold.
-Random number generation is done by XOR'ing simulation randoms between $X_{r}$ to $X_{r+b}$ and edge hash.
-Resulting random numbers are considered as fixed-point numbers and compared with the edge threshold $W_{u,v}$ which is also stored as a fixed-point number.
-After, 8x 32-bit aligned results are converted to compact 8-bit representation by extracting the first bits using the move mask operator.
-Finally, the result is appended to the live sample vector.
-Since the live sample vector is a one-hot 32-bit integer, if it is zero, the edge is blocked in all samples and we can skip merging sketch registers.
-
-% {\bf Regularization.} %FIXme
-
-% {\bf Vectorized Sketch Merge} can work with larger batch size, due to smaller item size.
-Before the merge, bitwise-AND is performed on live sample vector bits and the inverse of the visited set of source vertex $u$ to find samples where $u$ is not visited.
-Live sample vector expanded to 32x8bit vector, all 1 bits converted to 255, and 0 bits are converted to 0 bytes in AVX2 vector.
-
-% After expansion, Registers of source and target vertex, $M_u$ and $M_v$, are compared to get element-wise maximums.
-Then, only live samples were selected from the maximum vector by blending live sample byte vector.
-Finally, $M_u$ is compared against its previous value to check whether source vertex $u$ will be added to the next iteration's live vertices set.
-
-% \begin{algorithm}
-%     \caption{\sc{Vectorized-Merge} ({$u,v,X_r,M_u,M_v,$})}\label{algo:vector-merge}
-%     \algorithmicrequire{
-%     $u:$ source vertex\\
-%     \hspace*{7ex}$v:$ target vertex\\
-%     \hspace*{7ex}$X$: random number for simulations\\
-%     \hspace*{7ex}$M_u$: sketch registers of $u$\\
-%     \hspace*{7ex}$M_v$: sketch registers of $v$\\
-%     \hspace*{7ex}$visited$: one-hot visited vector grouped by samples}\\
-%     \algorithmicensure{$islive$: a boolean which state if $u$ is live}
-%     % \hspace*{8ex}$live_v$: a boolean which state if $v$ is live
-%     \begin{algorithmic}[1]
-%         \State $islive \leftarrow False$
-%         \For{$r \in [0,32,64,\dots,J)$}
-%             \State $hashvec \leftarrow \_mm256\_set1\_epi32(hash(u,v)$
-%             \State $threshold \leftarrow \_mm256\_set1\_epi32(w_{u,v})$
-%             \State $live \leftarrow 0$
-%             \For{$b\in [0,8,16,24]$}
-%                 \State $prob \leftarrow \_mm256\_xor\_si256(X_{r+b\dots8},hashvec)$
-%                 \State $cmp \leftarrow \_mm256\_cmpgt\_epi32(threshold, prob)$
-%                 \State $cmpmask \leftarrow \_mm256\_movemask\_ps(cmp))$
-%                 \State $live\leftarrow (cmpmask<<b)~|~live $
-%                 \EndFor
-%                 \If{$live = 0$}
-%                     \State continue
-%                 \EndIf
-%                 \State $live \leftarrow live~\&~\sim visited_{u}[r..32]$
-%                 \State $livebytes \leftarrow expand\_bits\_to\_bytes(live)$
-%                 % \State $M' \leftarrow 
-%                 %     \_mm256\_cmpgt\_epi8(M_u[r..32],M_v[r..32])$
-%                 % \State $select \leftarrow \_mm256\_and\_si256(livebytes,M')$
-%                 % \State $M_u \leftarrow \_mm256\_blendv\_epi8(M_u[r..32],M_v[r..32])$
-%                 % % \State $$
-%                 % \State $islive \leftarrow islive~|~  \_mm256\_cmp\_ps(\newline
-%                 %     \hspace*{4em}\_mm256\_setzero\_ps(), \newline
-%                 %     \hspace*{4em}\_mm256\_castsi256\_ps(sel))$
-
-%                 \State $max \leftarrow 
-%                     \_mm256\_max\_epi8(M_u[r..32],~M_v[r..32])$
-%                 \State $temp \leftarrow M_u[r..32] $
-%                 \State $M_u[r..32] \leftarrow \_mm256\_blendv\_epi8(\newline  
-%                 \hspace*{4em}M_u[r..32],~max,~livebytes)$
-%                 % \State $$
-%                 \State $islive \leftarrow islive~|~\_mm256\_cmp\_ps(M_u[r..32],~temp)$
-
-%                 % \State $live \leftarrow live \setminus \bigcup_{} j|u\notin R_{\hat{G}_j} $ 
-%             % \EndIf
-%         \EndFor
-%     \end{algorithmic}
-%     \end{algorithm}
+Up to 20\% performance can be gained by an early exit at line \ref{ln:early_exit} using sorted random values.
 
@@
 
-We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; Due to nature of diffusion algorithm, \acro traverses vertices even if they are blocked.
+We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; Due to the nature of the diffusion algorithm, \acro traverses vertices even if they are blocked.
 Also, for each live vertex \acro generates sample edges for all simulations regardless.
 Small $w$ values increases overhead operations we mentioned.
-Other two experiment settings are used to emulate experiments of Kempe et al.~\cite{kempe2003maximizing}
+The other two experiment settings are used to emulate experiments of Kempe et al.~\cite{kempe2003maximizing}
 
@@
 And, for performance we used global estimation error threshold $\epsilon_{global}=0.01$, local estimation error threshold $\epsilon=0.3$, and set non-converged vertices ratio as $\epsilon_{conv}=0.02$.
-The threshold values are chosen by observations and intuition, simple grid search over threshold most likely would give superior performance but we opt-to leave parameter selection to future work.
 
@@
 The algorithm performs the influence reachability sets for all vertices in an interaction graph performing a single pass over the data.
-Sketches build for each time window to estimate active edges where as \acro builds sketches for each vertex to estimate cumulative influence of the latent seed set.
+Sketches build for each time window to estimate active edges where as \acro builds sketches for each vertex to estimate the cumulative influence of the latent seed set.
 \acro also utilizes fused sampling and error adaptive rebuilding of sketches.
@@
 We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple CPU cores.
-In addition, we present performance comparison with state-of-the-art IM algorithms on real-world datasets.
+In addition, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
 With the proposed method, \acro{} can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.
@@
 of Biomedical Informatics.
-His current research interests include Parallel Programming, High Performance Computing, and Cryptography. 
+His current research interests include Parallel Programming, High-Performance Computing, and Cryptography. 
     \end{IEEEbiography}

### 2021-01-11 paper.tex
progress

@@
 \item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results.
-For large graphs, due to its \ggx{race condition indifferent} nature, performance scales near linearly with the number of threads available.
+For large graphs, due to its race condition indifferent nature, performance scales near linearly with the number of threads available.
 While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.
@@
     \centering
-    \includegraphics[width=1\linewidth]{./images/cdf.pdf}
+    \includegraphics[width=1\linewidth]{./images/CDF.pdf}
     \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
@@
 
+Sketches are very fast approximation methods that often provide less than gold standard results.
+In our case, sketches are very competent at finding the first few vertices, but after sketch registers saturate with high values.
+Register saturation causes the naive count-distinct sketch method to not distinguish between vertices.
+
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
+    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
+     }\label{fig:sketch-saturation} 
+    \end{center}
+\end{figure}
+
+In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed,for all iterations.
+Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set.
+Even though at first few vertices influence is comparable, we see observe near-linear drop-off in estimated influence.
+
 Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
@@
 but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.
+We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
+While rebuilding sketches, $R_G(S')$ is used to check whether if a vertex is blocked in a sample.
 
@@
         % \State $R_S \leftarrow run\_cascade(G,S,J)$
-        \State {Compute seed set $S$'s Reachability set $R_S(S)$ }
-        \State $\sigma_G(S) \leftarrow |R_S|/J$
+        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ }
+        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
         \State $\delta = \sigma - \varsigma$

### 2021-01-11 paper.tex
progress

@@
 Sketches are very fast approximation methods that often provide less than gold standard results.
-In our case, sketches are very competent at finding the first few vertices, but after sketch registers saturate with high values.
+In our case, sketches are very competent at finding the first few vertices.
+But, after sketch registers saturate with high values, we observe a significant drop in the quality of results.
 Register saturation causes the naive count-distinct sketch method to not distinguish between vertices.
@@
 Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set.
-Even though at first few vertices influence is comparable, we see observe near-linear drop-off in estimated influence.
+Even though at first few vertices expected influence is comparable, we see observe near-linear drop-off in estimated influence.
 
@@
 and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.
-Before rebuilding stale sketches, the reachability set of latent seed set is marked as visited, 
+
+Before rebuilding stale sketches, the reachability set of latent seed set,$R_G(S')$, is marked as visited, 
 and considered blocked in their respective simulations while rebuilding the sketches.
+Then, sketches are rebuild using Monte-Carlo simulations.
+After rebuilding, $mask$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.
+
 Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
-If a rebuild is not required, only the last added vertex's sketch is also merged with $mask$ to update $R_G(S)$.
-
-This approach allows us to keep sketches high quality even after many vertices are added to the seed set, 
-but on the other hand, forces us to perform Monte-Carlo simulations which can be very costly.
+If a rebuild is not required, we only update the $mask$ by merging it with the candidate vertex's sketch. 
+This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive.
 We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \begin{figure*}[htbp] 
-%     \centering
-%     \includegraphics[width=1\linewidth]{images/threads}
-%     \centering\caption{Speed-up obtained by \acro{} over {\sc Imm}($\epsilon\myeq 0.13$).
-%   \label{fig:scaling} }  
-% \end{figure*}
-
 \subsection{Scalability with multi-threaded parallelism}
@@
 However, since a (target) vertex can be being processed at the same time, the update operation at line~\ref {ln:update} of this {\em pull-based} approach can be seen as a potential source of race conditions.
-But, since iterations are performed until convergence, \ggx{the results are sound within our assumptions}.
+But, since iterations are performed until convergence, the results are sound within our assumptions.
 On the other hand, the performance may suffer due to false sharing.
@@
 The performance gap also narrows between \acro and {\sc Skim}, \acro only $30\%$ faster in small $w$.
-In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, \ggx{could not finish {\tt Orkut}; crashing after consuming all memory available}.
-\ggx{On larger} $w=0.1$, \acro is much faster than all other methods and still providing high-quality results.
+In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
+For $w=0.1$, \acro is much faster than all other methods and still providing high-quality results.
 While all methods are struggling with problem size, \acro is converging results much faster, even faster than previous experiment settings.
@@
 
-\section{Conclusion \ggx{and Future Work}}\label{sec:conclusion}
+\section{Conclusion and Future Work}\label{sec:conclusion}
 

### 2021-01-12 paper.tex
progress

@@
 
+\begin{figure*}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
+    \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
+    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
+    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
+Since the first register of vertex 1 is bigger, we only update the second register.
+Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register.
+Notice that, we are moving registers in reverse, from target to source of the edges.
+We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
+(d) All vertices have registers converged, there are no live vertices.
+}\label{fig:hf-processing}
+    \end{center}
+    \end{figure*}
 \subsection{Error-Adaptive Sketch Rebuilding}
@@
 
-Two threshold values allow the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
+The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
 If a rebuild is not required, we only update the $mask$ by merging it with the candidate vertex's sketch. 
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}[!h]
     \begin{center}
-\includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
-\caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
-% For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
-Since the first register of vertex 1 is bigger, we only update the second register.
-Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register.
-Notice that, we are moving registers in reverse, from target to source of the edges.
-We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
-(d) All vertices have registers converged, there are no live vertices.
-}\label{fig:hf-processing}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}\\
+
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
     \end{center}
+    \caption{Effect of $\epsilon$ parameters on \acro's performance.}\label{fig:parameter-smallmultiples} 
 \end{figure*}
+
+Our method's performance, both in terms of speed and quality of results, depends on parameter selection. 
+Even though,
 

### 2021-01-12 paper.tex
progress

@@
 
-In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed,for all iterations.
+In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed, for all iterations.
 Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set.
@@
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
-and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.
+The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
+and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.
 
@@
 
+Even though, \acro's behavior is not chaotic with respect to changes in parameters.
 Our method's performance, both in terms of speed and quality of results, depends on parameter selection.
-Even though,
+Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
+On the other hand, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked.
+But, quality of the results will suffer.
 

### 2021-01-12 paper.tex
progress

@@
 
+Since, $\epsilon_local$ is the maximum error allowed after the last rebuild.
+Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
+Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked.
+But, the result quality will suffer.
+$\epsilon_global$, on the other hand, is the minimum influence we expected to obtain via building the sketch.
+If we were to set $\epsilon_global$ to 0, \acro will not rebuild the sketches, but when $\epsilon_global$ is set to infinity, we skill need to compare $\epsilon_local$ to estimation error before rebuilding.
+
 Even though, \acro's behavior is not chaotic with respect to changes in parameters.
 Our method's performance, both in terms of speed and quality of results, depends on parameter selection.
-Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
-On the other hand, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked.
-But, quality of the results will suffer.
+We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters.
+In figure~\ref{fig:parameter-smallmultiples}, both speed and quality of results on some of the largest datasets we have experimented is shown.
+We found that, the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$ used in our experiments, performs decent in many datasets, both in terms of speed and quality.
 

### 2021-01-15 paper.tex
Progress

@@
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
+The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
 and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.
@@
 Even though, \acro's behavior is not chaotic with respect to changes in parameters.
-Our method's performance, both in terms of speed and quality of results, depends on parameter selection.
+The performance, both in terms of speed and quality of results, depends on parameter selection.
 We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters.
-In figure~\ref{fig:parameter-smallmultiples}, both speed and quality of results on some of the largest datasets we have experimented is shown.
-We found that, the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$ used in our experiments, performs decent in many datasets, both in terms of speed and quality.
+In figure~\ref{fig:parameter-smallmultiples}, both the speed and the quality of results on some of the largest datasets we have experimented is shown.
+We found that the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, performs decent in many datasets, both in terms of speed and quality.
 

### 2021-01-15 paper.tex
Progress

@@
     \end{center}
-    \caption{Effect of $\epsilon$ parameters on \acro's performance.}\label{fig:parameter-smallmultiples} 
+    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads.}\label{fig:parameter-smallmultiples} 
 \end{figure*}    
+\begin{figure}[h] 
+    \centering
+    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
+  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters. ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) 
+    \label{fig:conv-perf}} 
+\end{figure}
 
@@
 
+Performance characteristics of \acro is very different from its state-of-the-art competitors; \acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depends on the influence score.
+Due to reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
+In exceptional settings, such as Pokec dataset and $w=0.01$ where the diameter of the influence network is 43, \acro loses its edge against its fastest competitor.
+On the other hand in the same dataset with $w=0.1$, the diameter is 17; \acro is 6 times faster than its nearest competitor.
+
 \section{Related Work}\label{sec:relatedwork}
@@
 Although they can be inferior in terms of influence score, recent IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.
-% However, in this work, we show that \acro{}, which is a conventional algorithm, can be orders of magnitude faster than {\sc MixGreedy} while keeping the quality of the seed vertices the same. 
-Techniques such as using GPUs, sketches for finding set intersections, reverse sampling to estimate influence from a small subset of vertices, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time~\cite{leskovec2009community, borgs2014maximizing, minutoli2019fast, cohen2014sketch, IPA, IMGPU, curipples}.
+
+Techniques such as using GPUs\cite{IMGPU,curipples}, sketches for finding set intersections\cite{cohen2014sketch,IPA}, reverse sampling to estimate influence from a small subset of vertices\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time\cite{leskovec2009community}.
 
@@
 
-Two-phased Influence Maximization({\sc Tim+} )\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
+Two-phased Influence Maximization({\sc Tim+})\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
 The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets, and then uses the lower-bound to derive a parameter $\theta$.

### 2021-01-15 paper.tex
Update on Overleaf.

@@
 %%%%%%
+% add seconds to fig 7
+% fix yaxis
+% table 3-5 son satir 3-5
+% fontlari buyult, relative score/time , fig 10 11
+% notation
 % Notes: 
@@
         $\delta$        & Marginal Gain after last sketch build\\
-        $\epsilon_{global}$    & Global estimation error threshold\\
-        $\epsilon_{local}$    & Local estimation error threshold\\ 
-        $\epsilon_{conv}$    & Non-convergenced vertex threshold\\
+        $\epsilon_{g}$    & Global estimation error threshold\\
+        $\epsilon_{l}$    & Local estimation error threshold\\ 
+        $\epsilon_{c$    & Non-convergenced vertex threshold\\
       %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
@@
 
-Since, $\epsilon_local$ is the maximum error allowed after the last rebuild.
-Setting $\epsilon_local$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
+Since, $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
+Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
 Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked.
 But, the result quality will suffer.
-$\epsilon_global$, on the other hand, is the minimum influence we expected to obtain via building the sketch.
-If we were to set $\epsilon_global$ to 0, \acro will not rebuild the sketches, but when $\epsilon_global$ is set to infinity, we skill need to compare $\epsilon_local$ to estimation error before rebuilding.
+$\epsilon_{g}$, on the other hand, is the minimum influence we expected to obtain via building the sketch.
+If we were to set $\epsilon_{l}$ to 0, \acro will not rebuild the sketches, but when $\epsilon_{l}$ is set to infinity, we skill need to compare $\epsilon_{l}$ to estimation error before rebuilding.
 
@@
         \State $\delta = \sigma - \varsigma$
-        \If{$ (e - \delta) / \delta < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$}
+        \If{$ |(e - \delta) / \delta| < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$} %FIXME
             \State $mask \leftarrow merge(mask,M_s)$

### 2021-01-21 paper.tex
Progress

@@
 %%%%%%
-% add seconds to fig 7
-% fix yaxis
-% table 3-5 son satir 3-5
-% fontlari buyult, relative score/time , fig 10 11
 % notation 
-% Notes: 
-% plot grouping/hue +
-% table smallcaps +
-% Time score memory center +
-% Abstract
-% Differences between infuser and us+
-% time skecth diff between us +
-% neden 0.005 +
-% active vertex colors +
-
-% GRID PARAM SEARCH
-% Performance comparison vs others (why slowed down?)
-% Error-Adaptive rebuilding sat
 %%%%%
@@
 As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
-Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagates the information/influence effectively is essential.
+Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
 
@@
 
-Simulating a greedy algorithm in parallel is an obvious and straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
+Simulating a greedy algorithm in parallel is a straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
 However, for large networks, a greedy approach with a good approximation guarantee does not come cheap even if a large number of processing units/cores are available on networks with billions of vertices and edges.
@@
 Instead, it leverages Count-Distinct sketches.
-in this work, we apply parallelism in multiple levels; thread-level and instruction-level parallelism.
-While modern compilers employ instruction-level parallelism effectively and automatically for applications with regular memory access patterns, graph kernels are usually harder to deal with.
-The irregularity of the neighbor IDs.
-.....
-due to their irregular memory access patterns, it is not a straightforward task for graph processing kernels.
-Besides, vectorization attempts on such kernels typically fail to provide substantial speed-up in performance.
 
@@
 While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.
-
-% \item \acro can be around $200000\times$ faster compared to the traditional greedy approaches.
-It is usable on large graphs that have been considered as {\em too large} in the literature.
-For instance, the new algorithm runs in $2.09$, $0.08$, $0.36$ seconds on networks {\tt Amazon}, {\tt NetHEP}, {\tt NetPhy} with 16 threads where the sequential baseline takes $141.3$, $259.1$ and $1725.2$ seconds, respectively.
-In fact, with a 302,400 seconds~(3.5 days) timeout, the sequential baseline can process only the above-mentioned 3 (out of 12) real-life graphs, having 1.2M, 58.9K and 231.5K edges.
-On the other graphs, the original algorithm cannot complete the simulations within the time limit.
-However, \acro{} completes all of 12 graphs around 1200 seconds in total, where the maximum is 654 seconds for the {\tt Orkut} network having 3.1M vertices and 117.2M edges.
 
@@
         $\epsilon_{l}$    & Local estimation error threshold\\ 
-        $\epsilon_{c$    & Non-convergenced vertex threshold\\
+        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
       %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
@@
 Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
-In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
+In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via pre-processing.
 
@@
 
-%Each edge $e=(s,v) \in E$ has a weight $w_{s,v}$.
-Each vertex $v$ has incoming edge list $Adj^{-1}(v)$ and $\sum_{s\in Adj^{-1}(v) }{w_{s,v}} \leq 1$.
-Also, each vertex $v$ has associated with a threshold $\theta_v$.
-Initially, $\theta$ is sampled uniformly, and seed set is set as activated.
-Then, until convergence is reached simulation ran to transfer $w_ij$ values from activated vertices to their neighborhoods, activating each vertex $v$ that reach $\theta_v$ value.
-Weights can be uniform i.e 0.1, 0.01, or 0.001 for all edges, as we observed in many work.
-
 \item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize of previous models mentioned above.
@@
 The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models.
-% Current studies focus on reducing the number of simulations run \cite{goyal2011celf++, goyal2011simpath}, sketch-based speedup methods\cite{SKIM}, and proxy methods that solve similar yet simpler problems \cite{kempe2003maximizing}.
-%FIXME too many methods, one french paper in python
-%\cite{kempe2003maximizing} 
 We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to the other models in the literature.
-%  \[ \sigma(S^*)=\argmax_{S\subseteq V \land |S| \leq k } \sigma_{G}(S) \]
-
-%is a simple diffusion model that Vertex v can be activated by any of incoming edges from activated vertices w with probability $p$.
-Given a seed set $S$ and influence probability $p$, the cascade model starts from the activated seed set and tries to diffuse until each of the out-going edges of active vertices are considered.
-The diffusion process considers all edges only once.
 
@@
 If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
-if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(ackermann'(\sigma))$ complexity.
+if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(Ackermann'(\sigma))$ complexity.
 
@@
 Flajolet–Martin algorithm only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.
-The registers are initialized with zero values in beginning.
+The registers are initialized with zero values in the beginning.
 Items are added by storing the longest leading zero count.
@@
     % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
-Since the first register of vertex 1 is bigger, we only update the second register.
+    For the live edge between Vertex 1 and 4, the register set to the maximum of the respective register.
+Since the first register of vertex 1 has a larger value, we only update the second register.
 Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register.
-Notice that, we are moving registers in reverse, from target to source of the edges.
+Notice that we are moving registers in reverse, from target to source of the edges.
 We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
@@
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
-and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.
+The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
+and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.
 
-Before rebuilding stale sketches, the reachability set of latent seed set,$R_G(S')$, is marked as visited, 
+Before rebuilding stale sketches, the reachability set of latent seed set, $R_G(S')$, is marked as visited, 
 and considered blocked in their respective simulations while rebuilding the sketches.
@@
     \begin{center}
+        \subfloat[LiveJournal execution time in seconds\label{fig:lj-time}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
+    }
+    \subfloat[Orkut execution time in seconds\label{fig:orkut-time}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}\\
-
+        }
+    \subfloat[Pokec execution time in seconds\label{fig:pokec-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
+        }\\
+        \subfloat[LiveJournal Influence Score\label{fig:lj-score}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
+        }
+    \subfloat[Orkut Influence Score\label{fig:lj-score}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
+        }
+    \subfloat[Pokec Influence Score\label{fig:pokec-score}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
+        }\\
     \end{center}
@@
 \bottomrule
-Geo. Mean wrt.&1.00x&28.19x&1.69x&3.46x&1.00x&1.03x&1.00x&0.90x&1.00x&22.75x&1.65x&3.58x \\ \acro
+Geo. Mean wrt.&1.000x&28.191x&1.687x&3.465x&1.000x&1.032x&1.002x&0.899x&1.000x&22.750x&1.650x&3.581x \\ \acro
 \end{tabular}
@@
 \bottomrule
-Geo. Mean wrt.&1.00x&100.14x&5.45x&3.58x&1.00x&1.02x&1.00x&0.88x&1.00x&36.26x&1.91x&2.82x \\ \acro
+Geo. Mean wrt.&1.000x&100.140x&5.448x&3.582x&1.000x&1.016x&0.996x&0.879x&1.000x&36.264x&1.909x&2.820x \\ \acro
 \end{tabular}
@@
 \bottomrule
-Geo. Mean wrt.&1.00x&1449.41x&27.87x&11.06x&1.00x&1.00x&1.00x&0.97x&1.00x&163.77x&7.14x&2.63x \\ \acro
+Geo. Mean wrt.&1.000x&1449.408x&27.870x&11.062x&1.000x&1.002x&0.996x&0.972x&1.000x&163.771x&7.145x&2.634x \\ \acro
 \end{tabular}
@@
 It is $5.1\times$ faster than {\sc MixGreedy} on a CPU.
-The GPU implementation is up to $60\times$ faster with an average speedup of  $24.8\times$.
+The GPU implementation is up to $60\times$ faster with an average speed-up of  $24.8\times$.
 

### 2021-01-22 paper.tex
Update on Overleaf.

@@
 In addition to high-quality yet expensive approximation algorithms, to meet with the scale of today's networks, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature.
-As expected, the quality of the seed sets for the latter is inferior to those of the former.
-In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and the recently proposed hash-based, fused sampling.
-To estimate the vertex set sizes influenced throughout the simulations, we use per-vertex Flajolet-Martin sketches where each sketch register corresponds to a sample sub-graph.
+As expected, the quality of the seed sets for the latter is inferior to that of the former.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and the recently proposed hash-based fused sampling.
+To estimate the vertex set sizes influenced throughout the simulations, we use per-vertex Flajolet-Martin sketches where each sketch register corresponds to a sample subgraph.
 During the diffusion simulations, the reach set cardinalities of a single vertex are stored in adjacent registers in memory.
 This allows the proposed algorithm to find the number of influenced vertices in a single simulation step in different simulations at once.
-In addition, thanks to its efficiency and scalability of our parallel implementation can rebuild the sketches after observing large estimation errors.
+In addition, thanks to its efficiency and scalability of our parallel implementation, we can rebuild the sketches after observing large estimation errors.
 Our experimental results show that the proposed method finds high-quality seed sets while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
-In addition, it is shown to be $3.5\times$--$11.1\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
+In addition, it is $3.5\times$--$11.1\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
 \end{abstract}
@@
 
-The study of efficient information/influence propagation in networks becomes an important area of research with several applications from many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
+The study of efficient information/influence propagation in networks becomes an important area of research with several applications in many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
 As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
@@
 The time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
-Although they perform well in terms of seed-set quality, in consequence, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices.
+Although they perform well in terms of seed-set quality, as a consequence, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices.
 Due to this reason, many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.
@@
 \begin{itemize}[leftmargin=*]
-\item We propose, \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, a blazing-fast, and accurate Influence Maximization algorithm.
+\item We propose \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, a blazing-fast, and accurate Influence Maximization algorithm.
 The proposed scheme samples the edges as they are traversed across several simulations.
@@
 
-That is when the simulations traverse the same edge within close time intervals, the edge is accessed only once as long as the simulation timelines allow \acro to do so.
+That is, when the simulations traverse the same edge within close time intervals, the edge is accessed only once as long as the simulation timelines allow \acro to do so.
 The suggested approach, therefore, decreases the pressure on the memory management unit.
-In relation, for the cascade model, we employ a vector compute unit, near maximum efficiency to regularize memory accesses.
+In relation to the cascade model, we employ a vector compute unit, near maximum efficiency to regularize memory accesses.
 %\item In addition to instruction-level parallelism, we parallelize \acro on multi-core architectures.
@@
 \item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results.
-For large graphs, due to its race condition indifferent nature, performance scales near linearly with the number of threads available.
-While processing the graph, only we few GBs of memory is used, mostly for storing the graph itself.
+For large graphs, due to its race condition indifferent nature, the performance scales near linearly with the number of threads available.
+While processing the graph, only a few GBs of memory is used, mostly for storing the graph itself.
 
-\item We evaluate the performance, memory consumption, and influence score with a state-of-the-art influence maximization algorithms {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim}, {\sc Imm}~\cite{minutoli2019fast} in order to accurately position the performance of \acro{} in the IM literature.
+\item We evaluate the performance, memory consumption, and influence score with a state-of-the-art influence maximization algorithm {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim}, {\sc Imm}~\cite{minutoli2019fast} to accurately position the performance of \acro{} in the IM literature.
 The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than state-of-the-art while still being better in comparison in terms of scores, and using a comparable amount of memory.
@@
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. 
-Diffusion probability on edge $(u, v) \in G$ is noted as $w_{u,v}$.
+Diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$.
 $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.
@@
         \hline\hline
-        %$p$             & Sampling probability for edges\\
-%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
-        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
+        $w$             & Sampling probability for edges\\
+        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
         $h(u,v)$        & Hash function for edge $\{u,v\}$\\
@@
         \hline\hline
-        $B$             & Batch size\\
         $e$             & Estimated reachability set size\\
@@
         $\delta$        & Marginal Gain after last sketch build\\
+        $Err_l$         & Local estimation error of the sketch\\
+        $Err_g$         & Global estimation error of the sketch\\
         $\epsilon_{g}$    & Global estimation error threshold\\
@@
 Figure~\ref{fig:xx} shows a~(Fig.~\ref{fig:ic}) and directed~(Fig.~\ref{fig:wc})
-graph for which the weights on the edges are diffusion/influence probabilities.
+graph in which the weights on the edges are diffusion/influence probabilities.
 
@@
 \end{figure}
-
-The $\sigma_{G, M}(\cdot)$ influence spread function calculates the {\em estimated} number of agents / nodes / vertices affected~(activated) through a $M$ diffusion model. 
-We eliminate $M$ from the notation for the sake of elegant simplicity; in the remainder of the text, $\sigma_{G}$ refers to $\sigma_{G, M}$.
 In the literature, {\em independent} and {\em weighted cascade}~(IC and WC), and 
@@
 
-\item{\bf Linear threshold} generalizes the cascade models and activates the $v$ vertex once the cumulative activation coming from the neighbors of $v$ exceeds the $\theta v$ threshold. 
-All the $\{u, v\}$~(or $(u, v)$ in the directed graph) edges 
+\item{\bf Linear threshold} generalizes the independent cascade model and activates the $v$ vertex once the cumulative activation coming from the neighbors of $v$ exceeds the $\theta v$ threshold. 
+All $\{u, v\}$~(or $(u, v)$ in the directed graph) edges 
 with active $u$ vertices are taken into account in the process. Vertex $v$ is activated~\cite{kempe2003maximizing} when the number of these edge weights reaches $\theta v$.  
-Therefore, the cascade models are special variants of the linear threshold model with $\theta v = 0 $.
+Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta v = 0 $.
 
-\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize of previous models mentioned above.
-In the triggering model, each neighbor has a probability to influence vertex $v$.
-The diffusion process chooses a random subset of vertices called the "triggering set" to activate vertices at each instance.
+\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize of the previous models mentioned above.
+In the triggering model, each neighbor has a probability to influence the vertex $v$.
+The diffusion process chooses a random subset of vertices called the "triggering set" to activate the vertices at each instance.
 \end{itemize}
@@
 The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models.
-We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to the other models in the literature.
+We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to other models in the literature.
 
 \subsection{Count-Distinct Sketch}\label{sec:sketch}
-The count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
-Computing reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample sub-graphs from the given vertex.
+Count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
+Computing the reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample subgraphs from the given vertex.
 Exact cardinality calculations require memory proportional to the cardinality.
@@
 
-The methods based on Reverse reachability and Bottom-Up Traversal utilizes this property directly to merge reachability sets of connected vertices to estimate vertices influence.
+The methods based on Reverse Reachability and Bottom-Up Traversal utilize this property directly to merge the reachability sets of connected vertices to estimate vertices influence.
 MixGreedy method goes one step further; it utilizes that all vertices in a connected component that have the same reachability set in undirected graphs.
-So, for a sample graph, all reachability sets can be found in a single graph traversal.
+Therefore, for a sample graph, all reachability sets can be found in a single graph traversal.
 
-For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for non-trivial graphs. 
+For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
 If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
@@
 
-Flajolet–Martin algorithm only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.
+Flajolet–Martin algorithm only stores how rare elements are in a multiset.The rarity of the elements is often computed by counting the leading zeros in the item's hash value.
 The registers are initialized with zero values in the beginning.
@@
 Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
-Adding item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
+Adding the item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
 
@@
 \end{equation} 
-where $M'$ is union of set and $J$ is number of sketch registers.
+where $M'$ is union of set and $J$ is the number of sketch registers.
 
-Average of longest running zeros can be used compute the cardinality and the result is divided to correction factor $\phi \approx 0.77351$ to correct hash collisions.
+Average of the longest running zeros can be used compute the cardinality and the result is divided to the correction factor $\phi \approx 0.77351$ to correct hash collisions.
 \begin{equation}
@@
 
-In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate estimated influence, we use one register per simulation, and take the average of longest leading zero counts to calculate the average cardinality of reachability sets.
-Merge operations are performed if and only if there is an edge between the respective simulation.
+In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average of longest leading zero counts to calculate the average cardinality of reachability sets.
+Merge operations are performed if and only if there is an edge between the respective simulations.
 
@@
 \subsection{Hash-based Fused Sampling}
-The probabilistic nature of cascade models requires sampling sub-graphs $\hat{G}$ from $G = (V, E)$ to simulate the diffusion process.
-Sampling can be a dominating factor in processing; sampling may demand multiple passes on the graph, if samples are memoized, multiple times of the graph size needs to be stored.
+The probabilistic nature of cascade models requires sampling subgraphs $\hat{G}$ from $G = (V, E)$ to simulate the diffusion process.
+The sampling part of the algorithm can be a dominating factor in processing; sampling may demand multiple passes on the graph, if samples are memoized, multiple times of the graph size needs to be stored.
 In this work, we borrow hash-based fused sampling from {\sc InFuseR}\cite{infuser}.
-By using a hash-based fused sampling, we eliminate the necessity of in-memory creation and storage of the sample sub-graphs.
+By using a hash-based fused sampling, we eliminate the necessity of in-memory creation and storage of the sample subgraphs.
 While processing an edge, it is considered for all possible samples.
@@
 
-For performance considerations, edge hash values were pre-computed in our work and only existing pairs were considered.
+For performance considerations, edge hash values were precomputed in our work and only existing pairs were considered.
 The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
@@
 
-Multiple deterministic random values for each edge is generated by using the edge hash values and random numbers $X_r$ associated with each simulation $r$. 
+Multiple deterministic random values for each edge are generated by using the edge hash values and random numbers $X_r$ associated with each simulation $r$. 
 Sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed as follows; First, $h(u,v)$ is XOR'ed with a uniformly randomly chosen $X_r \in_R [0, h_{max}]$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
@@
 The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
-One of the benefits of this approach is, sampling an edge is only single XOR and compare-greater-than operations.
-Also, the following control flow branch can be removed using conditional move operations.
+One of the benefits of this approach is that an edge can be sampled using a single XOR and compare-greater-than operation.
+Moreover, the following control flow branch can be removed using conditional move operations.
 An efficient implementation of this approach will be discussed later in this section.
@@
 \end{figure}
-Using a strong hash function such as {{\sc Murmur3}} ensures all bits independently change if the input is changed.
+Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
 This property allows us to generate good enough pseudo-random values for fair sampling.
@@
 % For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
-Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. The sampling probability distribution with hash-based computation is almost identical to the uniform distribution with small bias.
+Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. The sampling probability distribution of hash-based computation is almost identical to the uniform distribution with small bias.
 
@@
 %Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-Being able to generate infinitely many samples on-the-fly, allows us to avoid many memory accesses.
-The only down-side of hash-based fused sampling is that we have to generate all random values,   $P(u,v)_r$, for each edge traversal.
+Being able to generate infinitely many samples on-the-fly allows us to avoid many memory accesses.
+The only downside of hash-based fused sampling is that we have to generate all random values,   $P(u,v)_r$, for each edge traversal.
 Fortunately, these computations are quite fast on modern computing hardware.
@@
 \subsection{Reachability Set Cardinality Estimation}
-A greedy solution to the influence maximization problem requires finding a vertex that maximizes marginal influence gain at each step until the seed set size reaches $K$.
-And, Single vertex influence estimation is the same problem as the count-distinct problem applied to all sample sub-graphs.
+A greedy solution to the influence maximization problem requires finding a vertex that maximizes the marginal influence gain at each step until the seed set size reaches $K$.
+And, single vertex influence estimation is the same problem as the count-distinct problem applied to all sample subgraphs.
 So, it is possible to use Count-distinct sketches to estimate influence scores in the greedy method.
 
-We propose an influence maximization method, that utilizes the Count-distinct sketch we mentioned in section \ref{sec:sketch} to estimate averages of distinct elements in sample subgraphs for both time and space efficiency.
+We propose an influence maximization method that utilizes the Count-distinct sketch we mentioned in section \ref{sec:sketch} to estimate the averages of distinct elements in sample subgraphs for both time and space efficiency.
 Algorithm \ref{algo:main} describes the method proposed as follows;
 
-First, reachability sets of all vertices are initialized with vertices themselves.
+First, the reachability sets of all vertices are initialized with the vertices themselves.
 For all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{\hat{G}_j}(u) = \{u\}$.
-Then, we perform diffusion process on the sketch registers.
+Then, we perform the diffusion process on the sketch registers.
 
@@
 All vertices added to live vertices set $L$.
-Then, incoming edges $(u,v)$ for all live vertices are processed.
-For all simulation $u$ is live, the sketch of both sides are merged and set to $u$ registers.
-If any of the sketch-registers change, vertex $u$ is added to the next iteration's live vertices set $L'$.
-After live edges are processed, if the next iteration's live vertices set is smaller than the convergence threshold $\epsilon_c$, the diffusion process concluded.
-If not, we swap $L$ and $L'$, clear $L'$, and then diffusion processed is repeated.
+Then, the incoming edges $(u,v)$ for all live vertices are processed.
+For all simulations where $u$ is live, the sketch of both sides are merged and set to $u$ registers.
+If any of the sketch registers change, the vertex $u$ is added to the next iteration's live vertices set $L'$.
+After the live edges are processed, if the next iteration's live vertices set is smaller than the convergence threshold $\epsilon_c$, the diffusion process concluded.
+If not, we swap $L$ and $L'$, clear $L'$, and then the diffusion processed is repeated.
 
@@
 On the other hand, diffusion on sketch registers allows finding all vertices reachability set.
-All vertices influence in a single-step distance only computed once.
-This dynamic programming like property allows fast selection of influence maximizing candidate.
+All vertices influence scores in a single-step distance only computed once.
+This dynamic programming like property allows fast selection of influence maximizing candidates.
 Only iterations as much as the diameter of sample graphs are required to converge the sketches.
@@
 Then, the actual Monte-Carlo simulations were performed to compute the reachability set of the seed set.
-Having actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
+Having an actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
 Blocked vertices skipped in the diffusion step in coming iterations.
-Besides, the real influence score allows us to know when to rebuild our sketch when the sketches have gone stale.
+Besides, the real influence score allows us to know when to rebuild our sketches when the sketches have gone stale.
 
@@
 
-In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after seed sets' reachability is removed, for all iterations.
-Other, builds the sketch once at the beginning, then only utilizes sketch merge operations to find the seed set.
-Even though at first few vertices expected influence is comparable, we see observe near-linear drop-off in estimated influence.
+In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after the seed sets' reachability is removed, for all iterations.
+Moreover, another one that builds the sketch once at the beginning, then only utilizes sketch merge operation to find the seed set.
+Even though at first few vertices the expected influence is comparable, we see observe near-linear drop-off in the estimated influence.
 
@@
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
-and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.
+The estimation error is calculated as the following; we store influence score after each sketch rebuild on $\varsigma$ and sketch cardinality estimate of the candidate vertex on $e$.
+We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$.
+Then, the local estimation error will be $Err_l=|e-\delta / \delta|$ and global error rate $Err_g=|e-\delta / \sigma|$.
+The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
+and the marginal gain estimation error, $Err_l$, after the last sketch is larger than a local threshold $\epsilon_{l}$.
 
-Before rebuilding stale sketches, the reachability set of latent seed set, $R_G(S')$, is marked as visited, 
+Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited 
 and considered blocked in their respective simulations while rebuilding the sketches.
-Then, sketches are rebuild using Monte-Carlo simulations.
+Then, the sketches are rebuilt using Monte-Carlo simulations.
 After rebuilding, $mask$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.
@@
 The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
-If a rebuild is not required, we only update the $mask$ by merging it with the candidate vertex's sketch. 
-This approach allows us to keep sketches high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive.
-We reuse the reachability sets of latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
-While rebuilding sketches, $R_G(S')$ is used to check whether if a vertex is blocked in a sample.
+If a rebuild is not required, we only update $mask$ by merging it with the candidate vertex's sketch. 
+This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive.
+We reuse the reachability sets of the latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
+While rebuilding the sketches, $R_G(S')$ is used to check whether a vertex is blocked in a sample.
 
-Other methods mentioned in this paper, doesn't report time spend on calculating the influence scores, 
-whereas our method includes the time since it is crucial for keeping sketches in high quality.
+Other methods mentioned in this paper do not report the time spent on calculating the influence scores, 
+whereas our method includes the time since it is crucial for keeping the sketches in high quality.
 
@@
 
-Since, $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
-Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method but it will give the best possible results.
-Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are build only once without checking vertices blocked.
+Since $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
+Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method, but it will give the best possible results.
+Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are built only once without checking the vertices blocked.
 But, the result quality will suffer.
-$\epsilon_{g}$, on the other hand, is the minimum influence we expected to obtain via building the sketch.
-If we were to set $\epsilon_{l}$ to 0, \acro will not rebuild the sketches, but when $\epsilon_{l}$ is set to infinity, we skill need to compare $\epsilon_{l}$ to estimation error before rebuilding.
+$\epsilon_{g}$, on the other hand, is the minimum influence we expected to obtain via rebuilding the sketch.
+If we were to set $\epsilon_{l}$ to 0, \acro will not rebuild the sketches, but when $\epsilon_{l}$ is set to infinity, we skill need to compare $\epsilon_{l}$ to the estimation error before rebuilding.
 
-Even though, \acro's behavior is not chaotic with respect to changes in parameters.
-The performance, both in terms of speed and quality of results, depends on parameter selection.
+Even though \acro's behavior is not chaotic with respect to changes in parameters.
+The performance, both in terms of speed and quality of the results, depends on parameter selection.
 We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters.
-In figure~\ref{fig:parameter-smallmultiples}, both the speed and the quality of results on some of the largest datasets we have experimented is shown.
-We found that the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, performs decent in many datasets, both in terms of speed and quality.
+In figure~\ref{fig:parameter-smallmultiples}, both the speed and the quality of the results on some of the largest datasets we have experimented are shown.
+We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, perform decent in many datasets, both in terms of speed and quality.
 
@@
         \State $\delta = \sigma - \varsigma$
-        \If{$ |(e - \delta) / \delta| < \epsilon_l \lor |e-\delta| / \sigma < \epsilon_g$} %FIXME
+        \State $Err_l=|(e - \delta) / \delta|$
+        \State $Err_g=|e-\delta| / \sigma $
+        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
             \State $mask \leftarrow merge(mask,M_s)$
@@
 \subsection{Regularization and Performance considerations}
-Traditional two-step, sample-then-diffuse computation model stores data loosely-coupled.
+Traditional two-step sample-then-diffuse computation model stores data loosely-coupled.
 Sampled edges are stored together, diffusion related information stored afar.
 This way, SIMD operation is allowed on consecutively located edges, requiring random memory accesses for the diffusion process.
-Even if samples or diffusion information stored closely, without fusing random access overhead is still there and much memory is wasted.
+Even if the sample or diffusion information are stored closely, without fusing, the random access overhead will be still there and much memory will be wasted.
 
@@
 Random number generation, sampling, and merging sketches are all vectorizable operations when coupled together.
-Vectorization also reduces branching on overall computation; When vectorized, many comparison operations are done without branching.
+Vectorization also reduces branching on the overall computation; When vectorized, many comparison operations are done without branching.
 
 We allow a single easy to predict branch after sample edges are generated to exit early without merging the registers.
-In our experiments, sorting random values $X_r$ significantly increases performance by clustering similar simulations together.
-Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non-taken edges are sampled together.
-Up to 20\% performance can be gained by an early exit at line \ref{ln:early_exit} using sorted random values.
+In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together.
+Since sorted random values are XOR'ed with the same edge hash values, it is more likely to nontaken edges are sampled together.
+Up to 20\% speed-up can be achieved by an early exit at line \ref{ln:early_exit} using sorted random values.
 
 \subsection{Implementation Details}
-The Compressed Sparse Row~(CSR) graph data the structure used by all the algorithms. 
-In CSR, an array, $index$, holds the starting indices of each neighboring vertex, while another vector, $adj$, holds consecutive neighbors of each vertex. 
+While implementing the \acro, we have used the Compressed Sparse Row~(CSR) graph data structure.
+In CSR, an array, $index$, holds the starting indices of each neighboring vertex, while another vector, $adj$, holds the consecutive neighbors of each vertex. 
 To enter the neighbors of vertex $i$ we first visit $index[i]$ and $index[i+1]$ 
@@
 
-We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; Due to the nature of the diffusion algorithm, \acro traverses vertices even if they are blocked.
-Also, for each live vertex \acro generates sample edges for all simulations regardless.
-Small $w$ values increases overhead operations we mentioned.
-The other two experiment settings are used to emulate experiments of Kempe et al.~\cite{kempe2003maximizing}
+We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; due to the nature of the diffusion algorithm, \acro traverses vertices even if they are blocked.
+Also, for each live vertex, \acro generates sample edges for all simulations regardless.
+The other two experiment settings are used to emulate the experiments of Kempe et al.~\cite{kempe2003maximizing}
 
@@
 
-In this paper, the algorithms are evaluated on execution time, influence score, and maximum resident memory use. In computing, these three are
-often traded off to each other; In the extreme, it is trivial to select random vertices as seed set or compute reachability sets of every possible seed set combination.
+In this paper, the algorithms are evaluated on execution time, influence score, and maximum resident memory . In computing, these three are
+often traded off to each other; in the extreme, it is trivial to select random vertices as the seed set or compute reachability sets of every possible seed set combination.
 
 The observed execution times and memory consumption of different algorithms are comparable when the algorithms run on the same computer.
-In this paper, the execution time measured is always the wall time reported by the programs. 
-All methods we benchmarked leave out the time spend on reading files and pre-processing.
-To be fair in evaluating our method, we only left out the time to spend on reading files, and respected authors' measurement schemes in other methods.
-In all benchmarks, we allowed methods to fully utilize all available CPU cores, except {\sc Tim+} which is a single-threaded software.
+In this paper, the execution times are always the wall time reported by the programs.
+All methods we benchmarked leave out the time spent on reading files and preprocessing. To be fair in evaluating our method, we only left out the time to spend on reading files.
+
+In all benchmarks, we allowed all methods to fully utilize all available CPU cores, except {\sc Tim+} which is a single-threaded software.
 Memory use we reported is Resident Set Size(RSS) and measured using GNU Time software.
@@
 Although, because the algorithms can use various methods to measure the impact score, the reported influence scores may be deceptive. 
-Due to reason, we implemented an oracle with a very simple, sample-than-diffuse algorithm without any optimization mentioned.
+Due to this reason, we implemented an oracle with a very simple, sample-than-diffuse algorithm without any optimization mentioned.
 The random oracle values are generated by the 32-bit Mersenne Twister pseudo-random generator with a state size of 19937 bits {\tt mt19937} from {\tt C++ standard library}.
-All influence scores in this paper are reported with the independent oracle.
+All influence scores in this paper are reported by the independent oracle.
 
@@
 First, Two-phased Influence Maximization({\sc Tim+})~\cite{tim},TIM consists of two phases, Parameter Estimation and Node Selection. The first phase computes a lower-bound
-of the maximum expected to spread among all size-k node sets,
-and then uses the lower-bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from
+of the maximum expected spread among all size-k node sets,
+and then uses the lower bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from
 G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
 
-Second, Sketch-based Influence Maximization({\sc Skim})~\cite{cohen2014sketch} constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-thread parallelization in some degree.
+Second, Sketch-based Influence Maximization({\sc Skim})~\cite{cohen2014sketch} constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multithread parallelization in some degree.
 
@@
 
-The influence of all vertices is generalized on a small set of sample graphs that is sampled from reachability sets of few vertices.
+The influence of all vertices is generalized on a small set of sample graphs that is sampled from the reachability sets of a few vertices.
 Experimentations are done with $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined hyper-parameter controlling the approximation boundaries.
@@
 Finally, our method \acro employs both Monte-Carlo simulations and count-distinct sketches for estimating reachability set cardinalities.
-Even-though, \acro is blazing-fast and accurate for limited $K$, we exploit the performance of the method to improve results by rebuilding sketches after removing residual influence networks.
+Even though \acro is blazing-fast and accurate for limited $K$, we exploit the performance of the method to improve the results by rebuilding sketches after removing residual influence networks.
 
@@
 
-\subsection{Scalability with multi-threaded parallelism}
+\subsection{Scalability with multithreaded parallelism}
 
@@
 In our implementation, the parallel processing of live vertices  (as source) is necessary to reduce the number of visited edges.
-However, since a (target) vertex can be being processed at the same time, the update operation at line~\ref {ln:update} of this {\em pull-based} approach can be seen as a potential source of race conditions.
-But, since iterations are performed until convergence, the results are sound within our assumptions.
+However, since a (target) vertex can be being processed at the same time, the update operation at the line~\ref {ln:update} of this {\em pull-based} approach can be seen as a potential source of race conditions.
+However, since iterations are performed until convergence, the results are sound within our assumptions.
 On the other hand, the performance may suffer due to false sharing.
@@
 \subsection{Comparing \acro with State-of-art}
-All algorithms mentioned in this paper, estimates influence maximizing seed sets, that are good enough but not optimal.
+All algorithms mentioned in this paper estimate the influence maximizing seed sets that are good enough but not optimal.
 For that reason, we compare both the performance and quality of the results.
@@
 It is infeasible to find exactly the corresponding parameter between any two methods in this setting.
-For that reason, we have used parameters that authors of the methods used in their papers.
+For that reason, we have used the parameters suggested by the  authors themselves.
 We performed experiments using following parameters; {\sc Tim+} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$).
 
-One of the drawbacks of \acro is that we do not have direct control over the approximation factor whereas other methods we compare against some form of an approximation control parameter.
-\acro can only control approximation quality indirectly by tuning the number of Monte-Carlo simulations $J$, and to some degree with estimation/convergence thresholds.
-For \acro, we used $J=256$ registers which is comparable in terms of quality of other methods.
-And, for performance we used global estimation error threshold $\epsilon_{global}=0.01$, local estimation error threshold $\epsilon=0.3$, and set non-converged vertices ratio as $\epsilon_{conv}=0.02$.
+One of the drawbacks of \acro is that we do not have direct control over the approximation factor, whereas the other methods have some form of an approximation control parameter.
+\acro can only control approximation quality indirectly by tuning the number of Monte-Carlo simulations $J$.
+
+For \acro, we used $J=256$ registers which is comparable in terms of quality to other methods.
+Also, we used the global estimation error threshold $\epsilon_{g}=0.01$, local estimation error threshold $\epsilon_l=0.3$, and set non-converged vertices ratio as $\epsilon_{c}=0.02$.
 
 For small $w=0.005$ and small graphs such as NetHep, NetPhy, or Amazon; we can see {\sc Tim+}  has ($4\sim 6\%$) better results, whereas {\sc Skim}  has much ($- 13\sim 44\%$) worse results than \acro in terms of quality.
-While \acro having a hard time to catch edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim+} won't suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
-On the performance side, \acro is superior to other methods, Amazon dataset only takes 1.3 seconds including Monte-Carlo influence oracle computations.
+While \acro is having a hard time to catch edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim+} won't suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
+On the performance side, \acro is superior to other methods, Amazon dataset only takes 1.3 seconds, including Monte-Carlo influence oracle computations.
 {\sc Skim} and {\sc Imm} take 63.73 and 124.38 seconds.
-For 4\% quality improvement, {\sc Imm} is $\sim$100 slower than \acro.
+For 4\% quality improvements, {\sc Imm} is $\sim$100 slower than \acro.
 For small improvements in quality, we can always double the number of registers/simulations $J=256$ to $512$, which would approximately double the wall time.
@@
 In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
-For $w=0.1$, \acro is much faster than all other methods and still providing high-quality results.
+For $w=0.1$, \acro is much faster than all other methods and still provides high-quality results.
 While all methods are struggling with problem size, \acro is converging results much faster, even faster than previous experiment settings.
-Also, memory consumption stays the same for all experimental settings, much smaller than other methods.
+Also, the memory consumption stays the same for all experimental settings, much smaller than other methods.
 
-Performance characteristics of \acro is very different from its state-of-the-art competitors; \acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depends on the influence score.
-Due to reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
+Performance characteristics of \acro is very different from its state-of-the-art competitors; \acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depend on the influence score.
+Due to this reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
 In exceptional settings, such as Pokec dataset and $w=0.01$ where the diameter of the influence network is 43, \acro loses its edge against its fastest competitor.
-On the other hand in the same dataset with $w=0.1$, the diameter is 17; \acro is 6 times faster than its nearest competitor.
+On the other hand, in the same dataset with $w=0.1$, the diameter is 17; \acro is 6 times faster than its nearest competitor.
 
@@
 {\sc InFuseR} computes influence by memoizing connected-components for all vertices and only works on {\em undirected} datasets.
-Also, employs CELF optimizations to reduce candidate seed set cardinality computations.
-Whereas, \acro can process both directed and undirected graphs, and uses sampled Flajolet–Martin sketches to both estimate cardinalities and choose candidates.
+In addition, it employs CELF optimization to reduce candidate seed set cardinality computations.
+Whereas, \acro can process both directed and undirected graphs, and uses sampled Flajolet–Martin sketches to both estimate cardinality and choose candidates.
 
-Sketch-based influence maximization improves theoretical efficiency against simulation-based methods.
+Sketch-based influence maximization improves the theoretical efficiency against simulation-based methods.
 The sketch-based approach pre-computes sketches for evaluating the influence spread instead of running simulations repetitively.
 One of the interesting methods for sketch-based influence maximization is {\sc Skim} ~\cite{cohen2014sketch} by Cohen~et~al.
-It constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-core, multi-CPU parallelization.
+It constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-core/multi-CPU parallelization.
 
-Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al runs a proxy model and prunes paths with probabilities less than a given threshold.
+Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al, runs a proxy model and prunes paths with probabilities less than a given threshold.
 IPA uses {\tt OpenMP} to work on independent paths in parallel.
-The approach only keeps a dense but small part of the network and scalable on only sparse networks.
+The approach only keeps a dense but small part of the network and scalable to only sparse networks.
 Liu~et~al.
@@
 The algorithm has an approximation guarantee of $(1-1/e-\epsilon)$.
-Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast}.
+Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multithreaded and distributed architectures~\cite{minutoli2019fast}.
 Recently, the authors extended the algorithm to work on GPUs~\cite{curipples}.
@@
 Two-phased Influence Maximization({\sc Tim+})\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
-The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets, and then uses the lower-bound to derive a parameter $\theta$.
+The first phase computes a lower-bound of the maximum expected spread among all size-k node sets, and then uses the lower bound to derive a parameter $\theta$.
 In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
@@
 Cohen\cite{cohen2015all} presented the Historic Inverse Probability (HIP) estimators.
-When applied to the All Distance Sketches, HIP outperforms in estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for approximate distinct counting on data streams.
+When applied to All Distance Sketches, HIP outperforms in the estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for approximate distinct counting on data streams.
 In this work, we preferred Flajolet-Martin\cite{flajolet1985probabilistic} sketches for simplicity and performance.
@@
 The algorithm performs the influence reachability sets for all vertices in an interaction graph performing a single pass over the data.
-Sketches build for each time window to estimate active edges where as \acro builds sketches for each vertex to estimate the cumulative influence of the latent seed set.
+Sketches are used for each time window to estimate active edges, whereas \acro builds sketches for each vertex to estimate the cumulative influence of the latent seed set.
 \acro also utilizes fused sampling and error adaptive rebuilding of sketches.
@@
 In addition, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
-With the proposed method, \acro{} can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.
+With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.
 
@@
 The main issue with \acro on such computation scheme is the broadcast of sketch registers; when vertices are partitioned to different computation units, resulting sketch updates should be communicated to all partitions.
-To overcome the issue, graph pre-processing and speculative diffusion strategies can reduce communication bottlenecks.
+To overcome the issue, graph preprocessing and speculative diffusion strategies can reduce communication bottlenecks.
 

### 2021-01-22 paper.tex
progress

@@
 
-That is, when the simulations traverse the same edge within close time intervals, the edge is accessed only once as long as the simulation timelines allow \acro to do so.
+\acro processes all samples of an edge together.
 The suggested approach, therefore, decreases the pressure on the memory management unit.
-In relation to the cascade model, we employ a vector compute unit, near maximum efficiency to regularize memory accesses.
-%\item In addition to instruction-level parallelism, we parallelize \acro on multi-core architectures.
+On the cascade models, \acro employs vector compute units to its near maximum efficiency to regularize memory accesses.
 
@@
 Although we focus on undirected graphs, for IM, the graph can be directed or undirected depending on the initial construction.
-Figure~\ref{fig:xx} shows a~(Fig.~\ref{fig:ic}) and directed~(Fig.~\ref{fig:wc})
-graph in which the weights on the edges are diffusion/influence probabilities.
 
@@
 \begin{itemize}[leftmargin=*]
-\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges, $(u, v)$, is 
-used during the iteration of diffusion, which has an expected probability of $w_{u, v}$, because $u$ was already influenced in the previous rounds. 
+\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges $(u, v)$ is 
+used during the iteration of diffusion, which has an expected probability of $w_{u, v}$ because $u$ was already influenced in the previous rounds. 
 Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
-In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via pre-processing.
+In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
 
@@
 \item{\bf Linear threshold} generalizes the independent cascade model and activates the $v$ vertex once the cumulative activation coming from the neighbors of $v$ exceeds the $\theta v$ threshold. 
-All $\{u, v\}$~(or $(u, v)$ in the directed graph) edges 
-with active $u$ vertices are taken into account in the process. Vertex $v$ is activated~\cite{kempe2003maximizing} when the number of these edge weights reaches $\theta v$.  
+All $\{u, v\}$~(or $(u, v)$ in the directed graph) edges with active $u$ vertices are taken into account in the process.
+Vertex $v$ is activated~\cite{kempe2003maximizing} when the number of these edge weights reaches $\theta v$.
 Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta v = 0 $.
 
-\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize of the previous models mentioned above.
+\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize the previous models mentioned above.
 In the triggering model, each neighbor has a probability to influence the vertex $v$.
@@
 
-The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models.
+The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}~(IC), {\em Weighted Cascade}~(WC), and {\em Linear Threshold}~(LT)  models.
 We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to other models in the literature.
@@
 \subsection{Count-Distinct Sketch}\label{sec:sketch}
-Count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
+The count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
 Computing the reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample subgraphs from the given vertex.
@@
 
-Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($J$), and most importantly union of these sets can be done in a constant number of operations.
+Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($J$), and most important, union operation on these sets can be done in a constant number of operations.
 
-Flajolet–Martin algorithm only stores how rare elements are in a multiset.The rarity of the elements is often computed by counting the leading zeros in the item's hash value.
+Flajolet–Martin algorithm only stores how rare elements are in a multiset.
+The rarity of the elements is often computed by counting the leading zeros in the item's hash value.
 The registers are initialized with zero values in the beginning.
@@
 Then, the incoming edges $(u,v)$ for all live vertices are processed.
-For all simulations where $u$ is live, the sketch of both sides are merged and set to $u$ registers.
+For all simulations where $u$ is live, the sketches of both sides are merged and set to $u$ registers.
 If any of the sketch registers change, the vertex $u$ is added to the next iteration's live vertices set $L'$.
@@
     % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-    For the live edge between Vertex 1 and 4, the register set to the maximum of the respective register.
+    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
 Since the first register of vertex 1 has a larger value, we only update the second register.
@@
 We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
-(d) All vertices have registers converged, there are no live vertices.
+(d) All vertices have registers converged.
+There are no live vertices.
 }\label{fig:hf-processing}
@@
 Moreover, another one that builds the sketch once at the beginning, then only utilizes sketch merge operation to find the seed set.
-Even though at first few vertices the expected influence is comparable, we see observe near-linear drop-off in the estimated influence.
+Even though at first few vertices the expected influence is comparable, we observe near-linear drop-off in the estimated influence.
 
@@
 
-Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited 
-and considered blocked in their respective simulations while rebuilding the sketches.
+Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited and considered blocked in their respective simulations while rebuilding the sketches.
 Then, the sketches are rebuilt using Monte-Carlo simulations.
@@
 If a rebuild is not required, we only update $mask$ by merging it with the candidate vertex's sketch. 
-This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set, but on the other hand, forces us to perform Monte-Carlo simulations which can be expensive.
+This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
 We reuse the reachability sets of the latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
@@
 Since $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
-Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slowdown the method, but it will give the best possible results.
+Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slow-down the method, but it will give the best possible results.
 Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are built only once without checking the vertices blocked.
@@
 We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters.
-In figure~\ref{fig:parameter-smallmultiples}, both the speed and the quality of the results on some of the largest datasets we have experimented are shown.
-We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, perform decent in many datasets, both in terms of speed and quality.
+Both the speed and the quality of the results on some of the largest datasets we have experimented shown in figure~\ref{fig:parameter-smallmultiples}.
+We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, perform well in many datasets, both in terms of speed and quality.
 
@@
 First, Two-phased Influence Maximization({\sc Tim+})~\cite{tim},TIM consists of two phases, Parameter Estimation and Node Selection. The first phase computes a lower-bound
-of the maximum expected spread among all size-k node sets,
+of the maximum expected to spread among all size-k node sets,
 and then uses the lower bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from
@@
 
-Performance characteristics of \acro is very different from its state-of-the-art competitors; \acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depend on the influence score.
+Performance characteristics of \acro are very different from its state-of-the-art competitors.
+\acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depends on the influence score.
 Due to this reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
-In exceptional settings, such as Pokec dataset and $w=0.01$ where the diameter of the influence network is 43, \acro loses its edge against its fastest competitor.
-On the other hand, in the same dataset with $w=0.1$, the diameter is 17; \acro is 6 times faster than its nearest competitor.
+In exceptional settings, such as the Pokec dataset and $w=0.01$ where the diameter of the influence network is around 43, \acro loses its edge against its fastest competitor.
+On the other hand, in the same dataset with $w=0.1$, the diameter is only around 17; \acro is 6 times faster than its nearest competitor.
 
@@
 
-Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS) which samples a fraction of all random reverse reachable sets.
+Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS), which samples a fraction of all random reverse reachable sets.
 Then it computes a set of $K$ seeds that covers the maximum number of those.
@@
 Two-phased Influence Maximization({\sc Tim+})\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
-The first phase computes a lower-bound of the maximum expected spread among all size-k node sets, and then uses the lower bound to derive a parameter $\theta$.
+The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets.
+Then, it uses the lower bound to derive a parameter $\theta$.
 In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
@@
 Cohen\cite{cohen2015all} presented the Historic Inverse Probability (HIP) estimators.
-When applied to All Distance Sketches, HIP outperforms in the estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for approximate distinct counting on data streams.
+When applied to All Distance Sketches, HIP outperforms in the estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for counting distinct elements on data streams.
 In this work, we preferred Flajolet-Martin\cite{flajolet1985probabilistic} sketches for simplicity and performance.
@@
 Cascade Model and an influence maximization algorithm that works on the model using versioned HyperLogLog sketches.
-The algorithm performs the influence reachability sets for all vertices in an interaction graph performing a single pass over the data.
+The algorithm computes the influence reachability sets for all vertices in an interaction graph while performing a single pass over the data.
 Sketches are used for each time window to estimate active edges, whereas \acro builds sketches for each vertex to estimate the cumulative influence of the latent seed set.
@@
 In conclusion, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and error-adaptive rebuilding.
-We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple CPU cores.
-In addition, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
+We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple cores.
+Also, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
 With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.

### 2021-01-23 paper.tex
Update on Overleaf.

@@
 
-\title{Fast and Error-Adaptive Count-Distinct Sketch
-\\for Influence Maximization}
+\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}
 
@@
 Due to the NP-Hardness of finding an optimal seed set, approximation methods are frequently used for IM.
-In addition to high-quality yet expensive approximation algorithms, to meet with the scale of today's networks, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature.
-As expected, the quality of the seed sets for the latter is inferior to that of the former.
+In addition to these high-quality, yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature to cope with the scale of today's networks.
+%As expected, the quality of the seed sets for the latter is inferior to that of the former.
 In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and the recently proposed hash-based fused sampling.
-To estimate the vertex set sizes influenced throughout the simulations, we use per-vertex Flajolet-Martin sketches where each sketch register corresponds to a sample subgraph.
-During the diffusion simulations, the reach set cardinalities of a single vertex are stored in adjacent registers in memory.
-This allows the proposed algorithm to find the number of influenced vertices in a single simulation step in different simulations at once.
-In addition, thanks to its efficiency and scalability of our parallel implementation, we can rebuild the sketches after observing large estimation errors.
-Our experimental results show that the proposed method finds high-quality seed sets while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
+To estimate the number of influenced vertices throughout a diffusion, we use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
+To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion.
+This allows the proposed algorithm to find the number of influenced vertices in a single simulation step of different simulations at once.
+In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary.
+For a faster IM kernel, we rebuild the sketches only after observing estimation errors above a given threshold.
+Our experimental results show that the proposed method yields high-quality seed sets while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
 In addition, it is $3.5\times$--$11.1\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
 \end{abstract}
+}
+
 % Note that keywords are not normally used for peer review papers.
-}
+% section 3, overview
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+% 
+%
 
@@
 As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
-Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
+Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time spent, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
 
-Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability under some diffusion model $M$.
-In addition to introducing the problem, Kempe et al.~\cite{kempe2003maximizing} proved it to be NP-hard and provided a greedy Monte-Carlo approach that has a constant approximation for the optimal solution.
+Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum number of vertices, under some diffusion model $M$.
+Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, proved it to be NP-hard, and provided a greedy Monte-Carlo approach that has a constant approximation ratio over the optimal solution.
 This greedy approach is one of the most frequently applied algorithms for IM.
 The time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
-Although they perform well in terms of seed-set quality, as a consequence, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices.
+Although they perform well in terms of seed-set quality, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices as a consequence of their expensive simulation costs.
 Due to this reason, many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.
@@
 Instead, it leverages Count-Distinct sketches.
+Below is a summary of our contributions:
 
-In this work;
-\begin{itemize}[leftmargin=*]
-\item We propose \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, a blazing-fast, and accurate Influence Maximization algorithm.
+\begin{itemize}
+\item We propose \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.
 The proposed scheme samples the edges as they are traversed across several simulations.
@@
 
-\item Running concurrent simulations on per-vertex count-distinct sketches reduces the number of memory accesses.
-While traversing an edge, any number of diffusion simulations can be performed between vertices, using only a single integer (8-bit) per vertex for each simulation.
+\item Running concurrent simulations on per-vertex Count-Distinct sketches reduces the number of memory accesses.
+While traversing an edge, any number of diffusion simulations can be performed between vertices, using only a single (8-bit) value per vertex for each simulation.
 
-\acro processes all samples of an edge together.
+\acro processes all samples of a single edge together.
 The suggested approach, therefore, decreases the pressure on the memory management unit.
@@
 For large graphs, due to its race condition indifferent nature, the performance scales near linearly with the number of threads available.
-While processing the graph, only a few GBs of memory is used, mostly for storing the graph itself.
+Furthermore, while processing the graph, only a few GBs of memory is used, mostly for storing the graph itself.
 
-\item We evaluate the performance, memory consumption, and influence score with a state-of-the-art influence maximization algorithm {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim}, {\sc Imm}~\cite{minutoli2019fast} to accurately position the performance of \acro{} in the IM literature.
-The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than state-of-the-art while still being better in comparison in terms of scores, and using a comparable amount of memory.
+\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} in the IM literature.
+The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than state-of-the-art sketch-based algorithms while having almost the same quality with the approximation-based algorithms in terms of scores, and using a comparable amount of memory.
 
@@
 In Section~\ref{sec:evaluation}, a thorough performance comparison over the traditional algorithms is provided by conducting experiments on various real-world datasets and influence settings.
-Besides, a comparison with the state-of-the-art from the literature is given.
+A detailed comparison with the state-of-the-art from the literature is also given.
 Section~\ref{sec:relatedwork} presents a comparative overview of the existing work. Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.
@@
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$.
-Diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$.
-$w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.
+The diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$, where $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.
 
@@
         $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
-        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
+        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
         % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
         \hline\hline
-        $w$             & Sampling probability for edges\\
+        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
         $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
@@
 Influence Maximization aims to find a seed set $S \subseteq V$ among all possible size $K$ subsets of $V$ that maximizes an {\em influence spread function} $\sigma$  when the diffusion process is initiated from $S$.
-Although we focus on undirected graphs, for IM, the graph can be directed or undirected depending on the initial construction.
+Although we focus on graphs with bidirectional edges, for IM, the edges can be unidirectional depending on the initial construction.
+That is although the edges $\{u, v\} \in E$ are assumed to be bidirectional, throughout the diffusion process, we use $(u, v)$~($(v, u)$) as the edge that may be used to influence/activate $v$~($u$) given that $u$~($v$) has already been influenced/activated.
+This being said, $w_{u,v}$ can be set to zero to make the edge $(v, u)$ practically unidirectional.
 
@@
   \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.50\linewidth]{images/ic.pdf}}
+       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
   \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.50\linewidth]{images/wc.pdf}}
+        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
     \\% IMAGES HERE
@@
 In the literature, {\em independent} and {\em weighted cascade}~(IC and WC), and 
-{\em linear threshold}~(LT)~\cite{kempe2003maximizing} are some of the widely recognized diffusion models for IM.
+{\em linear threshold}~(LT)~\cite{kempe2003maximizing} are three widely recognized diffusion models for IM.
 
 \begin{itemize}[leftmargin=*]
-\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges $(u, v)$ is 
-used during the iteration of diffusion, which has an expected probability of $w_{u, v}$ because $u$ was already influenced in the previous rounds. 
-Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
+\item An {\bf Independent Cascade} process performs in iterations and activates a vertex $v$  if one of $v$'s (incoming) edges $(u, v)$ is 
+used during the diffusion iteration, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
+The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
 In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
 
-\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set weights as shown in Figure~\ref{fig:wc}.
-The method, as described in ~\cite{MixGreedy}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
-of incoming edges of $v$ for introducing weight values(which in the original graph is equal to $\Gamma G(v)$).
-Therefore, if $v$ is triggered after the last round with $\ell$ neighbors, its activation probability in the new round is $1-( 1-1 / d_v)^\ell$.
+\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
+The method, as described in~\cite{MixGreedy}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
+of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
+Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$.
 
@@
 All $\{u, v\}$~(or $(u, v)$ in the directed graph) edges with active $u$ vertices are taken into account in the process.
-Vertex $v$ is activated~\cite{kempe2003maximizing} when the number of these edge weights reaches $\theta v$.
-Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta v = 0 $.
+Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.
+Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta_v = 0$. 
+\end{itemize}
 
-\item {\bf Triggering} proposed by Kempe et al.\cite{kempe2003maximizing} to generalize the previous models mentioned above.
-In the triggering model, each neighbor has a probability to influence the vertex $v$.
-The diffusion process chooses a random subset of vertices called the "triggering set" to activate the vertices at each instance.
-\end{itemize}
+As a generalization of these models, {\bf triggering} has been proposed by Kempe~et~al.~\cite{kempe2003maximizing} to generalize the previous models mentioned above.
+In this model, each neighbor has a probability to influence the vertex $v$.
+The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
 
@@
 \subsection{Count-Distinct Sketch}\label{sec:sketch}
-The count-distinct problem is the problem of finding the number of distinct elements in a stream with non-distinct elements.
+The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream with non-distinct elements.
 Computing the reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample subgraphs from the given vertex.
@@
 
-\section{Method}\label{sec:method}
+\section{Error-Adaptive Influence Maximization}\label{sec:method}
+
+\kktodo{burada bir giris gerekiyor - basit, 4-5 adimli bir algoritma, bir iki paragraf anlatim ne yapiyoruz, niye yapiyoruz}
 
@@
     \begin{center}
-    \includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
+    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
     \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
@@
     \begin{center}
-    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
+    \includegraphics[width=0.7\linewidth]{images/sketch-saturation.pdf}
     \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
-Dataset      &            &         &        &       &            &         &         &         &            &       &      &      \\
+Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+
+Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
+
 \midrule
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
 
-Dataset      &            &         &         &        &            &         &         &         &            &       &       &      \\
+Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
 \midrule
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
-Dataset      &            &         &         &        &            &         &         &         &            &        &       &      \\
+Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+
+Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
 \midrule
@@
 
-\subsection{Scalability with multithreaded parallelism}
+\subsection{Scalability with multi-threaded parallelism}
 
@@
 The algorithm has an approximation guarantee of $(1-1/e-\epsilon)$.
-Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multithreaded and distributed architectures~\cite{minutoli2019fast}.
+Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast}.
 Recently, the authors extended the algorithm to work on GPUs~\cite{curipples}.

### 2021-02-02 paper.tex
progress

@@
 
-\kktodo{burada bir giris gerekiyor - basit, 4-5 adimli bir algoritma, bir iki paragraf anlatim ne yapiyoruz, niye yapiyoruz}
+% \kktodo{burada bir giris gerekiyor - basit, 4-5 adimli bir algoritma, bir iki paragraf anlatim ne yapiyoruz, niye yapiyoruz} % gg:Anlatim ile aciklamayi birlestirdim.
+Most influence maximization methods have the same few steps to compute the seed set including; Sampling, building influence oracle, verifying candidates, then removing the residual reachability set of the latent seed set.
+\acro, on the other hand, fuses sampling step to other steps to accumulate memory accesses.
+
+\acro first performs a diffusion process; The process starts with per-vertex sketches that are initialized with their own vertices. 
+Then, for all edges sketch of the source vertex is merged with the target vertex until all registers converge. 
+The merge operation utilized in the process is slightly different from the conventional use and retrofitted to mimic the independent cascade diffusion model. 
+Registers of a sketch are assigned to a single sample/simulation; Merge operations are performed on the register only if both vertices are $live$ in the sample associated with the register. 
+This process relays reachability information between vertices. 
+At each iteration, all reachable vertices in a single step are added to the sketches. 
+Instead of performing diffusion for a single vertex/path/, all influence that passes through an edge in a single step is processed. 
+This dynamic programming like property allows us to estimate marginal influence for all vertices very fast. 
+After, \acro picks the vertex with the largest estimated reachability set by looking at sketches alone. 
+After, \acro calculates reachability sets of the latent seed set by performing Monte-Carlo simulations. 
+The Vertices in the reachability sets are labeled blocked in respective samples. 
+Finally, \acro computes whether to rebuild the sketches using the error between sketch estimate and Monte-Carlo estimate.
 
@@
 % For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
-Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. The sampling probability distribution of hash-based computation is almost identical to the uniform distribution with small bias.
+% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
+The sampling probability distribution of hash-based computation is almost identical to the uniform distribution with small bias.
 
-\begin{figure}[!ht] 
-    \centering
-    \includegraphics[width=1\linewidth]{./images/bias.pdf}
-    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.}
-    \label{fig:prob-bias} 
-\end{figure}
+% \begin{figure}[!ht] 
+%     \centering
+%     \includegraphics[width=1\linewidth]{./images/bias.pdf}
+%     \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.}
+%     \label{fig:prob-bias} 
+% \end{figure}
 
@@
 
-After diffusion, the following process is repeated until $K$ vertices are added to the seed set; For all vertex, $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $mask$ and their sketch registers.
-The $mask$ used for the sketch of $R_G(S)$ and initialized with zeros.
+After diffusion, the following process is repeated until $K$ vertices are added to the seed set; For all vertex, $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $M_S$ and their sketch registers.
+The $M_S$ used for the sketch of $R_G(S)$ and initialized with zeros.
 Vertex with maximum cardinality is selected to add to the seed set.
@@
 Then, the sketches are rebuilt using Monte-Carlo simulations.
-After rebuilding, $mask$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.
+After rebuilding, $M_S$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.
 
 The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
-If a rebuild is not required, we only update $mask$ by merging it with the candidate vertex's sketch. 
+If a rebuild is not required, we only update $M_S$ by merging it with the candidate vertex's sketch. 
 This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
@@
     \State $M \leftarrow simulate(G,M,\emptyset)$
-    \State $mask \leftarrow zeros(J)$
+    \State $M_{S'} \leftarrow zeros(J)$
     \State $\varsigma \leftarrow 0$
     \For{$k=1\ldots K$}
-        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
+        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(M_{S'},M_v))$
         \State $S \leftarrow S \cup \{s\}$
-        \State $e \leftarrow estimate(merge(mask,M_s))$
+        \State $e \leftarrow estimate(merge(M_{S'},M_s))$
         % \State $R_S \leftarrow run\_cascade(G,S,J)$
@@
         \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
-            \State $mask \leftarrow merge(mask,M_s)$
+            \State $M_{S'} \leftarrow merge(M_{S'},M_s)$
         \Else
@@
             \State $M \leftarrow simulate(G,M,R_S)$
-            \State $mask \leftarrow zeros(J) $ 
+            \State $M_{S'} \leftarrow zeros(J) $ 
             \State $\varsigma \leftarrow \sigma $ 

### 2021-04-02 paper.tex
Update on Overleaf.

--- 2021-01-23 paper.tex
@@
 Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
-Due to the NP-Hardness of finding an optimal seed set, approximation methods are frequently used for IM.
+Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
 In addition to these high-quality, yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature to cope with the scale of today's networks.
-%As expected, the quality of the seed sets for the latter is inferior to that of the former.
-In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and the recently proposed hash-based fused sampling.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling.
 To estimate the number of influenced vertices throughout a diffusion, we use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
 To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion.
-This allows the proposed algorithm to find the number of influenced vertices in a single simulation step of different simulations at once.
+This allows the proposed algorithm to estimate the number of influenced vertices in a single simulation step of different simulations at once.
 In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary.
@@
 
-The study of efficient information/influence propagation in networks becomes an important area of research with several applications in many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
-As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
-Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time spent, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
+Efficient information/influence dissemination in a network is an important research area with several applications in various fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
+As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have vital importance.
+Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
 
-Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum number of vertices, under some diffusion model $M$.
+Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model $M$.
 Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, proved it to be NP-hard, and provided a greedy Monte-Carlo approach that has a constant approximation ratio over the optimal solution.
@@
 Simulating a greedy algorithm in parallel is a straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
-However, for large networks, a greedy approach with a good approximation guarantee does not come cheap even if a large number of processing units/cores are available on networks with billions of vertices and edges.
+However, for large networks, a greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges even if a large number of processing units/cores are available.
 Following similar attempts in the literature, we propose a parallel, sketch-based greedy approach that approximates the Monte-Carlo processes.
-The proposed approach does not exactly count the number of influenced vertices.
+To further increase the performance, the proposed approach does not exactly count the number of influenced vertices.
 Instead, it leverages Count-Distinct sketches.
@@
 
-\item Running concurrent simulations on per-vertex Count-Distinct sketches reduces the number of memory accesses.
-While traversing an edge, any number of diffusion simulations can be performed between vertices, using only a single (8-bit) value per vertex for each simulation.
-
-\acro processes all samples of a single edge together.
-The suggested approach, therefore, decreases the pressure on the memory management unit.
-On the cascade models, \acro employs vector compute units to its near maximum efficiency to regularize memory accesses.
+\item Running concurrent simulations on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
+While traversing an edge, any number of diffusion simulations can be simultaneously performed over the graph, using only a single (8-bit) value per vertex for each simulation.
 
@@
 
-\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} in the IM literature.
-The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than state-of-the-art sketch-based algorithms while having almost the same quality with the approximation-based algorithms in terms of scores, and using a comparable amount of memory.
+\item Once it is read from the memory, \acro processes all samples of a single edge together.
+The suggested approach, therefore, decreases the pressure on the memory subsystem.
+Furthermore, it employs vector compute units to its near maximum efficiency to regularize memory accesses.
+
+\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having almost the same quality with the approximation-based algorithms in terms of influence, and using a comparable amount of memory.
 
@@
 Section~\ref{sec:method} describes the proposed approach in detail.
-In Section~\ref{sec:evaluation}, a thorough performance comparison over the traditional algorithms is provided by conducting experiments on various real-world datasets and influence settings.
-A detailed comparison with the state-of-the-art from the literature is also given.
-Section~\ref{sec:relatedwork} presents a comparative overview of the existing work. Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.
+In Section~\ref{sec:evaluation}, a thorough performance evaluation is provided by conducting experiments on various real-world datasets and influence settings.
+A detailed empirical comparison with the state-of-the-art from the literature is also given.
+Section~\ref{sec:relatedwork} presents a comparative overview of the existing work.
+Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.
 
@@
 
-Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations between the agents in $V$.
-The neighborhood of a vertex $u \in V$ is denoted as $\Gamma_{G}(v) = \{v: (u,v) \in E\}$. 
+Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations among them.
+An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$.
+The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma_{G}(v) = \{u: (u,v) \in E\}$.
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$.
@@
         \hline
+        \kktodo{uzerinden 
+        gecelim}\\
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
-        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
+        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
         $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
@@
 Influence Maximization aims to find a seed set $S \subseteq V$ among all possible size $K$ subsets of $V$ that maximizes an {\em influence spread function} $\sigma$  when the diffusion process is initiated from $S$.
-Although we focus on graphs with bidirectional edges, for IM, the edges can be unidirectional depending on the initial construction.
+%Although we focus on graphs with bidirectional edges, for IM, the edges can be unidirectional depending on the initial construction.
 That is although the edges $\{u, v\} \in E$ are assumed to be bidirectional, throughout the diffusion process, we use $(u, v)$~($(v, u)$) as the edge that may be used to influence/activate $v$~($u$) given that $u$~($v$) has already been influenced/activated.
 This being said, $w_{u,v}$ can be set to zero to make the edge $(v, u)$ practically unidirectional.
+In the literature, {\em independent} and {\em weighted cascade}~(IC and WC), and 
+{\em linear threshold}~(LT)~\cite{kempe2003maximizing} are three widely recognized diffusion models for IM.
 
@@
   \caption{\protect\subref{fig:ic} 
-The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
+\kktodo{a parti nonuniform weight olsun} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
 \protect\subref{fig:wc}
-The directed graph was obtained from the directed one by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. 
+The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?} 
   }
@@
 \end{figure}
-In the literature, {\em independent} and {\em weighted cascade}~(IC and WC), and 
-{\em linear threshold}~(LT)~\cite{kempe2003maximizing} are three widely recognized diffusion models for IM.
 
 \begin{itemize}[leftmargin=*]
-\item An {\bf Independent Cascade} process performs in iterations and activates a vertex $v$  if one of $v$'s (incoming) edges $(u, v)$ is 
-used during the diffusion iteration, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
-The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
+\item The {\bf Independent Cascade} model works in rounds and activates a vertex $v$ in the current round if one of $v$'s incoming edges $(u, v)$ is 
+used during the diffusion round, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
+The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model which we concentrate on this paper.
+A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
 In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
@@
 \item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
-The method, as described in~\cite{MixGreedy}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
+The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
 of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
 Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
+\kktodo{bu tanim [7]'dekine uymuyor.
+Orada undirected graph var } Note that the model is originally defined for undirected graphs in~\cite{MixGreedy}.
+However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.
 
@@
 
-\item{\bf Linear threshold} generalizes the independent cascade model and activates the $v$ vertex once the cumulative activation coming from the neighbors of $v$ exceeds the $\theta v$ threshold. 
-All $\{u, v\}$~(or $(u, v)$ in the directed graph) edges with active $u$ vertices are taken into account in the process.
+\item{\bf Linear threshold} generalizes the independent cascade model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
+All the $(u, v)$ edges with active $u$ vertices are taken into account in the process.
 Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.
@@
 
-As a generalization of these models, {\bf triggering} has been proposed by Kempe~et~al.~\cite{kempe2003maximizing} to generalize the previous models mentioned above.
+%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}.
 In this model, each neighbor has a probability to influence the vertex $v$.
 The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
+The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}~(IC), {\em Weighted Cascade}~(WC), and {\em Linear Threshold}~(LT)  models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+\kktodo{bu son cumle dogru mu}\ggx{Aklima tersini dogrulayacak bir ornek gelmiyor hocam.
+Dogru olmali.} We concentrate on the IC model in this paper, but the proposed methods are also relevant to other models in the literature.
 
-The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}~(IC), {\em Weighted Cascade}~(WC), and {\em Linear Threshold}~(LT)  models.
-We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to other models in the literature.
+\subsection{Count-Distinct Sketches}\label{sec:sketch}
+The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$.
+Finding the number of vertices to be influenced of a candidate seed vertex, i.e., the cardinality of the {\em reachability set}, is a similar problem.
+For each sample subgraph, the number of visited vertices is calculated while traversing the subgraphs starting from the candidate vertex.
+Note that an exact computation of set cardinality requires memory proportional to the cardinality which is ${\mathcal O}(|{\cal U}|)$.
 
-\subsection{Count-Distinct Sketch}\label{sec:sketch}
-The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream with non-distinct elements.
-Computing the reachability sets of a vertex is a similar problem; the cardinality of all vertices visited is calculated while traversing sample subgraphs from the given vertex.
-Exact cardinality calculations require memory proportional to the cardinality.
-
-The reachability set of a vertex is a distinct union of all connected vertices' reachability sets. Many other Influence Maximization methods exploit this property to some degree.
-
-The methods based on Reverse Reachability and Bottom-Up Traversal utilize this property directly to merge the reachability sets of connected vertices to estimate vertices influence.
-MixGreedy method goes one step further; it utilizes that all vertices in a connected component that have the same reachability set in undirected graphs.
-Therefore, for a sample graph, all reachability sets can be found in a single graph traversal.
+The reachability set of a vertex is the union of those of all its connected vertices (via outgoing edges).
+Many IM kernels exploit this property to some degree.
+The methods based on {\em reverse reachability} \kktodo{cite} and {\em bottom-up traversal} \kktodo{cite} utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced.
+{\em MixGreedy} \kktodo{cite} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
+Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.
 
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
-If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
-if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(Ackermann'(\sigma))$ complexity.
+If one-hot vectors are used to store the reachability sets for constant insertion time $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity.
+If disjoints sets are used for storing reachability sets; $\mathcal{O}(n\bar{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann function \kktodo{bu Ackermann'a atif verelim}.
 
-Count-distinct sketches have nice properties for such problems; Flajolet–Martin algorithm\cite{flajolet1985probabilistic} can estimate the cardinality of distinct elements in reachability sets with a constant number of registers($J$), and most important, union operation on these sets can be done in a constant number of operations.
+Count-Distinct Sketches can be leveraged to efficiently estimate the cardinality of reachability sets; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers.
+Furthermore, the union of two sketches can be computed in constant time.
+The FM sketch simply stores that how rare the elements are in a stream.
+The rarity of the elements is estimated by counting the maximum number of leading zeros in the hash values of the stream elements.
+Initially, each register is initialized with zero.
+The items are hashed one by one and the length of the longest all-zero prefix is stored in the register.
+With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.
 
-Flajolet–Martin algorithm only stores how rare elements are in a multiset.
-The rarity of the elements is often computed by counting the leading zeros in the item's hash value.
-The registers are initialized with zero values in the beginning.
-Items are added by storing the longest leading zero count.
-Cardinality estimation can be done by taking 2 to the power of the stored value.
-Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
-Adding the item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.
-
+In practice, multiple registers and hash values, $M[j]$ and $h_j$, are commonly used to reduce variance.
+For a sketch with multiple registers, the impact of adding an item $x \in \cal{U}$ is shown in~\eqref{eq:sketch-add}:
 \begin{equation}
     \label{eq:sketch-add}
-    M'[j] = max(M[j],clz(h_j(x)) ~ \forall j\in(0,J]
-\end{equation} where $clz$ is count leading zeros function and $J$ is the number of sketch registers.
-
-The merge operation for two sketches, $M_u$,$M_v$, can be performed by computing the pairwise maximum of the registers. Formally; 
-\begin{equation}
-    \label{eq:sketch-merge}
-    M'[j] = max(M_u[j],M_v[j]) ~ \forall j\in(0,J]
-\end{equation} 
-where $M'$ is union of set and $J$ is the number of sketch registers.
-
-Average of the longest running zeros can be used compute the cardinality and the result is divided to the correction factor $\phi \approx 0.77351$ to correct hash collisions.
+    M[j] = \max(M[j], clz(h_j(x)),~1 \leq j \leq J
+\end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and $J$ is the number of sketch registers.
+With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided to a correction factor $\phi \approx 0.77351$ to fix the error due to hash collisions.
+That is the estimated cardinality $e$ is computed as
 \begin{equation}
@@
 \end{equation} 
-where $e$ distinct cardinality and $\bar{M}$ is the mean of the registers.
+where $\bar{M} = {\tt{avg}}_j\{M[j]\}$ is the mean of the register values.
 
-In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average of longest leading zero counts to calculate the average cardinality of reachability sets.
-Merge operations are performed if and only if there is an edge between the respective simulations.
+In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros.
+Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed, by taking the pairwise maximums of their registers.
+Formally;
+\begin{equation}
+\label{eq:sketch-merge}
+    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
+\end{equation} 
+In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples \kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}.
+\ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim.
+Yanlis olmus.}
 
@@
 
-\kktodo{burada bir giris gerekiyor - basit, 4-5 adimli bir algoritma, bir iki paragraf anlatim ne yapiyoruz, niye yapiyoruz}
+Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, then removing the residual reachability set of the latent seed set.
+Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.
+
+\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
+Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
+The merge operation utilized in this process is slightly different than the conventional one and retrofitted to mimic the IC diffusion.
+
+Throughout the process, each register is used only for a single sample/simulation.
+A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim} $u$ is {\em live} in the current iteration.
+This process iteratively relays the reachability information among the vertices.
+At each iteration, the sketches of the current reachable vertices are modified.
+\kktodo{onceki cumleyi de degistirdim - dogru mu}
+Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, and/or path-by-path, all the influence that passes through the edges in a single step is processed together. 
+This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
+After the computation of reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches.
+Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations.
+The vertices in the reachability sets are labeled {\em blocked} \kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekildeydi} in the respective samples.
+Finally, the algorithm checks if a rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
+\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.
 
 \subsection{Hash-based Fused Sampling}
-The probabilistic nature of cascade models requires sampling subgraphs $\hat{G}$ from $G = (V, E)$ to simulate the diffusion process.
-The sampling part of the algorithm can be a dominating factor in processing; sampling may demand multiple passes on the graph, if samples are memoized, multiple times of the graph size needs to be stored.
-In this work, we borrow hash-based fused sampling from {\sc InFuseR}\cite{infuser}.
-By using a hash-based fused sampling, we eliminate the necessity of in-memory creation and storage of the sample subgraphs.
-While processing an edge, it is considered for all possible samples.
-It is sampled or skipped depending on the outcome of the hash-based random value. The hash function used is given in equation \ref{eq:hash}.
-\begin{equation}
-    \label{eq:hash}
-    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
-\end{equation}
-where $||$ is the concatenation operator.
-
-We have tried a few other hash algorithms as well; Ideally, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with maximum bias $0.5 \% $\cite{MurmurHash3Performance}.
-
-For performance considerations, edge hash values were precomputed in our work and only existing pairs were considered.
-The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
-
-Although the above-mentioned approach generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
+The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process.
+If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be an expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
+In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of in-memory creation and storage of the sample subgraphs.\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek}
 
@@
 
-Multiple deterministic random values for each edge are generated by using the edge hash values and random numbers $X_r$ associated with each simulation $r$. 
-Sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed as follows; First, $h(u,v)$ is XOR'ed with a uniformly randomly chosen $X_r \in_R [0, h_{max}]$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
+In \acro, when an edge of the original graph is being processed, i.e., when it is read from the memory, it is processed for all possible samples.
+That is for each sample, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value.
+Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
+\begin{equation}
+    \label{eq:hash}
+    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
+\end{equation}
+where $||$ is the concatenation operator.
+In our preliminary experiments, we have tried a set of hash algorithms.
+After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
+Although the above-mentioned approach generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
+To enable this for each edge, first a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated.
+Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: To do this, the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
 Formally,
@@
 \end{equation}
+% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
+The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
+One of the benefits of this approach is that an edge can be sampled using a single XOR and compare-greater-than operation.
+Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.
 
-% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
-The edge $\{u,v\}$ is exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
-One of the benefits of this approach is that an edge can be sampled using a single XOR and compare-greater-than operation.
-Moreover, the following control flow branch can be removed using conditional move operations.
-An efficient implementation of this approach will be discussed later in this section.
 \begin{figure}[!ht] 
@@
 \end{figure}
+
 Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
 This property allows us to generate good enough pseudo-random values for fair sampling.
-To prove the fairness of random values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed the bias of random values $P(u,v)_r$ used while sampling.
-
-% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
-Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. The sampling probability distribution of hash-based computation is almost identical to the uniform distribution with small bias.
+To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed (1) the cumulative distribution~(Fig.~\ref{fig:prob-cdf}) and (2) the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}).
+As the former figure shows, the sampling probability distribution of the values generated by hash-based computation resembles that of the uniform random distribution.
+Furthermore, the latter figure shows that the bias is small for each network.
 
@@
     \includegraphics[width=1\linewidth]{./images/bias.pdf}
-    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.}
+    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks. \kktodo{bias matematiksel olarak nasil hesaplanir. bunu buraya yazalim}}
     \label{fig:prob-bias} 
@@
 
+% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
+% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
 %Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-Being able to generate infinitely many samples on-the-fly allows us to avoid many memory accesses.
-The only downside of hash-based fused sampling is that we have to generate all random values,   $P(u,v)_r$, for each edge traversal.
-Fortunately, these computations are quite fast on modern computing hardware.
+Being able to generate the samples on-the-fly allows us to avoid many memory accesses.
+The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$.
+To reduce this cost and leverage the performance gains of fused sampling better, the edges' hash values are precomputed for all the edges in $E$.
+Fortunately, the rest of the operations, i.e., one XOR and one division, are quite fast on modern computing hardware.
+%The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
 
-\subsection{Reachability Set Cardinality Estimation}
+\subsection{Estimating Reachability Set Cardinality}
 A greedy solution to the influence maximization problem requires finding a vertex that maximizes the marginal influence gain at each step until the seed set size reaches $K$.
-And, single vertex influence estimation is the same problem as the count-distinct problem applied to all sample subgraphs.
-So, it is possible to use Count-distinct sketches to estimate influence scores in the greedy method.
+For an exact computation, one must find the reachability sets of all candidate vertices within all the samples.
+Such a task involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}.
+As explained above, the influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs.
+Hence, in this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
+In this work, we propose an effective and efficient IM kernel, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
+Algorithm~\ref{algo:main} shows the steps taken by the kernel.
 
-We propose an influence maximization method that utilizes the Count-distinct sketch we mentioned in section \ref{sec:sketch} to estimate the averages of distinct elements in sample subgraphs for both time and space efficiency.
-Algorithm \ref{algo:main} describes the method proposed as follows;
+\begin{algorithm}
+\caption{\sc{\acro}($G,K,J$)}
+\label{algo:main}
+\algorithmicrequire{$G = (V,E)$: the influence graph
+\\\hspace*{6.6ex}{$K$: number of seed vertices
+\\\hspace*{6.7ex}$J$: number of MC simulations}\\}
+\algorithmicensure{$S$: a seed set that maximizes influence on $G$
+}
+\begin{algorithmic}[1]
+    \State {$S \leftarrow \{\emptyset\}$}
+    \For{$ v\in V$} {\bf in parallel}
+        \For{$ j\in J$}
+            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
+        \EndFor
+    \EndFor
+    \State $M \leftarrow ${\sc Simulate}$(G,M,\emptyset)$
+    \State $M_{S'} \leftarrow zeros(J)$
+    \State $\varsigma \leftarrow 0$
+    \For{$k=1\ldots K$}
+        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}
+        \State $S \leftarrow S \cup \{s\}$
+        \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$
+        % \State $R_S \leftarrow run\_cascade(G,S,J)$
+        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }
+        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
+        \State $\delta = \sigma - \varsigma$
+        \State $Err_l=|(e - \delta) / \delta|$
+        \State $Err_g=|e-\delta| / \sigma $
+        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
+            \State $M_{S'} \leftarrow merge(M_{S'},M_s)$
+        \Else
+            \For{$ v\in V$} {\bf in parallel}
+                \For{$ j\in J$}
+                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
+                \EndFor
+            \EndFor
+            \State $M \leftarrow ${\sc Simulate}$(G,M,R_S)$
+            \State $M_{S'} \leftarrow zeros(J) $ 
+            \State $\varsigma \leftarrow \sigma $ 
+        \EndIf
+    \EndFor
+    \State \Return $S$
+\end{algorithmic}
+\end{algorithm}
 
-First, the reachability sets of all vertices are initialized with the vertices themselves.
-For all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{\hat{G}_j}(u) = \{u\}$.
+ Algorithm~\ref{algo:main} first initializes the reachability sets of all vertices by adding the vertices themselves.
+That is for all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{{G}_j}(u) = \{u\}$ where $G_j$ is the $j$th sampled graph.
 Then, we perform the diffusion process on the sketch registers.
-
-Second, the diffusion process is performed between vertex sketches.
-All vertices added to live vertices set $L$.
-Then, the incoming edges $(u,v)$ for all live vertices are processed.
-For all simulations where $u$ is live, the sketches of both sides are merged and set to $u$ registers.
-If any of the sketch registers change, the vertex $u$ is added to the next iteration's live vertices set $L'$.
-After the live edges are processed, if the next iteration's live vertices set is smaller than the convergence threshold $\epsilon_c$, the diffusion process concluded.
-If not, we swap $L$ and $L'$, clear $L'$, and then the diffusion processed is repeated.
-
-In Greedy algorithm\cite{kempe2003maximizing} for each candidate vertex, influence diffusion computations are performed for each vertex.
-On the other hand, diffusion on sketch registers allows finding all vertices reachability set.
-All vertices influence scores in a single-step distance only computed once.
-This dynamic programming like property allows fast selection of influence maximizing candidates.
-Only iterations as much as the diameter of sample graphs are required to converge the sketches.
-
-After diffusion, the following process is repeated until $K$ vertices are added to the seed set; For all vertex, $u$ reachability set cardinalities, $R_G(S\cup u)$, estimated by merging $mask$ and their sketch registers.
-The $mask$ used for the sketch of $R_G(S)$ and initialized with zeros.
-Vertex with maximum cardinality is selected to add to the seed set.
-Then, the actual Monte-Carlo simulations were performed to compute the reachability set of the seed set.
-Having an actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
-Blocked vertices skipped in the diffusion step in coming iterations.
-Besides, the real influence score allows us to know when to rebuild our sketches when the sketches have gone stale.
+To initiate the process, all the vertices are added to the {\em live vertex set} $L$.
+Then the incoming edges of the live vertices are processed.
+If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t.
+$v \in \Gamma_G(v)$ are processed and the sketches of $v$ are merged into those of $u$.
+\kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration.
+After the incoming edges of all live vertices are processed, the current iteration ends.
+If the cardinality of the next iteration's live vertex set, $|L'|$, is smaller than the convergence threshold $\epsilon_c$, the diffusion stops.
+Otherwise, $L$ is set to $L'$, and $L'$ is cleared.
+Then, the next iteration starts.
+Figure~\ref{fig:hf-processing} performs two simulations\kktodo{ bunu tamamlayalim}
 
@@
     \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
-    \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
+    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green) and their registers are initialized with the length of the zero prefix of their hashes. (b) 
     % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register.
+    For the live edge between Vertex 1 and 4, \kktodo{bu edge nedir - outgoing luyor?} the register is set to the maximum of the respective register.
 Since the first register of vertex 1 has a larger value, we only update the second register.
@@
     \end{figure*}
-\subsection{Error-Adaptive Sketch Rebuilding}
 
-Sketches are very fast approximation methods that often provide less than gold standard results.
-In our case, sketches are very competent at finding the first few vertices.
-But, after sketch registers saturate with high values, we observe a significant drop in the quality of results.
-Register saturation causes the naive count-distinct sketch method to not distinguish between vertices.
+The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations for each candidate vertex one-by-one and computes their reachability sets.
+On the other hand, \acro does not compute the actual reachability sets.
+Instead, it efficiently simulates the diffusion on sketch registers that allow estimating the cardinality of the reachability set.
+This step needs to be performed {\em at most} $d$ times where $d$ is the diameter of $G$.
+In fact, when processed individually, the $j$th simulation over the sampled subgraph $G_j$ may require fewer steps since the diameter $G_j$ is at most $d$.
+However, processing all the simulations at once has significant benefits: thanks to the compactness of the sketches, the influence scores in a single-step distance can be merged by using fast vectorized instructions and for many simulations at once.
+Furthermore, $d$ is a loose upper bound on the number of iterations.
+A better upper bound for the number of \acro iterations is {\tt max}$\{d_j: 1 \leq j \leq J\}$ where $d_j$ is the diameter of the $G_j$.
+To reduce the overhead of concurrent simulations further and avoid bottleneck simulations, as mentioned above, we employ a convergence threshold $\epsilon_c$ over the number of live vertices which is expected to be very small when only one or two simulations remain.
+
+After the diffusion process, the following steps are repeated until $K$ vertices are added to the seed set $S$; First, for each $u$, the cardinality of the reachability set, $R_G(S\cup u)$, is estimated by merging $M_S$ and $u$'s sketch registers.
+Here $M_S$ is the set of sketch registers for $S$ used to estimate the cardinality of $R_G(S)$.
+Before the kernel, these registers are initialized with zeros.
+Second, a vertex with the maximum cardinality estimation is selected and added to $S$.
+Third, the actual Monte-Carlo simulations are performed to compute the reachability set of the new seed set.
+Having an actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
+These blocked vertices can be skipped during the next diffusion steps.
+Besides, we leverage the real influence score to have an {\em error-adaptive kernel}, i.e, to compute the real sketch error and rebuild the sketches used when the accumulated error reaches a critical level which can deteriorate the quality for the next seed vertex selections.
+
+\subsubsection{Error-Adaptive Sketch Rebuilding}
+
+Sketches are fast.
+However, each operation, such as an update, a merge, etc., can decrease their estimation quality below a desired threshold.
+For influence maximization, our preliminary experiments revealed that sketches are extremely competent at finding the first few seed vertices.
+Unfortunately, after a few seed vertices, the sketch registers become large, lose their sensitivity, and a significant drop in the quality is observed.
+We observed that register saturation due to large values and  make Count-Distinct sketches incompetent while distinguishing good seed candidates.
 
@@
     \begin{center}
-    \includegraphics[width=0.7\linewidth]{images/sketch-saturation.pdf}
+    \includegraphics[width=0.8\linewidth]{images/sketch-saturation.pdf}
     \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
+\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel}
      }\label{fig:sketch-saturation} 
@@
 
-In figure \ref{fig:sketch-saturation}, we show the effect of register saturation by comparing two methods; one that uses a new sketch, that build on the residual graph after the seed sets' reachability is removed, for all iterations.
-Moreover, another one that builds the sketch once at the beginning, then only utilizes sketch merge operation to find the seed set.
-Even though at first few vertices the expected influence is comparable, we observe near-linear drop-off in the estimated influence.
+Figure~\ref{fig:sketch-saturation} shows the effect of register saturation by comparing two \acro variants; one that uses a new sketch to choose each candidate vertex.
+This sketch is built on the residual graph which remains after the overall reachability of the seed set is removed.
+The second variant built a  sketch once at the beginning and employs it through the IM kernel.
+As the figure shows, even though the seed selection quality for the first few vertices is comparable, a significant reduction on the quality is observed for later vertices.
 
@@
 We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$.
-Then, the local estimation error will be $Err_l=|e-\delta / \delta|$ and global error rate $Err_g=|e-\delta / \sigma|$.
+Then, the local estimation error will be $Err_l=|e-\delta / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz} and global error rate $Err_g=|e-\delta / \sigma|$.
 The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
@@
     \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
-  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters. ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) 
+  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$). 
     \label{fig:conv-perf}} 
@@
 We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, perform well in many datasets, both in terms of speed and quality.
-
-\begin{algorithm}
-\caption{\sc{\acro}($G,K,J$)}
-\label{algo:main}
-\algorithmicrequire{$G = (V,E)$: the influence graph
-\\\hspace*{6.6ex}{$K$: number of seed vertices
-\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations}\\}
-\algorithmicensure{$S$: a seed set that maximizes influence on $G$
-}
-\begin{algorithmic}[1]
-    \State {$S \leftarrow \{\emptyset\}$}
-    \For{$ v\in V$} {\bf in parallel}
-        \For{$ j\in J$}
-            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
-        \EndFor
-    \EndFor
-    \State $M \leftarrow simulate(G,M,\emptyset)$
-    \State $mask \leftarrow zeros(J)$
-    \State $\varsigma \leftarrow 0$
-    \For{$k=1\ldots K$}
-        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}} ~estimate(merge(mask,M_v))$
-        \State $S \leftarrow S \cup \{s\}$
-        \State $e \leftarrow estimate(merge(mask,M_s))$
-        % \State $R_S \leftarrow run\_cascade(G,S,J)$
-        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ }
-        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
-        \State $\delta = \sigma - \varsigma$
-        \State $Err_l=|(e - \delta) / \delta|$
-        \State $Err_g=|e-\delta| / \sigma $
-        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
-            \State $mask \leftarrow merge(mask,M_s)$
-        \Else
-            \For{$ v\in V$} {\bf in parallel}
-                \For{$ j\in J$}
-                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
-                \EndFor
-            \EndFor
-            \State $M \leftarrow simulate(G,M,R_S)$
-            \State $mask \leftarrow zeros(J) $ 
-            \State $\varsigma \leftarrow \sigma $ 
-        \EndIf
-    \EndFor
-    \State \Return $S$
-\end{algorithmic}
-\end{algorithm}
 
@@
 
-\section{Evaluation}\label{sec:evaluation}
+\section{Experimental Results}\label{sec:evaluation}
 We performed the experiments on a server with {\tt Intel Xeon Gold 6140}, running at 2.3 Ghz and 250 GB memory.
@@
 The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.2.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
-Multi-thread parallelization was achieved with {\tt OpenMP} pragmas.
+Multi-thread parallelization was achieved with {\tt OpenMP} pragwwmas.
 {\tt AVX2} instructions are utilized by handcrafted code with vector intrinsics.
@@
 
+\kktodo{an analysis of a fast and better sketch to reduce the number of rebuilding stages}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-04-05 paper.tex
progress

@@
         \kktodo{uzerinden 
-        gecelim}\\
+        gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
-        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
+        $A_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
+        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its incoming edges\\ %%FIXME
         $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
@@
   \caption{\protect\subref{fig:ic} 
-\kktodo{a parti nonuniform weight olsun} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
+\kktodo{a parti nonuniform weight olsun}\ggx{done.} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
 \protect\subref{fig:wc}
-The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?} 
+The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$.
+\kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
   }
@@
 Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
-\kktodo{bu tanim [7]'dekine uymuyor.
-Orada undirected graph var } Note that the model is originally defined for undirected graphs in~\cite{MixGreedy}.
+\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
+% Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}.
 However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.
@@
 
-The reachability set of a vertex is the union of those of all its connected vertices (via outgoing edges).
+The reachability set of a vertex is the union of all its connected vertices (via outgoing edges).
 Many IM kernels exploit this property to some degree.
-The methods based on {\em reverse reachability} \kktodo{cite} and {\em bottom-up traversal} \kktodo{cite} utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced.
-{\em MixGreedy} \kktodo{cite} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
+The methods based on {\em reverse reachability} \cite{borgs2014maximizing} \kktodo{cite}\ggx{done.}
+%and {\em bottom-up traversal} \\kktodo{cite} \ggx{buna referans dusunmem gerekli}
+utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced.
+{\em MixGreedy} \cite{MixGreedy} \kktodo{cite}\ggx{cited.} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
 Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.
@@
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
-If one-hot vectors are used to store the reachability sets for constant insertion time $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity.
-If disjoints sets are used for storing reachability sets; $\mathcal{O}(n\bar{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann function \kktodo{bu Ackermann'a atif verelim}.
+If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity.
+If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann\cite{ackermann1928hilbertschen} function.
+\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}
 
@@
 In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros.
-Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed, by taking the pairwise maximums of their registers.
+Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers.
 Formally;
@@
 
-Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, then removing the residual reachability set of the latent seed set.
+Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, and removing the latent seed set's residual reachability set.
 Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.
@@
 Throughout the process, each register is used only for a single sample/simulation. 
-A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim} $u$ is {\em live} in the current iteration.
-This process iteratively relays the reachability information among the vertices.
-At each iteration, the sketches of the current reachable vertices are modified.
-\kktodo{onceki cumleyi de degistirdim - dogru mu}
-Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, and/or path-by-path, all the influence that passes through the edges in a single step is processed together. 
+% A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration.
+A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
+
+This process iteratively relays the reachability information among the vertices. At each iteration, vertices neighbors' reachability sets are added to their sketches.
+%At each iteration, the sketches of the existing reachable vertices are modified.
+\kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
+Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together. 
 This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
@@
 Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations.
-The vertices in the reachability sets are labeled {\em blocked} \kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekildeydi} in the respective samples.
-Finally, the algorithm checks if a rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
-\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.
+The vertices in the reachability sets are removed from the live set, $L$.%labeled as {\em visited}.
+\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} in the respective samples.
+So that, in later iterations these vertices will not contribute to the marginal gain.
+Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
+\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
+$u \notin R_S$ şeklinde.}
 
@@
 The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process.
-If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be an expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
-In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of in-memory creation and storage of the sample subgraphs.\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek}
+If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
+In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
+\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek} 
+In figure \ref{fig:traversal}, we illustrate the fused sampling process; instead of processing samples independently as in \ref{fig:sims}, Fused-sampling approach process all samples for each edge as shown in \ref{fig:fused}.
+This allows us to process each edge only few times instead of traversing them repeatedly for all simulations.
 
@@
     \includegraphics[width=1\linewidth]{./images/bias.pdf}
-    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks. \kktodo{bias matematiksel olarak nasil hesaplanir. bunu buraya yazalim}}
+    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.
+\kktodo{bias matematiksel olarak nasil hesaplanir.
+bunu buraya yazalim}}\ggx{Python scipy ile hesaplamıştım, kodunu bulamadım.
+Bunun için süreye ihtiyacım var.
+Murmur3 ü tekrar test etmemize gerek olmamalı, bunu çıkartabiliriz diye düşünüyorum.
+}
     \label{fig:prob-bias} 
@@
 %Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-Being able to generate the samples on-the-fly allows us to avoid many memory accesses.
+Being able to generate the samples on the fly allows us to avoid many memory accesses.
 The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$.
-To reduce this cost and leverage the performance gains of fused sampling better, the edges' hash values are precomputed for all the edges in $E$.
-Fortunately, the rest of the operations, i.e., one XOR and one division, are quite fast on modern computing hardware.
+The edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage the performance gains of fused sampling better.
+Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware.
 %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
@@
     \For{$k=1\ldots K$}
-        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}
+        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}\ggx{ latent seed set after rebuild}
         \State $S \leftarrow S \cup \{s\}$
@@
         % \State $R_S \leftarrow run\_cascade(G,S,J)$
-        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }
+        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }\ggx{Yayın konusu dışında kalabilir diye çıkartmıştık.}
         \State $\sigma_G(S) \leftarrow |R_{G}|/J$
@@
             \EndFor
-            \State $M \leftarrow ${\sc Simulate}$(G,M,R_S)$
+            \State $M \leftarrow ${\sc Simulate}$(G,M,R_{S})$
             \State $M_{S'} \leftarrow zeros(J) $ 
@@
  Then the incoming edges of the live vertices are processed. 
-If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t.
+ For all vertices, $u$, its sketch, $M_u$, is updated by merging sketchs $M_v$ of all neighbors vertices $v \in {L}$.
+Merge result $M[j] = max(M_u[j],M_v[j])$ is written back to $M_u[j]$.
+This approach can be seen as a bottom-up diffusion process on underlying data-structure.
+At each iteration, one level of cardinality information is pulled from vertices neighbors to vertices itself.
+
+%  If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t.
 $v \in \Gamma_G(v)$ are processed and the sketches of $v$ are merged into those of $u$.
-\kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration.
+\kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} burasi yanlis
+
+ If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration.
 After the incoming edges of all live vertices are processed, the current iteration ends.
@@
 Then, the next iteration starts.
-Figure~\ref{fig:hf-processing} performs two simulations\kktodo{ bunu tamamlayalim}
+Figure~\ref{fig:hf-processing} shows how \acro performs two simulations at the same time using sketch registers.
 
@@
     \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
-    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green) and their registers are initialized with the length of the zero prefix of their hashes. (b) 
+    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes. (b) 
     % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
@@
     \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
-\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel}
+\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
+Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç) }
      }\label{fig:sketch-saturation} 
@@
 Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
+\acro allows us to work on smaller problem after each rebuilding.
+We remove influenced vertices from their respective samples and reachability sets are computed on this subgraph.
+Therefore, we only need to consider {\em latent} seed vertices, $S'$, that are chosen after the sketch rebuild.
+
 After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
@@
 We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$.
-Then, the local estimation error will be $Err_l=|e-\delta / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz} and global error rate $Err_g=|e-\delta / \sigma|$.
+Then, the local estimation error will be $Err_l=|(e-\delta) / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz}\ggx{c/p parantezi silmis, parantez ekledim.} and global error rate $Err_g=|(e-\delta) / \sigma|$.
 The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
@@
 Then, the sketches are rebuilt using Monte-Carlo simulations.
-After rebuilding, $M_S$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.
-
-The use of two threshold values allows the algorithm to rebuild after large local errors but skip rebuilding if the error is minuscule relative to the total score. 
-If a rebuild is not required, we only update $M_S$ by merging it with the candidate vertex's sketch. 
+After rebuilding, $M_{S'}$, which holds the seed vertices' cardinality estimate added after the last rebuild, is cleared with all zeros.
+
+The use of two threshold values allows the algorithm to rebuild after significant local errors but skip rebuilding if the error is minuscule relative to the total score. 
+If a rebuild is not required, we only update $M_{S'}$ by merging it with the candidate vertex's sketch. 
 This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
@@
 Other methods mentioned in this paper do not report the time spent on calculating the influence scores, 
-whereas our method includes the time since it is crucial for keeping the sketches in high quality.
+whereas our approach includes the time since it is crucial for keeping the sketches in high quality.
 
@@
 Since $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
-Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slow-down the method, but it will give the best possible results.
-Conversely, setting $\epsilon_local$ to infinity will be very fast, since sketches are built only once without checking the vertices blocked.
+Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slow down the method, but it will give the best possible results.
+Conversely, setting $\epsilon_local$ to infinity will be very fast since sketches are built only once without checking the vertices blocked.
 But, the result quality will suffer.
@@
 
-Even though \acro's behavior is not chaotic with respect to changes in parameters.
+Even though \acro's behavior is not chaotic concerning changes in parameters.
 The performance, both in terms of speed and quality of the results, depends on parameter selection.
@@
 
- All memory registers from different simulations are stored together for each vertex, this allows the use of vectorized computation hardware.
+ All memory registers from different simulations are stored together for each vertex; this allows the use of vectorized computation hardware.
 Random number generation, sampling, and merging sketches are all vectorizable operations when coupled together.
@@
 
-We allow a single easy to predict branch after sample edges are generated to exit early without merging the registers.
+We allow a single easy-to-predict branch after sample edges are generated to exit early without merging the registers.
 In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together.
-Since sorted random values are XOR'ed with the same edge hash values, it is more likely to nontaken edges are sampled together.
+Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non taken edges are sampled together.
 Up to 20\% speed-up can be achieved by an early exit at line \ref{ln:early_exit} using sorted random values.

### 2021-04-20 paper.tex
Update on Overleaf.

@@
 \usepackage{enumitem}
+\usepackage{balance}
+
 %%%%%%
@@
 As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have vital importance.
-Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.
+Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information effectively are essential.
 
@@
 \begin{itemize}
-\item We propose \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.
+\item We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.
 The proposed scheme samples the edges as they are traversed across several simulations.
@@
 
-\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
-The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having almost the same quality with the approximation-based algorithms in terms of influence, and using a comparable amount of memory.
+\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having the same quality with the approximation-based algorithms w.r.t.
+influence, and using a comparable amount of memory.
 
@@
 An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$.
-The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma_{G}(v) = \{u: (u,v) \in E\}$.
+The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^-_{G}(v) = \{u: (u,v) \in E\}$.
+Similarly, the {\em outgoing} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^+_{G}(v) = \{u: (v,u) \in E\}$.
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$.
-The diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$, where $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.
+The diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$, where $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship.
 
@@
         \hline
-        \kktodo{uzerinden 
-        gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
+        %\kktodo{uzerinden 
+        %gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
-        $A_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
-        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its incoming edges\\ %%FIXME
+         $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
+        $\Gamma^-_G(u)$  &The set of vertices $v$ where $(v, u) \in E$\\ %%FIXME
         $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
@@
         $\sigma $       & Influence Score\\
-        $\delta$        & Marginal Gain after last sketch build\\
-        $Err_l$         & Local estimation error of the sketch\\
-        $Err_g$         & Global estimation error of the sketch\\
+        $\delta$        & Marginal gain after last sketch build\\
+        $err_l$         & Local estimation error of the sketch\\
+        $err_g$         & Global estimation error of the sketch\\
         $\epsilon_{g}$    & Global estimation error threshold\\
@@
     \\% IMAGES HERE
-  \caption{\protect\subref{fig:ic} 
-\kktodo{a parti nonuniform weight olsun}\ggx{done.} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
+  \caption{\small{\protect\subref{fig:ic} 
+The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
 \protect\subref{fig:wc}
-The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$.
-\kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
-  }
+The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
+  }}
   %\label{fig_ic_model} 
@@
 The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
-of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
+of incoming edges of $v$~(which in the original graph is equal to $\Gamma^-_G(v)$).
 Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
-\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
+%\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
 % Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}.
@@
 Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.
-Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta_v = 0$. 
+Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
 \end{itemize}
@@
 The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
-The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}~(IC), {\em Weighted Cascade}~(WC), and {\em Linear Threshold}~(LT)  models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
-\kktodo{bu son cumle dogru mu}\ggx{Aklima tersini dogrulayacak bir ornek gelmiyor hocam.
-Dogru olmali.} We concentrate on the IC model in this paper, but the proposed methods are also relevant to other models in the literature.
+The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.
 
@@
 The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$.
-Finding the number of vertices to be influenced of a candidate seed vertex, i.e., the cardinality of the {\em reachability set}, is a similar problem.
-For each sample subgraph, the number of visited vertices is calculated while traversing the subgraphs starting from the candidate vertex.
-Note that an exact computation of set cardinality requires memory proportional to the cardinality which is ${\mathcal O}(|{\cal U}|)$.
+Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem.
+For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$.
+Note that an exact computation of set cardinality requires memory proportional to the cardinality, which is ${\mathcal O}(|{\cal U}|)$.
 
@@
 Many IM kernels exploit this property to some degree.
-The methods based on {\em reverse reachability} \cite{borgs2014maximizing} \kktodo{cite}\ggx{done.}
+The methods based on {\em reverse reachability} \cite{borgs2014maximizing} %\kktodo{cite}\ggx{done.}
 %and {\em bottom-up traversal} \\kktodo{cite} \ggx{buna referans dusunmem gerekli}
-utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced.
-{\em MixGreedy} \cite{MixGreedy} \kktodo{cite}\ggx{cited.} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
+utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \cite{MixGreedy} %\kktodo{cite}\ggx{cited.} 
+goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
 Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.
@@
 If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity.
-If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann\cite{ackermann1928hilbertschen} function.
-\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}
-
-Count-Distinct Sketches can be leveraged to efficiently estimate the cardinality of reachability sets; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers.
+If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
+%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
+memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function.
+%\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}
+
+Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers.
 Furthermore, the union of two sketches can be computed in constant time.
-The FM sketch simply stores that how rare the elements are in a stream.
-The rarity of the elements is estimated by counting the maximum number of leading zeros in the hash values of the stream elements.
+The FM sketch stores that how rare the elements are in a stream.
+The rarity of the elements is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
 Initially, each register is initialized with zero.
-The items are hashed one by one and the length of the longest all-zero prefix is stored in the register.
+The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register.
 With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.
@@
 \end{equation} 
-In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples \kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}.
+In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples.
+%\kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}.
 \ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim.
@@
 
-\section{Error-Adaptive Influence Maximization}\label{sec:method}
+\section{Efficient and Error-Adaptive Influence Maximization}\label{sec:method}
 
@@
 Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
-The merge operation utilized in this process is slightly different than the conventional one and retrofitted to mimic the IC diffusion.
+The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.
 
 Throughout the process, each register is used only for a single sample/simulation. 
-% A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration.
-A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
-
-This process iteratively relays the reachability information among the vertices. At each iteration, vertices neighbors' reachability sets are added to their sketches.
+For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
+%if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
+%A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
+That is, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
+This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
 %At each iteration, the sketches of the existing reachable vertices are modified.
 \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
-Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together. 
-This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
-After the computation of reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches.
-Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations.
-The vertices in the reachability sets are removed from the live set, $L$.%labeled as {\em visited}.
-\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} in the respective samples.
-So that, in later iterations these vertices will not contribute to the marginal gain.
+%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.
+
+After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches.
+Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations.
+The vertices in this reachability set are removed from the live set $L$.
+%labeled as {\em visited}.
+%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
+Hence, in later iterations, these vertices will not contribute to the marginal gain.
 Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
-\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
+%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
 $u \notin R_S$ şeklinde.}
@@
 The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process.
-If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
-In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
-\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek} 
-In figure \ref{fig:traversal}, we illustrate the fused sampling process; instead of processing samples independently as in \ref{fig:sims}, Fused-sampling approach process all samples for each edge as shown in \ref{fig:fused}.
-This allows us to process each edge only few times instead of traversing them repeatedly for all simulations.
+If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel.
+We identify two main bottlenecks; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
+In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
+In Fig.~\ref{fig:traversal}, we briefly illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}.
+This allows us to process each edge only a few times instead of once for every simulation.
 
@@
      \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
-  \caption{
+  \caption{\small{
   %\protect\subref{fig:toy} The toy graph 
   \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
-  \protect\subref{fig:fused} The simulations are performed in a way to be fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
-  }
+  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
+  }}
   \label{fig:traversal} 
@@
 
-In \acro, when an edge of the original graph is being processed, i.e., when it is read from the memory, it is processed for all possible samples.
-That is for each sample, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value.
+In \acro, when an edge of the original graph is being processed, it is processed for all possible samples.
+Then, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value for each sample.
 Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
@@
 After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
-Although the above-mentioned approach generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
-To enable this for each edge, first a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated.
+Although the approach as mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
+First, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated to enable this for each edge.
 Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: To do this, the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
@@
 The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
-One of the benefits of this approach is that an edge can be sampled using a single XOR and compare-greater-than operation.
+One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation.
 Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.
@@
     \includegraphics[width=1\linewidth]{./images/CDF.pdf}
-    \caption{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}
+    \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
     \label{fig:prob-cdf} 
@@
 This property allows us to generate good enough pseudo-random values for fair sampling.
-To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and graphed (1) the cumulative distribution~(Fig.~\ref{fig:prob-cdf}) and (2) the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}).
-As the former figure shows, the sampling probability distribution of the values generated by hash-based computation resembles that of the uniform random distribution.
-Furthermore, the latter figure shows that the bias is small for each network.
+To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and plotted the cumulative distribution~(Fig.~\ref{fig:prob-cdf}) and the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}).
+As the former shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution.
+Furthermore, the latter shows that the bias is insignificant for each network.
 
@@
     \includegraphics[width=1\linewidth]{./images/bias.pdf}
-    \caption{Bias distribution of hash-based sampling probabilities on various real-life networks.
-\kktodo{bias matematiksel olarak nasil hesaplanir.
-bunu buraya yazalim}}\ggx{Python scipy ile hesaplamıştım, kodunu bulamadım.
-Bunun için süreye ihtiyacım var.
-Murmur3 ü tekrar test etmemize gerek olmamalı, bunu çıkartabiliriz diye düşünüyorum.
-}
+    \caption{\small{Bias distribution of hash-based sampling probabilities on various real-life networks.}}
     \label{fig:prob-bias} 
@@
 The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$.
-The edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage the performance gains of fused sampling better.
+The edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains.
 Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware.
@@
 A greedy solution to the influence maximization problem requires finding a vertex that maximizes the marginal influence gain at each step until the seed set size reaches $K$.
-For an exact computation, one must find the reachability sets of all candidate vertices within all the samples.
+For an exact computation, one must find all candidate vertices' reachability sets within all the samples.
 Such a task involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}.
-As explained above, the influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs.
+The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs as explained above.
 Hence, in this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
-In this work, we propose an effective and efficient IM kernel, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
+In this work, we propose an efficient and effective IM kernel, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
 Algorithm~\ref{algo:main} shows the steps taken by the kernel.
@@
 \\\hspace*{6.6ex}{$K$: number of seed vertices
-\\\hspace*{6.7ex}$J$: number of MC simulations}\\}
-\algorithmicensure{$S$: a seed set that maximizes influence on $G$
+\\\hspace*{6.7ex}$J$: number of Monte-Carlo simulations}\\}
+\algorithmicensure{$S$: a seed set that maximizes the influence on $G$
 }
@@
         \For{$ j\in J$}
-            \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
+            \State $M_v[j] \leftarrow clz(hash(v) \oplus hash(j))$ 
         \EndFor
     \EndFor
-    \State $M \leftarrow ${\sc Simulate}$(G,M,\emptyset)$
+    \State $M \leftarrow ${\sc Simulate}$(G,M,J,\emptyset)$
     \State $M_{S'} \leftarrow zeros(J)$
     \State $\varsigma \leftarrow 0$
-    \For{$k=1\ldots K$}
-        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\kktodo{S' nedir}\ggx{ latent seed set after rebuild}
+    \For{$k=1\ldots K$} \label{line:for}
+        \State $s \leftarrow \underset{v\in V}{\mathrm{argmax}}\{${\sc Estimate}$(${\sc Merge}$(M_{S'},M_v))$\}\label{line:estimate}
+
+        %\kktodo{S' nedir}\ggx{ latent seed set after rebuild}
         \State $S \leftarrow S \cup \{s\}$     
-        \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$
+        \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$\label{line:e}
         % \State $R_S \leftarrow run\_cascade(G,S,J)$
-        \State {Compute seed set $S$'s Reachability set $R_{G}(S)$ \kktodo{buna da bir algoritma eklesek} }\ggx{Yayın konusu dışında kalabilir diye çıkartmıştık.}
-        \State $\sigma_G(S) \leftarrow |R_{G}|/J$
+        %\State {Compute $R_{G}(S)$; the reachability set of $S$}
+        %\kktodo{buna da bir algoritma eklesek} }\ggx{Yayın konusu dışında kalabilir diye çıkartmıştık.}
+        \State $R_G(S) \leftarrow$ reachability set of $S$ (for all simulations)
+        \State $\sigma \leftarrow$ Monte-Carlo-based (actual) influence of $S$
         \State $\delta = \sigma - \varsigma$
-        \State $Err_l=|(e - \delta) / \delta|$
-        \State $Err_g=|e-\delta| / \sigma $
-        \If{$ Err_l < \epsilon_l \lor Err_g < \epsilon_g$} %FIXME
-            \State $M_{S'} \leftarrow merge(M_{S'},M_s)$
+        \State $err_l=|(e - \delta) / \delta|$
+        \State $err_g=|(e-\delta) / \sigma|$
+        \If{$ err_l < \epsilon_l \lor err_g < \epsilon_g$} %FIXME
+            \State $M_{S'} \leftarrow$ {\sc Merge}$(M_{S'},M_s)$ \label{line:if}
         \Else 
-            \For{$ v\in V$} {\bf in parallel}
+            \For{$ v\in V$} {\bf in parallel}\label{line:else1}
                 \For{$ j\in J$}
-                    \State $M[j]_v \leftarrow clz(hash(v) \oplus hash(j))$ 
+                    \State $M_v[j] \leftarrow clz(hash(v) \oplus hash(j))$ 
                 \EndFor
             \EndFor
-            \State $M \leftarrow ${\sc Simulate}$(G,M,R_{S})$
+            \State $M \leftarrow ${\sc Simulate}$(G,M,J,R_{G}(S))$
             \State $M_{S'} \leftarrow zeros(J) $ 
-            \State $\varsigma \leftarrow \sigma $ 
+            \State $\varsigma \leftarrow \sigma $ \label{line:else2} 
         \EndIf
@@
  That is for all vertices $u$, its $j$th register is set to $M_u[j]=clz(h_j(u))$ meaning $R_{{G}_j}(u) = \{u\}$ where $G_j$ is the $j$th sampled graph. 
- Then, we perform the diffusion process on the sketch registers. 
- To initiate the process, all the vertices are added to the {\em live vertex set} $L$. 
- Then the incoming edges of the live vertices are processed. 
- For all vertices, $u$, its sketch, $M_u$, is updated by merging sketchs $M_v$ of all neighbors vertices $v \in {L}$.
-Merge result $M[j] = max(M_u[j],M_v[j])$ is written back to $M_u[j]$.
-This approach can be seen as a bottom-up diffusion process on underlying data-structure.
-At each iteration, one level of cardinality information is pulled from vertices neighbors to vertices itself.
-
+ Then, we perform the diffusion process on the sketch registers whose pseudocode is given in Algorithm~\ref{algo:diffusion-step}.
+The diffusion starts by adding all the vertices to the {\em live vertex set} $L$.
+ Then at each step, the incoming edges of the live vertices are processed. 
+ For a vertex $u$, its sketch, $M_u$, is updated by merging the sketches $M_v$ of all live outgoing neighbors vertices $v \in {L} \cap \Gamma^+_{G}(u)$.
+For each such vertex $v$ and simulation $j$, the operation $M_u[j] = max(M_u[j], M_v[j])$ is performed.
+This approach can be seen as a bottom-up, i.e., reversed,  diffusion process where at each iteration, the cardinality information is pulled from vertices neighbors.
 %  If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t.
@@
 \kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} burasi yanlis
-
- If any of $u$'s sketch registers change, it is added to the live vertex set $L'$ of the next iteration.
-After the incoming edges of all live vertices are processed, the current iteration ends.
-If the cardinality of the next iteration's live vertex set, $|L'|$, is smaller than the convergence threshold $\epsilon_c$, the diffusion stops.
-Otherwise, $L$ is set to $L'$, and $L'$ is cleared.
-Then, the next iteration starts.
+If any of $u$'s sketch registers changes during this operation it is added to the live vertex set $L'$ of the next iteration.
+Once the incoming edges of all live vertices are processed, the iteration ends.
 Figure~\ref{fig:hf-processing} shows how \acro performs two simulations at the same time using sketch registers.
-
-\begin{figure*}[!ht]
-    \begin{center}
-    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
-    \caption{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes. (b) 
-    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-    For the live edge between Vertex 1 and 4, \kktodo{bu edge nedir - outgoing luyor?} the register is set to the maximum of the respective register.
-Since the first register of vertex 1 has a larger value, we only update the second register.
-Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register.
-Notice that we are moving registers in reverse, from target to source of the edges.
-We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.
-(d) All vertices have registers converged.
-There are no live vertices.
-}\label{fig:hf-processing}
-    \end{center}
-    \end{figure*}
-
-The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations for each candidate vertex one-by-one and computes their reachability sets.
-On the other hand, \acro does not compute the actual reachability sets.
-Instead, it efficiently simulates the diffusion on sketch registers that allow estimating the cardinality of the reachability set.
-This step needs to be performed {\em at most} $d$ times where $d$ is the diameter of $G$.
-In fact, when processed individually, the $j$th simulation over the sampled subgraph $G_j$ may require fewer steps since the diameter $G_j$ is at most $d$.
-However, processing all the simulations at once has significant benefits: thanks to the compactness of the sketches, the influence scores in a single-step distance can be merged by using fast vectorized instructions and for many simulations at once.
-Furthermore, $d$ is a loose upper bound on the number of iterations.
-A better upper bound for the number of \acro iterations is {\tt max}$\{d_j: 1 \leq j \leq J\}$ where $d_j$ is the diameter of the $G_j$.
-To reduce the overhead of concurrent simulations further and avoid bottleneck simulations, as mentioned above, we employ a convergence threshold $\epsilon_c$ over the number of live vertices which is expected to be very small when only one or two simulations remain.
-
-After the diffusion process, the following steps are repeated until $K$ vertices are added to the seed set $S$; First, for each $u$, the cardinality of the reachability set, $R_G(S\cup u)$, is estimated by merging $M_S$ and $u$'s sketch registers.
-Here $M_S$ is the set of sketch registers for $S$ used to estimate the cardinality of $R_G(S)$.
-Before the kernel, these registers are initialized with zeros.
-Second, a vertex with the maximum cardinality estimation is selected and added to $S$.
-Third, the actual Monte-Carlo simulations are performed to compute the reachability set of the new seed set.
-Having an actual $R_G(S)$ allows both to calculate estimation errors and to find blocked vertices for all simulations.
-These blocked vertices can be skipped during the next diffusion steps.
-Besides, we leverage the real influence score to have an {\em error-adaptive kernel}, i.e, to compute the real sketch error and rebuild the sketches used when the accumulated error reaches a critical level which can deteriorate the quality for the next seed vertex selections.
-
-\subsubsection{Error-Adaptive Sketch Rebuilding}
-
-Sketches are fast.
-However, each operation, such as an update, a merge, etc., can decrease their estimation quality below a desired threshold.
-For influence maximization, our preliminary experiments revealed that sketches are extremely competent at finding the first few seed vertices.
-Unfortunately, after a few seed vertices, the sketch registers become large, lose their sensitivity, and a significant drop in the quality is observed.
-We observed that register saturation due to large values and make Count-Distinct sketches incompetent while distinguishing good seed candidates.
-
-\begin{figure}[!ht]
-    \begin{center}
-    \includegraphics[width=0.8\linewidth]{images/sketch-saturation.pdf}
-    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding.
-\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
-Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç) }
-     }\label{fig:sketch-saturation} 
-    \end{center}
-\end{figure}
-
-Figure~\ref{fig:sketch-saturation} shows the effect of register saturation by comparing two \acro variants; one that uses a new sketch to choose each candidate vertex.
-This sketch is built on the residual graph which remains after the overall reachability of the seed set is removed.
-The second variant built a  sketch once at the beginning and employs it through the IM kernel.
-As the figure shows, even though the seed selection quality for the first few vertices is comparable, a significant reduction on the quality is observed for later vertices.
-
-Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
-\acro allows us to work on smaller problem after each rebuilding.
-We remove influenced vertices from their respective samples and reachability sets are computed on this subgraph.
-Therefore, we only need to consider {\em latent} seed vertices, $S'$, that are chosen after the sketch rebuild.
-
-After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
-The estimation error is calculated as the following; we store influence score after each sketch rebuild on $\varsigma$ and sketch cardinality estimate of the candidate vertex on $e$.
-We calculate the marginal gain after the last sketch build, $\delta=\varsigma - \sigma$.
-Then, the local estimation error will be $Err_l=|(e-\delta) / \delta|$ \kktodo{deltayi deltaya niye boluyoruz, ne cikmasini bekliyoruz}\ggx{c/p parantezi silmis, parantez ekledim.} and global error rate $Err_g=|(e-\delta) / \sigma|$.
-The sketches are assumed as stale if the absolute error in the estimated total influence score, $Err_g$, is more than the global threshold, $\epsilon_{g}$, 
-and the marginal gain estimation error, $Err_l$, after the last sketch is larger than a local threshold $\epsilon_{l}$.
-
-Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited and considered blocked in their respective simulations while rebuilding the sketches.
-Then, the sketches are rebuilt using Monte-Carlo simulations.
-After rebuilding, $M_{S'}$, which holds the seed vertices' cardinality estimate added after the last rebuild, is cleared with all zeros.
-
-The use of two threshold values allows the algorithm to rebuild after significant local errors but skip rebuilding if the error is minuscule relative to the total score. 
-If a rebuild is not required, we only update $M_{S'}$ by merging it with the candidate vertex's sketch. 
-This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
-We reuse the reachability sets of the latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
-While rebuilding the sketches, $R_G(S')$ is used to check whether a vertex is blocked in a sample.
-
-Other methods mentioned in this paper do not report the time spent on calculating the influence scores, 
-whereas our approach includes the time since it is crucial for keeping the sketches in high quality.
-
-\begin{figure*}[!h]
-    \begin{center}
-        \subfloat[LiveJournal execution time in seconds\label{fig:lj-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
-    }
-    \subfloat[Orkut execution time in seconds\label{fig:orkut-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
-        }
-    \subfloat[Pokec execution time in seconds\label{fig:pokec-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
-        }\\
-        \subfloat[LiveJournal Influence Score\label{fig:lj-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
-        }
-    \subfloat[Orkut Influence Score\label{fig:lj-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
-        }
-    \subfloat[Pokec Influence Score\label{fig:pokec-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
-        }\\
-    \end{center}
-    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads.}\label{fig:parameter-smallmultiples} 
-\end{figure*}    
-\begin{figure}[h] 
-    \centering
-    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
-  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$). 
-    \label{fig:conv-perf}} 
-\end{figure}
-
-Since $\epsilon_{l}$ is the maximum error allowed after the last rebuild.
-Setting $\epsilon_{l}$ to $0$ means that \acro will always rebuild sketches, which would slow down the method, but it will give the best possible results.
-Conversely, setting $\epsilon_local$ to infinity will be very fast since sketches are built only once without checking the vertices blocked.
-But, the result quality will suffer.
-$\epsilon_{g}$, on the other hand, is the minimum influence we expected to obtain via rebuilding the sketch.
-If we were to set $\epsilon_{l}$ to 0, \acro will not rebuild the sketches, but when $\epsilon_{l}$ is set to infinity, we skill need to compare $\epsilon_{l}$ to the estimation error before rebuilding.
-
-Even though \acro's behavior is not chaotic concerning changes in parameters.
-The performance, both in terms of speed and quality of the results, depends on parameter selection.
-We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters.
-Both the speed and the quality of the results on some of the largest datasets we have experimented shown in figure~\ref{fig:parameter-smallmultiples}.
-We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, perform well in many datasets, both in terms of speed and quality.
 
@@
 \algorithmicrequire{$G = (V,E)$: the influence graph
-\\\hspace*{6.6ex}{$M$: Sketch vectors of vertices
-\\\hspace*{6.7ex}$\mathcal{J}$: number of MC simulations
-\\\hspace*{6.7ex}$R_S$: Reachability set of the seed set
+\\\hspace*{6.6ex}{$M$: sketch vectors of vertices
+\\\hspace*{6.7ex}${J}$: number of MC simulations
+\\\hspace*{6.7ex}$R_S$: reachability set of the seed set
 }
 \\}
-\algorithmicensure{$M$: Updated Sketch vectors
+\algorithmicensure{$M$: updated Sketch vectors
 }
@@
         \For{$e_{u,v} \in A(u) $}
-            \For{$j \in (0,J]$}
+            \For{$j \in (0,J]$} \label{ln:vec1}
                 \If{$P(u,v)_j < w_{u,v} \land u  \not\in R_S[j]$} \label{ln:early_exit}
@@
 
-\subsection{Regularization and Performance considerations}
-Traditional two-step sample-then-diffuse computation model stores data loosely-coupled.
-Sampled edges are stored together, diffusion related information stored afar.
+\begin{figure*}[!ht]
+    \begin{center}
+    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
+    \caption{\small{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes.
+(b)
+    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
+    For the ($1, 4$) edge which is live for both simulations, 1's registers are set to the maximum of both 1's and 4's registers.
+The ($4, 3$) edge is live only in the second simulation.
+Hence, the second register of $4$ is updated to $5$.
+For the second iteration, vertices 1 and 4 are live~(green) since their registers have changed.
+(c) For the live ($1, 4$) edge, 1's second is updated and 1 is set as live again.
+(d) All the registers converged.
+As no live vertices exist, the process stops.}}\label{fig:hf-processing}
+    \end{center}
+    \end{figure*}
+
+The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations one-by-one and computes the vertices' reachability sets.
+On the other hand, \acro efficiently performs multiple simulations at once in a single-step iteration.
+Since each iteration relays one level of cardinality information, this step requires at most $d$ iterations where $d$ is the diameter of $G$.
+When processed individually as the Greedy algorithm does, the $j$th simulation over the sampled subgraph $G_j$ would require only at most $d_j$ iterations, which is the diameter of $G_j$, and probably much smaller than $d$.
+Although \acro seems to perform much more iterations, $d$ is a loose upper bound for \acro.
+A better one is {\tt max}$\{d_j: 1 \leq j \leq J\}$ where $d_j$ is the diameter of $G_j$.
+To further reduce the overhead of concurrent simulations and avoid bottleneck simulations due to remaining perimeter vertices, we employ a early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two simulations remain.
+That is if $|L'| \leq |V| \times \epsilon_c$ the diffusion process in Algorithm~\ref{algo:diffusion-step} stops.
+Otherwise, $L$ is set to $L'$, $L'$ is cleared, and the next iteration starts.
+We used $\epsilon_c = 0.02$ to make \acro faster while keeping its quality almost the same.
+
+After the diffusion process, the following steps are repeated until $K$ vertices are added to the seed set $S$.
+First, for each $v \in V$, the cardinality of the reachability set, $R_G(S \cup v)$, is estimated by merging $M_{S'}$ and $v$'s sketch registers where $M_{S'}$ is the set of sketch registers for the seed set $S$ used to estimate the number of already influenced vertices by $S$.\footnote{In fact, the definition is exact only if sketch rebuilding is disabled.
+As it will be described in the following subsection, when \acro's error-adaptive mechanism is enabled, $M_{S'}$ is periodically rebuilt to estimate the cardinality of reachability sets over the remaining, unblocked vertices.
+This is why $S'$ is used instead of $S$.} Before the kernel, these registers are initialized with zeros.
+Second, a vertex $s$ with the maximum cardinality estimation is selected and added to $S$.
+Third, the actual Monte-Carlo simulations are performed to compute the reachability set of the new seed set.
+Having an actual $R_G(S)$ allows us to calculate the estimation errors and find the blocked vertices for all simulations, which is vital since these blocked vertices can be skipped during the next diffusion steps.
+Besides, we leverage the actual influence score to have an {\em error-adaptive kernel}, i.e., to compute the actual sketch error and rebuild the sketches when the accumulated error reaches a critical level which can deteriorate the quality for the following seed vertex selections.
+
+\subsubsection{Error-adaptive sketch rebuilding}
+
+Sketches are fast.
+However, each sketch operation, including update and merge, can decrease their estimation quality below a desired threshold.
+Our preliminary experiments revealed that sketches are highly competent at finding the first few seed vertices for influence maximization.
+Unfortunately, after a few seed vertices, the sketch registers $M_{S'}$, which are updated at line~\ref{line:if} of Algorithm~\ref{algo:main} via merging with new seed vertex $s$'s reachability set, become large.
+The saturation of $M_{S'}$ registers is important since \acro uses them to select the best seed candidate at line~\ref{line:estimate}.
+When they lose their sensitivity for seed selection, a significant drop in the quality is observed.
+
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
+    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
+%\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
+Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç)
+     }\label{fig:sketch-saturation} 
+    \end{center}
+\end{figure}
+
+\begin{figure*}[!ht]
+    \begin{center}
+        \subfloat[LiveJournal execution time in seconds\label{fig:lj-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
+    }
+    \subfloat[Orkut execution time in seconds\label{fig:orkut-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
+        }
+    \subfloat[Pokec execution time in seconds\label{fig:pokec-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
+        }\\
+        \subfloat[LiveJournal Influence Score\label{fig:lj-score}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
+        }
+    \subfloat[Orkut Influence Score\label{fig:orkut-score}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
+        }
+    \subfloat[Pokec Influence Score\label{fig:pokec-score}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
+        }\\
+    \end{center}
+    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
+\end{figure*}    
+%\begin{figure}[ht] 
+%    \centering
+%    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
+%  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) \kktodo{bu alttaki figurlerde sagdaki degerler sanki ters - kirmizi siyah bu sekilde mi siralanmali}.
+%    \label{fig:conv-perf}} 
+%\end{figure}
+
+Figure~\ref{fig:sketch-saturation} shows the effect of register saturation by comparing two \acro variants; the first one rebuilds a new sketch to choose each seed vertex $s$, i.e., the {\bf else} part in lines~\ref{line:else1}--\ref{line:else2} of Algorithm~\ref{algo:main} is executed for every iteration of the {\bf for} loop at line~\ref{line:for}.
+This sketch is built on the residual graph $G \setminus R_G(S)$, which remains after the current seed set's reachability is removed.
+The second variant builds a  sketch only once at the beginning and employs it through the IM kernel, i.e., the {\bf else} part is never executed.
+The figure shows that the latter's seed selection quality is comparable to that of the former for the first few seed vertices.
+However, a significant reduction in the quality is observed for the later vertices.
+Furthermore, the former approach's quality is on par with the expensive Greedy algorithm's quality, which computes actual reachability sets.
+This shows that sketch-based estimation can perform as well as the accurate but expensive approach.
+Note that rebuilding also allows \acro to work on a smaller problem for the following seed vertex selection since we remove the already influenced vertices from sample subgraphs and work on the remaining subgraphs.
+%Hence, for the remaining estimations, we only need to consider {\em latent} seed vertices of $S$ which are chosen after the sketch rebuild.
+
+Although its quality is on par with the traditional algorithm, the variant which rebuilds a sketch for all the seed vertex selections can be expensive.
+Here, we leverage an error-adaptive approach by rebuilding them when a significant cardinality estimation error is observed.
+%As After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
+The estimation error is calculated as follows; we store the influence score after each sketch rebuild in $\varsigma$~(line~\ref{line:else2} of Algorithm~\ref{algo:main}).
+Let $\sigma$ be the real influence for the seed set $S$ including the selected vertex.
+We first compute the marginal influence gain $\delta = \sigma - \varsigma$, which is the additional influence obtained since the last sketch rebuilt.
+Note that $e$, computed at line~\ref{line:e} is the sketch estimate for this value.
+\acro computes the local estimation error $err_l = |(e-\delta) / \delta|$ and the global error threshold $err_g=|(e-\delta) / \sigma|$.
+The sketches are assumed to be fresh if
+the local estimation error $err_l$ is smaller than a local threshold $\epsilon_{l}$ or the global error threshold $err_g=|(e-\delta) / \sigma|$ is smaller than a global threshold $\epsilon_{g}$.
+
+%Before rebuilding stale sketches, the reachability set of the latent seed set, $R_G(S')$, is marked as visited and considered blocked in their respective simulations while rebuilding the sketches.
+Then, the sketches are rebuilt using Monte-Carlo simulations.
+After rebuilding, $M_{S'}$, which holds the seed vertices' cardinality estimate added after the last rebuild, is cleared with all zeros.
+
+%This approach allows us to keep the sketches in high quality even after many vertices are added to the seed set. But on the other hand, it forces us to perform expensive Monte-Carlo simulations. 
+%We reuse the reachability sets of the latent seed set, $R_G(S')$, computed by Monte-Carlo simulations.
+While rebuilding the sketches, $R_G(S')$ is used to check whether a vertex is blocked in a sample.
+
+%Other methods mentioned in this paper do not report the time spent on calculating the influence scores, whereas our approach includes the time since it is crucial for keeping the sketches in high quality.
+
+The use of two different, local and global, thresholds allows the algorithm to rebuild the sketches after significant local errors and skip this expensive process if the estimation error is insignificant compared to the total influence.
+As explained above, when the rebuilding is skipped, \acro only updates $M_{S'}$ by merging it with the candidate vertex's sketch.
+Hence, the selected threshold values, $\epsilon_{l}$ and $\epsilon_{g}$, have a significant impact on the performance.
+Setting $\epsilon_{l} = \epsilon_{g} = 0$ means that the algorithm always rebuilds.
+Conversely, setting $\epsilon_l = \epsilon_{g} = \infty$ will make \acro fast since sketches are built only once.
+However, the influence scores will suffer, which is already shown by Fig.~\ref{fig:sketch-saturation}.
+To evaluate the interplay and find the thresholds that yield a nice tradeoff, we conducted a grid search in which \acro's execution time and influence quality are measured for different parameters.
+The results of this preliminary experiment are shown in Figure~\ref{fig:parameter-smallmultiples}.
+We found that the parameters $\epsilon_{l}=0.3$ and $\epsilon_{g}=0.01$ perform well on many datasets, both in terms of speed and quality.
+%For these experiments, $\epsilon_c = 0.02$ is used.
+
+\subsection{Implementation Details}
+%\subsection{Regularization and Vectorization}
+%Sampled edges are stored together, diffusion related information stored afar.
 This way, SIMD operation is allowed on consecutively located edges, requiring random memory accesses for the diffusion process.
@@
 
-One of the main advantages of fused sampling is allowing similar simulation data and computations together.
+%One of the main advantages of fused sampling is allowing similar simulation data and computations together.
 For processing samples for an edge in algorithm \ref{algo:diffusion-step}~(lines~\ref{ln:inner_start}--\ref{ln:inner_end}).
 
- All memory registers from different simulations are stored together for each vertex; this allows the use of vectorized computation hardware.
-Random number generation, sampling, and merging sketches are all vectorizable operations when coupled together.
-Vectorization also reduces branching on the overall computation; When vectorized, many comparison operations are done without branching.
-
-We allow a single easy-to-predict branch after sample edges are generated to exit early without merging the registers.
+To efficiently process real-life graphs, \acro uses the Compressed Sparse Row~(CSR) graph data structure.
+In CSR, an array, $xadj$, holds the starting indices of the adjacency lists for each vertex, while another array, $adj$, holds the actual adjacency lists (i.e., the outgoing neighbors) one after another.
+Hence, the adjacency list of vertex $i$ is located in $adj$ at locations $adj[index[i], \ldots, index[i+1] - 1]$.
+
+The traditional two-step (sample-then-diffuse) computation model stores the (graph) data in a loosely coupled fashion.
+% That is the data is clustered w.r.t. their simulation IDs. 
+While designing \acro, we fine-tuned it to be vectorization friendly, including its data layout and computation patterns.
+These design choices allow us to perform multiple operations, i.e., the same operations but on different data, at once.
+For instance, we keep all the memory registers of a single vertex from different simulations adjacent, and this allows the efficient use of vectorized computation hardware while performing lines~\ref{ln:vec1}--\ref{ln:update} of Algorithm~\ref{algo:diffusion-step}.
+Also, random number generation, fused sampling, and sketch merging are vectorizable operations when the data are stored in a coupled way as in \acro.
+%Vectorization also reduces branching on the overall computation; When vectorized, many comparison operations are done without branching.
+
+%We allow a single easy-to-predict branch after sample edges are generated to exit early without merging the registers.
 In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together.
@@
 
-\subsection{Implementation Details}
-While implementing the \acro, we have used the Compressed Sparse Row~(CSR) graph data structure.
-In CSR, an array, $index$, holds the starting indices of each neighboring vertex, while another vector, $adj$, holds the consecutive neighbors of each vertex. 
-To enter the neighbors of vertex $i$ we first visit $index[i]$ and $index[i+1]$ 
-to find the data's start and end positions, then search from $adj[index[i]]$ to $adj[index[i+1]]$.
-
 \section{Experimental Results}\label{sec:evaluation}
-We performed the experiments on a server with {\tt Intel Xeon Gold 6140}, running at 2.3 Ghz and 250 GB memory.
-All of the 18 cores are allowed in the experiments.
-The Operating System on the server was {\tt Ubuntu 16.04 LTS} with 5.4.0-48 kernel.
+We performed the experiments on a server with an 18-core {\tt Intel Xeon Gold 6140}, running at 2.3Ghz, and 250GB memory.
+The Operating System on the server is {\tt Ubuntu 16.04 LTS} with 5.4.0-48 kernel.
 The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.2.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
-Multi-thread parallelization was achieved with {\tt OpenMP} pragwwmas.
+Multi-thread parallelization was achieved with {\tt OpenMP} pragmas.
 {\tt AVX2} instructions are utilized by handcrafted code with vector intrinsics.
@@
 
-We performed experiments on twelve graphs~(six undirected, six directed) are used in the experiments. For relevancy, datasets that are frequently used for Influence Maximization are selected.
-
-The datasets are {\tt Amazon} co-purchase network~\cite{snapnets}, {\tt DBLP} co-laboration network~\cite{snapnets}, {\tt Epinions} consumer review trust network, {\tt LiveJournal}~\cite{snapnets}, {\tt NetHEP} citation network~\cite{MixGreedy}, {\tt NetPhy} citation network~\cite{MixGreedy}, {\tt Orkut}~\cite{snapnets}, {\tt Pokec} Slovakian poker game site friend network~\cite{snapnets}, {\tt Slashdot} friend-foe networks~(08-11, 09-11)~\cite{snapnets}, {\tt Twitter} list co-occurence network~\cite{snapnets}, and {\tt Youtube} friendship network~\cite{snapnets}.
-The properties of these datasets are given in Table~\ref{tab:NetProps}.
-
-The properties of these datasets are given in Table~\ref{tab:NetProps}.
+We performed the experiments on twelve graphs~(six undirected, six directed).
+For comparability, graphs that have been frequently used within the Influence Maximization literature are selected.
+These graphs are {\tt Amazon} co-purchase network~\cite{snapnets}, {\tt DBLP} co-laboration network~\cite{snapnets}, {\tt Epinions} consumer review trust network, {\tt LiveJournal}~\cite{snapnets}, {\tt NetHEP} citation network~\cite{MixGreedy}, {\tt NetPhy} citation network~\cite{MixGreedy}, {\tt Orkut}~\cite{snapnets}, {\tt Pokec} Slovakian poker game site friend network~\cite{snapnets}, {\tt Slashdot} friend-foe networks~(08-11, 09-11)~\cite{snapnets}, {\tt Twitter} list co-occurence network~\cite{snapnets}, and {\tt Youtube} friendship network~\cite{snapnets}.
+The properties of these graphs are given in Table~\ref{tab:NetProps}.
 
@@
 
-We selected $w=0.005$ as one of our benchmark settings to challenge ourselves; due to the nature of the diffusion algorithm, \acro traverses vertices even if they are blocked.
-Also, for each live vertex, \acro generates sample edges for all simulations regardless.
-The other two experiment settings are used to emulate the experiments of Kempe et al.~\cite{kempe2003maximizing}
+We selected $w=0.005$ as a benchmark-setting to challenge \acro.
+Due to its diffusion algorithm's nature, \acro traverses vertices even if they are blocked, which happens faster when the graph is sparser.
+Also, for each live vertex, \acro processes the sample edges for all simulations.
+The other two settings are selected to emulate the experiments of~\cite{kempe2003maximizing} and~\cite{MixGreedy}.
 
@@
 
-In this paper, the algorithms are evaluated on execution time, influence score, and maximum resident memory . In computing, these three are
-often traded off to each other; in the extreme, it is trivial to select random vertices as the seed set or compute reachability sets of every possible seed set combination.
-
-The observed execution times and memory consumption of different algorithms are comparable when the algorithms run on the same computer.
-In this paper, the execution times are always the wall time reported by the programs.
-All methods we benchmarked leave out the time spent on reading files and preprocessing. To be fair in evaluating our method, we only left out the time to spend on reading files.
-
-In all benchmarks, we allowed all methods to fully utilize all available CPU cores, except {\sc Tim+} which is a single-threaded software.
-Memory use we reported is Resident Set Size(RSS) and measured using GNU Time software.
-
-Although, because the algorithms can use various methods to measure the impact score, the reported influence scores may be deceptive. 
-Due to this reason, we implemented an oracle with a very simple, sample-than-diffuse algorithm without any optimization mentioned.
-The random oracle values are generated by the 32-bit Mersenne Twister pseudo-random generator with a state size of 19937 bits {\tt mt19937} from {\tt C++ standard library}.
-All influence scores in this paper are reported by the independent oracle.
+The algorithms are evaluated based on (1) execution time, (2) influence score, and (2) maximum memory used.
+For Influence Maximization, there is a trade-off among these performance metrics; in one extreme, it is trivial to select random vertices as the seed set.
+In another, one can compute the reachability sets of every possible seed set of size $K$ and choose the best one.
+%The observed execution times and memory consumption of different algorithms are comparable when the algorithms run on the same computer.
+In all our experiments, the execution times are the wall times reported by the programs.
+All the methods we benchmarked exclude the time spent on reading files and preprocessing.
+We only left out the time to spend on reading files for \acro.
+We allowed all methods to utilize all the CPU cores in all benchmarks, except {\sc Tim}, a single-threaded algorithm.
+The memory use reported in this paper is the {\em maximum resident set sizes}~(RSS), which are measured using GNU {\tt time} command.
+
+Since the algorithms may use different methods to measure the influence score, the reported influence scores may not be suitable for comparison purposes with high precision.
+Due to this reason, we implemented an oracle with a straightforward, sample-then-diffuse algorithm without any optimization mentioned.
+For sampling, the random values are generated by the 32-bit Mersenne Twister pseudo-random generator {\tt mt19937} from {\tt C++} standard library.
+The same independent oracle obtains all influence scores in this paper.
 
@@
 
-We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, and {\sc Imm}.
-
-First, Two-phased Influence Maximization({\sc Tim+})~\cite{tim},TIM consists of two phases, Parameter Estimation and Node Selection. The first phase computes a lower-bound
-of the maximum expected to spread among all size-k node sets,
-and then uses the lower bound to derive a parameter $\theta$. In the second phase, samples $\theta$ random RR sets from
-G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
-
-Second, Sketch-based Influence Maximization({\sc Skim})~\cite{cohen2014sketch} constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multithread parallelization in some degree.
-
-Third, Minutoli et al.'s {\sc Imm}~\cite{minutoli2019fast}. 
-{\sc Imm} is a fast algorithm that efficiently produces accurate seed sets. 
-The {\sc Imm}  algorithm\cite{tang2015influence} is an approximation method that improves the Reverse Influence Sampling(RIS)\cite{borgs2014maximizing} algorithm By eliminating the need for the threshold to be used.
-
-The influence of all vertices is generalized on a small set of sample graphs that is sampled from the reachability sets of a few vertices.
-Experimentations are done with $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined hyper-parameter controlling the approximation boundaries.
-
-Finally, our method \acro employs both Monte-Carlo simulations and count-distinct sketches for estimating reachability set cardinalities.
+We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim}, {\sc Skim}, and {\sc Imm}.
+The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account.
+Last, the third one is an approximation algorithm with a parameter to control the approximation quality.
+\begin{itemize}
+\item The two-phased Influence Maximization~({\sc Tim}) consists of two phases: {\em Parameter Estimation} and {\em Node Selection}~\cite{tim}.
+The first phase computes a lower bound on the maximum expected influence to spread among all size-$K$ node sets and then uses it to derive a parameter $\theta$.
+The second phase randomly samples $\theta$ reverse reachability sets from $G$ and then derives a size-$K$ vertex-set $S$ that covers a large number of these sets.
+
+\item The sketch-based Influence Maximization~({\sc Skim}) is a parallel algorithm which uses a combined bottom-$k$ min-hash reachability sketch~\cite{bottomk} with $k = 64$ to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
+{\sc Skim} employs $\ell = 64$ sampled subgraphs and designed and tuned to provide good seed sets in a short time.
+
+\item Minutoli et al.'s {\sc Imm} is a high-performance, parallel algorithm that efficiently produces accurate seed sets~\cite{minutoli2019fast}. 
+It is an approximation method that improves the Reverse Influence Sampling~(RIS)~\cite{borgs2014maximizing} algorithm by eliminating the need for the threshold to be used.
+%{\sc Imm} generalizes the influence of all vertices on a small set of sample graphs that is sampled from the reachability sets of a few vertices.
+We have used $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined parameter to control the approximation boundaries.
+\end{itemize}
+%Finally, our method \acro employs both Monte-Carlo simulations and count-distinct sketches for estimating reachability set cardinalities.
 Even though \acro is blazing-fast and accurate for limited $K$, we exploit the performance of the method to improve the results by rebuilding sketches after removing residual influence networks.
@@
     \centering
-    \scalebox{0.96}{
-
+    \scalebox{0.94}{
 \begin{tabular}{l|rrrr|rrrr|rrrr}
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
+Method & {\sc Hyper} &    {\sc Tim} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim} &  {\sc Imm} & {\sc Skim} \\
 
@@
 \bottomrule
-Geo. Mean wrt.&1.000x&28.191x&1.687x&3.465x&1.000x&1.032x&1.002x&0.899x&1.000x&22.750x&1.650x&3.581x \\ \acro
-\end{tabular}
-
+Norm. arit. mean &&69.39x&4.37x&8.13x&&1.032x&1.002x&0.909x& &42.60x&2.05x&9.76x \\ 
+Norm. geo. mean &\multicolumn{1}{c}{all}&28.19x&1.69x&3.47x&\multicolumn{1}{c}{all}&1.032x&1.002x&0.899x&\multicolumn{1}{c}{all}&22.75x&1.65x&3.58x \\ 
+Norm. max perf&\multicolumn{1}{c}{1.00x}&314.92x&25.82x&49.02x&\multicolumn{1}{c}{1.000x}&1.068x&1.027x&1.036x&\multicolumn{1}{c}{1.00x}&127.18x&5.29x&39.88x \\ 
+Norm. min perf&&5.88x&0.34x&0.85x&&1.006x&0.983x&0.562x&&5.43x&0.66x&0.34x \\
+
+\end{tabular}\\
     }
@@
     \centering
-    \scalebox{0.93}{
+    \scalebox{0.92}{
 
@@
 % {} & \multicolumn{4}{l}{Time} & \multicolumn{4}{l}{Score} & \multicolumn{4}{l}{Memory} \\
-% Method & HyperFuser &    TIM+ &     IMM &   SKIM & HyperFuser &    TIM+ &     IMM &    SKIM & HyperFuser &  TIM+ &   IMM & SKIM \\
+% Method & HyperFuser &    TIM &     IMM &   SKIM & HyperFuser &    TIM &     IMM &    SKIM & HyperFuser &  TIM &   IMM & SKIM \\
 \begin{tabular}{l|rrrr|rrrr|rrrr}
@@
 \bottomrule
-Geo. Mean wrt.&1.000x&100.140x&5.448x&3.582x&1.000x&1.016x&0.996x&0.879x&1.000x&36.264x&1.909x&2.820x \\ \acro
+Norm. arit. mean &&167.17x&9.73x&9.99x&&1.016x&0.996x&0.904& &42.91x&2.09x&8.26x \\ 
+Norm. geo. mean &\multicolumn{1}{c}{all}&100.14x&5.45x&3.58x&\multicolumn{1}{c}{all}&1.016x&0.996x&0.879x&\multicolumn{1}{c}{all}&36.26x&1.91x&2.82x \\ 
+Norm. max perf&\multicolumn{1}{c}{1.00x}&433.73x&44.14x&61.79x&\multicolumn{1}{c}{1.000x}&1.043x&1.024x&1.006x&\multicolumn{1}{c}{1.00x}&106.53x&3.88x&37.65x \\ 
+Norm. min perf&&7.08x&0.89x&0.62x&&1.003x&0.983x&0.390x&&9.73x&0.66x&0.37x \\
+
+% Geo. Mean wrt.&1.000x&100.140x&5.448x&3.582x&1.000x&1.016x&0.996x&0.879x&1.000x&36.264x&1.909x&2.820x \\ \acro
 \end{tabular}
@@
     \centering
-    \scalebox{0.90}{
+    \scalebox{0.92}{
 
@@
 \bottomrule
-Geo. Mean wrt.&1.000x&1449.408x&27.870x&11.062x&1.000x&1.002x&0.996x&0.972x&1.000x&163.771x&7.145x&2.634x \\ \acro
+Norm. arit. mean &&2624.61x&47.17x&15.37x&&1.002x&0.996x&0.974x& &199.54x&8.79x&5.32x \\ 
+Norm. geo. mean &\multicolumn{1}{c}{all}&1449.41x&27.87x&11.06x&\multicolumn{1}{c}{all}&1.002x&0.996x&0.972x&\multicolumn{1}{c}{all}&163.77x&7.15x&2.63x \\ 
+Norm. max perf&\multicolumn{1}{c}{1.00x}&6391.57x&118.72x&36.23x&\multicolumn{1}{c}{1.000x}&1.007x&1.000x&1.001x&\multicolumn{1}{c}{1.00x}&384.00x&16.85x&19.67x \\ 
+Norm. min perf&&141.80x&2.87x&2.13x&&1.000x&0.975x&0.815x&&32.29x&1.35x&0.35x \\ 
 \end{tabular}
@@
 
- \begin{figure}[!h] 
+ \begin{figure}[!ht] 
      \centering
@@
 
-\subsection{Scalability with multi-threaded parallelism}
-
-\begin{figure*}[!ht] 
-    \centering
-    \includegraphics[width=\linewidth]{images/threads.pdf}
-   \centering \caption{\acro scaling with multiple threads on some of largest datasets in the benchmarks.
-     \label{fig:scaling}} 
-\end{figure*}
-
-In our implementation, the parallel processing of live vertices  (as source) is necessary to reduce the number of visited edges.
-However, since a (target) vertex can be being processed at the same time, the update operation at the line~\ref {ln:update} of this {\em pull-based} approach can be seen as a potential source of race conditions.
-However, since iterations are performed until convergence, the results are sound within our assumptions.
-On the other hand, the performance may suffer due to false sharing.
-Figure~\ref{fig:scaling} shows the speedup values obtained via {\tt OpenMP} parallelization.
-
-Even though {\em pull-based} diffusion approach we employed in this work gives us superior performance in most of the benchmarks, it is possible to implement \acro using other approaches; E.g.
-{\em queue-based} approach is similarly feasible and may improve performance by only processing live vertices.
-The pull-based diffusion method is chosen due to its simplicity and scalability to a large number of threads/compute units.
-
 \subsection{Comparing \acro with State-of-art}
-All algorithms mentioned in this paper estimate the influence maximizing seed sets that are good enough but not optimal.
-For that reason, we compare both the performance and quality of the results.
-In addition to this trade-off, the parameters of the experimented methods are hard to compare directly.
-It is infeasible to find exactly the corresponding parameter between any two methods in this setting.
-For that reason, we have used the parameters suggested by the  authors themselves.
-We performed experiments using following parameters; {\sc Tim+} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$).
-
-One of the drawbacks of \acro is that we do not have direct control over the approximation factor, whereas the other methods have some form of an approximation control parameter.
-\acro can only control approximation quality indirectly by tuning the number of Monte-Carlo simulations $J$.
-
-For \acro, we used $J=256$ registers which is comparable in terms of quality to other methods.
-Also, we used the global estimation error threshold $\epsilon_{g}=0.01$, local estimation error threshold $\epsilon_l=0.3$, and set non-converged vertices ratio as $\epsilon_{c}=0.02$.
-
-For small $w=0.005$ and small graphs such as NetHep, NetPhy, or Amazon; we can see {\sc Tim+}  has ($4\sim 6\%$) better results, whereas {\sc Skim}  has much ($- 13\sim 44\%$) worse results than \acro in terms of quality.
-While \acro is having a hard time to catch edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim+} won't suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
+To compare the run time, memory use, and quality of \acro with those of the state-of-the-art, %As explained above, the parameters of the experimented methods are hard to compare directly.
+It is infeasible to find precisely the corresponding parameter between any two methods in this setting.
+For that reason, we have used the parameters suggested by the paper.
+we perform experiments using the parameters suggested by the authors of these tools: {\sc Tim} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$). 
+In short, these parameters are controlling the quality of the seed sets.
+In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim} and {\sc Imm} have one.
+Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations $J$ which also increases the number of sketches used per vertex.
+In the experiments, we set $J = 256$, which is comparable in quality to other methods.
+As explained in the previous section, we use global error threshold as $\epsilon_{g} = 0.01$, local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.
+
+Compared to \acro, for $w = 0.005$~(Table~\ref{tab:timings005}), i.e., sparser samples, \acro is
+
+For small graphs such as {\tt NetHep}, {\tt NetPhy}, and {\tt Amazon}, the results show that {\sc Tim} has $4\%$--$7\%$ more influence score, whereas the sketch-based algorithm {\sc Skim} has $13\%$--$44\%$ less influence.
+While \acro is having a hard time catching edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim} will not suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
 On the performance side, \acro is superior to other methods, Amazon dataset only takes 1.3 seconds, including Monte-Carlo influence oracle computations.
@@
 For small improvements in quality, we can always double the number of registers/simulations $J=256$ to $512$, which would approximately double the wall time.
-For the same $w=0.005$ and larger graphs such as {\tt LiveJournal} and {\tt Orkut}, the quality gap narrows {\sc Skim}  only $5\%$ behind, and {\sc Tim+} is marginally better.
+For the same $w=0.005$ and larger graphs such as {\tt LiveJournal} and {\tt Orkut}, the quality gap narrows {\sc Skim}  only $5\%$ behind, and {\sc Tim} is marginally better.
+
 The performance gap also narrows between \acro and {\sc Skim}, \acro only $30\%$ faster in small $w$.
-In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
+In the same setting, {\sc Tim}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
 For $w=0.1$, \acro is much faster than all other methods and still provides high-quality results.
-While all methods are struggling with problem size, \acro is converging results much faster, even faster than previous experiment settings.
+While all methods are struggling with problem size, \acro converge results much faster, even faster than previous experiment settings.
 Also, the memory consumption stays the same for all experimental settings, much smaller than other methods.
@@
 Performance characteristics of \acro are very different from its state-of-the-art competitors.
-\acro's performance directly depends on the diameter of the influence graph, whereas other methods mention in this paper depends on the influence score.
+\acro's performance depends on the influence graph's diameter, whereas other methods mentioned in this paper depend on the influence score.
 Due to this reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
-In exceptional settings, such as the Pokec dataset and $w=0.01$ where the diameter of the influence network is around 43, \acro loses its edge against its fastest competitor.
-On the other hand, in the same dataset with $w=0.1$, the diameter is only around 17; \acro is 6 times faster than its nearest competitor.
+In exceptional settings, such as the Pokec dataset and $w=0.01$ where the influence network's diameter is around 43, \acro loses its edge against its fastest competitor.
+On the other hand, in the same dataset with $w=0.1$, the diameter is only around 17; \acro is six times faster than its nearest competitor.
+Running time of \acro decreases as connections gets stronger and influence graph gets denser, whereas other methods gets slower.
+
+When we compare \acro's performance to {\sc Imm} in figure \ref{fig:vs-imm}, we can see that \acro is almost always faster except few settings.
+The setting $w=0.005$ is especially challenging for \acro due to the high diameter of the influence graph and low vector unit utilization.
+Except for the {\tt Pokec} dataset, all the other experiments \acro performs worse takes slightly longer than 1 second.
+In such a small time scale and small influence, \acro is suffering death by thousand cuts.
+Only a few hundreds of vertices can be activated, whereas we optimize \acro to work on much larger scale problems.
+For the {\tt Pokec} dataset, \acro performs many graph traversals for minimal gains and spends twice as much time, 11 seconds, yet still beating other competitors.
+For a small price of influence,\acro could have performed much faster, but in our experiments, we aimed for high-quality results.
+
+In figure \ref{fig:vs-skim}, we compared \acro's performance with {\sc Skim}.
+\acro performs much better, both in terms of quality and speed, in near all settings.
+For the notorious {\tt Pokec} dataset \acro performs better then {\sc Skim}, except for $w=0.01$; the diameter of influence graph does not affect {\sc Skim}'s performance.
+{\sc Skim} performs slightly better in terms of speed in that setting but it has worse result quality.
+In some settings such as {\tt Amazon}($w=0.01$), {\sc Skim} performed very poorly; only 39\% of the influence was achieved with respect to \acro, and {\sc Skim} spent 59.32 seconds where as \acro could finish in 0.96 seconds.
+
+Memory consumption of \acro is linearly dependent on the number of vertices in the graph.
+Both sketch-registers and visited information are stored per vertex so that \acro's memory consumption stays constant for any simulation parameters or any number of edges.
+In all benchmark settings, \acro consumed significantly less memory on average.
+The competitors' memory usage behavior differs between parameters and datasets; \acro's memory use is predictable for any graph, \acro consumes only $O(R)$ bytes per vertex.%12*R bits aslinda
+
+\subsection{Scalability with multi-threaded parallelism}
+
+\begin{figure*}[!ht] 
+    \centering
+    \includegraphics[width=\linewidth]{images/threads.pdf}
+   \centering \caption{Scaling of \acro with multiple threads on some of largest datasets in the benchmarks.
+     \label{fig:scaling}} 
+\end{figure*}
+
+In our implementation, we used a {\em pull-based} approach in which the vertices~(processed at line~\ref{ln:inner_start} of Algorithm~\ref{algo:diffusion-step}) pull the influence, i.e., reachability set cardinality estimations, from their outgoing neighbors.
+A classical {\em push-based} approach, in which the vertices relay their influence to their outgoing neighbors could also be leveraged.
+However, the push-based approach makes a (target) vertex register potentially updated at the same time in different computation units.
+Specifically, the update operation~(corresponding to the one at line~\ref{ln:update} of Algorithm~\ref{algo:diffusion-step}) of the {\em pull-based} approach will be the cause of race conditions.
+One can easily argue that since we are already using sketches, and not computing exact cardinalities, such race conditions are acceptable and they will not reduce the quality of influence estimations.
+However, the performance may suffer due to false sharing.
+Figure~\ref{fig:scaling} shows \acro's speedup values obtained via a simple {\tt OpenMP} parallelization at line~\ref{ln:inner_start} of Algorithm~\ref{algo:diffusion-step}.
+Even though the pull-based diffusion shows a nice parallel performance, it is possible to implement \acro using other approaches such as the {\em queue-based} approach which may improve performance by only processing live vertices.
+The pull-based diffusion method is chosen due to its simplicity and scalability to many threads/compute units.
 
@@
 
-Although they can be inferior in terms of influence score, recent IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.
-
-Techniques such as using GPUs\cite{IMGPU,curipples}, sketches for finding set intersections\cite{cohen2014sketch,IPA}, reverse sampling to estimate influence from a small subset of vertices\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time\cite{leskovec2009community}.
-
-\acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling and vertex parallel diffusion algorithm.
-{\sc InFuseR} computes influence by memoizing connected-components for all vertices and only works on {\em undirected} datasets.
-In addition, it employs CELF optimization to reduce candidate seed set cardinality computations.
-Whereas, \acro can process both directed and undirected graphs, and uses sampled Flajolet–Martin sketches to both estimate cardinality and choose candidates.
-
-Sketch-based influence maximization improves the theoretical efficiency against simulation-based methods.
-The sketch-based approach pre-computes sketches for evaluating the influence spread instead of running simulations repetitively.
-One of the interesting methods for sketch-based influence maximization is {\sc Skim} ~\cite{cohen2014sketch} by Cohen~et~al.
-It constructs bottom-$K^2$ min-hash sketches to estimate the reachability and utilizes multi-core/multi-CPU parallelization.
-
-Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al, runs a proxy model and prunes paths with probabilities less than a given threshold.
-IPA uses {\tt OpenMP} to work on independent paths in parallel.
+Although they can be inferior in terms of influence, modern IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.
+Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate influence from a small subset of vertices\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time~\cite{leskovec2009community}.
+
+\acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling.
+{\sc InFuseR} computes influence by memoizing connected components for all vertices and only can work on {\em undirected} datasets.
+It also employs CELF optimization to reduce cardinality computations.
+On the other hand, \acro can process both directed and undirected graphs and uses the Flajolet–Martin sketches in a novel way to estimate cardinality and choose seed candidates.
+
+Sketch-based IM methods are cheaper compared to simulation-based methods.
+They usually pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively.
+One of the popular methods for sketch-based influence maximization is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al.
+{\sc Skim} is a parallel algorithm which uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all} with $k = 64$, and $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
+In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} instead of bottom-$k$ min-hash sketches for simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
+
+The Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al.
+runs a proxy model and prunes paths with probabilities smaller than a given threshold in parallel.
 The approach only keeps a dense but small part of the network and scalable to only sparse networks.
@@
 Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS), which samples a fraction of all random reverse reachable sets.
-Then it computes a set of $K$ seeds that covers the maximum number of those.
-The number of samples is calculated concerning the number of visited vertices.
+The number of necessary samples to find the seed set with $K$ vertices is calculated based on the number of visited vertices.
 The algorithm has an approximation guarantee of $(1-1/e-\epsilon)$.
-Minutoli et al.~improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast}.
-Recently, the authors extended the algorithm to work on GPUs~\cite{curipples}.
-
-Two-phased Influence Maximization({\sc Tim+})\cite{tim} borrows ideas from RIS but overcomes its limitations with a novel algorithm design.
-The first phase computes a lower-bound of the maximum expected to spread among all size-k node sets.
-Then, it uses the lower bound to derive a parameter $\theta$.
-In the second phase, samples $\theta$ random RR sets from G, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
-
-Cohen\cite{cohen2015all} presented the Historic Inverse Probability (HIP) estimators.
-When applied to All Distance Sketches, HIP outperforms in the estimation quality of the HyperLogLog sketches\cite{flajolet2007hyperloglog} for counting distinct elements on data streams.
-In this work, we preferred Flajolet-Martin\cite{flajolet1985probabilistic} sketches for simplicity and performance.
-In future work, other estimators such as HIP can improve to improve \acro.
-
-Kumar and Calders\cite{kumar2017information} proposed Time Constrained Information
-Cascade Model and an influence maximization algorithm that works on the model using versioned HyperLogLog sketches.
-The algorithm computes the influence reachability sets for all vertices in an interaction graph while performing a single pass over the data.
-Sketches are used for each time window to estimate active edges, whereas \acro builds sketches for each vertex to estimate the cumulative influence of the latent seed set.
+Minutoli et al.
+improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast} with high efficiency.
+Recently, the authors extended the algorithm to work in a multi-GPU setting~\cite{curipples}.
+
+Two-phased Influence Maximization~({\sc Tim}) borrows ideas from RIS but overcomes its limitations with a novel algorithm design~\cite{tim}.
+The first phase computes a lower bound of the maximum expected to spread among all size-$k$ node sets.
+It then uses the lower bound to derive a parameter $\theta$.
+In the second phase, it samples $\theta$ random RR sets from $G$, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
+
+%Cohen~\cite{cohen2015all} presented the Historic Inverse Probability ({\sc HIP}) estimators which, when applied to All-Distance Sketches, outperforms the {\sc HyperLogLog} sketches~\cite{flajolet2007hyperloglog} while estimating the number of distinct elements on data streams.
+In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} instead of bottom-$k$ min-hash sketches for simplicity and execution-time performance.
+In future work, other estimators such as HIP can be used to improve \acro.
+
+Kumar and Calders~\cite{kumar2017information} proposed the Time Constrained Information Cascade Model and an IM kernel that works on the model using versioned HyperLogLog sketches.
+The algorithm computes the influence for all vertices in an interaction graph while performing a single pass over the data.
+The sketches are used for each time window to estimate active edges.
+On the other hand, \acro uses $J$ sketches for each vertex to estimate the marginal influence and employs a rebuilding strategy for fast processing.
 \acro also utilizes fused sampling and error adaptive rebuilding of sketches.
@@
 
-In conclusion, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and error-adaptive rebuilding.
+In this work, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and error-adaptive rebuilding.
 We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple cores.
 Also, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
-With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speed-up against {\sc Skim} and $\maxspeedupIMM\times$ speed-up against {\sc Imm} while producing high quality results.
-
-In the future, we would like to extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges.
-The main issue with \acro on such computation scheme is the broadcast of sketch registers; when vertices are partitioned to different computation units, resulting sketch updates should be communicated to all partitions.
-To overcome the issue, graph preprocessing and speculative diffusion strategies can reduce communication bottlenecks.
-
-\kktodo{an analysis of a fast and better sketch to reduce the number of rebuilding stages}
+With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speed-up against a sketch-based algorithm {\sc Skim} and $\maxspeedupIMM\times$ speed-up against an approximation-based algorithm {\sc Imm} while producing high-quality seed sets.
+
+In the future, we will extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges.
+The main issue with \acro on such an architecture is the broadcast of sketch registers.
+When the vertices are partitioned into different computation units, resulting sketch updates should be communicated to all partitions.
+To overcome the issue and reduce communication bottlenecks, graph preprocessing and speculative diffusion strategies will be employed.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{IEEEbiography}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Assistant Professor at the Faculty of Engineering and Natural Sciences at Sabancı University.
-He got his PhD from Dept.
-Computer Science and Engineering from Bilkent University.
-He worked at CERFACS, France, as a post-graduate researcher in the Parallel Algorithms Project.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Asst.
+Professor at Sabancı University.
+After receiving his PhD from Bilkent University, he worked at CERFACS, France, as a post-graduate researcher in the Parallel Algorithms Project.
 He then joined the Ohio State University in September 2011 as a postdoctoral researcher, and in December 2013, he became a Research Assistant Professor in the Dept.

### 2021-04-20 paper.tex
kamer

@@
 {\sc Skim} is a parallel algorithm which uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all} with $k = 64$, and $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
-In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} instead of bottom-$k$ min-hash sketches for simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
+In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} sketches instead for their simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
 

### 2021-05-03 paper.tex
Update on Overleaf.

@@
 Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
-In addition to these high-quality, yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not simulate the process exactly, have been proposed in the literature to cope with the scale of today's networks.
+% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks.
 In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling.
@@
 To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion.
-This allows the proposed algorithm to estimate the number of influenced vertices in a single simulation step of different simulations at once.
-In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary.
-For a faster IM kernel, we rebuild the sketches only after observing estimation errors above a given threshold.
-Our experimental results show that the proposed method yields high-quality seed sets while being up-to $1.7\times$--$27.9\times$ faster on average than a state-of-the-art approximation algorithm.
-In addition, it is $3.5\times$--$11.1\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
+This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once.
+%In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary.
+For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold.
+Our experimental results show that the proposed algorithm yields high-quality seed sets while being up to $119\times$ faster than a state-of-the-art approximation algorithm.
+In addition, it is up to $62\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
 \end{abstract}
@@
 
-Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model $M$.
+Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model.
 Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, proved it to be NP-hard, and provided a greedy Monte-Carlo approach that has a constant approximation ratio over the optimal solution.
 This greedy approach is one of the most frequently applied algorithms for IM.
-The time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+The time complexity of the greedy algorithm, with an influence score estimate $\sigma$, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
 Although they perform well in terms of seed-set quality, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices as a consequence of their expensive simulation costs.
@@
 Simulating a greedy algorithm in parallel is a straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
-However, for large networks, a greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges even if a large number of processing units/cores are available.
-Following similar attempts in the literature, we propose a parallel, sketch-based greedy approach that approximates the Monte-Carlo processes.
-To further increase the performance, the proposed approach does not exactly count the number of influenced vertices.
+However, for large networks, a parallel, greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges even if a large number of processing units/cores are available.
+Following similar attempts in the literature, we propose a parallel, sketch-based approach that approximates the Monte-Carlo processes.
+To boost the performance, the proposed approach does not exactly count the number of influenced vertices.
 Instead, it leverages Count-Distinct sketches.
@@
 
-\begin{itemize}
+\begin{itemize} [leftmargin=0.3cm]
 \item We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.
@@
 \item Running concurrent simulations on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
-While traversing an edge, any number of diffusion simulations can be simultaneously performed over the graph, using only a single (8-bit) value per vertex for each simulation.
-
-\item \acro{} can process very large graphs with millions of vertices and hundreds of millions of edges under a minute, without compromising the quality of results.
-For large graphs, due to its race condition indifferent nature, the performance scales near linearly with the number of threads available.
-Furthermore, while processing the graph, only a few GBs of memory is used, mostly for storing the graph itself.
+While traversing an edge, \acro concurrently performs multiple diffusion simulations while using only a single (8-bit) value per vertex for each simulation.
+
+\item \acro{} can process large-scale graphs with millions of vertices and hundreds of millions of edges under a minute without compromising the quality of results.
+Furthermore, the performance scales near linearly with the number of threads available.
+In addition, while processing a large-scale graph, only a few GBs of memory is used, where most of the memory is spent for storing the graph itself.
 
@@
 
-\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
-The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having the same quality with the approximation-based algorithms w.r.t.
-influence, and using a comparable amount of memory.
+\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+The experiments show that \acro can be $62\times$ and $119\times$ faster than a state-of-the-art sketch-based and approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.
 
@@
         $K$             & Size of the seed set\\
-        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
+        ${\cal J}$   & Number of Monte-Carlo simulations performed\\
         $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
@@
 \begin{itemize}[leftmargin=*]
-\item The {\bf Independent Cascade} model works in rounds and activates a vertex $v$ in the current round if one of $v$'s incoming edges $(u, v)$ is 
-used during the diffusion round, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
-The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model which we concentrate on this paper.
+\item The {\bf Independent Cascade} model works in rounds and activates a vertex $v$ in the current round if one of $v$'s incoming edges $(u, v)$ is used during the diffusion round, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
+The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model, which we focus on in this paper.
 A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
@@
 
-\item{\bf Linear threshold} generalizes the independent cascade model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
+\item{\bf Linear threshold} generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
 All the $(u, v)$ edges with active $u$ vertices are taken into account in the process.
 Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.
-Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
+%Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
 \end{itemize}
@@
 
-Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers.
+Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, ${\cal J}$, of registers.
 Furthermore, the union of two sketches can be computed in constant time.
@@
     \label{eq:sketch-add}
-    M[j] = \max(M[j], clz(h_j(x)),~1 \leq j \leq J
-\end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and $J$ is the number of sketch registers.
+    M[j] = \max(M[j], clz(h_j(x)),~1 \leq j \leq {\cal J}
+\end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and ${\cal J}$ is the number of sketch registers.
 With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided to a correction factor $\phi \approx 0.77351$ to fix the error due to hash collisions.
@@
 \label{eq:sketch-merge}
-    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
+    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq {\cal J}.
 \end{equation} 
-In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples.
+In our implementation, the merge operations are performed if and only if there is a sampled edge between the vertices.
 %\kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}.
@@
 
-\section{Efficient and Error-Adaptive Influence Maximization}\label{sec:method}
+\section{Error-Adaptive Influence Maximization}\label{sec:method}
 
@@
 After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
-Although the approach as mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
+Although the approach mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
 First, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated to enable this for each edge.
@@
 Such a task involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}.
-The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs as explained above.
+The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs, as explained above.
 Hence, in this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
@@
 
+\renewcommand{\baselinestretch}{0.95}
 \begin{algorithm}
-\caption{\sc{\acro}($G,K,J$)}
+\caption{\sc{\acro}($G,K,{\cal J}$)}
 \label{algo:main}
@@
 \\\hspace*{6.6ex}{$K$: number of seed vertices
-\\\hspace*{6.7ex}$J$: number of Monte-Carlo simulations}\\}
+\\\hspace*{6.7ex}${\cal J}$: number of Monte-Carlo simulations}\\}
 \algorithmicensure{$S$: a seed set that maximizes the influence on $G$
@@
     \For{$ v\in V$} {\bf in parallel}
-        \For{$ j\in J$}
+        \For{$ j \in \{1, \ldots, {\cal J}\}$}
             \State $M_v[j] \leftarrow clz(hash(v) \oplus hash(j))$ 
@@
     \EndFor
-    \State $M \leftarrow ${\sc Simulate}$(G,M,J,\emptyset)$
-    \State $M_{S'} \leftarrow zeros(J)$
+    \State $M \leftarrow ${\sc Simulate}$(G,M,{\cal J},\emptyset)$
+    \State $M_{S'} \leftarrow zeros({\cal J})$
     \State $\varsigma \leftarrow 0$
@@
         \State $e \leftarrow ${\sc Estimate}$(${\sc Merge}$(M_{S'},M_s))$\label{line:e}
-        % \State $R_S \leftarrow run\_cascade(G,S,J)$
+        % \State $R_S \leftarrow run\_cascade(G,S,{\cal J})$
         %\State {Compute $R_{G}(S)$; the reachability set of $S$}
@@
             \For{$ v\in V$} {\bf in parallel}\label{line:else1}
-                \For{$ j\in J$}
+                \For{$ j \in \{1, \ldots, {\cal J}\}$}
                     \State $M_v[j] \leftarrow clz(hash(v) \oplus hash(j))$ 
@@
             \EndFor
-            \State $M \leftarrow ${\sc Simulate}$(G,M,J,R_{G}(S))$
-            \State $M_{S'} \leftarrow zeros(J) $ 
+            \State $M \leftarrow ${\sc Simulate}$(G,M,{\cal J},R_{G}(S))$
+            \State $M_{S'} \leftarrow zeros({\cal J}) $ 
             \State $\varsigma \leftarrow \sigma $ \label{line:else2} 
@@
 \end{algorithm}
+\renewcommand{\baselinestretch}{1}
 
@@
 \kktodo{burada edgeleri tersten process ettigimizi aciklamamiz gerek} burasi yanlis
-If any of $u$'s sketch registers changes during this operation it is added to the live vertex set $L'$ of the next iteration.
+If any of $u$'s sketch registers changes during this operation, it is added to the live vertex set $L'$ of the next iteration.
 Once the incoming edges of all live vertices are processed, the iteration ends.
@@
 
+\renewcommand{\baselinestretch}{0.95}
 \begin{algorithm}[!ht]
-\caption{\sc{Simulate}($G,M,J,R_S$)}
+\caption{\sc{Simulate}($G,M,{\cal J},R_S$)}
 \label{algo:diffusion-step}
@@
 \\\hspace*{6.6ex}{$M$: sketch vectors of vertices
-\\\hspace*{6.7ex}${J}$: number of MC simulations
+\\\hspace*{6.7ex}${{\cal J}}$: number of MC simulations
 \\\hspace*{6.7ex}$R_S$: reachability set of the seed set
@@
         \For{$e_{u,v} \in A(u) $}
-            \For{$j \in (0,J]$} \label{ln:vec1}
+            \For{$j \in (0,{\cal J}]$} \label{ln:vec1}
                 \If{$P(u,v)_j < w_{u,v} \land u  \not\in R_S[j]$} \label{ln:early_exit}
@@
 Although \acro seems to perform much more iterations, $d$ is a loose upper bound for \acro.
-A better one is {\tt max}$\{d_j: 1 \leq j \leq J\}$ where $d_j$ is the diameter of $G_j$.
-To further reduce the overhead of concurrent simulations and avoid bottleneck simulations due to remaining perimeter vertices, we employ a early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two simulations remain.
+A better one is {\tt max}$\{d_j: 1 \leq j \leq {\cal J}\}$ where $d_j$ is the diameter of $G_j$.
+To further reduce the overhead of concurrent simulations and avoid bottleneck simulations due to remaining perimeter vertices, we employ an early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two simulations remain.
 That is if $|L'| \leq |V| \times \epsilon_c$ the diffusion process in Algorithm~\ref{algo:diffusion-step} stops.
@@
 Second, a vertex $s$ with the maximum cardinality estimation is selected and added to $S$.
-Third, the actual Monte-Carlo simulations are performed to compute the reachability set of the new seed set.
+Third, the actual simulations are performed to compute the reachability set of $S$.
 Having an actual $R_G(S)$ allows us to calculate the estimation errors and find the blocked vertices for all simulations, which is vital since these blocked vertices can be skipped during the next diffusion steps.
-Besides, we leverage the actual influence score to have an {\em error-adaptive kernel}, i.e., to compute the actual sketch error and rebuild the sketches when the accumulated error reaches a critical level which can deteriorate the quality for the following seed vertex selections.
+Besides, we leverage the actual influence to have an {\em error-adaptive kernel}, i.e., to compute the actual sketch error and rebuild the sketches when the accumulated error reaches a critical level which can deteriorate the quality for the following seed vertex selections.
 
@@
     \begin{center}
-    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
-    \caption{ Effect of register saturation on Amazon dataset using \acro($J=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
+    \includegraphics[width=0.93\linewidth]{images/sketch-saturation.pdf}
+    \caption{ Effect of register saturation on Amazon dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
 %\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
@@
     \begin{center}
-        \subfloat[LiveJournal execution time in seconds\label{fig:lj-time}]{%
+        \subfloat[{\tt LiveJournal} execution time in seconds\label{fig:lj-time}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
     }
-    \subfloat[Orkut execution time in seconds\label{fig:orkut-time}]{%
+    \subfloat[{\tt Orkut} execution time in seconds\label{fig:orkut-time}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
         }
-    \subfloat[Pokec execution time in seconds\label{fig:pokec-time}]{%
+    \subfloat[{\tt Pokec} execution time in seconds\label{fig:pokec-time}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
         }\\
-        \subfloat[LiveJournal Influence Score\label{fig:lj-score}]{%
+        \subfloat[{\tt LiveJournal} influence score\label{fig:lj-score}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
         }
-    \subfloat[Orkut Influence Score\label{fig:orkut-score}]{%
+    \subfloat[{\tt Orkut} influence score\label{fig:orkut-score}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
         }
-    \subfloat[Pokec Influence Score\label{fig:pokec-score}]{%
+    \subfloat[{\tt Pokec} influence score\label{fig:pokec-score}]{%
         \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
@@
     \end{center}
-    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
+    \caption{Effect of $\epsilon$ parameters on \acro(${\cal J} = 256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
 \end{figure*}    
@@
 %    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
-%  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) \kktodo{bu alttaki figurlerde sagdaki degerler sanki ters - kirmizi siyah bu sekilde mi siralanmali}.
+%  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters (${\cal J}=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) \kktodo{bu alttaki figurlerde sagdaki degerler sanki ters - kirmizi siyah bu sekilde mi siralanmali}.
 %    \label{fig:conv-perf}} 
@@
 Note that rebuilding also allows \acro to work on a smaller problem for the following seed vertex selection since we remove the already influenced vertices from sample subgraphs and work on the remaining subgraphs.
-%Hence, for the remaining estimations, we only need to consider {\em latent} seed vertices of $S$ which are chosen after the sketch rebuild.
+%Hence, for the remaining estimations, we only need to consider {\em latent} seed vertices of $S$, which are chosen after the sketch rebuild.
 
@@
 We only left out the time to spend on reading files for \acro.
-We allowed all methods to utilize all the CPU cores in all benchmarks, except {\sc Tim}, a single-threaded algorithm.
+We allowed all methods to utilize all the CPU cores in all benchmarks, except {\sc Tim+}, a single-threaded algorithm.
 The memory use reported in this paper is the {\em maximum resident set sizes}~(RSS), which are measured using GNU {\tt time} command.
 
-Since the algorithms may use different methods to measure the influence score, the reported influence scores may not be suitable for comparison purposes with high precision.
+Since the algorithms may use different methods to measure the influence, the reported influence scores may not be suitable for comparison purposes with high precision.
 Due to this reason, we implemented an oracle with a straightforward, sample-then-diffuse algorithm without any optimization mentioned.
@@
 
-We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim}, {\sc Skim}, and {\sc Imm}.
+We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, and {\sc Imm}.
 The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account.
-Last, the third one is an approximation algorithm with a parameter to control the approximation quality.
-\begin{itemize}
-\item The two-phased Influence Maximization~({\sc Tim}) consists of two phases: {\em Parameter Estimation} and {\em Node Selection}~\cite{tim}.
-The first phase computes a lower bound on the maximum expected influence to spread among all size-$K$ node sets and then uses it to derive a parameter $\theta$.
-The second phase randomly samples $\theta$ reverse reachability sets from $G$ and then derives a size-$K$ vertex-set $S$ that covers a large number of these sets.
-
-\item The sketch-based Influence Maximization~({\sc Skim}) is a parallel algorithm which uses a combined bottom-$k$ min-hash reachability sketch~\cite{bottomk} with $k = 64$ to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
-{\sc Skim} employs $\ell = 64$ sampled subgraphs and designed and tuned to provide good seed sets in a short time.
+The third one is an approximation algorithm with a parameter to control the influence quality.
+
+\begin{itemize} [leftmargin=0.3cm]
+\item The Two-phased Influence Maximization~({\sc Tim+}) runs in two phases: {\em Parameter Estimation} which estimates the maximum expected influence and a parameter $\theta$ and {\em Node Selection} which randomly samples $\theta$ reverse reachability sets from $G$ and then derives a size-$K$ vertex-set $S$ that covers a large number of these sets~\cite{tim}.
+The algorithm has a parameter $\epsilon$ which allows a trade-off between the seed set quality and execution time.
+In our experiments, we set  $\epsilon=0.3$ to have a high-quality influence maximization baseline.
+We also experimented with $\epsilon = 1.0$ as suggested, which gives around $7\times$ speedup on average but a reduction on the influence score up to $6\%$.
+
+\item The Sketch-based Influence Maximization~({\sc Skim}) uses a combined bottom-$k$ min-hash reachability sketch~\cite{bottomk} to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
+As suggested by the authors, in this work, we employ {\sc Skim} with $k = 64$ and $\ell = 64$ sampled subgraphs.
+The implementation (from the authors) is partially parallelized and leverages multicore processors.
 
@@
 \begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.005$.
+    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.005$.
 Influence scores are given relative to \acro{}.
+The runs that did not finish due to high memory use shown as "-".
+    % \kktodo{need to explain why we have a - for some graphs}
     }
@@
 \toprule
-{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim} &  {\sc Imm} & {\sc Skim} \\
+{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Influence Score} & \multicolumn{4}{c}{Memory} \\
+Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
 
@@
 \midrule
-{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041x &  1.000x &  0.562x &       0.17 & 21.62 & 0.90 & 6.78 \\
-{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068x &  1.027x &  1.036x &       0.27 & 31.24 & 0.95 & 3.12 \\
-{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026x &  1.001x &  0.939x &       0.06 &  0.78 & 0.07 & 1.04 \\
-{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010x &  0.995x &  0.957x &       3.97 & 27.43 & 2.78 & 2.00 \\
-{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065x &  0.993x &  0.871x &       0.01 &  0.80 & 0.04 & 0.33 \\
-{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042x &  0.999x &  0.777x &       0.03 &  2.01 & 0.08 & 0.16 \\
-{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997x &  1.001x &       5.19 &     - & 7.81 & 1.77 \\
-{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032x &  1.027x &  0.925x &       1.57 & 10.16 & 1.40 & 1.74 \\
-{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015x &  0.983x &  0.942x &       0.06 &  0.76 & 0.09 & 0.13 \\
-{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022x &  0.998x &  0.953x &       0.06 &  0.71 & 0.08 & 0.14 \\
-{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006x &  0.990x &  0.942x &       0.09 &  2.02 & 0.12 & 0.15 \\
-{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025x &  1.013x &  1.000x &       0.73 &  3.96 & 0.48 & 1.39 \\
+{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041$\times$&  1.000$\times$&  0.562$\times$&       0.17 & 21.62 & 0.90 & 6.78 \\
+{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068$\times$&  1.027$\times$&  1.036$\times$&       0.27 & 31.24 & 0.95 & 3.12 \\
+{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026$\times$&  1.001$\times$&  0.939$\times$&       0.06 &  0.78 & 0.07 & 1.04 \\
+{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010$\times$&  0.995$\times$&  0.957$\times$&       3.97 & 27.43 & 2.78 & 2.00 \\
+{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065$\times$&  0.993$\times$&  0.871$\times$&       0.01 &  0.80 & 0.04 & 0.33 \\
+{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042$\times$&  0.999$\times$&  0.777$\times$&       0.03 &  2.01 & 0.08 & 0.16 \\
+{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997$\times$&  1.001$\times$&       5.19 &     - & 7.81 & 1.77 \\
+{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032$\times$&  1.027$\times$&  0.925$\times$&       1.57 & 10.16 & 1.40 & 1.74 \\
+{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015$\times$&  0.983$\times$&  0.942$\times$&       0.06 &  0.76 & 0.09 & 0.13 \\
+{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022$\times$&  0.998$\times$&  0.953$\times$&       0.06 &  0.71 & 0.08 & 0.14 \\
+{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006$\times$&  0.990$\times$&  0.942$\times$&       0.09 &  2.02 & 0.12 & 0.15 \\
+{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025$\times$&  1.013$\times$&  1.000$\times$&       0.73 &  3.96 & 0.48 & 1.39 \\
 \bottomrule
-Norm. arit. mean &&69.39x&4.37x&8.13x&&1.032x&1.002x&0.909x& &42.60x&2.05x&9.76x \\ 
-Norm. geo. mean &\multicolumn{1}{c}{all}&28.19x&1.69x&3.47x&\multicolumn{1}{c}{all}&1.032x&1.002x&0.899x&\multicolumn{1}{c}{all}&22.75x&1.65x&3.58x \\ 
-Norm. max perf&\multicolumn{1}{c}{1.00x}&314.92x&25.82x&49.02x&\multicolumn{1}{c}{1.000x}&1.068x&1.027x&1.036x&\multicolumn{1}{c}{1.00x}&127.18x&5.29x&39.88x \\ 
-Norm. min perf&&5.88x&0.34x&0.85x&&1.006x&0.983x&0.562x&&5.43x&0.66x&0.34x \\
-
-\end{tabular}\\
+Norm. arit. mean &&69.39$\times$&4.37$\times$&8.13$\times$&&1.032$\times$&1.002$\times$&0.909$\times$& &42.60$\times$&2.05$\times$&9.76$\times$ \\ 
+Norm.
+geo.
+mean &\multicolumn{1}{c}{all}&28.19$\times$&1.69$\times$&3.47$\times$&\multicolumn{1}{c}{all}&1.032$\times$&1.002$\times$&0.899$\times$&\multicolumn{1}{c}{all}&22.75$\times$&1.65$\times$&3.58$\times$ \\
+Norm.
+max perf&\multicolumn{1}{c}{1.00$\times$}&314.92$\times$&25.82$\times$&49.02$\times$&\multicolumn{1}{c}{1.000$\times$}&1.068$\times$&1.027$\times$&1.036$\times$&\multicolumn{1}{c}{1.00$\times$}&127.18$\times$&5.29$\times$&39.88$\times$ \\
+Norm. min perf&&5.88$\times$&0.34$\times$&0.85$\times$&&1.006$\times$&0.983$\times$&0.562$\times$&&5.43$\times$&0.66$\times$&0.34$\times$
+\end{tabular}
     }
@@
     \begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.01$.
+    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs) on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.01$.
 Influence scores are given relative to \acro{}.
-}
+The runs that did not finish due to high memory use shown as "-".}
     \label{tab:timings01}
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim} &  {\sc Imm} & {\sc Skim} \\
+Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
 
@@
 \midrule
-{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037x &  1.024x &  0.390x &       0.17 & 18.11 &  0.55 & 6.40 \\
-{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043x &  1.005x &  0.997x &       0.27 & 11.92 &  0.52 & 2.05 \\
-{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006x &  0.983x &  0.984x &       0.06 &  1.95 &  0.10 & 0.68 \\
-{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996x &  0.993x &       3.97 &     - &  6.64 & 1.45 \\
-{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036x &  0.997x &  0.826x &       0.01 &  0.60 &  0.03 & 0.31 \\
-{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010x &  0.985x &  0.732x &       0.03 &  0.67 &  0.05 & 0.12 \\
-{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000x &  1.000x &       5.19 &     - & 20.13 & 3.43 \\
-{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004x &  0.996x &  0.988x &       1.57 & 39.98 &  2.09 & 0.78 \\
-{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003x &  0.984x &  0.976x &       0.06 &  2.01 &  0.10 & 0.08 \\
-{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008x &  0.992x &  0.980x &       0.06 &  2.42 &  0.11 & 0.08 \\
-{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004x &  0.992x &  0.978x &       0.09 &  4.91 &  0.23 & 0.09 \\
-{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009x &  0.994x &  1.006x &       0.73 &  7.10 &  0.48 & 1.73 \\
+{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037$\times$&  1.024$\times$&  0.390$\times$&       0.17 & 18.11 &  0.55 & 6.40 \\
+{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043$\times$&  1.005$\times$&  0.997$\times$&       0.27 & 11.92 &  0.52 & 2.05 \\
+{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006$\times$&  0.983$\times$&  0.984$\times$&       0.06 &  1.95 &  0.10 & 0.68 \\
+{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996$\times$&  0.993$\times$&       3.97 &     - &  6.64 & 1.45 \\
+{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036$\times$&  0.997$\times$&  0.826$\times$&       0.01 &  0.60 &  0.03 & 0.31 \\
+{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010$\times$&  0.985$\times$&  0.732$\times$&       0.03 &  0.67 &  0.05 & 0.12 \\
+{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000$\times$&  1.000$\times$&       5.19 &     - & 20.13 & 3.43 \\
+{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004$\times$&  0.996$\times$&  0.988$\times$&       1.57 & 39.98 &  2.09 & 0.78 \\
+{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003$\times$&  0.984$\times$&  0.976$\times$&       0.06 &  2.01 &  0.10 & 0.08 \\
+{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008$\times$&  0.992$\times$&  0.980$\times$&       0.06 &  2.42 &  0.11 & 0.08 \\
+{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004$\times$&  0.992$\times$&  0.978$\times$&       0.09 &  4.91 &  0.23 & 0.09 \\
+{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009$\times$&  0.994$\times$&  1.006$\times$&       0.73 &  7.10 &  0.48 & 1.73 \\
 \bottomrule
-Norm. arit. mean &&167.17x&9.73x&9.99x&&1.016x&0.996x&0.904& &42.91x&2.09x&8.26x \\ 
-Norm. geo. mean &\multicolumn{1}{c}{all}&100.14x&5.45x&3.58x&\multicolumn{1}{c}{all}&1.016x&0.996x&0.879x&\multicolumn{1}{c}{all}&36.26x&1.91x&2.82x \\ 
-Norm. max perf&\multicolumn{1}{c}{1.00x}&433.73x&44.14x&61.79x&\multicolumn{1}{c}{1.000x}&1.043x&1.024x&1.006x&\multicolumn{1}{c}{1.00x}&106.53x&3.88x&37.65x \\ 
-Norm. min perf&&7.08x&0.89x&0.62x&&1.003x&0.983x&0.390x&&9.73x&0.66x&0.37x \\
-
-% Geo. Mean wrt.&1.000x&100.140x&5.448x&3.582x&1.000x&1.016x&0.996x&0.879x&1.000x&36.264x&1.909x&2.820x \\ \acro
+Norm. arit. mean &&167.17$\times$&9.73$\times$&9.99$\times$&&1.016$\times$&0.996$\times$&0.904$\times$& &42.91$\times$&2.09$\times$&8.26$\times$ \\ 
+Norm.
+geo.
+mean &\multicolumn{1}{c}{all}&100.14$\times$&5.45$\times$&3.58$\times$&\multicolumn{1}{c}{all}&1.016$\times$&0.996$\times$&0.879$\times$&\multicolumn{1}{c}{all}&36.26$\times$&1.91$\times$&2.82$\times$ \\
+Norm.
+max perf&\multicolumn{1}{c}{1.00$\times$}&433.73$\times$&44.14$\times$&61.79$\times$&\multicolumn{1}{c}{1.000$\times$}&1.043$\times$&1.024$\times$&1.006$\times$&\multicolumn{1}{c}{1.00$\times$}&106.53$\times$&3.88$\times$&37.65$\times$ \\
+Norm. min perf&&7.08$\times$&0.89$\times$&0.62$\times$&&1.003$\times$&0.983$\times$&0.390$\times$&&9.73$\times$&0.66$\times$&0.37$\times$ 
+% Geo. Mean wrt.&1.000$\times$&100.140$\times$&5.448$\times$&3.582$\times$&1.000$\times$&1.016$\times$&0.996$\times$&0.879$\times$&1.000$\times$&36.264$\times$&1.909$\times$&2.820x \\ \acro
 \end{tabular}
-
     }
@@
     \begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), memory use~(in GBs), and influence scores on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.1$.
+    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs) on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.1$.
 Influence scores are given relative to \acro{}.
-}
+The runs that did not finish due to high memory use shown as "-".}
     \label{tab:timings1}
@@
 \midrule
-{\tt Amazon}       &       0.69 &  133.22 &    1.98 &  23.62 &    11797.0 &  1.006x &  0.990x &  0.815x &       0.17 &   5.49 &  0.23 & 2.59 \\
-{\tt DBLP }         &       0.54 & 1368.83 &   14.54 &   6.30 &    48549.9 &  1.001x &  0.995x &  1.001x &       0.27 &  35.19 &  1.06 & 0.65 \\
-{\tt Epinions }     &       0.26 &  439.33 &    5.46 &   9.42 &    18409.9 &  1.000x &  0.998x &  0.997x &       0.06 &  12.17 &  0.39 & 1.18 \\
-{\tt LiveJournal }  &      10.10 &       - & 1071.30 &  65.73 &  2134726.0 &       - &  1.000x &  1.000x &       3.97 &      - & 65.49 & 1.40 \\
-{\tt NetHEP }       &       0.10 &   14.18 &    0.33 &   0.61 &     2461.7 &  1.002x &  0.975x &  0.899x &       0.01 &   1.02 &  0.04 & 0.10 \\
-{\tt NetPhy }       &       0.16 &  107.52 &    1.53 &   0.34 &     8339.5 &  1.007x &  0.994x &  0.975x &       0.03 &   3.84 &  0.13 & 0.03 \\
-{\tt Orkut }        &      16.55 &       - & 1964.83 & 446.92 &  2692366.5 &       - &  1.000x &  1.000x &       5.19 &      - & 71.94 & 9.68 \\
-{\tt Pokec }        &       4.90 &       - &  514.79 &  31.80 &  1034859.8 &       - &  1.000x &  1.000x &       1.57 &      - & 26.46 & 0.98 \\
-{\tt Slashdot0811 } &       0.21 &  677.49 &    7.34 &   2.44 &    25871.8 &  1.000x &  1.000x &  0.999x &       0.06 &  19.10 &  0.59 & 0.25 \\
-{\tt Slashdot0902 } &       0.23 &  695.12 &    7.99 &   2.35 &    27519.5 &  1.000x &  1.000x &  0.999x &       0.06 &  18.45 &  0.66 & 0.24 \\
-{\tt Twitter }      &       0.33 & 1897.50 &   16.09 &   1.62 &    55327.3 &  1.000x &  0.998x &  0.998x &       0.09 &  34.56 &  1.04 & 0.05 \\
-{\tt Youtube }      &       1.12 & 7158.56 &   60.59 &  30.57 &   171392.9 &  1.000x &  0.999x &  1.001x &       0.73 & 139.12 &  4.19 & 2.88 \\
+{\tt Amazon}       &       0.69 &  133.22 &    1.98 &  23.62 &    11797.0 &  1.006$\times$&  0.990$\times$&  0.815$\times$&       0.17 &   5.49 &  0.23 & 2.59 \\
+{\tt DBLP }         &       0.54 & 1368.83 &   14.54 &   6.30 &    48549.9 &  1.001$\times$&  0.995$\times$&  1.001$\times$&       0.27 &  35.19 &  1.06 & 0.65 \\
+{\tt Epinions }     &       0.26 &  439.33 &    5.46 &   9.42 &    18409.9 &  1.000$\times$&  0.998$\times$&  0.997$\times$&       0.06 &  12.17 &  0.39 & 1.18 \\
+{\tt LiveJournal }  &      10.10 &       - & 1071.30 &  65.73 &  2134726.0 &       - &  1.000$\times$&  1.000$\times$&       3.97 &      - & 65.49 & 1.40 \\
+{\tt NetHEP }       &       0.10 &   14.18 &    0.33 &   0.61 &     2461.7 &  1.002$\times$&  0.975$\times$&  0.899$\times$&       0.01 &   1.02 &  0.04 & 0.10 \\
+{\tt NetPhy }       &       0.16 &  107.52 &    1.53 &   0.34 &     8339.5 &  1.007$\times$&  0.994$\times$&  0.975$\times$&       0.03 &   3.84 &  0.13 & 0.03 \\
+{\tt Orkut }        &      16.55 &       - & 1964.83 & 446.92 &  2692366.5 &       - &  1.000$\times$&  1.000$\times$&       5.19 &      - & 71.94 & 9.68 \\
+{\tt Pokec }        &       4.90 &       - &  514.79 &  31.80 &  1034859.8 &       - &  1.000$\times$&  1.000$\times$&       1.57 &      - & 26.46 & 0.98 \\
+{\tt Slashdot0811 } &       0.21 &  677.49 &    7.34 &   2.44 &    25871.8 &  1.000$\times$&  1.000$\times$&  0.999$\times$&       0.06 &  19.10 &  0.59 & 0.25 \\
+{\tt Slashdot0902 } &       0.23 &  695.12 &    7.99 &   2.35 &    27519.5 &  1.000$\times$&  1.000$\times$&  0.999$\times$&       0.06 &  18.45 &  0.66 & 0.24 \\
+{\tt Twitter }      &       0.33 & 1897.50 &   16.09 &   1.62 &    55327.3 &  1.000$\times$&  0.998$\times$&  0.998$\times$&       0.09 &  34.56 &  1.04 & 0.05 \\
+{\tt Youtube }      &       1.12 & 7158.56 &   60.59 &  30.57 &   171392.9 &  1.000$\times$&  0.999$\times$&  1.001$\times$&       0.73 & 139.12 &  4.19 & 2.88 \\
 \bottomrule
-Norm. arit. mean &&2624.61x&47.17x&15.37x&&1.002x&0.996x&0.974x& &199.54x&8.79x&5.32x \\ 
-Norm. geo. mean &\multicolumn{1}{c}{all}&1449.41x&27.87x&11.06x&\multicolumn{1}{c}{all}&1.002x&0.996x&0.972x&\multicolumn{1}{c}{all}&163.77x&7.15x&2.63x \\ 
-Norm. max perf&\multicolumn{1}{c}{1.00x}&6391.57x&118.72x&36.23x&\multicolumn{1}{c}{1.000x}&1.007x&1.000x&1.001x&\multicolumn{1}{c}{1.00x}&384.00x&16.85x&19.67x \\ 
-Norm. min perf&&141.80x&2.87x&2.13x&&1.000x&0.975x&0.815x&&32.29x&1.35x&0.35x \\ 
+Norm. arit. mean &&2624.61$\times$&47.17$\times$&15.37$\times$&&1.002$\times$&0.996$\times$&0.974$\times$& &199.54$\times$&8.79$\times$&5.32$\times$ \\ 
+Norm.
+geo.
+mean &\multicolumn{1}{c}{all}&1449.41$\times$&27.87$\times$&11.06$\times$&\multicolumn{1}{c}{all}&1.002$\times$&0.996$\times$&0.972$\times$&\multicolumn{1}{c}{all}&163.77$\times$&7.15$\times$&2.63$\times$ \\
+Norm.
+max perf&\multicolumn{1}{c}{1.00$\times$}&6391.57$\times$&118.72$\times$&36.23$\times$&\multicolumn{1}{c}{1.000$\times$}&1.007$\times$&1.000$\times$&1.001$\times$&\multicolumn{1}{c}{1.00$\times$}&384.00$\times$&16.85$\times$&19.67$\times$ \\
+Norm. min perf&&141.80$\times$&2.87$\times$&2.13$\times$&&1.000$\times$&0.975$\times$&0.815$\times$&&32.29$\times$&1.35$\times$&0.35$\times$ 
 \end{tabular}
@@
     \end{table*}
-
- \begin{figure}[!ht] 
-     \centering
-     \includegraphics[width=1\linewidth]{images/speedup-imm}
-   \centering \caption{Speed-up obtained by \acro{} over {\sc Imm}($\epsilon\myeq 0.5$) using $\tau=18$ threads.
-     \label{fig:vs-imm}} 
- \end{figure}
-
- \begin{figure}[!ht] 
-     \centering
-     \includegraphics[width=1\linewidth]{images/speedup-skim}
-   \centering \caption{Speed-up obtained by \acro{}($J=256$) over {\sc Skim}($r\myeq 64,l\myeq 64$) using $\tau=18$ threads.
-     \label{fig:vs-skim}} 
- \end{figure}
 
@@
 For that reason, we have used the parameters suggested by the paper.
-we perform experiments using the parameters suggested by the authors of these tools: {\sc Tim} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$). 
-In short, these parameters are controlling the quality of the seed sets.
-In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim} and {\sc Imm} have one.
-Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations $J$ which also increases the number of sketches used per vertex.
-In the experiments, we set $J = 256$, which is comparable in quality to other methods.
-As explained in the previous section, we use global error threshold as $\epsilon_{g} = 0.01$, local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.
-
-Compared to \acro, for $w = 0.005$~(Table~\ref{tab:timings005}), i.e., sparser samples, \acro is
-
-For small graphs such as {\tt NetHep}, {\tt NetPhy}, and {\tt Amazon}, the results show that {\sc Tim} has $4\%$--$7\%$ more influence score, whereas the sketch-based algorithm {\sc Skim} has $13\%$--$44\%$ less influence.
-While \acro is having a hard time catching edges in samples; \acro has a chance of capturing an edge is $1-(1-0.005)^{256}=0.72$, {\sc Tim} will not suffer from the situation but {\sc Skim}  suffer much worse capturing vertices in sketches.
-On the performance side, \acro is superior to other methods, Amazon dataset only takes 1.3 seconds, including Monte-Carlo influence oracle computations.
-{\sc Skim} and {\sc Imm} take 63.73 and 124.38 seconds.
-For 4\% quality improvements, {\sc Imm} is $\sim$100 slower than \acro.
-For small improvements in quality, we can always double the number of registers/simulations $J=256$ to $512$, which would approximately double the wall time.
-For the same $w=0.005$ and larger graphs such as {\tt LiveJournal} and {\tt Orkut}, the quality gap narrows {\sc Skim}  only $5\%$ behind, and {\sc Tim} is marginally better.
-
-The performance gap also narrows between \acro and {\sc Skim}, \acro only $30\%$ faster in small $w$.
-In the same setting, {\sc Tim}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
-For $w=0.1$, \acro is much faster than all other methods and still provides high-quality results.
+we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$). 
+In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Imm} have one.
+Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex.
+In the experiments, we set ${\cal J} = 256$.
+In addition, as explained in the previous section, we use a global error threshold $\epsilon_{g} = 0.01$, a local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.\looseness=-1
+
+We present the results in Tables~\ref{tab:timings005},~\ref{tab:timings01} and~\ref{tab:timings1} for edge weights $w = 0.005$, $0.01$, and $0.1$, respectively.
+The top part of each table shows the  results for the networks, and the bottom four rows are the arithmetic mean, geometric mean, maximum and minimum, respectively, of the scores after they are normalized w.r.t.
+those of \acro's scores.
+In all tables, for the execution time (2--5) and memory (10--13) columns, lower values are better.
+For the influence scores, i.e., for columns 6--9, higher values are better.
+% We note that the points missing are the runs that were unable to finished due to high memory use and killed by {\sc Out-Of-Memory Killer}.
+
+The tables show that for small and relatively sparser graphs such as {\tt NetHep}, {\tt NetPhy}, {\tt DBLP} and {\tt Amazon}, {\sc Tim+}, the high-quality baseline, has $0.1\%$--$7\%$ more influence score compared to the proposed approach.
+Except {\tt DBLP}, the other sketch-based algorithm, {\sc Skim} also performs bad on these graphs.
+For {\tt NetPhy}, {\tt NetHEP}, and {\tt Amazon}, its influence scores are $10\%$--$44\%$ worse that those of \acro{}.
+For the rest of the graphs, {\sc Tim+} is only up to $3\%$, $0.9\%$ and $0.1\%$ better in terms of influence for the edge weights $w = 0.005$, $0.01$, and $0.1$, respectively,  while being $69\times$, $167\times$, and $2624\times$ slower on average over all the graphs.
+It is clear that \acro{}'s influence performance is getting closer to that of {\sc Tim+} when $w$ increases.
+Indeed, when $w$ is small, e.g., $0.005$, it may have a hard time while catching potential influence paths; the probability an edge being captured is $1-(1-0.005)^{256}=0.72$.
+Using $\epsilon = 0.3$, {\sc Tim+} does not suffer from sparsity, but as the tables show, {\sc Skim} can suffer more.
+With respect to the execution-time performance, \acro is superior to other methods; for instance, when $w = 0.01$, it is $167\times$, $10\times$, and $10\times$ faster on average compared to {\sc Tim+}, {\sc Imm}, and {\sc Skim}, respectively.
+Although {\sc Imm} and {\sc Skim} look similar for $w = 0.01$ in terms of relative average execution time performance, for large graphs, {\sc Skim} is faster than  {\sc Imm}.
+When $w = 0.01$, the maximum execution times for $4148$, $1870$, and $114$ seconds for {\sc Tim+}, {\sc Imm}, and {\sc Skim}, respectively.
+For the proposed approach and with the same $w$, the maximum time spent is only $42$ seconds.
+%The performance gap also narrows between \acro and {\sc Skim}, \acro only $30\%$ faster in small $w$.
+In the same setting, {\sc Tim+}  takes 1.5 hours for {\tt LiveJournal}, could not finish {\tt Orkut}; crashing after consuming all memory available.
+%For $w=0.1$, \acro is much faster than all other methods and still provides high-quality results.
 While all methods are struggling with problem size, \acro converge results much faster, even faster than previous experiment settings.
-Also, the memory consumption stays the same for all experimental settings, much smaller than other methods.
-
-Performance characteristics of \acro are very different from its state-of-the-art competitors.
-\acro's performance depends on the influence graph's diameter, whereas other methods mentioned in this paper depend on the influence score.
-Due to this reason, we observe highly varying performance speed-up results in tables \ref{tab:timings005}-\ref{tab:timings1}.
-In exceptional settings, such as the Pokec dataset and $w=0.01$ where the influence network's diameter is around 43, \acro loses its edge against its fastest competitor.
-On the other hand, in the same dataset with $w=0.1$, the diameter is only around 17; \acro is six times faster than its nearest competitor.
-Running time of \acro decreases as connections gets stronger and influence graph gets denser, whereas other methods gets slower.
-
-When we compare \acro's performance to {\sc Imm} in figure \ref{fig:vs-imm}, we can see that \acro is almost always faster except few settings.
-The setting $w=0.005$ is especially challenging for \acro due to the high diameter of the influence graph and low vector unit utilization.
-Except for the {\tt Pokec} dataset, all the other experiments \acro performs worse takes slightly longer than 1 second.
-In such a small time scale and small influence, \acro is suffering death by thousand cuts.
+
+\acro{}'s memory consumption is less compared to those of others.
+Furthermore, it stays the same for all experimental settings with different $w$ values.
+This is partly due to fused sampling; the memory consumption is linearly dependent only on the number of vertices in $G$.
+Both sketch-registers and {\em visited} information are stored per vertex.
+Hence, \acro's memory consumption stays constant for any simulation parameters or any number of edges.
+That is given ${\cal J}$, \acro's memory use is predictable for any graph.
+On the other hand, the other methods' memory consumptions tend to increase with $w$, and their behaviours change with different parameters and graphs.
+
+Overall, the performance characteristics of the proposed algorithm are  different from its state-of-the-art competitors.
+\acro's performance is highly affected by $G$'s diameter.
+%Indeed, we observe highly varying performance speed-up results in the Tables \ref{tab:timings005}-\ref{tab:timings1}.
+For instance, for {\tt Pokec} with $w = 0.01$, the average diameter of the samples is 43, which makes \acro to lose its edge against its fastest competitor.
+On the other hand, with $w = 0.1$, the average diameter is only around 17, and \acro is six times faster than its nearest competitor.
+Indeed, its execution time decreases as the samples and the influence graph $G$ get denser.
+On the other hand, the other methods tend to get slower under these changes.
+
+ \begin{figure}[!ht] 
+     \centering
+     \includegraphics[width=0.93\linewidth]{images/speedup-imm}
+   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=18$ threads.
+     \label{fig:vs-imm}} 
+ \end{figure}
+
+ \begin{figure}[!ht] 
+     \centering
+     \includegraphics[width=0.93\linewidth]{images/speedup-skim}
+   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=18$ threads.
+     \label{fig:vs-skim}} 
+ \end{figure}
+
+Figure~\ref{fig:vs-imm} shows the speedups of \acro over {\sc Imm} for all the graphs and all $w$ values.
+As described above, the relatively sparser setting $w=0.005$ is especially challenging due to the high diameter of the influence graph and low vector unit utilization.
+Even with this $w$ value, \acro{} is only slower by a few seconds and only when the influence is small.
+For larger graphs with larger influences \acro{} is much faster than {\sc Imm}.
+As explained before, for larger $w$, \acro{}'s execution-time performance is usually better, and its influence quality is on par with that of {\sc Imm}.
+
+%, \acro is suffering death by thousand cuts.
 Only a few hundreds of vertices can be activated, whereas we optimize \acro to work on much larger scale problems.
@@
 
-In figure \ref{fig:vs-skim}, we compared \acro's performance with {\sc Skim}.
-\acro performs much better, both in terms of quality and speed, in near all settings.
-For the notorious {\tt Pokec} dataset \acro performs better then {\sc Skim}, except for $w=0.01$; the diameter of influence graph does not affect {\sc Skim}'s performance.
-{\sc Skim} performs slightly better in terms of speed in that setting but it has worse result quality.
-In some settings such as {\tt Amazon}($w=0.01$), {\sc Skim} performed very poorly; only 39\% of the influence was achieved with respect to \acro, and {\sc Skim} spent 59.32 seconds where as \acro could finish in 0.96 seconds.
-
-Memory consumption of \acro is linearly dependent on the number of vertices in the graph.
-Both sketch-registers and visited information are stored per vertex so that \acro's memory consumption stays constant for any simulation parameters or any number of edges.
-In all benchmark settings, \acro consumed significantly less memory on average.
-The competitors' memory usage behavior differs between parameters and datasets; \acro's memory use is predictable for any graph, \acro consumes only $O(R)$ bytes per vertex.%12*R bits aslinda
+Figure~\ref{fig:vs-skim} compares \acro's execution-time performance with that of {\sc Skim}.
+As the figure shows, the proposed approach performs much better, both in terms of quality and speed in almost all settings.
+For the notorious {\tt Pokec} dataset, \acro performs better than {\sc Skim}, except for $w = 0.01$.
+The diameter of $G$ does not affect {\sc Skim}'s performance as much as \acro.
+{\sc Skim} is faster in this setting, but it has worse influence quality.
+In some settings such as {\tt Amazon} and $w = 0.01$, {\sc Skim} performs very poorly; only $39\%$ of the influence is achieved with respect to \acro.
+In addition, under the same setting, {\sc Skim} spends $59.3$ seconds whereas \acro finishes in less than one second.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{images/threads.pdf}
+    \includegraphics[width=0.93\linewidth]{images/threads.pdf}
    \centering \caption{Scaling of \acro with multiple threads on some of largest datasets in the benchmarks.
@@
 Even though the pull-based diffusion shows a nice parallel performance, it is possible to implement \acro using other approaches such as the {\em queue-based} approach which may improve performance by only processing live vertices.
-The pull-based diffusion method is chosen due to its simplicity and scalability to many threads/compute units.
+The pull-based diffusion method is chosen due to its simplicity and scalability to many threads.
 
@@
 Although they can be inferior in terms of influence, modern IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.
-Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate influence from a small subset of vertices\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step greatly reduces asymptotic boundaries of execution time~\cite{leskovec2009community}.
-
+Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate the influence~\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step~\cite{leskovec2009community} greatly reduces the execution times.
 \acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling.
@@
 They usually pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively.
-One of the popular methods for sketch-based influence maximization is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al.
-{\sc Skim} is a parallel algorithm which uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all} with $k = 64$, and $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets~\cite{cohen2014sketch}.
-In this work, we preferred Flajolet-Martin~\cite{flajolet1985probabilistic} sketches instead for their simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
+A popular method for sketch-based IM is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al.
+{\sc Skim} uses combined bottom-$k$ min-hash reachability sketches~\cite{bottomk,cohen2015all}, built on $\ell$ sampled subgraphs, to estimate the influence scores of the seed sets.
+It is parallel in the sense that it uses {\tt OpenMP} parallelization during sketch utilization.
+However, the sketch building step is single-threaded.
+In this work, we choose Flajolet-Martin sketches~\cite{flajolet1985probabilistic} for their simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
+% \kktodo{further differences} 
+% {\sc Skim} build its sketches on randomly assigned ranks to vertex/sample pairs.
+First, each vertex/sample pairs, $(u, i)$, are sorted by their random ranks for processing.
+Then, vertex/sampled pairs, $(u, i)$ are processed in the order.
+For every incoming edge, $(v,u)$, of $u$ in sample graph $G_i$, sketch $X_u$ is updated by appending $(v,i)$'s rank to $X_u$, until any vertices' sketch size reaches $j$.
+After, the vertex with maximum estimated cardinality according to its sketch is added to the seed set $S$ and reachability set on $S$ is removed from all sketches and samples.
+The process is repeated until $K$ vertices are select, continuing from the last rank processed.
+ {\sc Skim} treats vertex/sample pairs as distinct elements and reduces edge traversals via their smallest ranks in bottom-$k$ ketches.
+On the other hand, \acro sees vertices as shared elements among the samples, and builds a sketch for each instance.
+This allows independent parallel processing of vertices and samples, fused sampling, and a better memory layout than the former.
+In addition, \acro does not require removing the reachable vertices from the samples.
+Instead, it uses a rebuilding strategy to improve the result quality.
 
@@
 It is $5.1\times$ faster than {\sc MixGreedy} on a CPU.
-The GPU implementation is up to $60\times$ faster with an average speed-up of  $24.8\times$.
-
-Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS), which samples a fraction of all random reverse reachable sets.
-The number of necessary samples to find the seed set with $K$ vertices is calculated based on the number of visited vertices.
+The GPU implementation is up to $60\times$ faster with an average speedup of  $24.8\times$.
+
+Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS) which samples a fraction of all random reverse reachable sets.
+The number of necessary samples to find the seed set is calculated based on the number of visited vertices.
 The algorithm has an approximation guarantee of $(1-1/e-\epsilon)$.
@@
 
-Two-phased Influence Maximization~({\sc Tim}) borrows ideas from RIS but overcomes its limitations with a novel algorithm design~\cite{tim}.
-The first phase computes a lower bound of the maximum expected to spread among all size-$k$ node sets.
-It then uses the lower bound to derive a parameter $\theta$.
-In the second phase, it samples $\theta$ random RR sets from $G$, and then derives a size-k node-set $\hat{S}$ that covers a large number of RR sets.
+Two-phased Influence Maximization~({\sc Tim+}) borrows ideas from RIS but overcomes its limitations with a novel algorithm~\cite{tim}.
+Its first phase computes a lower bound of the maximum expected influence over all size-$K$ node sets.
+It then uses this bound to derive a parameter $\theta$.
+In the second phase, it samples $\theta$ random RR sets from $G$, and then derives a size-$K$ node-set that covers a large number of RR sets.
 
@@
 
-Kumar and Calders~\cite{kumar2017information} proposed the Time Constrained Information Cascade Model and an IM kernel that works on the model using versioned HyperLogLog sketches.
-The algorithm computes the influence for all vertices in an interaction graph while performing a single pass over the data.
+Kumar and Calders~\cite{kumar2017information} proposed the Time Constrained Information Cascade Model and a kernel that works on the model using versioned HyperLogLog sketches.
+The algorithm computes the influence for all vertices in $G$ while performing a single pass over the data.
 The sketches are used for each time window to estimate active edges.
-On the other hand, \acro uses $J$ sketches for each vertex to estimate the marginal influence and employs a rebuilding strategy for fast processing.
-\acro also utilizes fused sampling and error adaptive rebuilding of sketches.
+On the other hand, \acro uses ${\cal J}$ sketches for each vertex to estimate the marginal influence and employs a rebuilding strategy for fast processing.
+\acro also utilizes fused sampling and error-adaptive rebuilding of sketches.
 
@@
 We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple cores.
-Also, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets.
-With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speed-up against a sketch-based algorithm {\sc Skim} and $\maxspeedupIMM\times$ speed-up against an approximation-based algorithm {\sc Imm} while producing high-quality seed sets.
-
-In the future, we will extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges.
-The main issue with \acro on such an architecture is the broadcast of sketch registers.
+Also, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets and show that \acro{} can be an order of magnitude faster while obtaining the same influence.
+%With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speedup against a sketch-based algorithm {\sc Skim} and $\maxspeedupIMM\times$ speedup against an approximation-based algorithm {\sc Imm} while producing high-quality seed sets.
+%\ggx{Bu kısım değişmeli}
+In the future, we will extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges under a minute. 
+%The main issue with \acro on such an architecture is the broadcast of sketch registers.
 When the vertices are partitioned into different computation units, resulting sketch updates should be communicated to all partitions.

### 2022-01-25 paper.tex
Update on Overleaf.

@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
+\documentclass[review]{elsarticle}
 \usepackage{subfiles}
 \usepackage{url}
-\usepackage[pdftex]{graphicx}
 \usepackage{amsmath}
@@
 \usepackage{balance}
-
-%%%%%%
-% notation 
-%%%%%
-\ifCLASSOPTIONcompsoc
-  \usepackage[nocompress]{cite}
-\else
-  \usepackage{cite}
-\fi
-
-\ifCLASSINFOpdf
-\else
-\fi
-\newcommand\ggx[1]{\textcolor{blue}{#1}}
-
-\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
-pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
-colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
-pdftitle={Bare Demo of IEEEtran.cls for Computer Society Journals},%<!CHANGE!
-pdfsubject={Typesetting},%<!CHANGE!
-pdfauthor={Gokhan Gokturk, Kamer Kaya},%<!CHANGE!
-pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch}}%<^!CHANGE!
-
+\usepackage{etoolbox}
+\usepackage{lineno,hyperref}
+\newcommand\acrotwo{
+\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
+}
+\renewcommand{\toprule}{}
 \newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
-\usepackage{xcolor}
 \newcommand\kktodo[1]{\textcolor{red}{#1}}
-
 \newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
 \newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
-
 \newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
@@
 
+\let\oldbibliography\thebibliography
+\renewcommand{\thebibliography}[1]{%
+  \oldbibliography{#1}%
+  \setlength{\itemsep}{0pt}%
+}
+
+\modulolinenumbers[5]
+
+\renewcommand{\floatpagefraction}{.98}
+\journal{Journal of Parallel and Distributed Computing}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}
-
-\author{G\"{o}khan~G\"{o}kt\"{u}rk
-        and~Kamer~Kaya% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G.
-G\"{o}kt\"{u}rk and K.
-Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, TR~34956, Istanbul, Turkey.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-}
-%FIXME
-
-% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-% {Shell \MakeLowercase{\textit{et al.}}: Bare Advanced Demo of IEEEtran.cls for IEEE Computer Society Journals}
-
-\IEEEtitleabstractindextext{%
+\begin{frontmatter}
+\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
+
+%% Group authors per affiliation:
+%% or include affiliations in footnotes:
+\author[add]{Gökhan Göktürk}
+\ead{gokhan.gokturk@sabanciuniv.edu}
+
+\author[add]{Kamer Kaya}
+\ead{kaya@sabanciuniv.edu}
+
+\address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}
+
+% \IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold.
-Our experimental results show that the proposed algorithm yields high-quality seed sets while being up to $119\times$ faster than a state-of-the-art approximation algorithm.
-In addition, it is up to $62\times$ faster than a sketch-based approach while producing seed sets with $3\%$--$12\%$ better influence scores.
+Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm.
+In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
 \end{abstract}
-}
-
-% Note that keywords are not normally used for peer review papers.
-% section 3, overview
-% 
-% 
-% 
-% 
-% 
-% 
-% 
-% 
-%
-
-\maketitle
-
-\IEEEdisplaynontitleabstractindextext
-\IEEEpeerreviewmaketitle
-
-\ifCLASSOPTIONcompsoc
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-\else
+% } 
+\begin{keyword}
+Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
+\end{keyword}
+\end{frontmatter}
+
 \section{Introduction}
-\label{sec:introduction}
-\fi
 
@@
 
-\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
-The experiments show that \acro can be $62\times$ and $119\times$ faster than a state-of-the-art sketch-based and approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.
+\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.
 
@@
     \label{tab:notation}
+          \renewcommand*{\arraystretch}{0.6}
     \centering
+        \begin{small}
+    % \tiny
     \begin{tabular}{|l|p{0.7\linewidth}|}
@@
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
+        $N$ & Number of vertices\\
+        $M$ & Number of edges\\
+        $T$ & Depth of the graph\\
         $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
@@
     \end{tabular}
+    \end{small}
 \end{table}
+\FloatBarrier
 \subsection{Influence Maximization}
@@
   \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
+       \includegraphics[width=0.26\linewidth]{images/ic.pdf}}
   \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
+        \includegraphics[width=0.26\linewidth]{images/wc.pdf}}
     \\% IMAGES HERE
@@
 
-\item{\bf Linear threshold} generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
+\item{\bf Linear Threshold} model generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
 All the $(u, v)$ edges with active $u$ vertices are taken into account in the process.
@@
 For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$.
-Note that an exact computation of set cardinality requires memory proportional to the cardinality, which is ${\mathcal O}(|{\cal U}|)$.
+Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$.
 
@@
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
-If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity.
+If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\Theta(n)$ time complexity. 
 If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
@@
 
-Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, ${\cal J}$, of registers.
-Furthermore, the union of two sketches can be computed in constant time.
-The FM sketch stores that how rare the elements are in a stream.
-The rarity of the elements is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
+Count-Distinct Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates.
+Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities.
+The essence of an FM sketch is that it keeps the track of how rare the elements are in a stream.
+The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
 Initially, each register is initialized with zero.
 The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register.
-With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.
-
-In practice, multiple registers and hash values, $M[j]$ and $h_j$, are commonly used to reduce variance.
+With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register.
+
+In practice, multiple, ${\mathcal J}$, registers and hash values, $M[j]$ and $h_j$, $1 \leq j \leq {\cal J}$, are used to reduce the variance of the estimation.
 For a sketch with multiple registers, the impact of adding an item $x \in \cal{U}$ is shown in~\eqref{eq:sketch-add}:
@@
 \acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
-Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
+Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
 The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.
@@
 Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
-%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
+The proposed approach and the algorithm will be described in this section in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
 $u \notin R_S$ şeklinde.}
@@
 If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel.
-We identify two main bottlenecks; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
+That is first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
 In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
-In Fig.~\ref{fig:traversal}, we briefly illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}.
-This allows us to process each edge only a few times instead of once for every simulation.
+In Fig.~\ref{fig:traversal}, we illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}.
+This allows us to process each edge only a few times instead of once per simulation.
 
@@
     \subfloat[\label{fig:sims}]{%
-        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
+        \includegraphics[width=0.35\linewidth]{images/samples.pdf}
     } 
     \subfloat[\label{fig:fused}]{%
-     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
+     \includegraphics[width=0.35\linewidth]{images/fused.pdf}}
   \caption{\small{
@@
 Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
+% \begin{equation}
+%     \label{eq:hash}
+%     h(u,v) = \mbox{{\sc CRC32}}(u||v)~mod~2^{31}  
+% \end{equation} %FIXME: does this mean this value be negative?
+
 \begin{equation}
     \label{eq:hash}
-    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
-\end{equation}
+    h(u,v) = \mbox{{\sc Hash}}(u||v)~mod~2^{31}  
+\end{equation} %FIXME: does this mean this value be negative?
 where $||$ is the concatenation operator.
-In our preliminary experiments, we have tried a set of hash algorithms.
-After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
-Although the approach mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities.
-First, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated to enable this for each edge.
-Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: To do this, the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
+In our preliminary experiments, we have tried a set of hash algorithms and found that {\sc Crc32}~\cite{koopman200232} and {{\sc Murmur3}} are good candidates for {\sc Hash}.
+{{\sc Murmur3}} was slightly faster than {\sc Crc32} with better randomness properties.
+After a preliminary analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
+An  important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory.
+To mitigate its overhead, using $\Theta(|E|)$ more memory, we precompute and memoize the hash values (and read them when we need them).
+We have also tried recomputing the hash values every time they are needed; this incurred around $5\%$ slowdown.
+Since {\acro} is designed for multi-core servers, extra $\Theta(|E|)$ memory is a practical overhead.
+However, considering its low overhead, the recomputation strategy can be promising for memory-restricted accelerators and devices such as GPUs.
+
+Although the $h(.)$ function described above generates a unique hash value for each edge, and hence can be used to generate a unique sampling probability, different simulations require different probabilities.
+To enable this, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated for each edge.
+Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
 Formally,
@@
 The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
-One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation.
+One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation which is crucial since \acro{} recomputes this probability value each time the corresponding edge is read from the memory.
+In practice, we do not apply the division operation since $h_{max}$ is a constant value and the same for every edge and simulation.
 Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.
@@
     \centering
-    \includegraphics[width=1\linewidth]{./images/CDF.pdf}
+    \includegraphics[width=0.8\linewidth]{./images/CDF.pdf}
     \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
@@
 Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
-This property allows us to generate good enough pseudo-random values for fair sampling.
-To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and plotted the cumulative distribution~(Fig.~\ref{fig:prob-cdf}) and the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}).
-As the former shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution.
-Furthermore, the latter shows that the bias is insignificant for each network.
-
-\begin{figure}[!ht] 
-    \centering
-    \includegraphics[width=1\linewidth]{./images/bias.pdf}
-    \caption{\small{Bias distribution of hash-based sampling probabilities on various real-life networks.}}
-    \label{fig:prob-bias} 
-\end{figure}
+This property allows us to generate good-enough pseudo-random values for fair sampling.
+To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and plotted the cumulative distribution.
+% and the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}). 
+As Figure~\ref{fig:prob-cdf} shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution. 
+% Furthermore, the latter shows that the bias is insignificant for each network.
+
+% \begin{figure}[!ht] 
+%     \centering
+%     \includegraphics[width=1\linewidth]{./images/bias.pdf}
+%     \caption{\small{Bias distribution of hash-based sampling probabilities on various real-life networks.}}
+%     \label{fig:prob-bias} 
+% \end{figure}
 
@@
 %Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-Being able to generate the samples on the fly allows us to avoid many memory accesses.
-The only downside of hash-based fused sampling is that we have to generate all these random values,   $P(u,v)_r$, for each edge traversal and each simulation $r$.
-The edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains.
-Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware.
+%Being able to generate the samples on the fly allows us to avoid many memory accesses. 
+One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$.
+As mentioned above, the edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains.
+%Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware.
 %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
@@
 \subsection{Estimating Reachability Set Cardinality}
-A greedy solution to the influence maximization problem requires finding a vertex that maximizes the marginal influence gain at each step until the seed set size reaches $K$.
-For an exact computation, one must find all candidate vertices' reachability sets within all the samples.
-Such a task involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}.
-The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs, as explained above.
-Hence, in this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
-In this work, we propose an efficient and effective IM kernel, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
-Algorithm~\ref{algo:main} shows the steps taken by the kernel.
+A greedy solution to IM requires finding a vertex with a maximum marginal influence at each step until the seed set size reaches $K$.
+An exact computation of marginal influences, i.e., the additional influence when a vertex $v$ is added to the seed set, requires the computation of all candidate vertices' reachability sets within all the samples.
+This involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}.
+%The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs, as explained above.
+Hence,
+In this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
+Here we propose an efficient and effective IM algorithm, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
+Algorithm~\ref{algo:main} shows the steps taken by \acro.
 
@@
     \begin{center}
-    \includegraphics[width=0.7\linewidth]{images/sketch-diffusion.pdf}
+    \includegraphics[width=0.85\linewidth]{images/sketch-diffusion.pdf}
     \caption{\small{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes.
@@
 The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations one-by-one and computes the vertices' reachability sets.
-On the other hand, \acro efficiently performs multiple simulations at once in a single-step iteration.
+On the other hand, \acro efficiently performs multiple simulations at once in a single-step iteration (which processes distance-1 neighborhoods).
 Since each iteration relays one level of cardinality information, this step requires at most $d$ iterations where $d$ is the diameter of $G$.
-When processed individually as the Greedy algorithm does, the $j$th simulation over the sampled subgraph $G_j$ would require only at most $d_j$ iterations, which is the diameter of $G_j$, and probably much smaller than $d$.
-Although \acro seems to perform much more iterations, $d$ is a loose upper bound for \acro.
-A better one is {\tt max}$\{d_j: 1 \leq j \leq {\cal J}\}$ where $d_j$ is the diameter of $G_j$.
-To further reduce the overhead of concurrent simulations and avoid bottleneck simulations due to remaining perimeter vertices, we employ an early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two simulations remain.
+Note that when processed individually (as the Greedy algorithm), the $j$th simulation over the sampled subgraph $G_j$ would require only at most $d_j$ iterations, which is the diameter of $G_j$, and probably much smaller than $d$ considering the sampled subgraphs being highly sparse.
+However, $d$ is also a loose upper bound for \acro.
+A better one is {\tt max}$\{d_j: 1 \leq j \leq {\cal J}\} + 1$ where $d_j$ is the diameter of $G_j$.
+We have observed that during these simulations later iterations have only a minor impact on the marginal influence scores.
+Hence, to further reduce the overhead of concurrent simulation processing and avoid bottleneck simulations due to remaining perimeter structures (e.g., paths on the perimeter), we employ an early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two (bottleneck) simulations remain.
 That is if $|L'| \leq |V| \times \epsilon_c$ the diffusion process in Algorithm~\ref{algo:diffusion-step} stops.
@@
 After the diffusion process, the following steps are repeated until $K$ vertices are added to the seed set $S$.
-First, for each $v \in V$, the cardinality of the reachability set, $R_G(S \cup v)$, is estimated by merging $M_{S'}$ and $v$'s sketch registers where $M_{S'}$ is the set of sketch registers for the seed set $S$ used to estimate the number of already influenced vertices by $S$.\footnote{In fact, the definition is exact only if sketch rebuilding is disabled.
+First, for each $v \in V$, the cardinality of the reachability set, $R_G(S \cup \{v\})$, is estimated by merging $M_{S'}$ and $v$'s sketch registers where $M_{S'}$ is the set of sketch registers for the seed set $S$ used to estimate the number of already influenced vertices by $S$\footnote{In fact, the definition is exact only if the error-adaptive, smart sketch rebuilding is disabled.
 As it will be described in the following subsection, when \acro's error-adaptive mechanism is enabled, $M_{S'}$ is periodically rebuilt to estimate the cardinality of reachability sets over the remaining, unblocked vertices.
-This is why $S'$ is used instead of $S$.} Before the kernel, these registers are initialized with zeros.
+This is why $S'$ is used instead of $S$.}.
+Before the kernel, these registers are initialized with zeros.
 Second, a vertex $s$ with the maximum cardinality estimation is selected and added to $S$.
@@
 Our preliminary experiments revealed that sketches are highly competent at finding the first few seed vertices for influence maximization.
-Unfortunately, after a few seed vertices, the sketch registers $M_{S'}$, which are updated at line~\ref{line:if} of Algorithm~\ref{algo:main} via merging with new seed vertex $s$'s reachability set, become large.
+Unfortunately, after a few seed vertices, the values inside the sketch registers $M_{S'}$, which are updated at line~\ref{line:if} of Algorithm~\ref{algo:main} via merging with new seed vertex $s$'s reachability set, become large.
 The saturation of $M_{S'}$ registers is important since \acro uses them to select the best seed candidate at line~\ref{line:estimate}.
@@
     \begin{center}
-    \includegraphics[width=0.93\linewidth]{images/sketch-saturation.pdf}
-    \caption{ Effect of register saturation on Amazon dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
+    \includegraphics[width=0.73\linewidth]{images/sketch-saturation.pdf}
+    \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
 %\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
@@
 
-\begin{figure*}[!ht]
-    \begin{center}
-        \subfloat[{\tt LiveJournal} execution time in seconds\label{fig:lj-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
-    }
-    \subfloat[{\tt Orkut} execution time in seconds\label{fig:orkut-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
-        }
-    \subfloat[{\tt Pokec} execution time in seconds\label{fig:pokec-time}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
-        }\\
-        \subfloat[{\tt LiveJournal} influence score\label{fig:lj-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
-        }
-    \subfloat[{\tt Orkut} influence score\label{fig:orkut-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
-        }
-    \subfloat[{\tt Pokec} influence score\label{fig:pokec-score}]{%
-        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
-        }\\
-    \end{center}
-    \caption{Effect of $\epsilon$ parameters on \acro(${\cal J} = 256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
-\end{figure*}    
+% \begin{figure*}[!ht]
+%     \begin{center}
+%         \subfloat[{\tt LiveJournal} execution time in seconds\label{fig:lj-time}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_time.pdf}
+%     }
+%     \subfloat[{\tt Orkut} execution time in seconds\label{fig:Orkut-time}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_time.pdf}
+%         }
+%     \subfloat[{\tt Pokec} execution time in seconds\label{fig:Pokec-time}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_time.pdf}
+%         }\\
+%         \subfloat[{\tt LiveJournal} influence score\label{fig:lj-score}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_score.pdf}
+%         }
+%     \subfloat[{\tt Orkut} influence score\label{fig:Orkut-score}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_score.pdf}
+%         }
+%     \subfloat[{\tt Pokec} influence score\label{fig:Pokec-score}]{%
+%         \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_score.pdf}
+%         }\\
+%     \end{center}
+%     \caption{Effect of $\epsilon$ parameters on \acro(${\cal J} = 256$, $\epsilon_c=0.02$) performance, using $\tau=16$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
+% \end{figure*}    
 %\begin{figure}[ht] 
@@
 Note that $e$, computed at line~\ref{line:e} is the sketch estimate for this value.
-\acro computes the local estimation error $err_l = |(e-\delta) / \delta|$ and the global error threshold $err_g=|(e-\delta) / \sigma|$.
+\acro computes the local estimation error $err_l = |(e-\delta) / \delta|$ and the global error $err_g=|(e-\delta) / \sigma|$.
 The sketches are assumed to be fresh if
-the local estimation error $err_l$ is smaller than a local threshold $\epsilon_{l}$ or the global error threshold $err_g=|(e-\delta) / \sigma|$ is smaller than a global threshold $\epsilon_{g}$.
+the local estimation error $err_l$ is smaller than a local threshold $\epsilon_{l}$ or the global error $err_g=|(e-\delta) / \sigma|$ is smaller than a global threshold $\epsilon_{g}$.
 
@@
 
+\begin{figure*}[!ht]
+    \begin{center}
+        \subfloat[{\tt LiveJournal} execution time in seconds\label{fig:lj-time}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_time.pdf}
+    }
+        \subfloat[{\tt LiveJournal} influence score\label{fig:lj-score}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_score.pdf}
+        }\\
+
+    \subfloat[{\tt Orkut} execution time in seconds\label{fig:Orkut-time}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_time.pdf}
+        }
+    \subfloat[{\tt Orkut} influence score\label{fig:Orkut-score}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_score.pdf}
+        }\\
+    \subfloat[{\tt Pokec} execution time in seconds\label{fig:Pokec-time}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_time.pdf}
+        }
+    \subfloat[{\tt Pokec} influence score\label{fig:Pokec-score}]{%
+        \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_score.pdf}
+        }
+    \end{center}
+    \caption{Effect of $\epsilon$ parameters on \acro(${\cal J} = 256$, $\epsilon_c=0.02$) performance, using $\tau=16$ threads. Lighter shades are better. }\label{fig:parameter-smallmultiples} 
+\end{figure*}
+
 The use of two different, local and global, thresholds allows the algorithm to rebuild the sketches after significant local errors and skip this expensive process if the estimation error is insignificant compared to the total influence.
@@
 Hence, the selected threshold values, $\epsilon_{l}$ and $\epsilon_{g}$, have a significant impact on the performance.
-Setting $\epsilon_{l} = \epsilon_{g} = 0$ means that the algorithm always rebuilds.
+In the setting $\epsilon_{l} = \epsilon_{g} = 0$, the algorithm always rebuilds.
 Conversely, setting $\epsilon_l = \epsilon_{g} = \infty$ will make \acro fast since sketches are built only once.
@@
 
+\subsection{Correctness of \acro{}} 
+The greedy solution for influence maximization is well studied and proven to be correct~\cite{kempe2003maximizing}.
+\acro uses the same optimization method but replaces reachability set computations with sketches instead of per-vertex graph traversal and labeling.
+Since only the reachability set computations are different, we will comment on the correctness of the sketches used.
+
+Flajolet-Martin sketches processes elements in a stream to estimate distinct elements observed; for reachability set computations, instead of a stream, we process a spanning tree on the sampled graph.
+Instead of adding the elements one by one, sketches that are connected is merged.
+This operation is identical to processing a spanning-tree in a sampled subgraph in parallel.
+The FM sketches used only store the maximum leading zero counts which are merged by taking the maximum of two where the {\tt max} operation is associative.
+\acro processes one level of depth at each iteration, and the maximum value observed is updated for each vertex.
+Assume that we have a toy graph with 3 edges, ($a\to b, a \to c, c \to d$); a sequential traversal  observes $a$, $b$, $c$, $d$ in order so $M[a] = max(max(max(a, b), c), d)$.
+On the other hand, our method pulls values from incoming edges $M[a] = max(max(a,b), max(c,d))$.
+Both methods produce the same results; $M[a] =max(max(max(a, b), c), d)=max(max(a,b), max(c,d))$.
+
+\subsection{Runtime Analysis}\label{sec:runtime}
+
+The seed selection process requires $K$ iterations to select $K$ seed vertices.
+For a single iteration, we have multiple steps each processing a single depth of information, e.g., neighborhood.
+The propagation process is actually a reverse influence process that starts with whole graph as frontier and diffuses register values with respect to the sample graphs.
+In the worst case, i.e., assuming all edges are processed and all the sketch registers are updated at each step, each iteration of the seed-set construction has ${\mathcal O}(d \times (|V|\times \mathcal{J} + |E|))$ time complexity where $d$ is the diameter of $G$ which is the number of steps at each iteration.
+However, on average, a single iteration of \acro performs much faster.
+First, as explained above, $d$ is a loose upper bound on the number of steps.
+Second, since only the recently updated registers are propagated to the next step, and only the edges in a sample are processed, a small fraction of the graph is processed for each step.
+Last, the complexity reduces for later iterations, since the nodes and their edges, which are already covered by the reachability set of the current seed set, are not processed.
+
+These analysis and observations tell us that when the probability of being influenced, i.e., the average probability of an edge being in a sampled subgraph, is high, the samples will be denser and hence, the actual number of steps \acro performs will be smaller.
+Furthermore, depending on the topology of $G$, the marginal influence scores of the first few vertices can be much higher with larger probability values and adding these vertices to the seed set will leave less number of vertices to be processed for later iterations.
+On the other hand, increasing the influence probabilities also increase the number of edges to be processed on the samples.
+Note that other factors that has an impact on the overall performance exist such as the number of iterations skipping the sketch rebuilding.
+This also depends on $G$'s structure as well as the influence probabilities.
+Still, as the experiments also will show, \acro's execution time tends to decrease for many graphs when the influence probabilities increase.
+
+%
+
+% \begin{equation}
+%  sketch-union-chance for \alpha-bit sketch = \frac{1}{2^{\alpha+1}}  \frac{2^{\alpha}-1}{2^\alpha}
+% \end{equation}
+
+% \begin{equation}
+%     \label{eq:activeverts}
+%     \begin{array}{l}
+%     A_0 = N\\
+%     A_t = \(\sum_{v \in V}^{} 1-(1-(0.32*A_{t-1}/N)^{p|\Gamma(v)|} \)\\
+%     % \mathcal{O}(max(\Gamma({A_t}), TN))
+%     \end{array}
+% \end{equation}
+
+% Sum[Divide[1,\(40)Power[2,\(40)a+1\(41)]\(41)]Divide[Power[2,a]-1,Power[2,a]],{a,0,6}]
+
+\subsection{Approximation Ratio of \acro}
+
+The influence function is non-negative, monotone, and sub-modular; hence, adding a single vertex to the current seed set can only increase the overall influence and decreases the marginal influence scores for the remaining vertices that are not in the set.
+A greedy solution of final size $K$ is at least $1-(1-1/K)^K \approx 63.5\%$ of the optimal solution~\cite{nemhauser1978analysis}.
+Since it uses sketches, \acro's approximation guarantee is not straightforward to derive.
+This being said, based on the average approximation performance of the sketches, we can argue the following.
+\acro is a greedy algorithm; vertices with a maximum reachability which is estimated via sketches.
+At each iteration, \acro can choose a vertex worse than the local optimum due to its estimation errors.
+Since the standard error for the FM sketch is $~1.30/\sqrt{\mathcal{J}}$~\cite{durand2003loglog}, we can expect $(1-1.3/\sqrt{256}) \times (1-(1-1/50)^{50}) \approx 58.4\%$ of the optimal solution for $K = 50$ and $\mathcal{J} = 256$.
+However, as the greedy algorithm, the practical performance is better.
+Furthermore, the mistakes in previous iterations can be rectified in later iterations due to submodularity.
+
 \subsection{Implementation Details}
@@
 To efficiently process real-life graphs, \acro uses the Compressed Sparse Row~(CSR) graph data structure.
-In CSR, an array, $xadj$, holds the starting indices of the adjacency lists for each vertex, while another array, $adj$, holds the actual adjacency lists (i.e., the outgoing neighbors) one after another.
-Hence, the adjacency list of vertex $i$ is located in $adj$ at locations $adj[index[i], \ldots, index[i+1] - 1]$.
+In CSR, an array, $ptrs$, holds the starting indices of the adjacency lists for each vertex, while another array, $adj$, holds the actual adjacency lists (i.e., the outgoing neighbors) one after another.
+Hence, the adjacency list of vertex $i$ is located in $adj$ at locations $adj[ptrs[i], \ldots, ptrs[i+1] - 1]$.
 
@@
 %Vectorization also reduces branching on the overall computation; When vectorized, many comparison operations are done without branching. 
-
-%We allow a single easy-to-predict branch after sample edges are generated to exit early without merging the registers.
-In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together.
-Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non taken edges are sampled together.
-Up to 20\% speed-up can be achieved by an early exit at line \ref{ln:early_exit} using sorted random values.
-
+%%%%%%%%%%%%%%%NEW
+
+We allow a single easy-to-predict branch after the sample edges are generated to exit early without merging the registers.
+In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together while preserving branch locality.
+Since sorted random values are XOR'ed with the same edge hash values, it is more likely to non-taken edges are sampled together.
+For example, the naive approach has only $13\%$ vector units filled while processing Amazon dataset with $0.01$ edge probabilities.
+Sorting the $X_r$ values increases the fill rate  $32\%$.
+This shows that, the early-exit branch is taken $2.4\times$ more, reducing the total number of arithmetic operations from $23$ to $9$ per edge traversal.
+
+% Up to 20\% speed-up can be achieved by an early exit at line \ref{ln:early_exit} using sorted random values.   
+Multi-thread parallelization is achieved using OpenMP pragmas; the sketch computation and Monte-Carlo simulations are performed in per-vertex tasks.
+This approach allow us to preserve both temporal and spatial locality.
+The OpenMP tasks are distributed to the threads via dynamic scheduling with large enough chunks~(8192) to mitigate scheduling costs.
+Even though dynamic scheduling has a higher cost than the static scheduling, it is preferable due to uneven edge distribution among the vertices of $G$ (as well as of the sampled subgraphs).
+
+\acro computes the actual influence via an iterative processing of the vertices' neighborhoods starting with a queue containing the seed set.
+This approach allows multiple threads to process different vertices at the same time.
+The visited vertices are labeled in parallel without any synchronization since the operations are idempotent, and they can be done simultaneously in any order.
+In addition, we utilize SIMD vectors to process multiple samples simultaneously for each thread.
+This approach is wasteful for small influence graphs, but the error-adaptive rebuilding strategy allows us to mitigate the cost in such conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%NEW END
 \section{Experimental Results}\label{sec:evaluation}
-We performed the experiments on a server with an 18-core {\tt Intel Xeon Gold 6140}, running at 2.3Ghz, and 250GB memory.
-The Operating System on the server is {\tt Ubuntu 16.04 LTS} with 5.4.0-48 kernel.
-The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.2.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
+We performed the experiments on a server with an 16-core {\tt Intel Xeon E5-2620 v4} CPU, running at 2.10GHz, and 192GB memory.
+The Operating System on the server is {\tt Ubuntu 20.04.2 LTS} with  5.4.0-65 kernel.
+The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.3.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
 Multi-thread parallelization was achieved with {\tt OpenMP} pragmas.
@@
 \centering
-\scalebox{0.95}{
+% \scalebox{0.95}{
+\resizebox{0.75\columnwidth}{!}{
 \begin{tabular}{ll||r|r|r|r}
-& & No. of           & No. of    & Avg.  &  Avg.  \\
-&Dataset & Vertices          & Edges     &    Weight         &  Degree               \\
+& & No. of           & No. of    & Avg.  & Diameter\\
+&Dataset & Vertices          & Edges           &  Degree               \\
 \hline
-\multirow{6}{*}{\rotatebox[origin=c]{90}{Undirected}}& {\tt Amazon} & 262,113 & 1,234,878 & 1.00 & 4.71 \\
-&{\tt DBLP} & 317,081 & 1,049,867 & 1.00 & 3.31 \\
-&{\tt NetHEP} & 15,235 & 58,892 & 1.83 & 3.87 \\
-&{\tt NetPhy} & 37,151 & 231,508 & 1.28 & 6.23 \\
-&{\tt Orkut} & 3,072,441 & 117,185,083 & 1.00 & 38.14 \\
-&{\tt Youtube} & 1,134,891 & 2,987,625 & 1.00 & 2.63 \\
+\multirow{3}{*}{\rotatebox[origin=c]{90}{Undirected}}& {\tt Amazon0302} & 262,113 & 1,234,878 & 4.71 & 32\\
+&{\tt DBLP} & 317,081 & 1,049,867  & 3.31 & 21\\
+% &{\tt NetHEP} & 15,235 & 58,892 & 1.83 & 3.87 \\
+% &{\tt NetPhy} & 37,151 & 231,508 & 1.28 & 6.23 \\
+&{\tt Orkut} & 3,072,441 & 117,185,083& 38.14 & 9\\
+&{\tt Youtube} & 1,134,891 & 2,987,625  & 2.63 & 20\\
 
 \hline
-\multirow{6}{*}{\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838 & 1.00 & 6.71 \\
-&{\tt LiveJournal} & 4,847,571 & 68,993,773 & 1.00 & 14.23 \\
-&{\tt Pokec} & 1,632,803 & 30,622,564 & 1.00 & 18.75 \\
-&{\tt Slashdot0811} & 77,360 & 905,468 & 1.00 & 11.70 \\
-&{\tt Slashdot0902} & 82,168 & 948,464 & 1.00 & 11.54 \\
-&{\tt Twitter} & 81,306 & 2,420,766 & 1.37 & 29.77 
+\multirow{6}{*}{\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838  & 6.71 & 14\\
+&{\tt Friendster} & 65,608,366 & 1,806,067,135  & 27.53 & 32\\
+&{\tt LiveJournal} & 4,847,571 & 68,993,773  & 14.23 & 16\\
+&{\tt Pokec} & 1,632,803 & 30,622,564  & 18.75 & 11\\
+&{\tt Slashdot0811} & 77,360 & 905,468  & 11.70 & 10\\
+&{\tt Slashdot0902} & 82,168 & 948,464  & 11.54 & 11\\
+% &{\tt Twitter} & 81,306 & 2,420,766 & 1.37 & 29.77 
 \end{tabular}
@@
 \end{table}
-\subsection{Experiment Settings}
-
-We performed the experiments on twelve graphs~(six undirected, six directed).
+\FloatBarrier
+\subsection{Experiment Settings} \label{sec:expset}
+
+We performed the experiments on ten graphs~(four undirected, six directed).
 For comparability, graphs that have been frequently used within the Influence Maximization literature are selected.
-These graphs are {\tt Amazon} co-purchase network~\cite{snapnets}, {\tt DBLP} co-laboration network~\cite{snapnets}, {\tt Epinions} consumer review trust network, {\tt LiveJournal}~\cite{snapnets}, {\tt NetHEP} citation network~\cite{MixGreedy}, {\tt NetPhy} citation network~\cite{MixGreedy}, {\tt Orkut}~\cite{snapnets}, {\tt Pokec} Slovakian poker game site friend network~\cite{snapnets}, {\tt Slashdot} friend-foe networks~(08-11, 09-11)~\cite{snapnets}, {\tt Twitter} list co-occurence network~\cite{snapnets}, and {\tt Youtube} friendship network~\cite{snapnets}.
-The properties of these graphs are given in Table~\ref{tab:NetProps}.
-
-Three diffusion settings are simulated for a comprehensive experimental evaluation; for each network, we use 
+The properties of these graphs are given in Table~\ref{tab:NetProps}:  {\tt Amazon0302} is an Amazon co-purchase network, {\tt DBLP} is DBLP collaboration network, {\tt Orkut} is an online social network where users form friendship,  {\tt Youtube} is a video social video sharing platform that allows friendship relations, {\tt Epinions} is a consumer review trust network, {\tt Friendster} is a social gaming website where users can form friendship edge each other, {\tt LiveJournal} is a blogging site that allows users to add friends, {\tt Pokec} is the Slovakian poker game site friend network, and {\tt Slashdot} networks are friend-foe networks~(08-11, 09-11).
+
+Five diffusion settings are simulated for a comprehensive experimental evaluation; for each network, we use 
 \begin{enumerate}
+  \setlength{\itemsep}{0.2pt}
+  \setlength{\parskip}{0pt}
+  \setlength{\parsep}{0pt}
     \item constant edge weights $w = 0.005$,
@@
     \item constant edge weights $w = 0.1$~(as in~\cite{kempe2003maximizing}),
+    \item normally distributed edge weights $w \in N(0.05,0.025)$,
+    \item uniform distributed edge weights $w \in U(0,0.1)$.
     % \item weighted cascade edge weights $w_{u,v} = 1/|\Gamma(v)|$.
@@
 
-We selected $w=0.005$ as a benchmark-setting to challenge \acro.
-Due to its diffusion algorithm's nature, \acro traverses vertices even if they are blocked, which happens faster when the graph is sparser.
-Also, for each live vertex, \acro processes the sample edges for all simulations.
-The other two settings are selected to emulate the experiments of~\cite{kempe2003maximizing} and~\cite{MixGreedy}.
+\noindent We selected $w=0.005$ as a setting to challenge \acro.
+As explained in Section~\ref{sec:runtime}, due to the nature of its diffusion algorithm, \acro is expected to perform slower on sparser samples.
+The later two settings, i.e., $w = 0.01$  and $w = 0.1$, are selected to emulate the experiments of~\cite{kempe2003maximizing} and~\cite{MixGreedy}.
+In addition to constant edge weights, we performed experiments on two different statistical distributed edge weights to test how algorithms behave on mixed (large and small edge weights together) edge weights.
+The normal distribution setting incurs a small number of extreme sketch values and uniform distribution setting incurs a large number of large sketch values.
 
@@
 All the methods we benchmarked exclude the time spent on reading files and preprocessing.
-We only left out the time to spend on reading files for \acro.
-We allowed all methods to utilize all the CPU cores in all benchmarks, except {\sc Tim+}, a single-threaded algorithm.
+%We only left out the time to spend on reading files for \acro.
+We allowed all methods to utilize the given number of CPU cores in all benchmarks, except {\sc Tim+}, which is a single-threaded algorithm.
 The memory use reported in this paper is the {\em maximum resident set sizes}~(RSS), which are measured using GNU {\tt time} command.
@@
 Since the algorithms may use different methods to measure the influence, the reported influence scores may not be suitable for comparison purposes with high precision.
-Due to this reason, we implemented an oracle with a straightforward, sample-then-diffuse algorithm without any optimization mentioned.
+Due to this reason, we implemented an independent oracle with a straightforward, sample-then-diffuse algorithm without any optimizations.
 For sampling, the random values are generated by the 32-bit Mersenne Twister pseudo-random generator {\tt mt19937} from {\tt C++} standard library.
-The same independent oracle obtains all influence scores in this paper.
+This algorithm-independent oracle obtains all the influence scores in this paper.
 
@@
 
-We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, and {\sc Imm}.
+We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, {\sc Imm}, and {\sc Ssa}.
 The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account.
-The third one is an approximation algorithm with a parameter to control the influence quality.
+The third one is a scalable, parallel approximation algorithm with a parameter to control the influence quality, and the last one leverages a Stop-and-Stare strategy.
 
@@
 The algorithm has a parameter $\epsilon$ which allows a trade-off between the seed set quality and execution time.
-In our experiments, we set  $\epsilon=0.3$ to have a high-quality influence maximization baseline.
-We also experimented with $\epsilon = 1.0$ as suggested, which gives around $7\times$ speedup on average but a reduction on the influence score up to $6\%$.
+In our experiments, we set  $\epsilon=0.2$ to have a high-quality influence maximization baseline as suggested by the software.
+We also experimented with $\epsilon = 1.0$ as authors' suggested, which gives around $8\times$ speedup on average but a reduction on the influence score up to $9\%$.
 
@@
 The implementation (from the authors) is partially parallelized and leverages multicore processors.
+However, it  assumes a constant $w$ value; hence, we only used {\sc Skim} for the first three settings given in Section~\ref{sec:expset}.
 
@@
 We have used $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined parameter to control the approximation boundaries.
+
+\item Nguyen et al.
+proposed {\sc Ssa} and {\sc D-Ssa}~\cite{nguyen2016stop}, two novel sampling approaches for Influence Maximization problem.
+{\sc Ssa} and its dynamic network variant {\sc D-Ssa} are fast methods compared to previously mentioned approaches while providing similar approximation guarantees.
+The approach employs a novel Stop-and-Stare strategy.
+It stops at exponential checkpoints to verify (stare) if there is adequate statistical evidence on the solution quality.
+We used {\sc Ssa} for our benchmarks since our networks are static.
+
 \end{itemize}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.005$.
-Influence scores are given relative to \acro{}.
-The runs that did not finish due to high memory use shown as "-".
-    % \kktodo{need to explain why we have a - for some graphs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.005$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.005}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrrr|rrrrrr|rrrrrr}
+% \toprule
+% {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+% R &        256 &     512 &    0.2 &    0.5 &   64-64 &     0.1 &        256 &        512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &  0.5 &  64-64 &  0.1 \\
+% Dataset                 &            &         &        &        &         &         &            &            &         &         &         &         &            &        &       &      &        &      \\
+% \midrule
+% \tt{Amazon0302}              &       2.18 &    3.99 & 295.32 &  64.45 &   12.69 &   11.40 &      96.19 &       99.1 &  1.023x &  0.998x &  0.557x &  0.988x &       0.10 &   0.18 & 45.03 & 1.01 &   1.51 & 1.35 \\
+% \tt{DBLP}                &       2.92 &    4.39 & 480.22 &  64.91 &   13.18 &   28.40 &     107.86 &      111.7 &  1.017x &  0.967x &  0.977x &  0.996x &       0.16 &   0.27 & 66.98 & 1.05 &   1.38 & 2.68 \\
+% \tt{Friendster}          &    1088.25 & 1775.58 &      - &      - & 4055.92 &       - & 4942827.00 &  4942856.5 &       - &       - &  1.000x &       - &      88.94 & 122.42 &     - &    - & 112.33 &    - \\
+% \tt{Orkut}               &      39.38 &   69.93 &      - & 253.44 &   49.02 & 1245.28 &  158915.22 &   158994.0 &       - &  0.997x &  1.001x &  0.995x &       4.36 &   5.18 &     - & 7.97 &   1.77 & 5.81 \\
+% \tt{Youtube}             &       5.40 &    7.59 &  82.08 &  63.71 &    5.67 &    3.76 &    1827.39 &     1834.4 &  1.023x &  1.010x &  1.005x &  1.009x &       0.42 &   0.73 &  7.41 & 0.63 &   0.53 & 0.37 \\
+% \tt{Epinions}           &       1.79 &    2.84 &  13.61 &  47.93 &    1.86 &    0.58 &     238.65 &      241.7 &  1.009x &  0.973x &  0.986x &  0.965x &       0.03 &   0.05 &  3.70 & 0.24 &   0.17 & 0.10 \\
+% \tt{LiveJournal}        &      15.02 &   26.13 & 684.52 &  74.62 &   22.28 &   16.98 &    5559.85 &     5748.5 &  1.030x &  1.015x &  1.005x &  1.006x &       2.40 &   3.70 & 17.06 & 2.19 &   2.05 & 1.38 \\
+% \tt{Pokec} &      13.21 &   21.63 & 312.19 &  78.59 &   23.19 &   16.85 &     588.87 &      594.2 &  1.012x &  0.985x &  0.984x &  0.978x &       0.92 &   1.36 & 33.18 & 1.80 &   1.78 & 1.09 \\
+% \tt{Slashdot0811}        &       2.02 &    3.64 &  12.83 &  38.49 &    1.34 &    1.02 &     326.32 &      328.1 &  1.017x &  1.000x &  0.987x &  0.989x &       0.04 &   0.06 &  2.47 & 0.20 &   0.13 & 0.10 \\
+% \tt{Slashdot0902}        &       1.86 &    3.10 &  14.87 &  38.17 &    1.41 &    0.47 &     338.85 &      341.5 &  1.017x &  0.987x &  0.992x &  0.978x &       0.04 &   0.06 &  2.66 & 0.21 &   0.13 & 0.06 \\
+% \bottomrule
+
+% Avg. Perf.&0.61x&1.00x&31.00x&9.91x&1.33x&3.30x&0.99x&1.00x&1.02x&0.99x&0.95x&0.99x&0.66x&1.00x&87.14x&2.79x&2.50x&2.78x \\
+% Max. Perf.&0.71x&1.00x&109.39x&16.88x&3.18x&17.81x&1.00x&1.00x&1.03x&1.02x&1.01x&1.01x&0.84x&1.00x&257.27x&5.76x&8.64x&9.93x \\
+% Geo. Mean&0.61x&1.00x&15.09x&8.19x&1.01x&0.96x&0.99x&1.00x&1.02x&0.99x&0.94x&0.99x&0.65x&1.00x&41.46x&2.19x&1.59x&1.51x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.01$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.01}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrrr|rrrrrr|rrrrrr}
+% \toprule
+% {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% R &        256 &     512 &     0.2 &    0.5 &   64-64 &     0.1 &         256 &         512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &   0.5 & 64-64 &   0.1 \\
+% Dataset                 &            &         &         &        &         &         &             &             &         &         &         &         &            &        &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.62 &    2.74 &  211.25 &  52.76 &   12.48 &    7.33 &      155.81 &       156.8 &  1.009x &  0.978x &  0.393x &  0.991x &       0.10 &   0.18 & 35.22 &  0.67 &  1.43 &  0.70 \\
+% \tt{DBLP}                &       2.03 &    2.05 &  145.54 &  59.23 &    7.36 &   13.95 &      232.12 &       234.7 &  1.027x &  1.002x &  0.978x &  1.006x &       0.16 &   0.27 & 24.53 &  0.61 &  0.82 &  1.38 \\
+% \tt{Friendster}          &     902.78 & 1334.65 &       - &      - & 2641.58 &       - & 11504743.00 &  11504801.0 &       - &       - &  1.000x &       - &      88.94 & 122.42 &     - &     - & 78.17 &     - \\
+% \tt{Orkut}               &      46.63 &   73.82 &       - & 606.07 &  125.15 & 5613.07 &   650214.62 &    650243.1 &       - &  1.000x &  1.000x &  1.000x &       4.36 &   5.18 &     - & 20.48 &  3.33 & 27.19 \\
+% \tt{Youtube}             &       4.21 &    5.85 & 1056.41 &  50.45 &    8.50 &   19.82 &     9049.47 &      9072.9 &  1.010x &  0.994x &  1.006x &  0.983x &       0.42 &   0.73 & 14.15 &  0.62 &  0.73 &  0.41 \\
+% \tt{Epinions}           &       2.20 &    3.80 &   13.13 &  37.47 &    1.17 &    0.35 &      662.66 &       671.8 &  1.007x &  0.982x &  0.995x &  0.982x &       0.03 &   0.05 &  1.51 &  0.17 &  0.11 &  0.04 \\
+% \tt{LiveJournal}        &      21.32 &   34.07 &       - &  88.36 &   18.38 &  195.23 &    47272.62 &     47353.7 &       - &  0.995x &  0.999x &  0.990x &       2.40 &   3.70 &     - &  2.96 &  1.47 &  2.52 \\
+% \tt{Pokec} &      12.53 &   19.26 &  145.32 &  59.37 &    7.50 &    7.29 &     1843.17 &      1858.2 &  1.015x &  0.985x &  0.979x &  0.988x &       0.92 &   1.36 & 11.43 &  1.12 &  0.76 &  0.61 \\
+% \tt{Slashdot0811}        &       2.62 &    5.90 &   39.86 &  35.37 &    1.00 &    1.65 &     1181.84 &      1201.4 &  1.012x &  0.990x &  0.984x &  0.987x &       0.04 &   0.06 &  1.29 &  0.16 &  0.08 &  0.06 \\
+% \tt{Slashdot0902}        &       3.09 &    6.29 &   44.51 &  35.27 &    1.12 &    1.00 &     1299.36 &      1305.0 &  1.010x &  0.985x &  0.989x &  0.967x &       0.04 &   0.06 &  1.43 &  0.16 &  0.08 &  0.04 \\
+% \bottomrule
+
+% Avg. Perf.&0.64x&1.00x&50.50x&10.24x&1.49x&10.62x&0.99x&1.00x&1.01x&0.99x&0.93x&0.99x&0.66x&1.00x&56.05x&2.33x&1.91x&2.04x \\
+% Max. Perf.&0.99x&1.00x&180.58x&28.89x&4.56x&76.04x&1.00x&1.00x&1.03x&1.00x&1.01x&1.01x&0.84x&1.00x&201.20x&3.95x&8.19x&5.24x \\
+% Geo. Mean&0.63x&1.00x&19.89x&7.78x&0.83x&1.51x&0.99x&1.00x&1.01x&0.99x&0.90x&0.99x&0.65x&1.00x&32.82x&1.96x&1.23x&1.27x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrrr|rrrrrr|rrrrrr}
+% \toprule
+% {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% R &        256 &    512 &     0.2 &     0.5 &   64-64 &     0.1 &         256 &         512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &   0.5 & 64-64 &   0.1 \\
+% Dataset                 &            &        &         &         &         &         &             &             &         &         &         &         &            &        &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.75 &   2.47 &  297.11 &   46.78 &    4.86 &    6.65 &    12072.88 &     12268.8 &  0.991x &  0.973x &  0.786x &  0.941x &       0.10 &   0.18 & 11.26 &  0.37 &  0.54 &  0.20 \\
+% \tt{DBLP}                &       0.87 &   1.24 & 2903.95 &   45.21 &    3.84 &   55.24 &    48511.03 &     48528.0 &  1.001x &  0.993x &  1.001x &  0.991x &       0.16 &   0.27 & 69.72 &  1.18 &  0.27 &  1.10 \\
+% \tt{Friendster}          &     445.79 & 630.91 &       - &       - & 5660.24 &       - & 36995828.00 &  36995920.0 &       - &       - &  1.000x &       - &      88.94 & 122.42 &     - &     - & 90.95 &     - \\
+% \tt{Orkut}               &      16.69 &  24.47 &       - & 1148.06 &  490.06 &       - &  2692305.25 &   2692316.5 &       - &  1.000x &  1.000x &       - &       4.36 &   5.18 &     - & 71.76 & 10.08 &     - \\
+% \tt{Youtube}             &       1.84 &   2.57 &       - &   71.50 &   15.78 &  352.45 &   171338.61 &    171374.0 &       - &  0.999x &  1.001x &  0.999x &       0.42 &   0.73 &     - &  4.29 &  1.11 &  5.15 \\
+% \tt{Epinions}           &       0.44 &   0.73 &  436.89 &   34.37 &    2.12 &   16.03 &    10463.58 &     10463.0 &  1.004x &  0.996x &  1.004x &  0.995x &       0.03 &   0.05 & 14.77 &  0.37 &  0.18 &  0.36 \\
+% \tt{LiveJournal}        &      10.45 &  15.65 &       - &  553.49 &   71.03 &       - &  1683952.25 &   1685214.1 &       - &  0.998x &  1.001x &       - &       2.40 &   3.70 &     - & 46.07 &  1.35 &     - \\
+% \tt{Pokec} &       5.08 &   6.65 &       - &  255.79 &   37.06 & 3256.58 &   773994.19 &    774123.9 &       - &  0.999x &  1.001x &  0.999x &       0.92 &   1.36 &     - & 19.60 &  0.99 & 35.56 \\
+% \tt{Slashdot0811}        &       0.49 &   0.77 &  994.78 &   33.35 &    3.05 &   31.97 &    23198.49 &     23211.0 &  1.000x &  0.998x &  1.001x &  0.997x &       0.04 &   0.06 & 27.16 &  0.51 &  0.24 &  0.63 \\
+% \tt{Slashdot0902}        &       0.53 &   0.91 &  897.28 &   33.07 &    2.89 &   23.58 &    24282.60 &     24294.9 &  1.000x &  0.995x &  1.000x &  0.994x &       0.04 &   0.06 & 26.39 &  0.53 &  0.23 &  0.63 \\
+% \bottomrule
+
+% Avg. Perf.&0.68x&1.00x&1067.72x&36.74x&6.04x&109.07x&1.00x&1.00x&1.00x&0.99x&0.98x&0.99x&0.66x&1.00x&293.39x&8.56x&2.03x&9.34x \\
+% Max. Perf.&0.76x&1.00x&2341.90x&47.08x&20.03x&489.71x&1.00x&1.00x&1.00x&1.00x&1.00x&1.00x&0.84x&1.00x&451.59x&14.44x&4.01x&26.19x \\
+% Geo. Mean&0.67x&1.00x&735.18x&35.56x&4.78x&40.86x&1.00x&1.00x&1.00x&0.99x&0.98x&0.99x&0.65x&1.00x&243.98x&7.42x&1.56x&6.65x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w \in N(0.05,0.0025)$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timingsN0.05}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+% R &        256 &    512 &    0.2 &     0.5 &     0.1 &         256 &         512 &     0.2 &     0.5 &     0.1 &        256 &    512 &   0.2 &   0.5 &   0.1 \\
+% Dataset                 &            &        &        &         &         &             &             &         &         &         &            &        &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.29 &   1.78 &  27.01 &   43.25 &    1.18 &     1163.06 &      1166.8 &  1.007x &  0.994x &  0.970x &       0.10 &   0.18 &  2.71 &  0.26 &  0.09 \\
+% \tt{DBLP}                &       1.37 &   1.80 & 472.64 &   41.12 &   10.69 &     9907.50 &      9959.2 &  1.004x &  0.991x &  0.974x &       0.16 &   0.27 & 13.37 &  0.40 &  0.25 \\
+% \tt{Friendster}          &     507.40 & 693.26 &      - &       - &       - & 29459630.00 &  29459654.0 &       - &       - &       - &      88.94 & 122.42 &     - &     - &     - \\
+% \tt{Orkut}               &      20.35 &  31.09 &      - & 1158.88 &       - &  2323092.25 &   2323098.8 &       - &  1.000x &       - &       4.36 &   5.18 &     - & 62.48 &     - \\
+% \tt{Youtube}             &       1.99 &   2.81 &      - &   65.20 &  231.59 &    86502.31 &     86551.0 &       - &  0.998x &  0.998x &       0.42 &   0.73 &     - &  2.43 &  2.31 \\
+% \tt{Epinions}           &       0.78 &   1.16 & 273.44 &   37.02 &    8.23 &     5879.96 &      5880.4 &  1.006x &  0.987x &  0.985x &       0.03 &   0.05 &  7.92 &  0.27 &  0.20 \\
+% \tt{LiveJournal}        &      13.77 &  19.94 &      - &  402.54 &       - &   921589.50 &    921552.3 &       - &  0.997x &       - &       2.40 &   3.70 &     - & 26.52 &     - \\
+% \tt{Pokec} &       6.48 &   8.95 &      - &  186.87 & 1417.99 &   463128.94 &    463145.3 &       - &  0.998x &  0.998x &       0.92 &   1.36 &     - & 12.00 & 14.09 \\
+% \tt{Slashdot0811}        &       0.71 &   0.97 & 549.78 &   39.24 &   22.45 &    13947.56 &     13957.3 &  1.001x &  0.994x &  0.994x &       0.04 &   0.06 & 14.79 &  0.39 &  0.46 \\
+% \tt{Slashdot0902}        &       0.72 &   1.08 & 608.24 &   38.43 &   20.22 &    14532.23 &     14548.2 &  1.001x &  0.991x &  0.991x &       0.04 &   0.06 & 16.58 &  0.40 &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&0.71x&1.00x&328.69x&28.52x&42.35x&1.00x&1.00x&1.00x&0.99x&0.99x&0.66x&1.00x&144.08x&5.80x&4.78x \\
+% Max. Perf.&0.76x&1.00x&566.78x&40.46x&158.43x&1.00x&1.00x&1.01x&1.00x&1.00x&0.84x&1.00x&261.41x&12.05x&10.38x \\
+% Geo. Mean&0.71x&1.00x&197.41x&27.60x&14.84x&1.00x&1.00x&1.00x&0.99x&0.99x&0.65x&1.00x&93.93x&4.73x&3.17x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w \in U(0,0.1)$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         The runs that did not finish in 5 hours or due to high memory use shown as "-"
+%         }
+%         \label{tab:timingsU0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+% R &        256 &    512 &    0.2 &     0.5 &     0.1 &         256 &         512 &     0.2 &     0.5 &     0.1 &        256 &    512 &   0.2 &   0.5 &   0.1 \\
+% Dataset                 &            &        &        &         &         &             &             &         &         &         &            &        &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.35 &   1.79 &  24.34 &   43.84 &    1.16 &     1148.70 &      1149.3 &  1.014x &  0.996x &  0.971x &       0.10 &   0.18 &  2.74 &  0.27 &  0.09 \\
+% \tt{DBLP}                &       1.33 &   2.08 & 431.47 &   41.08 &   18.10 &     9863.24 &      9977.6 &  0.999x &  0.981x &  0.980x &       0.16 &   0.27 & 12.64 &  0.39 &  0.38 \\
+% \tt{Friendster}          &     479.16 & 720.54 &      - &       - &       - & 29411772.00 &  29411858.0 &       - &       - &       - &      88.94 & 122.42 &     - &     - &     - \\
+% \tt{Orkut}               &      20.98 &  31.93 &      - & 1163.91 &       - &  2320279.50 &   2320295.5 &       - &  1.000x &       - &       4.36 &   5.18 &     - & 62.30 &     - \\
+% \tt{Youtube}             &       1.97 &   2.76 &      - &   64.23 &  152.21 &    86122.30 &     86140.3 &       - &  0.998x &  0.998x &       0.42 &   0.73 &     - &  2.35 &  2.10 \\
+% \tt{Epinions}           &       0.76 &   1.05 & 297.24 &   36.89 &    8.10 &     5830.02 &      5834.5 &  1.006x &  0.987x &  0.982x &       0.03 &   0.05 &  8.63 &  0.27 &  0.18 \\
+% \tt{LiveJournal}        &      14.59 &  18.99 &      - &  402.02 &       - &   917259.25 &    917036.2 &       - &  0.997x &       - &       2.40 &   3.70 &     - & 26.39 &     - \\
+% \tt{Pokec} &       6.59 &   8.76 &      - &  186.23 & 1220.47 &   461323.28 &    461434.3 &       - &  0.998x &  0.998x &       0.92 &   1.36 &     - & 12.19 & 13.49 \\
+% \tt{Slashdot0811}        &       0.65 &   0.91 & 533.28 &   38.76 &   23.31 &    13890.58 &     13903.5 &  1.001x &  0.994x &  0.994x &       0.04 &   0.06 & 12.63 &  0.39 &  0.45 \\
+% \tt{Slashdot0902}        &       0.83 &   1.16 & 637.75 &   38.54 &   19.87 &    14490.73 &     14498.4 &  1.001x &  0.991x &  0.991x &       0.04 &   0.06 & 16.90 &  0.40 &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&0.71x&1.00x&327.98x&28.59x&36.32x&1.00x&1.00x&1.00x&0.99x&0.99x&0.66x&1.00x&139.99x&5.80x&4.68x \\
+% Max. Perf.&0.77x&1.00x&586.02x&42.60x&139.32x&1.00x&1.00x&1.01x&1.00x&1.00x&0.84x&1.00x&266.19x&12.02x&9.93x \\
+% Geo. Mean&0.71x&1.00x&191.45x&27.56x&14.68x&1.00x&1.00x&1.00x&0.99x&0.99x&0.65x&1.00x&92.09x&4.70x&3.25x \\
+% \end{tabular}
+% }\end{table*}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.005$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.005}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+% Dataset                 &            &        &        &         &         &            &         &         &         &         &            &       &      &        &      \\
+% \midrule
+% \tt{Amazon0302}              &       1.99 & 295.32 &  64.45 &   12.69 &   11.40 &       96.5 &  1.047x &  1.021x &  0.571x &  1.014x &       0.09 & 45.03 & 1.01 &   1.51 & 1.35 \\
+% \tt{DBLP}                &       2.51 & 480.22 &  64.91 &   13.18 &   28.40 &      107.7 &  1.046x &  1.008x &  1.010x &  1.005x &       0.14 & 66.98 & 1.05 &   1.38 & 2.68 \\
+% \tt{Friendster}          &    1054.02 &      - &      - & 4055.92 &       - &  4942428.5 &       - &       - &  1.000x &       - &      62.03 &     - &    - & 112.33 &    - \\
+% \tt{Orkut}               &      37.28 &      - & 253.44 &   49.02 & 1245.28 &   159429.9 &       - &  0.997x &  1.001x &  0.995x &       2.61 &     - & 7.97 &   1.77 & 5.81 \\
+% \tt{Youtube}             &       5.35 &  82.08 &  63.71 &    5.67 &    3.76 &     1829.5 &  1.031x &  1.013x &  1.012x &  1.016x &       0.37 &  7.41 & 0.63 &   0.53 & 0.37 \\
+% \tt{Epinions}           &       1.34 &  13.61 &  47.93 &    1.86 &    0.58 &      245.0 &  1.013x &  0.974x &  0.988x &  0.962x &       0.03 &  3.70 & 0.24 &   0.17 & 0.10 \\
+% \tt{LiveJournal}        &      12.27 & 684.52 &  74.62 &   22.28 &   16.98 &     5892.2 &  1.046x &  1.034x &  1.030x &  1.029x &       1.88 & 17.06 & 2.19 &   2.05 & 1.38 \\
+% \tt{Pokec} &      15.34 & 312.19 &  78.59 &   23.19 &   16.85 &      593.6 &  1.011x &  0.988x &  0.982x &  0.978x &       0.69 & 33.18 & 1.80 &   1.78 & 1.09 \\
+% \tt{Slashdot0811}        &       2.12 &  12.83 &  38.49 &    1.34 &    1.02 &      323.3 &  1.013x &  1.001x &  0.986x &  0.990x &       0.03 &  2.47 & 0.20 &   0.13 & 0.10 \\
+% \tt{Slashdot0902}        &       1.71 &  14.87 &  38.17 &    1.41 &    0.47 &      341.8 &  1.023x &  0.985x &  0.989x &  0.978x &       0.03 &  2.66 & 0.21 &   0.13 & 0.06 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&57.01x&18.27x&2.40x&6.09x&1.00x&1.03x&1.00x&0.96x&1.00x&1.00x&166.16x&5.28x&4.77x&5.32x \\
+% Max. Perf.&1.00x&191.32x&35.77x&6.38x&33.40x&1.00x&1.05x&1.03x&1.03x&1.03x&1.00x&493.46x&11.06x&16.57x&19.17x \\
+% Geo. Mean&1.00x&26.78x&14.63x&1.80x&1.72x&1.00x&1.03x&1.00x&0.95x&1.00x&1.00x&78.94x&4.19x&3.05x&2.88x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.01$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.01}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.28 &  211.25 &  52.76 &   12.48 &    7.33 &       153.3 &  1.034x &  1.001x &  0.402x &  1.014x &       0.09 & 35.22 &  0.67 &  1.43 &  0.70 \\
+% \tt{DBLP}                &       1.65 &  145.54 &  59.23 &    7.36 &   13.95 &       236.8 &  1.027x &  0.994x &  0.981x &  1.003x &       0.14 & 24.53 &  0.61 &  0.82 &  1.38 \\
+% \tt{Friendster}          &     871.74 &       - &      - & 2641.58 &       - &  11504926.0 &       - &       - &  1.000x &       - &      62.03 &     - &     - & 78.17 &     - \\
+% \tt{Orkut}               &      45.24 &       - & 606.07 &  125.15 & 5613.07 &    653881.2 &       - &  1.000x &  1.000x &  1.000x &       2.61 &     - & 20.48 &  3.33 & 27.19 \\
+% \tt{Youtube}             &       3.57 & 1056.41 &  50.45 &    8.50 &   19.82 &      9098.2 &  1.007x &  0.993x &  1.004x &  0.982x &       0.37 & 14.15 &  0.62 &  0.73 &  0.41 \\
+% \tt{Epinions}           &       2.19 &   13.13 &  37.47 &    1.17 &    0.35 &       673.6 &  1.037x &  1.007x &  1.026x &  0.996x &       0.03 &  1.51 &  0.17 &  0.11 &  0.04 \\
+% \tt{LiveJournal}        &      19.09 &       - &  88.36 &   18.38 &  195.23 &     48182.6 &       - &  1.000x &  1.004x &  0.995x &       1.88 &     - &  2.96 &  1.47 &  2.52 \\
+% \tt{Pokec} &      16.21 &  145.32 &  59.37 &    7.50 &    7.29 &      1842.6 &  1.015x &  0.990x &  0.983x &  0.987x &       0.69 & 11.43 &  1.12 &  0.76 &  0.61 \\
+% \tt{Slashdot0811}        &       2.71 &   39.86 &  35.37 &    1.00 &    1.65 &      1194.0 &  1.023x &  1.005x &  0.993x &  0.997x &       0.03 &  1.29 &  0.16 &  0.08 &  0.06 \\
+% \tt{Slashdot0902}        &       2.82 &   44.51 &  35.27 &    1.12 &    1.00 &      1270.4 &  1.027x &  0.998x &  1.006x &  0.984x &       0.03 &  1.43 &  0.16 &  0.08 &  0.04 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&84.94x&17.29x&2.51x&17.29x&1.00x&1.02x&1.00x&0.94x&1.00x&1.00x&106.97x&4.44x&3.64x&3.95x \\
+% Max. Perf.&1.00x&295.91x&41.22x&9.75x&124.07x&1.00x&1.04x&1.01x&1.03x&1.01x&1.00x&385.78x&7.84x&15.71x&10.40x \\
+% Geo. Mean&1.00x&34.11x&13.33x&1.41x&2.59x&1.00x&1.02x&1.00x&0.91x&1.00x&1.00x&62.23x&3.75x&2.36x&2.42x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.92 &  297.11 &   46.78 &    4.86 &    6.65 &     12387.2 &  1.006x &  0.985x &  0.823x &  0.953x &       0.09 & 11.26 &  0.37 &  0.54 &  0.20 \\
+% \tt{DBLP}                &       0.87 & 2903.95 &   45.21 &    3.84 &   55.24 &     48809.6 &  1.001x &  0.992x &  1.000x &  0.990x &       0.14 & 69.72 &  1.18 &  0.27 &  1.10 \\
+% \tt{Friendster}          &     455.26 &       - &       - & 5660.24 &       - &  36993668.0 &       - &       - &  1.000x &       - &      62.03 &     - &     - & 90.95 &     - \\
+% \tt{Orkut}               &      16.37 &       - & 1148.06 &  490.06 &       - &   2694161.0 &       - &  1.000x &  1.000x &       - &       2.61 &     - & 71.76 & 10.08 &     - \\
+% \tt{Youtube}             &       1.72 &       - &   71.50 &   15.78 &  352.45 &    171123.3 &       - &  0.999x &  1.001x &  0.999x &       0.37 &     - &  4.29 &  1.11 &  5.15 \\
+% \tt{Epinions}           &       0.50 &  436.89 &   34.37 &    2.12 &   16.03 &     10479.6 &  1.005x &  0.997x &  1.005x &  0.996x &       0.03 & 14.77 &  0.37 &  0.18 &  0.36 \\
+% \tt{LiveJournal}        &       9.80 &       - &  553.49 &   71.03 &       - &   1698055.4 &       - &  0.999x &  1.002x &       - &       1.88 &     - & 46.07 &  1.35 &     - \\
+% \tt{Pokec} &       4.47 &       - &  255.79 &   37.06 & 3256.58 &    774797.1 &       - &  1.000x &  1.001x &  1.000x &       0.69 &     - & 19.60 &  0.99 & 35.56 \\
+% \tt{Slashdot0811}        &       0.45 &  994.78 &   33.35 &    3.05 &   31.97 &     23216.4 &  1.000x &  0.998x &  1.001x &  0.998x &       0.03 & 27.16 &  0.51 &  0.24 &  0.63 \\
+% \tt{Slashdot0902}        &       0.53 &  897.28 &   33.07 &    2.89 &   23.58 &     24259.3 &  1.001x &  0.996x &  1.001x &  0.995x &       0.03 & 26.39 &  0.53 &  0.23 &  0.63 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&1654.00x&56.33x&9.05x&164.00x&1.00x&1.00x&1.00x&0.98x&0.99x&1.00x&545.28x&16.46x&3.83x&17.82x \\
+% Max. Perf.&1.00x&3337.87x&74.12x&29.94x&728.54x&1.00x&1.01x&1.00x&1.01x&1.00x&1.00x&832.20x&28.35x&7.40x&51.41x \\
+% Geo. Mean&1.00x&1110.53x&53.82x&7.17x&61.50x&1.00x&1.00x&1.00x&0.98x&0.99x&1.00x&456.57x&14.18x&2.99x&12.61x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=N0.05$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timingsN0.05}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} & {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &        &         &      &         &             &         &         &      &         &            &       &       &      &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.39 &  27.01 &   43.25 &    - &    1.18 &      1151.8 &  1.020x &  1.007x &    - &  0.973x &       0.09 &  2.71 &  0.26 &    - &  0.09 \\
+% \tt{DBLP}                &       1.36 & 472.64 &   41.12 &    - &   10.69 &     10010.3 &  1.004x &  0.989x &    - &  0.972x &       0.14 & 13.37 &  0.40 &    - &  0.25 \\
+% \tt{Friendster}          &     492.07 &      - &       - &    - &       - &  29458476.0 &       - &       - &    - &       - &      62.03 &     - &     - &    - &     - \\
+% \tt{Orkut}               &      18.26 &      - & 1158.88 &    - &       - &   2325622.2 &       - &  1.000x &    - &       - &       2.61 &     - & 62.48 &    - &     - \\
+% \tt{Youtube}             &       1.92 &      - &   65.20 &    - &  231.59 &     86486.2 &       - &  0.998x &    - &  0.998x &       0.37 &     - &  2.43 &    - &  2.31 \\
+% \tt{Epinions}           &       0.79 & 273.44 &   37.02 &    - &    8.23 &      5869.9 &  1.007x &  0.984x &    - &  0.983x &       0.03 &  7.92 &  0.27 &    - &  0.20 \\
+% \tt{LiveJournal}        &      13.48 &      - &  402.54 &    - &       - &    929435.8 &       - &  0.997x &    - &       - &       1.88 &     - & 26.52 &    - &     - \\
+% \tt{Pokec} &       6.38 &      - &  186.87 &    - & 1417.99 &    463591.5 &       - &  0.999x &    - &  0.998x &       0.69 &     - & 12.00 &    - & 14.09 \\
+% \tt{Slashdot0811}        &       0.63 & 549.78 &   39.24 &    - &   22.45 &     13942.5 &  1.001x &  0.994x &    - &  0.995x &       0.03 & 14.79 &  0.39 &    - &  0.46 \\
+% \tt{Slashdot0902}        &       0.73 & 608.24 &   38.43 &    - &   20.22 &     14522.0 &  1.002x &  0.992x &    - &  0.991x &       0.03 & 16.58 &  0.40 &    - &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&483.79x&42.19x&-&60.76x&1.00x&1.01x&1.00x&-&0.99x&1.00x&266.05x&11.15x&-&9.05x \\
+% Max. Perf.&1.00x&872.66x&63.47x&-&222.26x&1.00x&1.02x&1.01x&-&1.00x&1.00x&482.03x&23.90x&-&20.38x \\
+% Geo. Mean&1.00x&279.30x&40.17x&-&21.07x&1.00x&1.01x&1.00x&-&0.99x&1.00x&175.72x&9.04x&-&6.01x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=U0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timingsU0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} & {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &        &         &      &         &             &         &         &      &         &            &       &       &      &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.38 &  24.34 &   43.84 &    - &    1.16 &      1129.6 &  1.004x &  0.991x &    - &  0.969x &       0.09 &  2.74 &  0.27 &    - &  0.09 \\
+% \tt{DBLP}                &       1.29 & 431.47 &   41.08 &    - &   18.10 &      9971.0 &  1.008x &  0.986x &    - &  0.982x &       0.14 & 12.64 &  0.39 &    - &  0.38 \\
+% \tt{Friendster}          &     519.72 &      - &       - &    - &       - &  29411706.0 &       - &       - &    - &       - &      62.03 &     - &     - &    - &     - \\
+% \tt{Orkut}               &      18.90 &      - & 1163.91 &    - &       - &   2322648.5 &       - &  1.000x &    - &       - &       2.61 &     - & 62.30 &    - &     - \\
+% \tt{Youtube}             &       1.91 &      - &   64.23 &    - &  152.21 &     86133.5 &       - &  0.998x &    - &  0.998x &       0.37 &     - &  2.35 &    - &  2.10 \\
+% \tt{Epinions}           &       0.78 & 297.24 &   36.89 &    - &    8.10 &      5851.2 &  1.007x &  0.987x &    - &  0.979x &       0.03 &  8.63 &  0.27 &    - &  0.18 \\
+% \tt{LiveJournal}        &      13.99 &      - &  402.02 &    - &       - &    924652.4 &       - &  0.997x &    - &       - &       1.88 &     - & 26.39 &    - &     - \\
+% \tt{Pokec} &       6.34 &      - &  186.23 &    - & 1220.47 &    462030.1 &       - &  0.998x &    - &  0.998x &       0.69 &     - & 12.19 &    - & 13.49 \\
+% \tt{Slashdot0811}        &       0.57 & 533.28 &   38.76 &    - &   23.31 &     13895.8 &  1.001x &  0.994x &    - &  0.994x &       0.03 & 12.63 &  0.39 &    - &  0.45 \\
+% \tt{Slashdot0902}        &       0.66 & 637.75 &   38.54 &    - &   19.87 &     14484.7 &  1.002x &  0.992x &    - &  0.992x &       0.03 & 16.90 &  0.40 &    - &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&527.01x&43.40x&-&52.63x&1.00x&1.00x&0.99x&-&0.99x&1.00x&258.70x&11.14x&-&8.85x \\
+% Max. Perf.&1.00x&966.29x&68.01x&-&192.50x&1.00x&1.01x&1.00x&-&1.00x&1.00x&492.75x&23.83x&-&19.50x \\
+% Geo. Mean&1.00x&289.46x&41.07x&-&21.76x&1.00x&1.00x&0.99x&-&0.99x&1.00x&172.40x&9.00x&-&6.16x \\
+% \end{tabular}
+% }\end{table*}
+
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.005$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.005}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+% Dataset                 &            &        &        &         &         &            &         &         &         &         &            &       &      &        &      \\
+% \midrule
+% \tt{Amazon0302}              &       4.07 & 295.32 &  64.45 &   12.69 &   11.40 &       99.1 &  1.019x &  0.994x &  0.557x &  0.988x &       0.16 & 45.03 & 1.01 &   1.51 & 1.35 \\
+% \tt{DBLP}                &       4.28 & 480.22 &  64.91 &   13.18 &   28.40 &      111.9 &  1.007x &  0.971x &  0.973x &  0.968x &       0.25 & 66.98 & 1.05 &   1.38 & 2.68 \\
+% \tt{Friendster}          &    1707.28 &      - &      - & 4055.92 &       - &  4942465.5 &       - &       - &  1.000x &       - &      95.51 &     - &    - & 112.33 &    - \\
+% \tt{Orkut}               &      71.20 &      - & 253.44 &   49.02 & 1245.28 &   159489.7 &       - &  0.997x &  1.001x &  0.994x &       3.44 &     - & 7.97 &   1.77 & 5.81 \\
+% \tt{Youtube}             &       8.27 &  82.08 &  63.71 &    5.67 &    3.76 &     1857.0 &  1.015x &  0.998x &  0.997x &  1.001x &       0.68 &  7.41 & 0.63 &   0.53 & 0.37 \\
+% \tt{Epinions}           &       2.72 &  13.61 &  47.93 &    1.86 &    0.58 &      247.8 &  1.002x &  0.963x &  0.976x &  0.951x &       0.05 &  3.70 & 0.24 &   0.17 & 0.10 \\
+% \tt{LiveJournal}        &      25.77 & 684.52 &  74.62 &   22.28 &   16.98 &     6031.5 &  1.022x &  1.011x &  1.007x &  1.005x &       3.18 & 17.06 & 2.19 &   2.05 & 1.38 \\
+% \tt{Pokec} &      18.01 & 312.19 &  78.59 &   23.19 &   16.85 &      582.1 &  1.031x &  1.007x &  1.002x &  0.997x &       1.13 & 33.18 & 1.80 &   1.78 & 1.09 \\
+% \tt{Slashdot0811}        &       3.21 &  12.83 &  38.49 &    1.34 &    1.02 &      327.5 &  1.001x &  0.988x &  0.973x &  0.977x &       0.05 &  2.47 & 0.20 &   0.13 & 0.10 \\
+% \tt{Slashdot0902}        &       2.97 &  14.87 &  38.17 &    1.41 &    0.47 &      345.8 &  1.011x &  0.974x &  0.977x &  0.967x &       0.06 &  2.66 & 0.21 &   0.13 & 0.06 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&31.57x&10.22x&1.37x&3.30x&1.00x&1.01x&0.99x&0.95x&0.98x&1.00x&94.51x&3.13x&2.77x&3.06x \\
+% Max. Perf.&1.00x&112.20x&17.62x&3.12x&17.49x&1.00x&1.03x&1.01x&1.01x&1.01x&1.00x&278.64x&6.24x&9.36x&10.54x \\
+% Geo. Mean&1.00x&15.72x&8.48x&1.05x&1.00x&1.00x&1.01x&0.99x&0.93x&0.98x&1.00x&46.11x&2.52x&1.85x&1.73x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.01$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.01}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       2.27 &  211.25 &  52.76 &   12.48 &    7.33 &       157.2 &  1.008x &  0.976x &  0.392x &  0.989x &       0.16 & 35.22 &  0.67 &  1.43 &  0.70 \\
+% \tt{DBLP}                &       2.41 &  145.54 &  59.23 &    7.36 &   13.95 &       240.8 &  1.010x &  0.978x &  0.965x &  0.986x &       0.25 & 24.53 &  0.61 &  0.82 &  1.38 \\
+% \tt{Friendster}          &    1304.76 &       - &      - & 2641.58 &       - &  11505070.0 &       - &       - &  1.000x &       - &      95.51 &     - &     - & 78.17 &     - \\
+% \tt{Orkut}               &      73.54 &       - & 606.07 &  125.15 & 5613.07 &    653921.8 &       - &  1.000x &  1.000x &  1.000x &       3.44 &     - & 20.48 &  3.33 & 27.19 \\
+% \tt{Youtube}             &       5.95 & 1056.41 &  50.45 &    8.50 &   19.82 &      9066.8 &  1.011x &  0.996x &  1.007x &  0.985x &       0.68 & 14.15 &  0.62 &  0.73 &  0.41 \\
+% \tt{Epinions}           &       3.50 &   13.13 &  37.47 &    1.17 &    0.35 &       697.2 &  1.002x &  0.973x &  0.992x &  0.962x &       0.05 &  1.51 &  0.17 &  0.11 &  0.04 \\
+% \tt{LiveJournal}        &      29.39 &       - &  88.36 &   18.38 &  195.23 &     48228.8 &       - &  0.999x &  1.003x &  0.995x &       3.18 &     - &  2.96 &  1.47 &  2.52 \\
+% \tt{Pokec} &      15.91 &  145.32 &  59.37 &    7.50 &    7.29 &      1843.0 &  1.015x &  0.990x &  0.982x &  0.987x &       1.13 & 11.43 &  1.12 &  0.76 &  0.61 \\
+% \tt{Slashdot0811}        &       5.01 &   39.86 &  35.37 &    1.00 &    1.65 &      1204.8 &  1.014x &  0.996x &  0.985x &  0.988x &       0.05 &  1.29 &  0.16 &  0.08 &  0.06 \\
+% \tt{Slashdot0902}        &       5.20 &   44.51 &  35.27 &    1.12 &    1.00 &      1292.0 &  1.010x &  0.981x &  0.989x &  0.968x &       0.06 &  1.43 &  0.16 &  0.08 &  0.04 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&51.49x&10.65x&1.56x&10.71x&1.00x&1.01x&0.99x&0.93x&0.98x&1.00x&60.78x&2.74x&2.12x&2.46x \\
+% Max. Perf.&1.00x&177.55x&24.58x&5.50x&76.33x&1.00x&1.01x&1.00x&1.01x&1.00x&1.00x&217.91x&5.96x&8.87x&7.91x \\
+% Geo. Mean&1.00x&21.78x&8.49x&0.90x&1.65x&1.00x&1.01x&0.99x&0.90x&0.98x&1.00x&36.28x&2.25x&1.43x&1.46x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timings0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
+% \midrule
+% \tt{Amazon0302}              &       2.47 &  297.11 &   46.78 &    4.86 &    6.65 &     12524.4 &  0.995x &  0.974x &  0.814x &  0.943x &       0.16 & 11.26 &  0.37 &  0.54 &  0.20 \\
+% \tt{DBLP}                &       1.27 & 2903.95 &   45.21 &    3.84 &   55.24 &     48850.0 &  1.000x &  0.991x &  1.000x &  0.989x &       0.25 & 69.72 &  1.18 &  0.27 &  1.10 \\
+% \tt{Friendster}          &     676.89 &       - &       - & 5660.24 &       - &  36993740.0 &       - &       - &  1.000x &       - &      95.51 &     - &     - & 90.95 &     - \\
+% \tt{Orkut}               &      24.22 &       - & 1148.06 &  490.06 &       - &   2694175.0 &       - &  1.000x &  1.000x &       - &       3.44 &     - & 71.76 & 10.08 &     - \\
+% \tt{Youtube}             &       2.50 &       - &   71.50 &   15.78 &  352.45 &    171176.4 &       - &  0.999x &  1.001x &  0.999x &       0.68 &     - &  4.29 &  1.11 &  5.15 \\
+% \tt{Epinions}           &       0.70 &  436.89 &   34.37 &    2.12 &   16.03 &     10500.4 &  1.003x &  0.995x &  1.003x &  0.994x &       0.05 & 14.77 &  0.37 &  0.18 &  0.36 \\
+% \tt{LiveJournal}        &      15.17 &       - &  553.49 &   71.03 &       - &   1699002.2 &       - &  0.998x &  1.001x &       - &       3.18 &     - & 46.07 &  1.35 &     - \\
+% \tt{Pokec} &       6.61 &       - &  255.79 &   37.06 & 3256.58 &    774991.6 &       - &  0.999x &  1.000x &  0.999x &       1.13 &     - & 19.60 &  0.99 & 35.56 \\
+% \tt{Slashdot0811}        &       0.79 &  994.78 &   33.35 &    3.05 &   31.97 &     23226.3 &  1.000x &  0.998x &  1.001x &  0.997x &       0.05 & 27.16 &  0.51 &  0.24 &  0.63 \\
+% \tt{Slashdot0902}        &       0.85 &  897.28 &   33.07 &    2.89 &   23.58 &     24287.9 &  1.000x &  0.995x &  1.000x &  0.994x &       0.06 & 26.39 &  0.53 &  0.23 &  0.63 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&1069.17x&37.33x&6.05x&110.14x&1.00x&1.00x&0.99x&0.98x&0.99x&1.00x&323.79x&10.28x&2.33x&10.65x \\
+% Max. Perf.&1.00x&2286.57x&49.10x&20.23x&492.67x&1.00x&1.00x&1.00x&1.00x&1.00x&1.00x&509.03x&20.87x&4.53x&31.48x \\
+% Geo. Mean&1.00x&744.14x&36.10x&4.81x&41.42x&1.00x&1.00x&0.99x&0.98x&0.99x&1.00x&266.99x&8.53x&1.81x&7.35x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=N0.05$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timingsN0.05}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} & {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &        &         &      &         &             &         &         &      &         &            &       &       &      &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.52 &  27.01 &   43.25 &    - &    1.18 &      1157.1 &  1.016x &  1.002x &    - &  0.969x &       0.16 &  2.71 &  0.26 &    - &  0.09 \\
+% \tt{DBLP}                &       2.06 & 472.64 &   41.12 &    - &   10.69 &     10057.1 &  1.000x &  0.984x &    - &  0.967x &       0.25 & 13.37 &  0.40 &    - &  0.25 \\
+% \tt{Friendster}          &     721.99 &      - &       - &    - &       - &  29458564.0 &       - &       - &    - &       - &      95.51 &     - &     - &    - &     - \\
+% \tt{Orkut}               &      29.66 &      - & 1158.88 &    - &       - &   2325639.5 &       - &  1.000x &    - &       - &       3.44 &     - & 62.48 &    - &     - \\
+% \tt{Youtube}             &       2.79 &      - &   65.20 &    - &  231.59 &     86477.7 &       - &  0.998x &    - &  0.998x &       0.68 &     - &  2.43 &    - &  2.31 \\
+% \tt{Epinions}           &       1.18 & 273.44 &   37.02 &    - &    8.23 &      5884.2 &  1.004x &  0.981x &    - &  0.981x &       0.05 &  7.92 &  0.27 &    - &  0.20 \\
+% \tt{LiveJournal}        &      18.88 &      - &  402.54 &    - &       - &    928962.7 &       - &  0.998x &    - &       - &       3.18 &     - & 26.52 &    - &     - \\
+% \tt{Pokec} &       9.00 &      - &  186.87 &    - & 1417.99 &    463754.6 &       - &  0.998x &    - &  0.998x &       1.13 &     - & 12.00 &    - & 14.09 \\
+% \tt{Slashdot0811}        &       0.94 & 549.78 &   39.24 &    - &   22.45 &     13954.5 &  1.001x &  0.994x &    - &  0.994x &       0.05 & 14.79 &  0.39 &    - &  0.46 \\
+% \tt{Slashdot0902}        &       1.10 & 608.24 &   38.43 &    - &   20.22 &     14539.0 &  1.001x &  0.991x &    - &  0.990x &       0.06 & 16.58 &  0.40 &    - &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&323.35x&29.00x&-&42.25x&1.00x&1.00x&0.99x&-&0.99x&1.00x&159.97x&7.08x&-&5.43x \\
+% Max. Perf.&1.00x&584.87x&41.75x&-&157.55x&1.00x&1.02x&1.00x&-&1.00x&1.00x&294.02x&18.17x&-&12.48x \\
+% Geo. Mean&1.00x&198.16x&27.98x&-&14.88x&1.00x&1.00x&0.99x&-&0.99x&1.00x&102.81x&5.44x&-&3.50x \\
+% \end{tabular}
+% }\end{table*}
+% \begin{table*}
+%     \setlength{\tabcolsep}{1.2pt}
+%         \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs)  on the networks with $K = 50$ seeds using $\tau=16$ threads and constant edge weights $w=U0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+%         }
+%         \label{tab:timingsU0.1}
+%         \centering
+%         \resizebox{\linewidth}{!}{
+
+% \begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+% \toprule
+% {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} & {\sc Skim} &   {\sc Ssa} \\
+% Dataset                 &            &        &         &      &         &             &         &         &      &         &            &       &       &      &       \\
+% \midrule
+% \tt{Amazon0302}              &       1.26 &  24.34 &   43.84 &    - &    1.16 &      1128.5 &  1.005x &  0.991x &    - &  0.970x &       0.16 &  2.74 &  0.27 &    - &  0.09 \\
+% \tt{DBLP}                &       2.08 & 431.47 &   41.08 &    - &   18.10 &     10036.0 &  1.001x &  0.980x &    - &  0.976x &       0.25 & 12.64 &  0.39 &    - &  0.38 \\
+% \tt{Friendster}          &     740.47 &      - &       - &    - &       - &  29411774.0 &       - &       - &    - &       - &      95.51 &     - &     - &    - &     - \\
+% \tt{Orkut}               &      33.52 &      - & 1163.91 &    - &       - &   2322654.0 &       - &  1.000x &    - &       - &       3.44 &     - & 62.30 &    - &     - \\
+% \tt{Youtube}             &       2.86 &      - &   64.23 &    - &  152.21 &     86132.5 &       - &  0.998x &    - &  0.998x &       0.68 &     - &  2.35 &    - &  2.10 \\
+% \tt{Epinions}           &       1.21 & 297.24 &   36.89 &    - &    8.10 &      5864.6 &  1.004x &  0.984x &    - &  0.977x &       0.05 &  8.63 &  0.27 &    - &  0.18 \\
+% \tt{LiveJournal}        &      19.76 &      - &  402.02 &    - &       - &    924881.8 &       - &  0.997x &    - &       - &       3.18 &     - & 26.39 &    - &     - \\
+% \tt{Pokec} &       9.07 &      - &  186.23 &    - & 1220.47 &    462019.5 &       - &  0.998x &    - &  0.998x &       1.13 &     - & 12.19 &    - & 13.49 \\
+% \tt{Slashdot0811}        &       0.96 & 533.28 &   38.76 &    - &   23.31 &     13900.2 &  1.001x &  0.994x &    - &  0.994x &       0.05 & 12.63 &  0.39 &    - &  0.45 \\
+% \tt{Slashdot0902}        &       1.15 & 637.75 &   38.54 &    - &   19.87 &     14504.8 &  1.000x &  0.991x &    - &  0.990x &       0.06 & 16.90 &  0.40 &    - &  0.45 \\
+% \bottomrule
+
+% Avg. Perf.&1.00x&316.49x&28.55x&-&35.09x&1.00x&1.00x&0.99x&-&0.99x&1.00x&155.33x&7.07x&-&5.31x \\
+% Max. Perf.&1.00x&555.50x&40.38x&-&134.56x&1.00x&1.01x&1.00x&-&1.00x&1.00x&299.53x&18.12x&-&11.94x \\
+% Geo. Mean&1.00x&197.85x&27.58x&-&14.87x&1.00x&1.00x&0.99x&-&0.99x&1.00x&100.82x&5.41x&-&3.59x \\
+% \end{tabular}
+% }\end{table*}
+
+\subsection{Comparing \acro with State-of-the-Art}
+To compare the run time, memory use, and quality of \acro with those of the state-of-the-art, %As explained above, the parameters of the experimented methods are hard to compare directly.
+It is infeasible to find precisely the corresponding parameter between any two methods in this setting.
+For that reason, we have used the parameters suggested by the paper.
+we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.2$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$), and {\sc Ssa}($\epsilon=0.1$).
+In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Imm} have one.
+Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex.
+In the experiments, we have used ${\cal J} = 256$ for \acro.
+In addition, as explained in the previous section, we use a global error threshold $\epsilon_{g} = 0.01$, a local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.\looseness=-1
+
+We present the results in Tables~\ref{tab:timings0.005},~\ref{tab:timings0.01},~\ref{tab:timings0.1},~\ref{tab:timingsN0.05} and \ref{tab:timingsU0.1}  for constant edge weights $w = 0.005$, $0.01$, $0.1$, normally distributed edge weights $w \in N(0.05,0.025)$ and uniformly distributed $w \in U(0,0.1)$, respectively.
+The top part of each table shows the  results for the networks, and the bottom four rows are the arithmetic mean, geometric mean, maximum and minimum, respectively, of the scores after they are normalized w.r.t.
+those of \acro's scores.
+In all tables, for the execution time and memory columns, lower values are better.
+For the influence score columns, higher values are better.
+
+\begin{table*}
+
+    \setlength{\tabcolsep}{1.2pt}
+        \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds,  $\tau=16$ threads, and $w=0.005$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
         }
-    \label{tab:timings005}
+        \label{tab:timings0.005}
         \centering
-    \scalebox{0.94}{
-\begin{tabular}{l|rrrr|rrrr|rrrr}
+        \resizebox{\linewidth}{!}{
+
+\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
 \toprule
-{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Influence Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
-
-Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
-
+{} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+Method & {\sc Hyp.} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc Hyp.}   &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc Hyp.}  &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+Dataset                 &   {\sc Fus.}         &        &        &         &         & {\sc Fus.}           &         &         &         &      &      {\sc Fus.}         &       &      &        &      \\
 \midrule
-{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041$\times$&  1.000$\times$&  0.562$\times$&       0.17 & 21.62 & 0.90 & 6.78 \\
-{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068$\times$&  1.027$\times$&  1.036$\times$&       0.27 & 31.24 & 0.95 & 3.12 \\
-{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026$\times$&  1.001$\times$&  0.939$\times$&       0.06 &  0.78 & 0.07 & 1.04 \\
-{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010$\times$&  0.995$\times$&  0.957$\times$&       3.97 & 27.43 & 2.78 & 2.00 \\
-{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065$\times$&  0.993$\times$&  0.871$\times$&       0.01 &  0.80 & 0.04 & 0.33 \\
-{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042$\times$&  0.999$\times$&  0.777$\times$&       0.03 &  2.01 & 0.08 & 0.16 \\
-{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997$\times$&  1.001$\times$&       5.19 &     - & 7.81 & 1.77 \\
-{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032$\times$&  1.027$\times$&  0.925$\times$&       1.57 & 10.16 & 1.40 & 1.74 \\
-{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015$\times$&  0.983$\times$&  0.942$\times$&       0.06 &  0.76 & 0.09 & 0.13 \\
-{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022$\times$&  0.998$\times$&  0.953$\times$&       0.06 &  0.71 & 0.08 & 0.14 \\
-{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006$\times$&  0.990$\times$&  0.942$\times$&       0.09 &  2.02 & 0.12 & 0.15 \\
-{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025$\times$&  1.013$\times$&  1.000$\times$&       0.73 &  3.96 & 0.48 & 1.39 \\
+\tt{Amazon0302}              &       2.0 & 295.3 &  64.5 &   12.7 &   11.4 &       96.5 &  1.047$\times$ &  1.021$\times$ &  0.571$\times$ &  1.014$\times$ &       0.09 & 45.03 & 1.01 &   1.51 & 1.35 \\
+\tt{DBLP}                &       2.5 & 480.2 &  64.9 &   13.2 &   28.4 &      107.7 &  1.046$\times$ &  1.008$\times$ &  1.010$\times$ &  1.014$\times$ &       0.14 & 66.98 & 1.05 &   1.38 & 2.68 \\
+\tt{Friendster}          &    1054.0 &      - &      - & 4055.9 &       - &  
+% 4942428.5
+4.94M
+&       - &       - &  1.000$\times$ &       - &      62.0 &     - &    - & 112.3 &    - \\
+\tt{Orkut}               &      37.3 &      - & 253.4 &   49.0 & 1245.3 &   
+% 159429.9 
+0.16M
+&       - &  0.997$\times$ &  1.001$\times$ &  0.995$\times$ &       2.61 &     - & 7.97 &   1.77 & 5.81 \\
+\tt{Youtube}             &       5.4 &  82.1 &  63.7 &    5.7 &    3.8 &     1829.5 &  1.031$\times$ &  1.013$\times$ &  1.012$\times$ &  1.016$\times$ &       0.37 &  7.41 & 0.63 &   0.53 & 0.37 \\
+\tt{Epinions}           &       1.3 &  13.6 &  47.9 &    1.9 &    0.6 &      245.0 &  1.013$\times$ &  0.974$\times$ &  0.988$\times$ &  0.962$\times$ &       0.03 &  3.70 & 0.24 &   0.17 & 0.10 \\
+\tt{LiveJournal}        &      12.3 & 684.5 &  74.6 &   22.3 &   17.0 &     5892.2 &  1.046$\times$ &  1.034$\times$ &  1.030$\times$ &  1.029$\times$ &       1.88 & 17.06 & 2.19 &   2.05 & 1.38 \\
+\tt{Pokec} &      15.3 & 312.2 &  78.6 &   23.2 &   16.9 &      593.6 &  1.011$\times$ &  0.988$\times$ &  0.982$\times$ &  0.978$\times$ &       0.69 & 33.18 & 1.80 &   1.78 & 1.09 \\
+\tt{Slashdot0811}        &       2.1 &  12.8 &  38.5 &    1.3 &    1.0 &      323.3 &  1.013$\times$ &  1.001$\times$ &  0.986$\times$ &  0.990$\times$ &       0.03 &  2.47 & 0.20 &   0.13 & 0.10 \\
+\tt{Slashdot0902}        &       1.7 &  14.9 &  38.2 &    1.4 &    0.5 &      341.8 &  1.023$\times$ &  0.985$\times$ &  0.989$\times$ &  0.978$\times$ &       0.03 &  2.66 & 0.21 &   0.13 & 0.06 \\
 \bottomrule
-Norm. arit. mean &&69.39$\times$&4.37$\times$&8.13$\times$&&1.032$\times$&1.002$\times$&0.909$\times$& &42.60$\times$&2.05$\times$&9.76$\times$ \\ 
-Norm.
-geo.
-mean &\multicolumn{1}{c}{all}&28.19$\times$&1.69$\times$&3.47$\times$&\multicolumn{1}{c}{all}&1.032$\times$&1.002$\times$&0.899$\times$&\multicolumn{1}{c}{all}&22.75$\times$&1.65$\times$&3.58$\times$ \\
-Norm.
-max perf&\multicolumn{1}{c}{1.00$\times$}&314.92$\times$&25.82$\times$&49.02$\times$&\multicolumn{1}{c}{1.000$\times$}&1.068$\times$&1.027$\times$&1.036$\times$&\multicolumn{1}{c}{1.00$\times$}&127.18$\times$&5.29$\times$&39.88$\times$ \\
-Norm. min perf&&5.88$\times$&0.34$\times$&0.85$\times$&&1.006$\times$&0.983$\times$&0.562$\times$&&5.43$\times$&0.66$\times$&0.34$\times$
+Avg.
+Perf.&1.0$\times$&57.0$\times$&18.3$\times$&2.4$\times$&6.1$\times$&1.00$\times$&1.03$\times$&1.00$\times$&0.96$\times$&1.00$\times$&1.00$\times$&166.16$\times$&5.28$\times$&4.77$\times$&5.32$\times$ \\
+Max.
+Perf.&1.0$\times$&191.3$\times$&35.8$\times$&6.4$\times$&33.4$\times$&1.00$\times$&1.05$\times$&1.03$\times$&1.03$\times$&1.03$\times$&1.00$\times$&493.46$\times$&11.06$\times$&16.57$\times$&19.17$\times$ \\
+Geo.
+Mean&1.0$\times$&26.8$\times$&14.6$\times$&1.8$\times$&1.7$\times$&1.00$\times$&1.03$\times$&1.00$\times$&0.95$\times$&1.00$\times$&1.00$\times$&78.94$\times$&4.19$\times$&3.05$\times$&2.88$\times$ \\
 \end{tabular}
+}\end{table*}
+\begin{table*}
+    \setlength{\tabcolsep}{1.2pt}
+        \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds,  $\tau=16$ threads, and $w=0.01$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
         }
-    \end{table*}
-
-    \begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs) on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.01$.
-Influence scores are given relative to \acro{}.
-The runs that did not finish due to high memory use shown as "-".}
-    \label{tab:timings01}
+        \label{tab:timings0.01}
         \centering
-    \scalebox{0.92}{
-
-% \begin{tabular}{lrrrrrrrrrrrr}
-% \toprule
-% {} & \multicolumn{4}{l}{Time} & \multicolumn{4}{l}{Score} & \multicolumn{4}{l}{Memory} \\
-% Method & HyperFuser &    TIM &     IMM &   SKIM & HyperFuser &    TIM &     IMM &    SKIM & HyperFuser &  TIM &   IMM & SKIM \\
+        \resizebox{\linewidth}{!}{
+
+\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+\toprule
+{} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+Method & \acrotwo &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
+\midrule
+\tt{Amazon0302}              &       1.2 &  211.2 &  52.7 &   12.4 &    7.3 &       153.3 &  1.034$\times$ &  1.001$\times$ &  0.402$\times$ &  1.014$\times$ &       0.09 & 35.22 &  0.67 &  1.43 &  0.70 \\
+\tt{DBLP}                &       1.6 &  145.5 &  59.2 &    7.3 &   13.9 &       236.8 &  1.027$\times$ &  0.994$\times$ &  0.981$\times$ &  1.003$\times$ &       0.14 & 24.53 &  0.61 &  0.82 &  1.38 \\
+\tt{Friendster}          &     871.7 &       - &      - & 2641.5 &       - &  
+11.50M
+% 11504926.0 
+&       - &       - &  1.000$\times$ &       - &      62.03 &     - &     - & 78.17 &     - \\
+\tt{Orkut}               &      45.2 &       - & 606.0 &  125.1 & 5613.0 &    
+% 653881.2
+0.65M
+&       - &  1.000$\times$ &  1.000$\times$ &  1.000$\times$ &       2.61 &     - & 20.48 &  3.33 & 27.19 \\
+\tt{Youtube}             &       3.5 & 1056.4 &  50.4 &    8.5 &   19.8 &      9098.2 &  1.007$\times$ &  0.993$\times$ &  1.004$\times$ &  0.982$\times$ &       0.37 & 14.15 &  0.62 &  0.73 &  0.41 \\
+\tt{Epinions}           &       2.1 &   13.1 &  37.4 &    1.1 &    0.3 &       673.6 &  1.037$\times$ &  1.007$\times$ &  1.026$\times$ &  0.996$\times$ &       0.03 &  1.51 &  0.17 &  0.11 &  0.04 \\
+\tt{LiveJournal}        &      19.0 &       - &  88.3 &   18.3 &  195.2 &     48182.6 &       - &  1.000$\times$ &  1.004$\times$ &  0.995$\times$ &       1.88 &     - &  2.96 &  1.47 &  2.52 \\
+\tt{Pokec} &      16.2 &  145.3 &  59.3 &    7.5 &    7.2 &      1842.6 &  1.015$\times$ &  0.990$\times$ &  0.983$\times$ &  0.987$\times$ &       0.69 & 11.43 &  1.12 &  0.76 &  0.61 \\
+\tt{Slashdot0811}        &       2.7 &   39.8 &  35.3 &    1.0 &    1.6 &      1194.0 &  1.023$\times$ &  1.005$\times$ &  0.993$\times$ &  0.997$\times$ &       0.03 &  1.29 &  0.16 &  0.08 &  0.06 \\
+\tt{Slashdot0902}        &       2.8 &   44.5 &  35.2 &    1.1 &    1.0 &      1270.4 &  1.027$\times$ &  0.998$\times$ &  1.006$\times$ &  0.984$\times$ &       0.03 &  1.43 &  0.16 &  0.08 &  0.04 \\
+\bottomrule
+
+Avg.
+Perf.&1.0$\times$&84.9$\times$&17.3$\times$&2.5$\times$&17.3$\times$&1.00$\times$&1.02$\times$&1.00$\times$&0.94$\times$&1.00$\times$&1.00$\times$&106.97$\times$&4.44$\times$&3.64$\times$&3.95$\times$ \\
+Max.
+Perf.&1.0$\times$&295.9$\times$&41.2$\times$&9.8$\times$&124.1$\times$&1.00$\times$&1.04$\times$&1.01$\times$&1.03$\times$&1.01$\times$&1.00$\times$&385.78$\times$&7.84$\times$&15.71$\times$&10.40$\times$ \\
+Geo.
+Mean&1.0$\times$&34.1$\times$&13.3$\times$&1.4$\times$&2.6$\times$&1.00$\times$&1.02$\times$&1.00$\times$&0.91$\times$&1.00$\times$&1.00$\times$&62.23$\times$&3.75$\times$&2.36$\times$&2.42$\times$ \\
+\end{tabular}
+}\end{table*}
+\begin{table*}
+    \setlength{\tabcolsep}{1.2pt}
+        \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds, $\tau=16$ threads, and $w=0.1$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+        }
+        \label{tab:timings0.1}
+        \centering
+        \resizebox{\linewidth}{!}{
+
+\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+\toprule
+{} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
+Method & \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
+\midrule
+\tt{Amazon0302}              &       1.9 &  297.1 &   46.8 &    4.9 &    6.7 &     12387.2 &  1.006x &  0.985x &  0.823x &  0.953x &       0.09 & 11.26 &  0.37 &  0.54 &  0.20 \\
+\tt{DBLP}                &       0.9 & 2904.0 &   45.2 &    3.8 &   55.2 &     48809.6 &  1.001x &  0.992x &  1.000x &  0.990x &       0.14 & 69.72 &  1.18 &  0.27 &  1.10 \\
+\tt{Friendster}          &     455.3 &       - &       - & 5660.2 &       - &  
+% 36993668.0
+36.99M
+&       - &       - &  1.000x &       - &      62.03 &     - &     - & 90.95 &     - \\
+\tt{Orkut}               &      16.4 &       - & 1148.1 &  490.1 &       - &   
+% 2694161.0
+2.69M
+&       - &  1.000x &  1.000x &       - &       2.61 &     - & 71.76 & 10.08 &     - \\
+\tt{Youtube}             &       1.7 &       - &   71.5 &   15.8 &  352.5 &    
+% 171123.3 
+0.17
+&       - &  0.999x &  1.001x &  0.999x &       0.37 &     - &  4.29 &  1.11 &  5.15 \\
+\tt{Epinions}           &       0.5 &  436.9 &   34.4 &    2.1 &   16.0 &     10479.6 &  1.005x &  0.997x &  1.005x &  0.996x &       0.03 & 14.77 &  0.37 &  0.18 &  0.36 \\
+\tt{LiveJournal}        &       9.8 &       - &  553.4 &   71.0 &       - &   
+% 1698055.4
+1.69M
+&       - &  0.999x &  1.002x &       - &       1.88 &     - & 46.07 &  1.35 &     - \\
+\tt{Pokec} &       4.5 &       - &  255.8 &   37.1 & 3256.6 &    
+% 774797.1
+0.77M
+&       - &  1.000x &  1.001x &  1.000x &       0.69 &     - & 19.60 &  0.99 & 35.56 \\
+\tt{Slashdot0811}        &       0.5 &  994.8 &   33.5 &    3.1 &   32.0 &     23216.4 &  1.000x &  0.998x &  1.001x &  0.998x &       0.03 & 27.16 &  0.51 &  0.24 &  0.63 \\
+\tt{Slashdot0902}        &       0.5 &  897.3 &   33.1 &    2.9 &   23.6 &     24259.3 &  1.001x &  0.996x &  1.001x &  0.995x &       0.03 & 26.39 &  0.53 &  0.23 &  0.63 \\
+\bottomrule
+
+Avg. Perf.&1.0x&1654.0x&56.3x&9.1x&164.0x&1.00x&1.00x&1.00x&0.98x&0.99x&1.00x&545.28x&16.46x&3.83x&17.82x \\
+Max. Perf.&1.0x&3337.9x&74.1x&29.9x&728.5x&1.00x&1.01x&1.00x&1.01x&1.00x&1.00x&832.20x&28.35x&7.40x&51.41x \\
+Geo. Mean&1.0x&1110.5x&53.8x&7.2x&61.5x&1.00x&1.00x&1.00x&0.98x&0.99x&1.00x&456.57x&14.18x&2.99x&12.61x \\
+\end{tabular}
+}\end{table*}
+\begin{table*}
+    \setlength{\tabcolsep}{2.5pt}
+        \caption{Execution times~(in secs), inf.
+scores, and memory use~(in GBs) with $K = 50$ seeds, $\tau=16$ threads, and $w \in N(0.05,0.025)$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
+        }
+        \label{tab:timingsN0.05}
+        \centering
+        \resizebox{\linewidth}{!}{
+
 \begin{tabular}{l|rrrr|rrrr|rrrr}
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
-
-Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
+Method & \acrotwo &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+Dataset                 &            &        &         &         &             &         &         &         &            &       &       &       \\
 \midrule
-{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037$\times$&  1.024$\times$&  0.390$\times$&       0.17 & 18.11 &  0.55 & 6.40 \\
-{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043$\times$&  1.005$\times$&  0.997$\times$&       0.27 & 11.92 &  0.52 & 2.05 \\
-{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006$\times$&  0.983$\times$&  0.984$\times$&       0.06 &  1.95 &  0.10 & 0.68 \\
-{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996$\times$&  0.993$\times$&       3.97 &     - &  6.64 & 1.45 \\
-{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036$\times$&  0.997$\times$&  0.826$\times$&       0.01 &  0.60 &  0.03 & 0.31 \\
-{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010$\times$&  0.985$\times$&  0.732$\times$&       0.03 &  0.67 &  0.05 & 0.12 \\
-{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000$\times$&  1.000$\times$&       5.19 &     - & 20.13 & 3.43 \\
-{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004$\times$&  0.996$\times$&  0.988$\times$&       1.57 & 39.98 &  2.09 & 0.78 \\
-{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003$\times$&  0.984$\times$&  0.976$\times$&       0.06 &  2.01 &  0.10 & 0.08 \\
-{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008$\times$&  0.992$\times$&  0.980$\times$&       0.06 &  2.42 &  0.11 & 0.08 \\
-{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004$\times$&  0.992$\times$&  0.978$\times$&       0.09 &  4.91 &  0.23 & 0.09 \\
-{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009$\times$&  0.994$\times$&  1.006$\times$&       0.73 &  7.10 &  0.48 & 1.73 \\
+\tt{Amazon0302}              &       1.4 &  27.0 &   43.3 &    1.2 &      1151.8 &  1.020x &  1.007x &  0.973x &       0.09 &  2.71 &  0.26 &  0.09 \\
+\tt{DBLP}                &       1.4 & 472.6 &   41.1 &   10.7 &     10010.3 &  1.004x &  0.989x &  0.972x &       0.14 & 13.37 &  0.40 &  0.25 \\
+\tt{Friendster}          &     492.1 &      - &       - &       - &  
+% 29458476.0
+29.45M
+&       - &       - &       - &      62.03 &     - &     - &     - \\
+\tt{Orkut}               &      18.3 &      - & 1158.9 &       - &   
+% 2325622.2
+2.32M
+&       - &  1.000x &       - &       2.61 &     - & 62.48 &     - \\
+\tt{Youtube}             &       1.9 &      - &   65.2 &  231.6 &     86486.2 &       - &  0.998x &  0.998x &       0.37 &     - &  2.43 &  2.31 \\
+\tt{Epinions}           &       0.8 & 273.4 &   37.0 &    8.2 &      5869.9 &  1.007x &  0.984x &  0.983x &       0.03 &  7.92 &  0.27 &  0.20 \\
+\tt{LiveJournal}        &      13.5 &      - &  402.5 &       - &    
+% 929435.8
+0.93M
+&       - &  0.997x &       - &       1.88 &     - & 26.52 &     - \\
+\tt{Pokec} &       6.4 &      - &  186.9 & 1418.0 &    
+% 463591.5
+0.46M
+&       - &  0.999x &  0.998x &       0.69 &     - & 12.00 & 14.09 \\
+\tt{Slashdot0811}        &       0.6 & 549.8 &   39.2 &   22.5 &     13942.5 &  1.001x &  0.994x &  0.995x &       0.03 & 14.79 &  0.39 &  0.46 \\
+\tt{Slashdot0902}        &       0.7 & 608.2 &   38.4 &   20.2 &     14522.0 &  1.002x &  0.992x &  0.991x &       0.03 & 16.58 &  0.40 &  0.45 \\
 \bottomrule
-Norm. arit. mean &&167.17$\times$&9.73$\times$&9.99$\times$&&1.016$\times$&0.996$\times$&0.904$\times$& &42.91$\times$&2.09$\times$&8.26$\times$ \\ 
-Norm.
-geo.
-mean &\multicolumn{1}{c}{all}&100.14$\times$&5.45$\times$&3.58$\times$&\multicolumn{1}{c}{all}&1.016$\times$&0.996$\times$&0.879$\times$&\multicolumn{1}{c}{all}&36.26$\times$&1.91$\times$&2.82$\times$ \\
-Norm.
-max perf&\multicolumn{1}{c}{1.00$\times$}&433.73$\times$&44.14$\times$&61.79$\times$&\multicolumn{1}{c}{1.000$\times$}&1.043$\times$&1.024$\times$&1.006$\times$&\multicolumn{1}{c}{1.00$\times$}&106.53$\times$&3.88$\times$&37.65$\times$ \\
-Norm. min perf&&7.08$\times$&0.89$\times$&0.62$\times$&&1.003$\times$&0.983$\times$&0.390$\times$&&9.73$\times$&0.66$\times$&0.37$\times$ 
-% Geo. Mean wrt.&1.000$\times$&100.140$\times$&5.448$\times$&3.582$\times$&1.000$\times$&1.016$\times$&0.996$\times$&0.879$\times$&1.000$\times$&36.264$\times$&1.909$\times$&2.820x \\ \acro
+
+Avg. Perf.&1.0x&483.8x&42.2x&60.8x&1.00x&1.01x&1.00x&0.99x&1.00x&266.05x&11.15x&9.05x \\
+Max. Perf.&1.0x&872.7x&63.5x&222.3x&1.00x&1.02x&1.01x&1.00x&1.00x&482.03x&23.90x&20.38x \\
+Geo. Mean&1.0x&279.3x&40.2x&21.1x&1.00x&1.01x&1.00x&0.99x&1.00x&175.72x&9.04x&6.01x \\
+
 \end{tabular}
+}\end{table*}
+\begin{table*}
+    \setlength{\tabcolsep}{2.5pt}
+        \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds, $\tau=16$ threads and $w \in U(0,0.1)$.
+Influence scores are given relative to \acro{}.
+The runs that did not finish in 5 hours or due to high memory use shown as "-".
         }
-    \end{table*}
-    \begin{table*} %TABLE 5+7
-    \caption{\acro execution times~(in secs), influence scores, and memory use~(in GBs) on the networks with $K = 50$ seeds using $\tau=18$ threads and constant edge weights $w=0.1$.
-Influence scores are given relative to \acro{}.
-The runs that did not finish due to high memory use shown as "-".}
-    \label{tab:timings1}
+        \label{tab:timingsU0.1}
         \centering
-    \scalebox{0.92}{
+        \resizebox{\linewidth}{!}{
 
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & {\sc Hyper} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc Hyper} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc Hyper} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
-
-Dataset      & {\sc Fuser} &         &         &         & {\sc Fuser} &         &         &         & {\sc Fuser} &       &       &      \\
+Method & \acrotwo &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+Dataset                 &            &        &         &         &             &         &         &         &            &       &       &       \\
 \midrule
-{\tt Amazon}       &       0.69 &  133.22 &    1.98 &  23.62 &    11797.0 &  1.006$\times$&  0.990$\times$&  0.815$\times$&       0.17 &   5.49 &  0.23 & 2.59 \\
-{\tt DBLP }         &       0.54 & 1368.83 &   14.54 &   6.30 &    48549.9 &  1.001$\times$&  0.995$\times$&  1.001$\times$&       0.27 &  35.19 &  1.06 & 0.65 \\
-{\tt Epinions }     &       0.26 &  439.33 &    5.46 &   9.42 &    18409.9 &  1.000$\times$&  0.998$\times$&  0.997$\times$&       0.06 &  12.17 &  0.39 & 1.18 \\
-{\tt LiveJournal }  &      10.10 &       - & 1071.30 &  65.73 &  2134726.0 &       - &  1.000$\times$&  1.000$\times$&       3.97 &      - & 65.49 & 1.40 \\
-{\tt NetHEP }       &       0.10 &   14.18 &    0.33 &   0.61 &     2461.7 &  1.002$\times$&  0.975$\times$&  0.899$\times$&       0.01 &   1.02 &  0.04 & 0.10 \\
-{\tt NetPhy }       &       0.16 &  107.52 &    1.53 &   0.34 &     8339.5 &  1.007$\times$&  0.994$\times$&  0.975$\times$&       0.03 &   3.84 &  0.13 & 0.03 \\
-{\tt Orkut }        &      16.55 &       - & 1964.83 & 446.92 &  2692366.5 &       - &  1.000$\times$&  1.000$\times$&       5.19 &      - & 71.94 & 9.68 \\
-{\tt Pokec }        &       4.90 &       - &  514.79 &  31.80 &  1034859.8 &       - &  1.000$\times$&  1.000$\times$&       1.57 &      - & 26.46 & 0.98 \\
-{\tt Slashdot0811 } &       0.21 &  677.49 &    7.34 &   2.44 &    25871.8 &  1.000$\times$&  1.000$\times$&  0.999$\times$&       0.06 &  19.10 &  0.59 & 0.25 \\
-{\tt Slashdot0902 } &       0.23 &  695.12 &    7.99 &   2.35 &    27519.5 &  1.000$\times$&  1.000$\times$&  0.999$\times$&       0.06 &  18.45 &  0.66 & 0.24 \\
-{\tt Twitter }      &       0.33 & 1897.50 &   16.09 &   1.62 &    55327.3 &  1.000$\times$&  0.998$\times$&  0.998$\times$&       0.09 &  34.56 &  1.04 & 0.05 \\
-{\tt Youtube }      &       1.12 & 7158.56 &   60.59 &  30.57 &   171392.9 &  1.000$\times$&  0.999$\times$&  1.001$\times$&       0.73 & 139.12 &  4.19 & 2.88 \\
+\tt{Amazon0302}              &       1.4 &  24.3 &   43.9 &    1.2 &      1129.6 &  1.004x &  0.991x &  0.969x &       0.09 &  2.74 &  0.27 &  0.09 \\
+\tt{DBLP}                &       1.3 & 431.5 &   41.1 &   18.1 &      9971.0 &  1.008x &  0.986x &  0.982x &       0.14 & 12.64 &  0.39 &  0.38 \\
+\tt{Friendster}          &     519.7 &      - &       - &       - &  
+% 29411706.0
+29.41M
+&       - &       - &       - &      62.03 &     - &     - &     - \\
+\tt{Orkut}               &      18.9 &      - & 1163.9 &       - &   
+% 2322648.5
+2.32M
+&       - &  1.000x &       - &       2.61 &     - & 62.30 &     - \\
+\tt{Youtube}             &       1.9 &      - &   64.2 &  152.2 &     86133.5 &       - &  0.998x &  0.998x &       0.37 &     - &  2.35 &  2.10 \\
+\tt{Epinions}           &       0.8 & 297.2 &   36.9 &    8.1 &      5851.2 &  1.007x &  0.987x &  0.979x &       0.03 &  8.63 &  0.27 &  0.18 \\
+\tt{LiveJournal}        &      14.0 &      - &  402.0 &       - &    924652.4 &       - &  0.997x &       - &       1.88 &     - & 26.39 &     - \\
+\tt{Pokec} &       6.3 &      - &  186.2 & 1220.5 &    462030.1 &       - &  0.998x &  0.998x &       0.69 &     - & 12.19 & 13.49 \\
+\tt{Slashdot0811}        &       0.6 & 533.3 &   38.8 &   23.3 &     13895.8 &  1.001x &  0.994x &  0.994x &       0.03 & 12.63 &  0.39 &  0.45 \\
+\tt{Slashdot0902}        &       0.7 & 637.8 &   38.6 &   19.9 &     14484.7 &  1.002x &  0.992x &  0.992x &       0.03 & 16.90 &  0.40 &  0.45 \\
 \bottomrule
-Norm. arit. mean &&2624.61$\times$&47.17$\times$&15.37$\times$&&1.002$\times$&0.996$\times$&0.974$\times$& &199.54$\times$&8.79$\times$&5.32$\times$ \\ 
-Norm.
-geo.
-mean &\multicolumn{1}{c}{all}&1449.41$\times$&27.87$\times$&11.06$\times$&\multicolumn{1}{c}{all}&1.002$\times$&0.996$\times$&0.972$\times$&\multicolumn{1}{c}{all}&163.77$\times$&7.15$\times$&2.63$\times$ \\
-Norm.
-max perf&\multicolumn{1}{c}{1.00$\times$}&6391.57$\times$&118.72$\times$&36.23$\times$&\multicolumn{1}{c}{1.000$\times$}&1.007$\times$&1.000$\times$&1.001$\times$&\multicolumn{1}{c}{1.00$\times$}&384.00$\times$&16.85$\times$&19.67$\times$ \\
-Norm. min perf&&141.80$\times$&2.87$\times$&2.13$\times$&&1.000$\times$&0.975$\times$&0.815$\times$&&32.29$\times$&1.35$\times$&0.35$\times$ 
+
+Avg. Perf.&1.0x&527.0x&43.4x&52.6x&1.00x&1.00x&0.99x&0.99x&1.00x&258.70x&11.14x&8.85x \\
+Max. Perf.&1.0x&966.3x&68.0x&192.5x&1.00x&1.01x&1.00x&1.00x&1.00x&492.75x&23.83x&19.50x \\
+Geo. Mean&1.0x&289.5x&41.1x&21.8x&1.00x&1.00x&0.99x&0.99x&1.00x&172.40x&9.00x&6.16x \\
 \end{tabular}
-
-    }
-    \end{table*}
-
-\subsection{Comparing \acro with State-of-art}
-To compare the run time, memory use, and quality of \acro with those of the state-of-the-art, %As explained above, the parameters of the experimented methods are hard to compare directly.
-It is infeasible to find precisely the corresponding parameter between any two methods in this setting.
-For that reason, we have used the parameters suggested by the paper.
-we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.3$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$). 
-In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Imm} have one.
-Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex.
-In the experiments, we set ${\cal J} = 256$.
-In addition, as explained in the previous section, we use a global error threshold $\epsilon_{g} = 0.01$, a local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.\looseness=-1
-
-We present the results in Tables~\ref{tab:timings005},~\ref{tab:timings01} and~\ref{tab:timings1} for edge weights $w = 0.005$, $0.01$, and $0.1$, respectively.
-The top part of each table shows the  results for the networks, and the bottom four rows are the arithmetic mean, geometric mean, maximum and minimum, respectively, of the scores after they are normalized w.r.t.
-those of \acro's scores.
-In all tables, for the execution time (2--5) and memory (10--13) columns, lower values are better.
-For the influence scores, i.e., for columns 6--9, higher values are better.
+}\end{table*}
+
 % We note that the points missing are the runs that were unable to finished due to high memory use and killed by {\sc Out-Of-Memory Killer}.
 
-The tables show that for small and relatively sparser graphs such as {\tt NetHep}, {\tt NetPhy}, {\tt DBLP} and {\tt Amazon}, {\sc Tim+}, the high-quality baseline, has $0.1\%$--$7\%$ more influence score compared to the proposed approach.
+% The tables show that for small and relatively sparser graphs such as {\tt NetHep}, {\tt NetPhy}, {\tt DBLP} and {\tt Amazon}, {\sc Tim+}, the high-quality baseline, has $0.1\%$--$7\%$ more influence score compared to the proposed approach.
 Except {\tt DBLP}, the other sketch-based algorithm, {\sc Skim} also performs bad on these graphs.
@@
 That is given ${\cal J}$, \acro's memory use is predictable for any graph.
-On the other hand, the other methods' memory consumptions tend to increase with $w$, and their behaviours change with different parameters and graphs.
+On the other hand, the other methods' memory consumption tend to increase with $w$, and their behaviours change with different parameters and graphs.
 
@@
 Indeed, its execution time decreases as the samples and the influence graph $G$ get denser.
-On the other hand, the other methods tend to get slower under these changes.
+On the other hand, the other methods tend to get relatively slower under these changes.
+For instance, when the influence probability increases from $w = 0.005$ to $w = 0.01$, the average speedups of \acro over the baselines, i.e., {\sc Tim+}, {\sc Imm}, {\sc Skim}, and {\sc Ssa}, increase by 29$\times$, 3.1$\times$,  3.8$\times$, and 27$\times$, respectively.
 
@@
      \centering
-     \includegraphics[width=0.93\linewidth]{images/speedup-imm}
-   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=18$ threads.
+     \includegraphics[width=0.83\linewidth]{images/speedup-imm}
+   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
      \label{fig:vs-imm}} 
@@
 
- \begin{figure}[!ht] 
-     \centering
-     \includegraphics[width=0.93\linewidth]{images/speedup-skim}
-   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=18$ threads.
-     \label{fig:vs-skim}} 
- \end{figure}
+In terms of influence scores, as expected, the average influence probability seems to have a significant impact on the expected number of influenced vertices.
+For $w \in \{0.005, 0.01, 0.1\}$ this is clear; for instance, on the graph {\tt LiveJournal}, the influences obtained by \acro{} are 5892, 48182, and 1698955, respectively.
+The uniform and normal distribution with mean $w_{mean} = 0.05$ also generate influence values in between the ones generated for $w = 0.01$ and $w = 0.1$.
+On the other hand, the changes on the influence vary for different graph; for instance, when $w$ is increased from $0.01$ to $0.1$, for {\tt Slashdot} graphs, the influence increases from around $1200$ to $24000$, whereas it increases from around 1850 to 775000 for {\tt Pokec}.
 
@@
 As explained before, for larger $w$, \acro{}'s execution-time performance is usually better, and its influence quality is on par with that of {\sc Imm}.
+ \begin{figure}[!ht] 
+     \centering
+     \includegraphics[width=0.83\linewidth]{images/speedup-skim}
+   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=16$ threads.
+     \label{fig:vs-skim}} 
+ \end{figure}
 
@@
 {\sc Skim} is faster in this setting, but it has worse influence quality.
-In some settings such as {\tt Amazon} and $w = 0.01$, {\sc Skim} performs very poorly; only $39\%$ of the influence is achieved with respect to \acro.
-In addition, under the same setting, {\sc Skim} spends $59.3$ seconds whereas \acro finishes in less than one second.
+In some settings such as {\tt Amazon} and $w = 0.01$, {\sc Skim} performs very poorly; only $40\%$ of the influence is achieved with respect to \acro.
+In addition, under the same setting, {\sc Skim} spends $12.48$ seconds whereas \acro finishes in $1.2$ seconds.
+  \begin{figure}[!ht] 
+     \centering
+     \includegraphics[width=0.83\linewidth]{images/speedup-ssa}
+   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Ssa}~($\epsilon=0.2$) using $\tau=16$ threads.
+     \label{fig:vs-ssa}} 
+ \end{figure}
+
+Figure~\ref{fig:vs-ssa} compares \acro's execution-time performance with {\sc Ssa}.
+The figure shows that the proposed approach can process much larger datasets efficiently.
+For smaller datasets, {\sc Ssa} can be competitive with our approach.
+However, when the influence graph is denser, \acro{} is a few orders of magnitude faster.
+
+% both in terms of quality and speed in almost all settings.
+For the notorious {\tt Pokec} dataset, \acro performs better than {\sc Skim}, except for $w = 0.01$.
+The diameter of $G$ does not affect {\sc Skim}'s performance as much as \acro.
+{\sc Skim} is faster in this setting, but it has worse influence quality.
+In some settings such as {\tt Amazon} and $w = 0.01$, {\sc Skim} performs very poorly; only $40\%$ of the influence is achieved with respect to \acro.
+In addition, under the same setting, {\sc Skim} spends $12.48$ seconds whereas \acro finishes in 1.2 seconds.
 
@@
     \centering
-    \includegraphics[width=0.93\linewidth]{images/threads.pdf}
+    \includegraphics[width=\linewidth]{images/threads.pdf}
    \centering \caption{Scaling of \acro with multiple threads on some of largest datasets in the benchmarks.
@@
 
+The stop-and-stare algorithm proposed by Nguyen~et~al.~\cite{nguyen2016stop} utilizes an exponential checkpoint strategy for the Influence Maximization problem to verify statistical evidence on the quality of its solution.
+At each iteration, it utilizes the RIS framework to generate RR sets to find a candidate solution.
+If the quality of the solution is inferior to the expectation, the sample size is doubled.
+
 %Cohen~\cite{cohen2015all} presented the Historic Inverse Probability ({\sc HIP}) estimators which, when applied to All-Distance Sketches, outperforms the {\sc HyperLogLog} sketches~\cite{flajolet2007hyperloglog} while estimating the number of distinct elements on data streams.
@@
 
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-\bibliographystyle{IEEEtran}
+\section*{Acknowledgements}
+
+This work was supported by Scientific and Technological Research Council of Turkey (TÜBİTAK) and EuroHPC Joint Undertaking through grant agreement No 220N254 and grant agreement No 956213 (SparCity), respectively.
+The numerical calculations reported in this paper were partially performed at T{\"{U}}B\.{I}TAK ULAKB\.{I}M, High Performance and Grid Computing Center (TRUBA resources).
+
+% \ifCLASSOPTIONcaptionsoff
+%   \newpage
+% \fi
+
+% \bibliographystyle{IEEEtran}
+% \bibliographystyle{elsarticle-num}
 \bibliography{refs}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/gokhan.png}}]{G\"{o}khan~G\"{o}kt\"{u}rk} is a PhD candidate at the Faculty of Engineering and Natural Sciences in Sabancı University.
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/gokhan.png}}]{G\"{o}khan~G\"{o}kt\"{u}rk} is a PhD candidate at the Faculty of Engineering and Natural Sciences in Sabancı University.
 He has received his BS and MS degrees from Sabancı University as well.
 He is interested in High Performance Computing, Parallel Programming, and Graph Processing.
-\end{IEEEbiography}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Asst.
+% \end{IEEEbiography}
+% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./images/kamer.jpg}}]{Kamer Kaya} is an Asst.
 Professor at Sabancı University.
@@
 of Biomedical Informatics.
-His current research interests include Parallel Programming, High-Performance Computing, and Cryptography. 
-\end{IEEEbiography}
+% His current research interests include Parallel Programming, High-Performance Computing, and Cryptography. 
+% \end{IEEEbiography}
 

### 2022-09-07 paper.tex
Cleanup progress for IEEE

@@
-\documentclass[review]{elsarticle}
-\usepackage{subfiles}
+% \documentclass[10pt,journal,compsoc]{IEEEtran}
+% \usepackage{subfiles}
+% \usepackage{url}
+% \usepackage{amsmath}
+% \usepackage{xspace}
+% \usepackage{multirow}
+% \usepackage{amssymb}
+% \usepackage{algorithm}
+% \usepackage{subfig}
+% \usepackage[noend]{algpseudocode}
+% \renewcommand{\algorithmicrequire}{\textbf{Input:~}}
+% \renewcommand{\algorithmicensure}{\textbf{Output:~}}
+% \newcommand\ovr[1]{\overrightarrow{#1}}
+% \newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
+% \usepackage{booktabs}
+% \usepackage{array}
+% \usepackage{color}
+% \usepackage{listings}
+% \usepackage{placeins}
+% \usepackage{enumitem}
+% \usepackage{balance}
+% \usepackage{etoolbox}
+% \usepackage{lineno,hyperref}
+% \newcommand\acrotwo{
+% \multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
+% }
+% \renewcommand{\toprule}{}
+% \newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
+% \newcommand\kktodo[1]{\textcolor{red}{#1}}
+% \newcommand\fixme[1]{\textcolor{red}{#1}}
+% \newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
+% \newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
+% \newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
+% \newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
+% \newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}
+
+% \let\oldbibliography\thebibliography
+% \renewcommand{\thebibliography}[1]{%
+%   \oldbibliography{#1}%
+%   \setlength{\itemsep}{0pt}%
+% }
+
+% \modulolinenumbers[5]
+
+% \renewcommand{\floatpagefraction}{.98}
+% % \journal{Journal of Parallel and Distributed Computing}
+
+% %% `Elsevier LaTeX' style
+% \bibliographystyle{elsarticle-num}
+% %%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{document}
+
+% % \begin{frontmatter}
+% % \title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
+
+% % %% Group authors per affiliation:
+% % %% or include affiliations in footnotes:
+% % \author[add]{Gökhan Göktürk}
+% % % \ead{gokhan.gokturk@sabanciuniv.edu}
+
+% % \author[add]{Kamer Kaya}
+% % % \ead{kaya@sabanciuniv.edu}
+
+% % \address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}
+
+% % \IEEEtitleabstractindextext{%
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+\makeatletter
+\long\def\@makecaption#1#2{\ifx\@captype\@IEEEtablestring%
+\footnotesize\begin{center}{\normalfont\footnotesize #1}\\
+{\normalfont\footnotesize\scshape #2}\end{center}%
+\@IEEEtablecaptionsepspace
+\else
+\@IEEEfigurecaptionsepspace
+\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ #2}%
+\ifdim \wd\@tempboxa >\hsize%
+\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ }%
+\parbox[t]{\hsize}{\normalfont\footnotesize \noindent\unhbox\@tempboxa#2}%
+\else
+\hbox to\hsize{\normalfont\footnotesize\hfil\box\@tempboxa\hfil}\fi\fi}
+\makeatother
+
+%\DeclareUnicodeCharacter{2212}{-}
+\usepackage[utf8]{inputenc}
+\ifCLASSOPTIONcompsoc
+  % The IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+
+\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
+
+\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
+colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
+pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
+pdfsubject={Typesetting},%<!CHANGE!
+pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
+pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!
+
+\newcommand\rev[1]{{#1}}
+% \newcommand\rev[1]{{#1}}
+\usepackage{color,soul}
+\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
+\DeclareRobustCommand{\hll}[1]{{\sethlcolor{lightgray}\hl{#1}}}
+\newcommand\B[1]{\textbf{{{#1}}}}
+
+\usepackage{amsfonts}
 \usepackage{url}
+
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+  \graphicspath{{./images/}}
+  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}
+\else 
+\fi
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
+\usepackage{wrapfig}
+\usepackage[]{booktabs}
 \usepackage{algorithm}
-\usepackage{subfig}
 \usepackage[noend]{algpseudocode}
@@
 \newcommand\ovr[1]{\overrightarrow{#1}}
-\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
-\usepackage{booktabs}
+\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
+\newcommand\kktodo[1]{\textcolor{red}{#1}}
+\newcommand\ggx[1]{\textcolor{blue}{#1}}
+\newcommand\fixme[1]{\textcolor{red}{#1}}
+\newcommand\acrotwo{
+\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
+}
+\setlength{\intextsep}{0pt}%
+
 \usepackage{array}
@@
 \usepackage{enumitem}
-\usepackage{balance}
-\usepackage{etoolbox}
-\usepackage{lineno,hyperref}
-\newcommand\acrotwo{
-\multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
+\newcommand{\resultsize}{0.8}
+\algnewcommand{\algorithmicforeach}{\textbf{for each}}
+\algdef{SE}[FOR]{ForEach}{EndForEach}[1]
+  {\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
+  {\algorithmicend\ \algorithmicforeach}% \EndForEach
+
+\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+
+%\newcommand{\mycaption}[1]{\stepcounter{figure}\raisebox{-7pt}
+%  {\footnotesize Fig. \thefigure.\hspace{3pt} #1}}
+
+\begin{document}
+\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}
+
+\author{G\"{o}khan~G\"{o}kt\"{u}rk
+        and~Kamer~Kaya% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G.
+G\"{o}kt\"{u}rk and K.
+Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, Istanbul, Turkey.}% <-this % stops a space
+%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
 }
-\renewcommand{\toprule}{}
-\newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
-\newcommand\kktodo[1]{\textcolor{red}{#1}}
-\newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
-\newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
-\newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
-\newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
-\newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}
-
-\let\oldbibliography\thebibliography
-\renewcommand{\thebibliography}[1]{%
-  \oldbibliography{#1}%
-  \setlength{\itemsep}{0pt}%
+%FIXME
+\markboth{}%
+{G\"{o}kt\"{u}rk \MakeLowercase{\textit{et al.}}: Boosting Parallel Influence-Maximization Kernels for Undirected Networks with Fusing and Vectorization}
+
+\maketitle
+\begin{abstract}
+%     \fixme{
+% Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
+Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
 }
-
-\modulolinenumbers[5]
-
-\renewcommand{\floatpagefraction}{.98}
-\journal{Journal of Parallel and Distributed Computing}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-
-\begin{frontmatter}
-\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
-
-%% Group authors per affiliation:
-%% or include affiliations in footnotes:
-\author[add]{Gökhan Göktürk}
-\ead{gokhan.gokturk@sabanciuniv.edu}
-
-\author[add]{Kamer Kaya}
-\ead{kaya@sabanciuniv.edu}
-
-\address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}
-
-% \IEEEtitleabstractindextext{%
-\begin{abstract}
-Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
-Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
 % In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks.
-In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling.
-To estimate the number of influenced vertices throughout a diffusion, we use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate the number of influenced vertices throughout a diffusion.
+We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
 To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion.
@@
 % } 
-\begin{keyword}
-Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
-\end{keyword}
-\end{frontmatter}
+% \begin{keyword}
+% Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
+% \end{keyword}
+% \end{frontmatter}
 
@@
 
-Efficient information/influence dissemination in a network is an important research area with several applications in various fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
-As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have vital importance.
+Efficient information/influence dissemination in a network is an important research area with several applications in various fields, \fixme{such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.}
+As the study of these networks is imperative for \fixme{educational, political, economic, and social purposes,} a high-quality seed set to initiate the diffusion may have vital importance.
 Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information effectively are essential.
@@
 Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model.
-Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, proved it to be NP-hard, and provided a greedy Monte-Carlo approach that has a constant approximation ratio over the optimal solution.
+Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, \fixme{proved it to be NP-hard,} and provided a greedy Monte-Carlo approach that has a \fixme{constant approximation ratio over the optimal solution}.
 This greedy approach is one of the most frequently applied algorithms for IM.
@@
 Although they perform well in terms of seed-set quality, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices as a consequence of their expensive simulation costs.
-Due to this reason, many heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}.
+Due to this reason, many \fixme{heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}}.
 
@@
 
-Simulating a greedy algorithm in parallel is a straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
+Simulating a greedy algorithm in \fixme{parallel} is a \fixme{straightforward} workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
 However, for large networks, a parallel, greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges even if a large number of processing units/cores are available.
@@
 \begin{itemize} [leftmargin=0.3cm]
-\item We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.
-The proposed scheme samples the edges as they are traversed across several simulations.
+\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.} The proposed scheme samples the edges as they are traversed across several simulations.
 Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
 
-\item Running concurrent simulations on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
+\item \fixme{Running concurrent simulations} on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
 While traversing an edge, \acro concurrently performs multiple diffusion simulations while using only a single (8-bit) value per vertex for each simulation.
@@
 
-The paper is organized as follows: 
-In Section~\ref{sec:background}, we present 
-the background on IM and introduce the mathematical notation. 
-Section~\ref{sec:method} describes the proposed approach in detail.
-In Section~\ref{sec:evaluation}, a thorough performance evaluation is provided by conducting experiments on various real-world datasets and influence settings.
+% \fixme{The paper is organized as follows: 
+% In Section~\ref{sec:background}, we present 
+% the background on IM and introduce the mathematical notation. 
+% Section~\ref{sec:method} describes the proposed approach in detail.}
+% In Section~\ref{sec:evaluation}, a thorough performance evaluation \fixme{is provided by conducting experiments on various real-world datasets and influence settings.
 A detailed empirical comparison with the state-of-the-art from the literature is also given.
 Section~\ref{sec:relatedwork} presents a comparative overview of the existing work.
-Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.
+Finally, Section~\ref{sec:conclusion} discusses future work and concludes the paper.}
 
@@
 
-Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations among them.
+\fixme{Let $G = (V,E)$ be a} directed \fixme{graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations} among them.
 An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$.
-The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^-_{G}(v) = \{u: (u,v) \in E\}$.
-Similarly, the {\em outgoing} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^+_{G}(v) = \{u: (v,u) \in E\}$.
+The {\em incoming} \fixme{neighborhood of a vertex $v \in V$ is denoted as $\Gamma^-_{G}(v) = \{u: (u,v) \in E\}$.} Similarly, the {\em outgoing} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^+_{G}(v) = \{u: (v,u) \in E\}$.
 A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$.
@@
 \end{table}
-\FloatBarrier
+% \FloatBarrier
 \subsection{Influence Maximization}
 
-Influence Maximization aims to find a seed set $S \subseteq V$ among all possible size $K$ subsets of $V$ that maximizes an {\em influence spread function} $\sigma$  when the diffusion process is initiated from $S$.
-%Although we focus on graphs with bidirectional edges, for IM, the edges can be unidirectional depending on the initial construction.
+Influence Maximization aims to find a seed set $S \subseteq V$ among \fixme{all possible size $K$ subsets of $V$ that maximizes an {\em influence spread function} $\sigma$  when the diffusion process is initiated from $S$.} %Although we focus on graphs with bidirectional edges, for IM, the edges can be unidirectional depending on the initial construction.
 That is although the edges $\{u, v\} \in E$ are assumed to be bidirectional, throughout the diffusion process, we use $(u, v)$~($(v, u)$) as the edge that may be used to influence/activate $v$~($u$) given that $u$~($v$) has already been influenced/activated.
@@
 
-\begin{figure}[!ht] 
-    \centering
-  \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.26\linewidth]{images/ic.pdf}}
-  \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.26\linewidth]{images/wc.pdf}}
-    \\% IMAGES HERE
-  \caption{\small{\protect\subref{fig:ic} 
-The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
-\protect\subref{fig:wc}
-The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
-  }}
-  %\label{fig_ic_model} 
-  \label{fig:xx} 
-\end{figure}
-
-\begin{itemize}[leftmargin=*]
-\item The {\bf Independent Cascade} model works in rounds and activates a vertex $v$ in the current round if one of $v$'s incoming edges $(u, v)$ is used during the diffusion round, which happens with the activation probability $w_{u, v}$, given that $u$ has already been influenced in the previous rounds.
-The activation probabilities are independent (from each other and previous activations) in the {\em independent cascade} model, which we focus on in this paper.
+% \begin{figure}[!ht] 
+%     \centering
+%   \subfloat[\small{IC}\label{fig:ic}]{%
+%        \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
+%   \subfloat[\small{WC}\label{fig:wc}]{%
+%         \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
+%     \\% IMAGES HERE
+%   \caption{\small{\protect\subref{fig:ic} 
+% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
+% \protect\subref{fig:wc}
+% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
+%   }}
+%   %\label{fig_ic_model} 
+%   \label{fig:xx} 
+% \end{figure}
+
+% \begin{itemize}[leftmargin=*]
+% \item The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds.
+The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper.
 A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
-In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
-
-\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
-The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
-of incoming edges of $v$~(which in the original graph is equal to $\Gamma^-_G(v)$).
-Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
-%\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
-% Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}.
+% In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.
+
+% \item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
+% The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
+% of incoming edges of $v$~(which in the original graph is equal to $\Gamma^-_G(v)$).
+% Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
+% %\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
+% % Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}.
 However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.
 
-%$ {|E^G_{u,v}|}/{|E^G_{u}|}$ where $|E^G_{u,v}|$ is the number of parallel $\{u, v\}$ edges and $|E^G_{u}|$ is the number of $\{u, .\}$ edges, i.e., all of $u$'s edges in the undirected graph.
-
-\item{\bf Linear Threshold} model generalizes the IC model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
-All the $(u, v)$ edges with active $u$ vertices are taken into account in the process.
+% %$ {|E^G_{u,v}|}/{|E^G_{u}|}$ where $|E^G_{u,v}|$ is the number of parallel $\{u, v\}$ edges and $|E^G_{u}|$ is the number of $\{u, .\}$ edges, i.e., all of $u$'s edges in the undirected graph.
+
+% \item{\bf Linear Threshold} model \fixme{generalizes} the IC \fixme{model and activates the vertex $v$} once the cumulative \fixme{activation coming} from its \fixme{neighbors} exceeds a given \fixme{threshold $\theta_v$}.
+% \fixme{All the $(u, v)$ edges with active $u$ vertices are taken into account} in the process.
 Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.
-%Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
-\end{itemize}
-
+% %Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
+% \end{itemize}
+
+% \setlength{\columnsep}{1.2pt}%
+\begin{wrapfigure}{r}{0.3\linewidth}
+    \begin{center}
+      \includegraphics[width=1\linewidth]{images/ic.pdf}
+    \end{center}
+    \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
+  \end{wrapfigure}
+  The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds.
+The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper.
+A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
+  % In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing. 
 %As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}.
@@
 \subsection{Count-Distinct Sketches}\label{sec:sketch}
+
+% \begin{figure}[!ht] 
+%     \centering
+%   \subfloat[\small{IC}\label{fig:fminit}]{%
+%        \includegraphics[width=0.5\linewidth]{images/fminit.pdf}}
+%   \subfloat[\small{WC}\label{fig:fmmerge}]{%
+%         \includegraphics[width=0.5\linewidth]{images/fmmerge.pdf}}
+%     \\% IMAGES HERE
+%   \caption{\small{\protect\subref{fig:fm} 
+% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
+% \protect\subref{fig:wc}
+% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
+%   }}
+%   %\label{fig_ic_model} 
+%   \label{fig:xx} 
+% \end{figure}
+
 The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$.
@@
 
-Count-Distinct Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates.
+Count-Distinct~Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates.
 Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities.
@@
 
-\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
+\begin{wrapfigure}{l}{0.45\linewidth}
+    \begin{center}
+      \includegraphics[width=1\linewidth]{images/fminit.pdf}
+    \end{center}
+    \caption{Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.}
+  \end{wrapfigure}
+The method first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
 Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
@@
 
+\begin{wrapfigure}{l}{0.35\linewidth}
+    \begin{center}
+      \includegraphics[width=1\linewidth]{images/fmmerge.pdf}
+    \end{center}
+    \caption{Example of merging vertex $x$ and $y$ with four registers.}
+  \end{wrapfigure}
 Throughout the process, each register is used only for a single sample/simulation. 
@@
 \subsection{Hash-based Fused Sampling}
-The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process.
+The probabilistic nature of cascade models \fixme{requires} sampling \fixme{subgraphs from $G = (V, E)$ to simulate the diffusion process}.
 If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel.
@@
     \subfloat[\label{fig:sims}]{%
-        \includegraphics[width=0.35\linewidth]{images/samples.pdf}
+        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
     } 
     \subfloat[\label{fig:fused}]{%
-     \includegraphics[width=0.35\linewidth]{images/fused.pdf}}
+     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
   \caption{\small{
@@
 where $||$ is the concatenation operator. 
-In our preliminary experiments, we have tried a set of hash algorithms and found that {\sc Crc32}~\cite{koopman200232} and {{\sc Murmur3}} are good candidates for {\sc Hash}.
+% In our preliminary experiments, we have tried a set of hash algorithms and found that {\sc Crc32}~\cite{koopman200232} and {{\sc Murmur3}} are good candidates for {\sc Hash}.
 {{\sc Murmur3}} was slightly faster than {\sc Crc32} with better randomness properties.
-After a preliminary analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
+% After a preliminary analysis, \fixme{we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.} 
 An  important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory.
@@
 
-Although the $h(.)$ function described above generates a unique hash value for each edge, and hence can be used to generate a unique sampling probability, different simulations require different probabilities.
-To enable this, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated for each edge.
-Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
+% Although the $h(.)$ function described above \fixme{generates a unique hash value for each edge, and hence can be used to generate a unique sampling probability, different simulations require different probabilities.} To enable this,
+
+A set of uniformly \fixme{ randomly chosen numbers $X_r \in_R [0, h_{max}]$ } associated with each sample $r$ are generated for each edge to generate a unique sampling probabilities for all samples.
+Then, the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
 Formally,
@@
 % The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
-The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.
-One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation which is crucial since \acro{} recomputes this probability value each time the corresponding edge is read from the memory.
+The edge $(u,v)$ exists \fixme{in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.} One of this approach's benefits is that an edge can be sampled using \fixme{a single XOR and compare-greater-than operation} which is crucial since \acro{} recomputes this probability value each time the corresponding edge is read from the memory.
 In practice, we do not apply the division operation since $h_{max}$ is a constant value and the same for every edge and simulation.
-Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.
-
-\begin{figure}[!ht] 
-    \centering
-    \includegraphics[width=0.8\linewidth]{./images/CDF.pdf}
-    \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
-    \label{fig:prob-cdf} 
-\end{figure}
-
-Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
+Moreover, the corresponding control flow branch overhead can be \fixme{removed} using {\em conditional move} \fixme{instructions}.
+
+% \begin{figure}[!ht] 
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{./images/CDF.pdf}
+%     \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
+%     \label{fig:prob-cdf} 
+% \end{figure}
+
+% Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
 This property allows us to generate good-enough pseudo-random values for fair sampling.
@@
 % and the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}). 
-As Figure~\ref{fig:prob-cdf} shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution. 
+% As Figure~\ref{fig:prob-cdf} shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution. 
 % Furthermore, the latter shows that the bias is insignificant for each network.
@@
 %Being able to generate the samples on the fly allows us to avoid many memory accesses. 
-One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$.
+% One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$.
 As mentioned above, the edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains.
@@
 Once the incoming edges of all live vertices are processed, the iteration ends.
-Figure~\ref{fig:hf-processing} shows how \acro performs two simulations at the same time using sketch registers.
+% Figure~\ref{fig:hf-processing} shows how \acro performs two simulations at the same time using sketch registers.
 
@@
 
-\begin{figure*}[!ht]
-    \begin{center}
-    \includegraphics[width=0.85\linewidth]{images/sketch-diffusion.pdf}
-    \caption{\small{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes.
+% \begin{figure*}[!ht]
+%     \begin{center}
+%     \includegraphics[width=0.85\linewidth]{images/sketch-diffusion.pdf}
+%     \caption{\small{(a) The initial state on the toy graph for \acro{}; all vertices are set as live~(green), and their registers are initialized with the length of the zero prefix of their hashes.
 (b)
-    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
-    For the ($1, 4$) edge which is live for both simulations, 1's registers are set to the maximum of both 1's and 4's registers.
+%     % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
+%     For the ($1, 4$) edge which is live for both simulations, 1's registers are set to the maximum of both 1's and 4's registers.
 The ($4, 3$) edge is live only in the second simulation.
@@
 As no live vertices exist, the process stops.}}\label{fig:hf-processing}
-    \end{center}
-    \end{figure*}
+%     \end{center}
+%     \end{figure*}
 
@@
     \begin{center}
-    \includegraphics[width=0.73\linewidth]{images/sketch-saturation.pdf}
+    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
     \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
@@
         \subfloat[{\tt LiveJournal} execution time in seconds\label{fig:lj-time}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_time.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
     }
+    \subfloat[{\tt Orkut} execution time in seconds\label{fig:Orkut-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
+        }
+    \subfloat[{\tt Pokec} execution time in seconds\label{fig:Pokec-time}]{%
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
+        }\\
         \subfloat[{\tt LiveJournal} influence score\label{fig:lj-score}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_LiveJournal_score.pdf}
-        }\\
-
-    \subfloat[{\tt Orkut} execution time in seconds\label{fig:Orkut-time}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_time.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
         }
         \subfloat[{\tt Orkut} influence score\label{fig:Orkut-score}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_Orkut_score.pdf}
-        }\\
-    \subfloat[{\tt Pokec} execution time in seconds\label{fig:Pokec-time}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_time.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
         }
     \subfloat[{\tt Pokec} influence score\label{fig:Pokec-score}]{%
-        \includegraphics[width=0.48\linewidth]{images/heatmap_Pokec_score.pdf}
+        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
         }
@@
 
-\subsection{Correctness of \acro{}} 
-The greedy solution for influence maximization is well studied and proven to be correct~\cite{kempe2003maximizing}.
+% \subsection{Correctness of \acro{}} 
+% The greedy solution for influence maximization is well studied and proven to be correct~\cite{kempe2003maximizing}.
 \acro uses the same optimization method but replaces reachability set computations with sketches instead of per-vertex graph traversal and labeling.
@@
 
-Flajolet-Martin sketches processes elements in a stream to estimate distinct elements observed; for reachability set computations, instead of a stream, we process a spanning tree on the sampled graph.
+% Flajolet-Martin sketches processes elements in a stream to estimate distinct elements observed; for reachability set computations, instead of a stream, we process a spanning tree on the sampled graph.
 Instead of adding the elements one by one, sketches that are connected is merged.
@@
 
-To efficiently process real-life graphs, \acro uses the Compressed Sparse Row~(CSR) graph data structure.
-In CSR, an array, $ptrs$, holds the starting indices of the adjacency lists for each vertex, while another array, $adj$, holds the actual adjacency lists (i.e., the outgoing neighbors) one after another.
+To efficiently process real-life graphs, \acro uses the Compressed Sparse Row~(CSR) graph data structure.\fixme{ In CSR, an array, $ptrs$, holds the starting indices} of the adjacency lists for each vertex, while \fixme{another} array, \fixme{$adj$, holds} the actual adjacency lists (i.e., the outgoing neighbors) one after another.
 Hence, the adjacency list of vertex $i$ is located in $adj$ at locations $adj[ptrs[i], \ldots, ptrs[i+1] - 1]$.
@@
 % \scalebox{0.95}{
-\resizebox{0.75\columnwidth}{!}{
+\resizebox{1\columnwidth}{!}{
 \begin{tabular}{ll||r|r|r|r}
@@
 \hline
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Undirected}}& {\tt Amazon0302} & 262,113 & 1,234,878 & 4.71 & 32\\
+\multirow{3}{*}{\scriptsize\rotatebox[origin=c]{90}{Undirected}}& {\tt Amazon0302} & 262,113 & 1,234,878 & 4.71 & 32\\
 &{\tt DBLP} & 317,081 & 1,049,867  & 3.31 & 21\\
@@
 \hline
-\multirow{6}{*}{\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838  & 6.71 & 14\\
+\multirow{6}{*}{\scriptsize\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838  & 6.71 & 14\\
 &{\tt Friendster} & 65,608,366 & 1,806,067,135  & 27.53 & 32\\
@@
 Five diffusion settings are simulated for a comprehensive experimental evaluation; for each network, we use 
+\fixme{
 \begin{enumerate}
@@
 \end{enumerate}
-
+}
 \noindent We selected $w=0.005$ as a setting to challenge \acro.
@@
         \centering
-        \resizebox{\linewidth}{!}{
+        \resizebox{\resultsize\linewidth}{!}{
 
@@
 \begin{table*}
-    \setlength{\tabcolsep}{2.5pt}
+    \setlength{\tabcolsep}{1.2pt}
         \caption{Execution times~(in secs), inf.
@@
 \begin{table*}
-    \setlength{\tabcolsep}{2.5pt}
+    \setlength{\tabcolsep}{1.2pt}
         \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds, $\tau=16$ threads and $w \in U(0,0.1)$.
@@
      \centering
-     \includegraphics[width=0.83\linewidth]{images/speedup-imm}
-   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
+     \includegraphics[width=1\linewidth]{images/speedup-imm}
+   \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
      \label{fig:vs-imm}} 
@@
      \centering
-     \includegraphics[width=0.83\linewidth]{images/speedup-skim}
-   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=16$ threads.
+     \includegraphics[width=1\linewidth]{images/speedup-skim}
+   \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=16$ threads.
      \label{fig:vs-skim}} 
@@
      \centering
-     \includegraphics[width=0.83\linewidth]{images/speedup-ssa}
-   \centering \caption{Speedups obtained by \acro{}~(${\cal J} = 256$) over {\sc Ssa}~($\epsilon=0.2$) using $\tau=16$ threads.
+     \includegraphics[width=1\linewidth]{images/speedup-ssa}
+   \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Ssa}~($\epsilon=0.2$) using $\tau=16$ threads.
      \label{fig:vs-ssa}} 
@@
 
-\begin{figure*}[!ht] 
-    \centering
-    \includegraphics[width=\linewidth]{images/threads.pdf}
-   \centering \caption{Scaling of \acro with multiple threads on some of largest datasets in the benchmarks.
-     \label{fig:scaling}} 
-\end{figure*}
+% \begin{figure*}[!ht] 
+%     \centering
+%     \includegraphics[width=0\linewidth]{images/threads.pdf}
+%    \centering \caption{Scaling of \acro with multiple threads on some of largest datasets in the benchmarks.
+%      \label{fig:scaling}} 
+% \end{figure*}
 
@@
 However, the performance may suffer due to false sharing.
-Figure~\ref{fig:scaling} shows \acro's speedup values obtained via a simple {\tt OpenMP} parallelization at line~\ref{ln:inner_start} of Algorithm~\ref{algo:diffusion-step}.
+% Figure~\ref{fig:scaling} shows \acro's speedup values obtained via a simple {\tt OpenMP} parallelization at line~\ref{ln:inner_start} of Algorithm~\ref{algo:diffusion-step}. 
 Even though the pull-based diffusion shows a nice parallel performance, it is possible to implement \acro using other approaches such as the {\em queue-based} approach which may improve performance by only processing live vertices.
@@
 
-Although they can be inferior in terms of influence, modern IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.
-Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate the influence~\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step~\cite{leskovec2009community} greatly reduces the execution times.
+% \fixme{Although they can be inferior in terms of influence, modern IM algorithms are shown to be quite fast compared to conventional simulation-based approaches such as {\sc MixGreedy}.} 
+% \ggx{Note: The next line is taken from another place.}
+% \fixme{Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate the influence~\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step~\cite{leskovec2009community} greatly reduces} the execution times.
 \acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling.
@@
 Sketch-based IM methods are cheaper compared to simulation-based methods. 
-They usually pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively.
+% They usually \fixme{pre-compute the sketches by processing the graph for evaluating the influence spread instead of running simulations repetitively.} 
 A popular method for sketch-based IM is {\sc Skim}~\cite{cohen2014sketch} by Cohen~et~al.
@@
 
-The Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al.
-runs a proxy model and prunes paths with probabilities smaller than a given threshold in parallel.
-The approach only keeps a dense but small part of the network and scalable to only sparse networks.
+% \fixme{The Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al.
+runs a proxy model and prunes paths with probabilities} smaller \fixme{than a given threshold} in parallel.
+\fixme{The approach only keeps a dense but small part of the network and scalable to only sparse networks.
 Liu~et~al.
@@
 The GPU implementation is up to $60\times$ faster with an average speedup of  $24.8\times$.
-
-Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS) which samples a fraction of all random reverse reachable sets.
+}
+
+% \fixme{Borgs~et~al.~\cite{borgs2014maximizing} proposed Reverse Influence Sampling~(RIS) which samples a fraction of all random reverse reachable sets.
 The number of necessary samples to find the seed set is calculated based on the number of visited vertices.
@@
 improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast} with high efficiency.
-Recently, the authors extended the algorithm to work in a multi-GPU setting~\cite{curipples}.
+Recently, the authors extended the algorithm to work in a multi-GPU setting~\cite{curipples}.}
 
@@
 % \bibliographystyle{elsarticle-num}
+\bibliographystyle{IEEEtranS}
+% argument is your BibTeX string definitions and bibliography database(s)
 \bibliography{refs}

### 2022-10-07 paper.tex
progress

@@
 \newcommand\ggx[1]{\textcolor{blue}{#1}}
-\newcommand\fixme[1]{\textcolor{red}{#1}}
+\newcommand\fixme[1]{#1}
+% \newcommand\fixme[1]{\textcolor{red}{#1}}
 \newcommand\acrotwo{
@@
 }
-\setlength{\intextsep}{0pt}%
+% \setlength{\intextsep}{1pt}%
 
@@
 \usepackage{enumitem}
-\newcommand{\resultsize}{0.8}
+\newcommand{\resultsize}{0.6}
 \algnewcommand{\algorithmicforeach}{\textbf{for each}}
@@
 
+HyperFuser uses \emph{directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy.
+On the other hand, {\sc InFuseR}~\cite{infuser} employs {\emph {undirected}} hash-based fused sampling and CELF optimizations for seed selection.
+
 Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, and removing the latent seed set's residual reachability set.
@@
 
-\begin{wrapfigure}{l}{0.45\linewidth}
-    \begin{center}
-      \includegraphics[width=1\linewidth]{images/fminit.pdf}
-    \end{center}
-    \caption{Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.}
-  \end{wrapfigure}
-The method first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
+% \begin{wrapfigure}{l}{0.45\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fminit.pdf}
+%     \end{center}
+%     \caption{Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.}
+%   \end{wrapfigure}
+
+% The method first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
 Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
@@
 
-\begin{wrapfigure}{l}{0.35\linewidth}
-    \begin{center}
-      \includegraphics[width=1\linewidth]{images/fmmerge.pdf}
-    \end{center}
-    \caption{Example of merging vertex $x$ and $y$ with four registers.}
-  \end{wrapfigure}
+% \begin{wrapfigure}{l}{0.35\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fmmerge.pdf}
+%     \end{center}
+%     \caption{\label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers.}
+%   \end{wrapfigure}
+
 Throughout the process, each register is used only for a single sample/simulation. 
 For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
+The toy example in Fig.~\ref{fig:fmops} shows how the sketch operations are done on a toy problem.
+In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers.
+In Fig.~\ref{fig:fmops}(a), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets.
+Fig.~\ref{fig:fmops} shows writing the merged reachability sets back to registers w.r.t sampling using a conditional move operation.
+
 %if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
 %A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
+
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/fmops.pdf}
+    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.
+(b) \label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers.
+(c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t sampling in $\hat{G}$.
+     }\label{fig:fmops} 
+    \end{center}
+\end{figure}
+
 That is, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
@@
 %Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.
+
+% \begin{wrapfigure}{l}{0.35\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fmwrite.pdf}
+%     \end{center}
+%     \caption{Example of writing merged sketch $M_{xy}$ in fig.\ref{fmmerge} back to $M_x$ w.r.t diffusion process.}
+%   \end{wrapfigure}
 
@@
 This approach can be seen as a bottom-up, i.e., reversed,  diffusion process where at each iteration, the cardinality information is pulled from vertices neighbors.
+ \begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/infuserdiff.pdf}
+    \caption{InFuseR diffusion process illustrated for only vertex $1$ on toy sample graph.
+(a) \label{fig:infuserinit} Toy graph InFuseR initialization.
+(b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$.
+(c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
+     }\label{fig:infuserdiff} 
+    \end{center}
+\end{figure}
+ \begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/sketchdiff.pdf}
+    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
+(a)\label{hyperinit} Toy sketch initialization.
+(b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices.
+(c) \label{hyperdiff2} Second level diffusion following Fig.\ref{fig:hyperdiff}(a), only updated vertices' sketches are pulled.
+     }\label{fig:hyperdiff} 
+    \end{center}
+\end{figure}
+
 %  If a vertex $u$ is live, its outgoing edges $(u, v)$ s.t.
@@
 We used $\epsilon_c = 0.02$ to make \acro faster while keeping its quality almost the same.
+Figure~\ref{fig:hyperdiff} shows a toy problem diffusion process on 4 vertices and a single sample, the process initializes sketches using respective hashes' leading zeros and bigger numbers are pulled from all recently changed neighbors.
+Whereas Infuser works vertices one by one, labeling visited vertices for the processed vertex.
+The process is repeated for multiple vertices until a seed vertex is found.
+Figure~\ref{fig:infuserdiff} shows an example in the same settings as Figure~\ref{fig:hyperdiff} to emphasize the difference between the two algorithms.
 
@@
 {\tt AVX2} instructions are utilized by handcrafted code with vector intrinsics.
+\\
 
@@
 \end{table}
-\FloatBarrier
+% \FloatBarrier
 \subsection{Experiment Settings} \label{sec:expset}
@@
 
-In this work, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and error-adaptive rebuilding.
+In this work, we propose a sketch-based Influence Maximization algorithm that employs fused sampling and a novel error-adaptive rebuilding strategy.
 We provide a fast implementation of the algorithm that utilizes multi-threading to exploit multiple cores.

### 2022-10-13 paper.tex
progress

@@
 %     \fixme{
-% Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
+Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
 Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
-}
-% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks.
+% }
+In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks.
 In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate the number of influenced vertices throughout a diffusion.
@@
 Fig.~\ref{fig:fmops} shows writing the merged reachability sets back to registers w.r.t sampling using a conditional move operation.
+In the example, we see four possible situations that can happen; The operations on the first registers show moving bigger register $M_v[1]$ to $M_u[0]$.
+The second one shows the opposite, a bigger number is on the target register and there is no edge between $u$ and $v$ in sample graph $\hat{G}$.
+The third one shows an example when $M_v[3]$ is bigger than $M_u[3]$ but there is no edge between $u$ and $v$ in sample graph $\hat{G}$.
+The operations on the fourth register show when there is an edge between $u$ and $v$ but $M_u[4]$ is smaller than $M_v[4]$ so the move operation is not needed.
 
@@
 This approach can be seen as a bottom-up, i.e., reversed,  diffusion process where at each iteration, the cardinality information is pulled from vertices neighbors.
- \begin{figure}[!ht]
-    \begin{center}
-    \includegraphics[width=\linewidth]{images/infuserdiff.pdf}
-    \caption{InFuseR diffusion process illustrated for only vertex $1$ on toy sample graph.
-(a) \label{fig:infuserinit} Toy graph InFuseR initialization.
-(b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$.
-(c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
-     }\label{fig:infuserdiff} 
-    \end{center}
-\end{figure}
- \begin{figure}[!ht]
-    \begin{center}
-    \includegraphics[width=\linewidth]{images/sketchdiff.pdf}
-    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
-(a)\label{hyperinit} Toy sketch initialization.
-(b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices.
-(c) \label{hyperdiff2} Second level diffusion following Fig.\ref{fig:hyperdiff}(a), only updated vertices' sketches are pulled.
-     }\label{fig:hyperdiff} 
-    \end{center}
-\end{figure}
 
@@
 Figure~\ref{fig:infuserdiff} shows an example in the same settings as Figure~\ref{fig:hyperdiff} to emphasize the difference between the two algorithms.
+Please notice that in the given examples, \acro{} computes estimated influence for \emph{all} vertices, whereas InFuseR only computes influence for vertex $1$.
+Due to this reason, on Figure~\ref{fig:infuserdiff} reachability sets are shown for all vertices with dense vectors, the sets that are not currently manipulated are greyed out in the figure.
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/sketchdiff.pdf}
+    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
+(a)\label{hyperinit} Toy sketch initialization.
+(b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices.
+(c) \label{hyperdiff2} Second level diffusion following Fig.\ref{fig:hyperdiff}(a), only updated vertices' sketches are pulled.
+     }\label{fig:hyperdiff} 
+    \end{center}
+\end{figure}
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/infuserdiff.pdf}
+    \caption{InFuseR diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.
+(a) \label{fig:infuserinit} Toy graph InFuseR initialization.
+(b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$.
+(c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
+     }\label{fig:infuserdiff} 
+    \end{center}
+\end{figure}
 

### 2022-11-08 paper.tex
Update on Overleaf.

--- 2022-10-07 paper.tex
@@
 %     \fixme{
-% Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
+Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
 Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
-}
-% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks.
-In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate the number of influenced vertices throughout a diffusion.
+% }
+In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not step-by-step simulate the diffusion process, have been proposed in the literature to cope with the scale of today's networks.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate, not to count, the number of influenced vertices throughout a diffusion.
 We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
@@
 
-\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Ripples}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
 The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.
@@
 % \setlength{\columnsep}{1.2pt}%
-\begin{wrapfigure}{r}{0.3\linewidth}
+\begin{wrapfigure}{r}{0.35\linewidth}
     \begin{center}
@@
 Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$.
+Via sketches, \acro can estimate the reachability set cardinalities with much less memory and computation compared to the exact counting solutions.
 
@@
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
-If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\Theta(n)$ time complexity. 
+If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory are required where each merge operation has $\Theta(n)$ time complexity.
 If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
@@
 Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities.
-The essence of an FM sketch is that it keeps the track of how rare the elements are in a stream.
+The essence of an FM sketch is that it keeps track of how rare the elements are in a stream.
 The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
@@
 
-HyperFuser uses \emph{directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy.
-On the other hand, {\sc InFuseR}~\cite{infuser} employs {\emph {undirected}} hash-based fused sampling and CELF optimizations for seed selection.
+\acro{} uses {\em directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy.
+An IM tool leveraging fusing is~{\sc InFuseR}~\cite{infuser} which employs {\emph {undirected}} hash-based fused sampling and CELF optimizations~\cite{CELF} for seed selection to find the best seed set.
+Unlike {\sc InFuseR}, \acro{} follows a completely different approach and only estimates the cardinalities of the reachability sets and do not compute them.
 
@@
 
-Throughout the process, each register is used only for a single sample/simulation. 
-For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
-The toy example in Fig.~\ref{fig:fmops} shows how the sketch operations are done on a toy problem.
-In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers.
-In Fig.~\ref{fig:fmops}(a), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets.
-Fig.~\ref{fig:fmops} shows writing the merged reachability sets back to registers w.r.t sampling using a conditional move operation.
-
-%if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
-%A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
-
-\begin{figure}[!ht]
-    \begin{center}
-    \includegraphics[width=\linewidth]{images/fmops.pdf}
-    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.
-(b) \label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers.
-(c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t sampling in $\hat{G}$.
-     }\label{fig:fmops} 
-    \end{center}
-\end{figure}
-
-That is, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
-This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
 %At each iteration, the sketches of the existing reachable vertices are modified.
@@
 
-After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches.
-Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations.
+\acro performs $K$ iterations to find $K$ vertices.
+Each iteration starts by estimating the reachability set cardinalities for all the vertices and keeping this information within sketches.
+After this, \acro picks the vertex $v$ with the largest cardinality by evaluating these sketches.
+It then finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations.
 The vertices in this reachability set are removed from the live set $L$.
@@
 Hence, in later iterations, these vertices will not contribute to the marginal gain.
-Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate.
-The proposed approach and the algorithm will be described in this section in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
+Although the same sketch memory can be used for a couple of iterations, i.e., seed vertex searches, we have observed that sketches become dirty and a rebuild is necessary.
+Hence, finally, the algorithm checks if sketch rebuilding is necessary based on the difference between the sketch estimate and Monte-Carlo estimate.
+The proposed approach and the algorithm is described here in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
 $u \notin R_S$ şeklinde.}
@@
 %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
-
-\subsection{Estimating Reachability Set Cardinality}
+\subsection{Estimating Reachability Set Cardinalities}
+
+To estimate the cardinality of a reachability set, \acro{} performs a cheap diffusion process over the sample subgraphs by using a single sketch register for a single sample/simulation. 
+For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
+The toy example in Fig.~\ref{fig:fmops} with  ${\cal J} = 4$ shows how the sketch operations are done on a toy problem.
+In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers.
+In Fig.~\ref{fig:fmops}(b), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets.
+All these operations are performed using vectorized instructions.
+
+ To vectorize the rest of the process, we leverage conditional move operations.
+Although an edge ($u, v$) is inside the graph, it may not be in all the samples.
+In the toy example of Fig.~\ref{fig:fmops}, we assume that ($u, v$) only exists in the first and the last sample.
+ Fig.~\ref{fig:fmops}(c) writes the merged reachability sets back to $u$'s registers.
+For the first sample, $M_u[1]$ needs an update.
+The operations for the second and the third rows/samples are skipped since ($u, v$) does not exist in these samples.
+The fourth row shows the case with ($u$, $v$) is in the sample but $M_u[4] < M_v[4]$.
+Hence, the move operation is not needed.
+However, for such cases, we still perform this write as a part of the vectorized operation.
+This being said, we skip the whole Fig.~\ref{fig:fmops}(c) when ($u, v$) is not in any of these samples.
+
+%if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
+%A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
+
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=\linewidth]{images/fmops.pdf}
+    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $u$ with four registers and 4-bit hash functions.
+(b) \label{fmmerge} Example of union operation on sketches of vertices $u$ and $v$ with four registers.
+(c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t.
+sampled subgraph.
+     }\label{fig:fmops} 
+    \end{center}
+\end{figure}
+
+To summarize, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
+This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
+
+\subsection{Finding the Seed Set}
 A greedy solution to IM requires finding a vertex with a maximum marginal influence at each step until the seed set size reaches $K$.
@@
 We used $\epsilon_c = 0.02$ to make \acro faster while keeping its quality almost the same.
-Figure~\ref{fig:hyperdiff} shows a toy problem diffusion process on 4 vertices and a single sample, the process initializes sketches using respective hashes' leading zeros and bigger numbers are pulled from all recently changed neighbors.
-Whereas Infuser works vertices one by one, labeling visited vertices for the processed vertex.
-The process is repeated for multiple vertices until a seed vertex is found.
-Figure~\ref{fig:infuserdiff} shows an example in the same settings as Figure~\ref{fig:hyperdiff} to emphasize the difference between the two algorithms.
+
+Figure~\ref{fig:hyperdiff} shows a toy diffusion process on four vertices and a single sample.
+The process initializes sketches using respective hashes' number of leading zeros.
+Then larger numbers are started to be pulled from all recently changed neighbors.
+The same process is repeated for multiple vertices until the new seed vertex is found.
+To understand the benefits of estimating (instead of counting), we present Fig.~\ref{fig:infuserdiff} which shows an example in the same settings as Fig.~\ref{fig:hyperdiff}.
+One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas {\sc InFuseR}, or another counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example).
+Doing otherwise, i.e., computing the reachability set cardinalities for all the vertices at once for a given sample, may require $\mathcal{O}(n^2)$ memory and union operations with $\mathcal{O}(n)$ complexity.
+Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
+%This is why although the reachability sets in Fig.~\ref{fig:infuserdiff} are shown for all vertices with dense vectors, the ones except that of vertex 1 are greyed out since they are not manipulated.
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=0.95\linewidth]{images/sketchdiff.pdf}
+    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
+(a)\label{hyperinit} Toy sketch initialization.
+(b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices.
+(c) \label{hyperdiff2} Second level diffusion following (a); only updated vertices' sketches are pulled.
+     }\label{fig:hyperdiff} 
+    \end{center}
+\end{figure}
+\begin{figure}[!ht]
+    \begin{center}
+    \includegraphics[width=0.85\linewidth]{images/infuserdiff.pdf}
+    \caption{{\sc InFuseR} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.
+(a) \label{fig:infuserinit} Toy graph InFuseR initialization.
+(b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$.
+(c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
+     }\label{fig:infuserdiff} 
+    \end{center}
+\end{figure}
 
@@
 % \FloatBarrier
-\subsection{Experiment Settings} \label{sec:expset}
+\subsection{Experimental Settings} \label{sec:expset}
 
@@
 
-We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, {\sc Imm}, and {\sc Ssa}.
+We evaluated our method against four other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, {\sc Ripples}, and {\sc Ssa}.
 The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account.
@@
 
-\item Minutoli et al.'s {\sc Imm} is a high-performance, parallel algorithm that efficiently produces accurate seed sets~\cite{minutoli2019fast}. 
+\item Minutoli et al.'s {\sc Ripples} is a high-performance, parallel algorithm that efficiently produces accurate seed sets~\cite{minutoli2019fast}. 
 It is an approximation method that improves the Reverse Influence Sampling~(RIS)~\cite{borgs2014maximizing} algorithm by eliminating the need for the threshold to be used.
-%{\sc Imm} generalizes the influence of all vertices on a small set of sample graphs that is sampled from the reachability sets of a few vertices.
+%{\sc Ripples} generalizes the influence of all vertices on a small set of sample graphs that is sampled from the reachability sets of a few vertices.
 We have used $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined parameter to control the approximation boundaries.
@@
 % {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
-% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &  {\sc Ripples} &   {\sc Skim} &  {\sc Ssa} \\
 % R &        256 &     512 &    0.2 &    0.5 &   64-64 &     0.1 &        256 &        512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &  0.5 &  64-64 &  0.1 \\
@@
 % {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
-% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 % R &        256 &     512 &     0.2 &    0.5 &   64-64 &     0.1 &         256 &         512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &   0.5 & 64-64 &   0.1 \\
@@
 % {} & \multicolumn{6}{c|}{Time} & \multicolumn{6}{c|}{Score} & \multicolumn{6}{c}{Memory} \\
-% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 % R &        256 &    512 &     0.2 &     0.5 &   64-64 &     0.1 &         256 &         512 &     0.2 &     0.5 &   64-64 &     0.1 &        256 &    512 &   0.2 &   0.5 & 64-64 &   0.1 \\
@@
 % {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+% Method & \multicolumn{2}{c}{{\sc \acro}} &   {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &    {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} & \multicolumn{2}{c}{{\sc \acro}} &  {\sc Tim+} &   {\sc Ripples} &   {\sc Ssa} \\
 % R &        256 &    512 &    0.2 &     0.5 &     0.1 &         256 &         512 &     0.2 &     0.5 &     0.1 &        256 &    512 &   0.2 &   0.5 &   0.1 \\
@@
 % {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-% Method & {\sc \acro} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+% Method & {\sc \acro} &   {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &  {\sc Ripples} &   {\sc Skim} &  {\sc Ssa} \\
 % Dataset                 &            &        &        &         &         &            &         &         &         &         &            &       &      &        &      \\
@@
 % {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-% Method & {\sc \acro} &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Method & {\sc \acro} &    {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 % Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
 % {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-% Method & {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+% Method & {\sc \acro} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 % Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
 % {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Imm} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Imm} & {\sc Skim} &   {\sc Ssa} \\
+% Method & {\sc \acro} &   {\sc Tim+} &     {\sc Ripples} & {\sc Skim} &     {\sc Ssa} &  {\sc \acro} &    {\sc Tim+} &     {\sc Ripples} & {\sc Skim} &     {\sc Ssa} & {\sc \acro} &  {\sc Tim+} &   {\sc Ripples} & {\sc Skim} &   {\sc Ssa} \\
 % Dataset                 &            &        &         &      &         &             &         &         &      &         &            &       &       &      &       \\
@@
 For that reason, we have used the parameters suggested by the paper.
-we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.2$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$), and {\sc Ssa}($\epsilon=0.1$).
-In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Imm} have one.
+we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.2$), {\sc Ripples} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$), and {\sc Ssa}($\epsilon=0.1$).
+In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Ripples} have one.
 Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex.
@@
 
-    \setlength{\tabcolsep}{1.2pt}
+    \setlength{\tabcolsep}{1.5pt}
         \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds,  $\tau=16$ threads, and $w=0.005$.
@@
         \centering
-        \resizebox{\resultsize\linewidth}{!}{
+        \resizebox{0.75\linewidth}{!}{
 
@@
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & {\sc Hyp.} &   {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  {\sc Hyp.}   &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & {\sc Hyp.}  &  {\sc Tim+} &  {\sc Imm} &   {\sc Skim} &  {\sc Ssa} \\
+Method & {\sc Hyp.} &   {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  {\sc Hyp.}   &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc Hyp.}  &  {\sc Tim+} &  {\sc Ripples} &   {\sc Skim} &  {\sc Ssa} \\
 Dataset                 &   {\sc Fus.}         &        &        &         &         & {\sc Fus.}           &         &         &         &      &      {\sc Fus.}         &       &      &        &      \\
@@
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & \acrotwo &    {\sc Tim+} &    {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+Method & \acrotwo &    {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &  {\sc Skim} &   {\sc Ssa} \\
+Method & \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
 Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & \acrotwo &   {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Imm} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Imm} &   {\sc Ssa} \\
+Method & \acrotwo &   {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &   {\sc Ssa} \\
 Dataset                 &            &        &         &         &             &         &         &         &            &       &       &       \\
@@
 Using $\epsilon = 0.3$, {\sc Tim+} does not suffer from sparsity, but as the tables show, {\sc Skim} can suffer more.
-With respect to the execution-time performance, \acro is superior to other methods; for instance, when $w = 0.01$, it is $167\times$, $10\times$, and $10\times$ faster on average compared to {\sc Tim+}, {\sc Imm}, and {\sc Skim}, respectively.
-Although {\sc Imm} and {\sc Skim} look similar for $w = 0.01$ in terms of relative average execution time performance, for large graphs, {\sc Skim} is faster than  {\sc Imm}.
-When $w = 0.01$, the maximum execution times for $4148$, $1870$, and $114$ seconds for {\sc Tim+}, {\sc Imm}, and {\sc Skim}, respectively.
+With respect to the execution-time performance, \acro is superior to other methods; for instance, when $w = 0.01$, it is $167\times$, $10\times$, and $10\times$ faster on average compared to {\sc Tim+}, {\sc Ripples}, and {\sc Skim}, respectively.
+Although {\sc Ripples} and {\sc Skim} look similar for $w = 0.01$ in terms of relative average execution time performance, for large graphs, {\sc Skim} is faster than  {\sc Ripples}.
+When $w = 0.01$, the maximum execution times for $4148$, $1870$, and $114$ seconds for {\sc Tim+}, {\sc Ripples}, and {\sc Skim}, respectively.
 For the proposed approach and with the same $w$, the maximum time spent is only $42$ seconds.
@@
 On the other hand, the other methods tend to get relatively slower under these changes.
-For instance, when the influence probability increases from $w = 0.005$ to $w = 0.01$, the average speedups of \acro over the baselines, i.e., {\sc Tim+}, {\sc Imm}, {\sc Skim}, and {\sc Ssa}, increase by 29$\times$, 3.1$\times$,  3.8$\times$, and 27$\times$, respectively.
+For instance, when the influence probability increases from $w = 0.005$ to $w = 0.01$, the average speedups of \acro over the baselines, i.e., {\sc Tim+}, {\sc Ripples}, {\sc Skim}, and {\sc Ssa}, increase by 29$\times$, 3.1$\times$,  3.8$\times$, and 27$\times$, respectively.
 
@@
      \includegraphics[width=1\linewidth]{images/speedup-imm}
-   \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Imm}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
+   \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Ripples}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
      \label{fig:vs-imm}} 
@@
 
-Figure~\ref{fig:vs-imm} shows the speedups of \acro over {\sc Imm} for all the graphs and all $w$ values.
+Figure~\ref{fig:vs-imm} shows the speedups of \acro over {\sc Ripples} for all the graphs and all $w$ values.
 As described above, the relatively sparser setting $w=0.005$ is especially challenging due to the high diameter of the influence graph and low vector unit utilization.
 Even with this $w$ value, \acro{} is only slower by a few seconds and only when the influence is small.
-For larger graphs with larger influences \acro{} is much faster than {\sc Imm}.
-As explained before, for larger $w$, \acro{}'s execution-time performance is usually better, and its influence quality is on par with that of {\sc Imm}.
+For larger graphs with larger influences \acro{} is much faster than {\sc Ripples}.
+As explained before, for larger $w$, \acro{}'s execution-time performance is usually better, and its influence quality is on par with that of {\sc Ripples}.
  \begin{figure}[!ht] 
@@
 Minutoli et al.
-improved RIS and proposed {\sc Imm} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast} with high efficiency.
+improved RIS and proposed {\sc Ripples} that works on multi-threaded and distributed architectures~\cite{minutoli2019fast} with high efficiency.
 Recently, the authors extended the algorithm to work in a multi-GPU setting~\cite{curipples}.}
@@
 %\ggx{Bu kısım değişmeli}
-In the future, we will extend our work to a distributed GPGPU setting to process graphs with billions of vertices and edges under a minute. 
+In the future, we will extend our work to a distributed GPU setting to process graphs with billions of vertices and edges under a minute. 
 %The main issue with \acro on such an architecture is the broadcast of sketch registers.

### 2022-11-30 paper.tex
format change for elsevier

@@
-% \documentclass[10pt,journal,compsoc]{IEEEtran}
-% \usepackage{subfiles}
-% \usepackage{url}
-% \usepackage{amsmath}
-% \usepackage{xspace}
-% \usepackage{multirow}
-% \usepackage{amssymb}
-% \usepackage{algorithm}
-% \usepackage{subfig}
-% \usepackage[noend]{algpseudocode}
-% \renewcommand{\algorithmicrequire}{\textbf{Input:~}}
-% \renewcommand{\algorithmicensure}{\textbf{Output:~}}
-% \newcommand\ovr[1]{\overrightarrow{#1}}
-% \newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
-% \usepackage{booktabs}
-% \usepackage{array}
-% \usepackage{color}
-% \usepackage{listings}
-% \usepackage{placeins}
-% \usepackage{enumitem}
-% \usepackage{balance}
-% \usepackage{etoolbox}
-% \usepackage{lineno,hyperref}
-% \newcommand\acrotwo{
-% \multirow{2}{*}{ \shortstack{ \sc{Hyp.}\\\sc{Fus.}} }
-% }
-% \renewcommand{\toprule}{}
-% \newcommand\acro{{\sc{HyperFuseR\xspace}\xspace}\xspace}
-% \newcommand\kktodo[1]{\textcolor{red}{#1}}
-% \newcommand\fixme[1]{\textcolor{red}{#1}}
-% \newcommand\minspeedup{{{3.5\xspace}\xspace}\xspace}
-% \newcommand\maxspeedup{{{11\xspace}\xspace}\xspace}
-% \newcommand\maxspeedupTIM{{{1500\xspace}\xspace}\xspace}
-% \newcommand\maxspeedupIMM{{{27.87\xspace}\xspace}\xspace}
-% \newcommand\maxspeedupSKIM{{{11\xspace}\xspace}\xspace}
-
-% \let\oldbibliography\thebibliography
-% \renewcommand{\thebibliography}[1]{%
-%   \oldbibliography{#1}%
-%   \setlength{\itemsep}{0pt}%
-% }
-
-% \modulolinenumbers[5]
-
-% \renewcommand{\floatpagefraction}{.98}
-% % \journal{Journal of Parallel and Distributed Computing}
+\documentclass[review]{elsarticle}
+\usepackage{etoolbox}
+\usepackage{lineno,hyperref}
+\let\oldbibliography\thebibliography
+\renewcommand{\thebibliography}[1]{%
+  \oldbibliography{#1}%
+  \setlength{\itemsep}{0pt}%
+}
+
+\modulolinenumbers[5]
+
+\renewcommand{\floatpagefraction}{.98}
+\journal{Expert Systems With Applications}
 
 % %% `Elsevier LaTeX' style
-% \bibliographystyle{elsarticle-num}
+\bibliographystyle{elsarticle-num}
 % %%%%%%%%%%%%%%%%%%%%%%%
 
-% \begin{document}
-
-% % \begin{frontmatter}
-% % \title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
-
-% % %% Group authors per affiliation:
-% % %% or include affiliations in footnotes:
-% % \author[add]{Gökhan Göktürk}
-% % % \ead{gokhan.gokturk@sabanciuniv.edu}
-
-% % \author[add]{Kamer Kaya}
-% % % \ead{kaya@sabanciuniv.edu}
-
-% % \address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}
-
-% % \IEEEtitleabstractindextext{%
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-\makeatletter
-\long\def\@makecaption#1#2{\ifx\@captype\@IEEEtablestring%
-\footnotesize\begin{center}{\normalfont\footnotesize #1}\\
-{\normalfont\footnotesize\scshape #2}\end{center}%
-\@IEEEtablecaptionsepspace
-\else
-\@IEEEfigurecaptionsepspace
-\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ #2}%
-\ifdim \wd\@tempboxa >\hsize%
-\setbox\@tempboxa\hbox{\normalfont\footnotesize {#1.}~~ }%
-\parbox[t]{\hsize}{\normalfont\footnotesize \noindent\unhbox\@tempboxa#2}%
-\else
-\hbox to\hsize{\normalfont\footnotesize\hfil\box\@tempboxa\hfil}\fi\fi}
-\makeatother
-
-%\DeclareUnicodeCharacter{2212}{-}
-\usepackage[utf8]{inputenc}
-\ifCLASSOPTIONcompsoc
-  % The IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-
 \newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
 
-\newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
-colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
-pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
-pdfsubject={Typesetting},%<!CHANGE!
-pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
-pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!
+% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
+% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
+% pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
+% pdfsubject={Typesetting},%<!CHANGE!
+% pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
+% pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!
 
@@
 
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  \graphicspath{{./images/}}
-  \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}
-\else 
-\fi
+% \usepackage[pdftex]{graphicx}
+% \graphicspath{{./images/}}
+% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}
+
 \usepackage{amsmath}
@@
 \begin{document}
-\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}
-
-\author{G\"{o}khan~G\"{o}kt\"{u}rk
-        and~Kamer~Kaya% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem G.
-G\"{o}kt\"{u}rk and K.
-Kaya are with Computer Science and Engineering, Faculty of Engineering and Natural Sciences, Sabanci University, Istanbul, Turkey.}% <-this % stops a space
-%\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-}
-%FIXME
-\markboth{}%
-{G\"{o}kt\"{u}rk \MakeLowercase{\textit{et al.}}: Boosting Parallel Influence-Maximization Kernels for Undirected Networks with Fusing and Vectorization}
-
-\maketitle
+
+\begin{frontmatter}
+\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
+
+% % %% Group authors per affiliation:
+% % %% or include affiliations in footnotes:
+\author[add]{Gökhan Göktürk}
+% \ead{gokhan.gokturk@sabanciuniv.edu}
+
+\author[add]{Kamer Kaya}
+% \ead{kaya@sabanciuniv.edu}
+
+\address[add]{Faculty of Engineering and Natural Sciences, Sabancı University, Turkey}
+
 \begin{abstract}
@@
 % } 
-% \begin{keyword}
-% Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
-% \end{keyword}
-% \end{frontmatter}
+\begin{keyword}
+Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
+\end{keyword}
+\end{frontmatter}
 
@@
 % \end{figure}
-
+% \FloatBarrier
 % \begin{itemize}[leftmargin=*]
@@
 % \setlength{\columnsep}{1.2pt}%
-\begin{wrapfigure}{r}{0.35\linewidth}
-    \begin{center}
-      \includegraphics[width=1\linewidth]{images/ic.pdf}
-    \end{center}
-    \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
-  \end{wrapfigure}
+% \begin{wrapfigure}{r}{0.35\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/ic.pdf}
+%     \end{center}
+%     \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
+%   \end{wrapfigure}
 The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds.
@@
     \begin{center}
-    \includegraphics[width=\linewidth]{images/fmops.pdf}
+    \includegraphics[width=0.8\linewidth]{images/fmops.pdf}
     \caption{ (a) \label{fminit} Toy sketch initialization of vertex $u$ with four registers and 4-bit hash functions.
@@
     \begin{center}
-    \includegraphics[width=0.95\linewidth]{images/sketchdiff.pdf}
+    \includegraphics[width=0.85\linewidth]{images/sketchdiff.pdf}
     \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
@@
     \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
-%\kktodo{buna TIMS'in sonuclarini da ekleyebilir miyiz - en kaliteli o diye, eger mavinin ustunde kaliyorsa guzel} \ggx{Bunun için süreye ihtiyacım var.
-Diğer algorithmlar mavi çizgi gibi olmalı,(SKIM hariç)
      }\label{fig:sketch-saturation} 
@@
 % \bibliographystyle{elsarticle-num}
-\bibliographystyle{IEEEtranS}
+% \bibliographystyle{IEEEtranS}
 % argument is your BibTeX string definitions and bibliography database(s)

### 2022-11-30 paper.tex
Overleaf commit, converted the paper to two columns format.
fixed IC figure and it's reference

@@
-\documentclass[review]{elsarticle}
+\documentclass[final,5p,times,twocolumn]{elsarticle}
+% \documentclass[review]{elsarticle}
 \usepackage{etoolbox}
@@
 
-%\newcommand{\mycaption}[1]{\stepcounter{figure}\raisebox{-7pt}
-%  {\footnotesize Fig. \thefigure.\hspace{3pt} #1}}
-
 \begin{document}
@@
 
-% % %% Group authors per affiliation:
-% % %% or include affiliations in footnotes:
 \author[add]{Gökhan Göktürk}
-% \ead{gokhan.gokturk@sabanciuniv.edu}
+\ead{gokhan.gokturk@sabanciuniv.edu}
 
 \author[add]{Kamer Kaya}
-% \ead{kaya@sabanciuniv.edu}
+\ead{kaya@sabanciuniv.edu}
 
@@
 Due to this reason, many \fixme{heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% However, these simulation-based, greedy algorithms provide the best possible approximation guarantees. Therefore they are considered as the gold standard for IM.
 
@@
 
-% \begin{figure}[!ht] 
-%     \centering
-%   \subfloat[\small{IC}\label{fig:ic}]{%
-%        \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
-%   \subfloat[\small{WC}\label{fig:wc}]{%
-%         \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
-%     \\% IMAGES HERE
-%   \caption{\small{\protect\subref{fig:ic} 
-% The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
-% \protect\subref{fig:wc}
-% The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
-%   }}
-%   %\label{fig_ic_model} 
-%   \label{fig:xx} 
-% \end{figure}
+\begin{figure}[!ht] 
+    \centering
+  \subfloat[\small{IC}\label{fig:ic}]{%
+       \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
+  \subfloat[\small{WC}\label{fig:wc}]{%
+        \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
+    \\% IMAGES HERE
+  \caption{\small{\protect\subref{fig:ic} 
+The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
+\protect\subref{fig:wc}
+The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
+  }}
+  %\label{fig_ic_model} 
+  \label{fig:xx} 
+\end{figure}
 % \FloatBarrier

### 2022-12-01 paper.tex
Updates from Overleaf

@@
 \begin{itemize} [leftmargin=0.3cm]
-\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm.} The proposed scheme samples the edges as they are traversed across several simulations.
-Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
+\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, error-adaptive, sketch-based Influence Maximization algorithm.} The proposed scheme removes the contamination of sketches in.
+Error-adaptive sketch rebuilding strategy we employed lets the algorithm rebuild sketches only when necessary, allowing substantial performance gains while retaining high-quality results.
+
+\item The edges are sampled as they are traversed across several simulations. Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
 
@@
 The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
-Initially, each register is initialized with zero.
-The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register.
-With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register.
+In this work, we utilize a variant of the Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence.
+We use one register per simulation and take the average length of the longest leading zeros to estimate cardinalities for reachability sets.
+
+\subsubsection{Initialization}
+FM sketches initialize each register to zero in the beginning.
+Since every vertices reachability set includes itself at zero distance, we immediately add the vertices to its sketches.
+The vertices are hashed one by one, and the length of the longest all-zero prefix is stored in the register.
+Initialization for vertex $u$'s register can be formulated as following:
+\begin{equation}
+    \label{eq:sketch-add}
+    M_u[j] = clz(h_j(u)),~1 \leq j \leq {\cal J}
+\end{equation} where $clz(y)$ returns the number of leading zeros in $y$, $h_j$ is the $j$th hash function, and ${\cal J}$ is the number of sketch registers.
+
+\subsubsection{Adding Items}
 
@@
 \end{equation} where $clz(y)$ returns the number of leading zeros in $y$ and ${\cal J}$ is the number of sketch registers.
-With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided to a correction factor $\phi \approx 0.77351$ to fix the error due to hash collisions.
-That is the estimated cardinality $e$ is computed as
+
+\subsubsection{Union}
+Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers. Formally; 
+\begin{equation}
+\label{eq:sketch-merge}
+    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq {\cal J}.
+\end{equation} 
+In our implementation, the merge operations are performed if and only if there is a sampled edge between the vertices.
+The union operation requires constant number($\mathcal{O}(J)$ operations for any size set.
+
+\subsubsection{Cardinality Estimation}
+With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register and applying a correction factor.
+With multiple registers, the average of the register values can be used to estimate the cardinality, and the result is divided by a correction factor $\phi$ to fix the error due to hash collisions.
+Flajolet et al.
+\cite{flajolet1985probabilistic} suggests $\phi \approx 0.77351$ for $\mathcal{J}>=16$ registers.
+The estimated cardinality $e$ is computed as
 \begin{equation}
@@
 where $\bar{M} = {\tt{avg}}_j\{M[j]\}$ is the mean of the register values.
-
-In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros.
-Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers.
-Formally;
-\begin{equation}
-\label{eq:sketch-merge}
-    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq {\cal J}.
-\end{equation} 
-In our implementation, the merge operations are performed if and only if there is a sampled edge between the vertices.
-%\kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}.
-\ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim.
-Yanlis olmus.}
 
@@
 % After a preliminary analysis, \fixme{we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.}
+
+% For undirected graphs, a symmetric hash function, i.e $h(u,v) = \mbox{{\sc Hash}}(min(u,v)||max(u,v))~mod~2^{31}$, can be used to produce the same sampling random value for both ends of the edge (u,v)\cite{infuser}.
+
 An  important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory.
@@
 \end{equation}
-% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
+
 The edge $(u,v)$ exists \fixme{in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.} One of this approach's benefits is that an edge can be sampled using \fixme{a single XOR and compare-greater-than operation} which is crucial since \acro{} recomputes this probability value each time the corresponding edge is read from the memory.
@@
 
-% \begin{figure}[!ht] 
-%     \centering
-%     \includegraphics[width=0.8\linewidth]{./images/CDF.pdf}
-%     \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
-%     \label{fig:prob-cdf} 
-% \end{figure}
-
-% Using a strong hash function such as {{\sc Murmur3}} ensures that all bits independently change if the input is changed.
-This property allows us to generate good-enough pseudo-random values for fair sampling.
-To evaluate the randomness and fairness of the values generated with the hash-based approach, we generated a large number of samples for various real-life networks and plotted the cumulative distribution.
-% and the bias of the random values $P(u,v)_r$ used~(Fig.~\ref{fig:prob-bias}). 
-% As Figure~\ref{fig:prob-cdf} shows, the sampling distribution of the hash-based computation values resembles a uniform random distribution. 
-% Furthermore, the latter shows that the bias is insignificant for each network.
-
-% \begin{figure}[!ht] 
-%     \centering
-%     \includegraphics[width=1\linewidth]{./images/bias.pdf}
-%     \caption{\small{Bias distribution of hash-based sampling probabilities on various real-life networks.}}
-%     \label{fig:prob-bias} 
-% \end{figure}
-
-% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
-% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
-%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
-%Being able to generate the samples on the fly allows us to avoid many memory accesses. 
-% One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$.
-As mentioned above, the edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains.
-%Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware.
-%The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
 \subsection{Estimating Reachability Set Cardinalities}

### 2022-12-01 paper.tex
Updates from Overleaf

@@
 \begin{itemize} [leftmargin=0.3cm]
-\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, error-adaptive, sketch-based Influence Maximization algorithm.} The proposed scheme removes the contamination of sketches in.
+\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, error-adaptive, sketch-based Influence Maximization algorithm.} The proposed scheme removes the contamination of sketches in an efficient way.
 Error-adaptive sketch rebuilding strategy we employed lets the algorithm rebuild sketches only when necessary, allowing substantial performance gains while retaining high-quality results.
 
-\item The edges are sampled as they are traversed across several simulations. Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
-
-\item \fixme{Running concurrent simulations} on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
+\item The edges are sampled as they are traversed across several simulations.
+Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
+\fixme{Running concurrent simulations} on per-vertex Count-Distinct sketches reduces the number of memory accesses which is the main bottleneck for many graph kernels in the literature.
 While traversing an edge, \acro concurrently performs multiple diffusion simulations while using only a single (8-bit) value per vertex for each simulation.
@@
 
-\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Ripples}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
+\item We evaluate the run-time performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Ripples}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature.
 The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.
@@
 
-% \fixme{The paper is organized as follows: 
-% In Section~\ref{sec:background}, we present 
-% the background on IM and introduce the mathematical notation. 
-% Section~\ref{sec:method} describes the proposed approach in detail.}
-% In Section~\ref{sec:evaluation}, a thorough performance evaluation \fixme{is provided by conducting experiments on various real-world datasets and influence settings.
+\fixme{The paper is organized as follows: 
+In Section~\ref{sec:background}, we present 
+the background on IM and introduce the mathematical notation. 
+Section~\ref{sec:method} describes the proposed approach in detail.}
+In Section~\ref{sec:evaluation}, a thorough performance evaluation \fixme{is provided by conducting experiments on various real-world datasets and influence settings.
 A detailed empirical comparison with the state-of-the-art from the literature is also given.
@@
         \hline
-        %\kktodo{uzerinden 
-        %gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
@@
         $M$ & Number of edges\\
-        $T$ & Depth of the graph\\
+        % $T$ & Depth of the graph\\
         $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
@@
         $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
-        %$SCC(v) $       & Strongly connected component of vertex $v$\\
         $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
-%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
         \hline\hline
@@
         $h_{max}$       & Maximum value hash function $h$ can return\\
-        %$X_r$           & Random number/hash generated for simulation $r$  \\
+        $X_r$           & Random number/hash generated for simulation $r$  \\
         \hline\hline
@@
 
-% For undirected graphs, a symmetric hash function, i.e $h(u,v) = \mbox{{\sc Hash}}(min(u,v)||max(u,v))~mod~2^{31}$, can be used to produce the same sampling random value for both ends of the edge (u,v)\cite{infuser}.
+Besides Sketching and Error-Adaptive Rebuilding, one of the many differences between {\sc InFuseR}~\cite{infuser} and \acro is that {\sc InFuseR} only works on undirected graphs and uses a symmetric hash function, i.e.
+$h(u,v) = \mbox{{\sc Hash}}(min(u,v)||max(u,v))~mod~2^{31}$, to produce the same sampling random value for both ends of the edge (u,v).
+Whereas \acro only uses hash-based sampling to generate {\em reproducible random numbers} fast.
 
@@
 For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
-The toy example in Fig.~\ref{fig:fmops} with  ${\cal J} = 4$ shows how the sketch operations are done on a toy problem.
+The toy example with ${\cal J} = 4$ registers in Fig.~\ref{fig:fmops} shows how the sketch operations are done on a toy problem.
 In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers.
@@
 Also, we present a performance comparison with state-of-the-art IM algorithms on real-world datasets and show that \acro{} can be an order of magnitude faster while obtaining the same influence.
-%With the proposed method, \acro can achieve $\maxspeedupSKIM\times$ speedup against a sketch-based algorithm {\sc Skim} and $\maxspeedupIMM\times$ speedup against an approximation-based algorithm {\sc Imm} while producing high-quality seed sets.
-%\ggx{Bu kısım değişmeli}
-In the future, we will extend our work to a distributed GPU setting to process graphs with billions of vertices and edges under a minute. 
-%The main issue with \acro on such an architecture is the broadcast of sketch registers.
-When the vertices are partitioned into different computation units, resulting sketch updates should be communicated to all partitions.
-To overcome the issue and reduce communication bottlenecks, graph preprocessing and speculative diffusion strategies will be employed.
+In the future, we will extend our work to a distributed GPU setting to process graphs, with the aim of processing billions of vertices and edges in under a minute.
 

### 2022-12-22 paper.tex
Updates from Overleaf

@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-% \documentclass[review]{elsarticle}
+% \documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[review]{elsarticle}
 \usepackage{etoolbox}
@@
 
-% %% `Elsevier LaTeX' style
 \bibliographystyle{elsarticle-num}
-% %%%%%%%%%%%%%%%%%%%%%%%
-
 \newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
-
-% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true, pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
-% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
-% pdftitle={Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches},%<!CHANGE!
-% pdfsubject={Typesetting},%<!CHANGE!
-% pdfauthor={G\"{o}khan G\"{o}kt\"{u}rk and Kamer Kaya},%<!CHANGE!
-% pdfkeywords={Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization}}%<^!CHANGE!
+\newcommand\tablewidth{1.0}
 
 \newcommand\rev[1]{{#1}}
-% \newcommand\rev[1]{{#1}}
 \usepackage{color,soul}
@@
 \usepackage{url}
-
-% \usepackage[pdftex]{graphicx}
-% \graphicspath{{./images/}}
-% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.svg}
 
@@
 \newcommand\fixme[1]{#1}
-% \newcommand\fixme[1]{\textcolor{red}{#1}}
 \newcommand\acrotwo{
@@
 }
-% \setlength{\intextsep}{1pt}%
 
@@
 \algdef{SE}[FOR]{ForEach}{EndForEach}[1]
-  {\algorithmicforeach\ #1\ \algorithmicdo}% \ForEach{#1}
-  {\algorithmicend\ \algorithmicforeach}% \EndForEach
+  {\algorithmicforeach\ #1\ \algorithmicdo}
+  {\algorithmicend\ \algorithmicforeach}
 
@@
 \begin{frontmatter}
-\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}%\tnoteref{t1,t2}}
+\title{Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches}
 
@@
 Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model.
-Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM.
-% }
-In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not step-by-step simulate the diffusion process, have been proposed in the literature to cope with the scale of today's networks.
-In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate, not to count, the number of influenced vertices throughout a diffusion.
-We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph.
-To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion.
-This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once.
-%In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary.
-For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold.
-Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm.
-In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
+Due to the NP-Hardness of finding an optimal seed set, high-quality yet expensive approximation algorithms have been frequently used.
+In addition, lightweight, sketch-based approaches, which do not step-by-step simulate the influence process, have been proposed in the literature to cope with the scale of today's networks.
+In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to avoid step-by-step simulations and estimate the number of influenced vertices throughout a diffusion.
+Furthermore, for faster estimations, the sketches of a vertex for consecutive simulations are stored adjacently in memory.
+This allows the proposed algorithm to estimate the number of influenced vertices for multiple simulations at once.
+For faster processing, \acro automatically rebuilds the sketches after observing estimation errors above a given threshold.
+Our experimental results show that the proposed algorithm yields seed sets with comparable quality while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm.
+In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.\looseness=-1
 \end{abstract}
@@
 \begin{keyword}
-Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
+Influence Maximization, Graph Processing, Count-Distinct Sketch, Error-Adaptive Cardinality Estimation.
 \end{keyword}
@@
 
-Efficient information/influence dissemination in a network is an important research area with several applications in various fields, \fixme{such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.}
-As the study of these networks is imperative for \fixme{educational, political, economic, and social purposes,} a high-quality seed set to initiate the diffusion may have vital importance.
-Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information effectively are essential.
-
-Influence maximization is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model.
+%Efficient information/influence dissemination in a network is an important research area with several applications in various fields, \fixme{such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.}
+%As the study of these networks is imperative for \fixme{educational, political, economic, and social purposes,} a high-quality seed set to initiate the diffusion may have vital importance.
+%Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information effectively are essential.
+
+Influence maximization~(IM) is the problem of finding a subset $S \subset V$ of $K$ vertices in a graph $G = (V, E)$ with the vertex set $V$ and edge set $E$ such that $S$ reaches the maximum reachability, i.e., influences the maximum expected number of vertices, under some diffusion model.
+The problem has several applications in various fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
 Kempe et al.~\cite{kempe2003maximizing} introduced the IM problem, \fixme{proved it to be NP-hard,} and provided a greedy Monte-Carlo approach that has a \fixme{constant approximation ratio over the optimal solution}.
-This greedy approach is one of the most frequently applied algorithms for IM.
-The time complexity of the greedy algorithm, with an influence score estimate $\sigma$, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
-Although they perform well in terms of seed-set quality, the greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices as a consequence of their expensive simulation costs.
+% which is one of the most frequently applied algorithms. 
+The time complexity of this greedy algorithm, with an influence score estimate $\sigma$, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+Although they perform well in terms of seed-set quality, greedy Monte-Carlo solutions are impractical for real-life networks featuring millions of vertices as a consequence of their expensive simulation costs.
 Due to this reason, many \fixme{heuristics and proxy methods have been proposed in the literature~\cite{MixGreedy, narayanam2010shapley, kimura2007extracting, chen2010PMIA,chen2010LDAG, kim2013scalable, cohen2014sketch, goyal2011simpath, jung2012irie,cheng2014imrank,liu2014influence,galhotra2016holistic}}.
 
-Simulating a greedy algorithm in \fixme{parallel} is a \fixme{straightforward} workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks.
-However, for large networks, a parallel, greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges even if a large number of processing units/cores are available.
-Following similar attempts in the literature, we propose a parallel, sketch-based approach that approximates the Monte-Carlo processes.
-To boost the performance, the proposed approach does not exactly count the number of influenced vertices.
-Instead, it leverages Count-Distinct sketches.
+Parallelization is an immediate remedy to mitigate the overhead of performing independent simulations.
+However, even a highly parallel, greedy approach with a good approximation guarantee does not come cheap on networks with billions of vertices and edges.
+In this work, we propose a parallel, sketch-based approach, \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, which approximates the counting performed by the Monte-Carlo processes.
+That is to boost the performance, our approach does not exactly count the number of influenced vertices.
+Instead, it leverages Count-Distinct sketches to estimate their number.
+\acro is an open-source, blazing-fast, sketch-based IM algorithm employing an error-adaptive sketch management mechanism to remove the contamination from sketches in an efficient way.
+This strategy lets \acro rebuild sketches only when necessary, allowing substantial performance gains while retaining high-quality results.
 Below is a summary of our contributions:
@@
 \begin{itemize} [leftmargin=0.3cm]
-\item \fixme{We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, error-adaptive, sketch-based Influence Maximization algorithm.} The proposed scheme removes the contamination of sketches in an efficient way.
-Error-adaptive sketch rebuilding strategy we employed lets the algorithm rebuild sketches only when necessary, allowing substantial performance gains while retaining high-quality results.
-
-\item The edges are sampled as they are traversed across several simulations.
+%\item The edges are sampled as they are traversed across several simulations.
 Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.
@@
 
-\item \acro{} can process large-scale graphs with millions of vertices and hundreds of millions of edges under a minute without compromising the quality of results.
-Furthermore, the performance scales near linearly with the number of threads available.
-In addition, while processing a large-scale graph, only a few GBs of memory is used, where most of the memory is spent for storing the graph itself.
-
-\item Once it is read from the memory, \acro processes all samples of a single edge together.
-The suggested approach, therefore, decreases the pressure on the memory subsystem.
-Furthermore, it employs vector compute units to its near maximum efficiency to regularize memory accesses.
+\item Thanks to leveraging Count-Distinct sketches, \acro{} can process large-scale graphs with millions of vertices and hundreds of millions of edges under a minute without compromising the quality of results.
+Furthermore, the performance scales almost linearly with the number of threads available.
+
+\item \acro is extremely memory efficient; while processing a large-scale graph, only a few GBs of memory is used, where most of the memory is spent for storing the graph itself.
+
+\item When updated frequently, the sketches used by \acro get dirty, i.e., contaminated with noise.
+However, the error-adaptive mechanism of the proposed method tracks the amount of this noise and reduces the number of sketch resets while keeping the seed-set quality on par with the state-of-the-art.
 
@@
 In Section~\ref{sec:evaluation}, a thorough performance evaluation \fixme{is provided by conducting experiments on various real-world datasets and influence settings.
-A detailed empirical comparison with the state-of-the-art from the literature is also given.
+A detailed empirical comparison with the state-of-the-art is also given.
 Section~\ref{sec:relatedwork} presents a comparative overview of the existing work.
@@
 
-\fixme{Let $G = (V,E)$ be a} directed \fixme{graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations} among them.
+\fixme{Let $G = (V,E)$ be a} directed \fixme{graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent their (pairwise) relations}.
 An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$.
@@
     % \tiny
-    \begin{tabular}{|l|p{0.7\linewidth}|}
+    \begin{tabular}{|l|p{0.8\linewidth}|}
         \hline
@@
         $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
-        $N$ & Number of vertices\\
-        $M$ & Number of edges\\
+        $n$ & Number of vertices\\
+        $m$ & Number of edges\\
         % $T$ & Depth of the graph\\
@@
         $\Gamma^-_G(u)$  &The set of vertices $v$ where $(v, u) \in E$\\ %%FIXME
-        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
+        $w_{u,v}$       & Probability of $u$ directly influencing $v$, $(u,v) \in E$ \\
         $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
@@
         ${\cal J}$   & Number of Monte-Carlo simulations performed\\
-        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
+        $\sigma_{G}(S)$ & The influence score, i.e., the expected \#vertices reached from $S$ in $G$\\
         % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
@@
         $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
-        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
+        $P(s,v)_r $     & Random value in $[0,1]$ used to select an edge $(s,v)$ in simulation $r$\\
         $h(u,v)$        & Hash function for edge $\{u,v\}$\\
@@
         $\varsigma $    & Influence gained before last sketch build\\
-        $\sigma $       & Influence Score\\
+%        $\sigma $       & Influence Score\\
         $\delta$        & Marginal gain after last sketch build\\
@@
   \subfloat[\small{IC}\label{fig:ic}]{%
-       \includegraphics[width=0.4\linewidth]{images/ic.pdf}}
+       \includegraphics[width=0.26\linewidth]{images/ic.pdf}}
   \subfloat[\small{WC}\label{fig:wc}]{%
-        \includegraphics[width=0.4\linewidth]{images/wc.pdf}}
+        \includegraphics[width=0.26\linewidth]{images/wc.pdf}}
     \\% IMAGES HERE
@@
 \protect\subref{fig:wc}
-The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.}
+The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.
   }}
-  %\label{fig_ic_model} 
   \label{fig:xx} 
@@
 The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
-The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
-We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.
+%The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; 
+Under this model, the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices.
+We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature such as {\em Weighted Cascade} and {\em Linear Threshold}.
 
@@
 The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$.
-Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem.
-For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$.
-Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$.
-Via sketches, \acro can estimate the reachability set cardinalities with much less memory and computation compared to the exact counting solutions.
-
-The reachability set of a vertex is the union of all its connected vertices (via outgoing edges).
+In this work, we argue that finding the number of vertices in a randomly selected subgraph to be influenced by $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem.
+%For each (sub)graph, starting from $u$, the number of visited vertices can be found while traversing the (sub)graph.
+However, this linear-time computation requires memory proportional to $n$.
+Via sketches, \acro can estimate the reachability set cardinalities with much less memory and computation compared to these exact counting solutions.
+
+\begin{figure}[!ht] 
+    \centering
+    %\subfloat[\label{fig:toy}]{%
+    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
+    \subfloat[\label{fig:sims}]{%
+        \includegraphics[width=0.35\linewidth]{images/samples.pdf}
+    } 
+    \subfloat[\label{fig:fused}]{%
+     \includegraphics[width=0.35\linewidth]{images/fused.pdf}}
+  \caption{\small{
+  %\protect\subref{fig:toy} The toy graph 
+  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
+  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
+  }}
+  \label{fig:traversal} 
+\end{figure}
+
+The reachability set of a vertex $u$ is the union of $\{u\}$ and all its connected vertices' (via outgoing edges) reachability sets.
+For instance, Figure~\ref{fig:sims} shows two subgraphs samples from the toy graph in Figure~\ref{fig:xx}.
+The reachability set of vertex $1$ in these subgraphs are $\{1, 2, 4\}$ and $\{1,3,4\}$, respectively, where the first one is obtained by $\{1\} \cup \{2\} \cup \{4\}$ and the second one is obtained by $\{1\} \cup \{3, 4\}$.
 Many IM kernels exploit this property to some degree.
@@
 utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \cite{MixGreedy} %\kktodo{cite}\ggx{cited.} 
-goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set.
+goes one step further; it utilizes the fact that for an {\em undirected graph}, all vertices in a connected component have the same reachability set.
 Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.
@@
 For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
-If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory are required where each merge operation has $\Theta(n)$ time complexity.
+If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory are required where each merge/union operation has $\Theta(n)$ time complexity.
 If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
@@
 
-Count-Distinct~Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates.
-Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities.
-The essence of an FM sketch is that it keeps track of how rare the elements are in a stream.
+Count-Distinct~Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} keeps track of how rare the elements are in a stream within a register.
 The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values.
-In this work, we utilize a variant of the Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence.
-We use one register per simulation and take the average length of the longest leading zeros to estimate cardinalities for reachability sets.
-
-\subsubsection{Initialization}
+The number of registers, ${\cal J}$, can be increased for better estimates.
+ The union of two sketches, which can be used to estimate the cardinality of the corresponding streams, can be computed in constant time.
+Hence, sketches are excellent tools for efficient estimation of reachability set cardinalities.
+
+In this work, we utilize a variant of the FM sketch where  ${\cal J}$ is equal to the number of Monte-Carlo simulations performed to calculate the estimated influence.
+That is we use one register per simulation and take the average length of the longest leading zeros to estimate cardinalities for reachability sets.
+Below are the details of our sketch operations:
+
+\begin{itemize}
+\item{{\bf Initialization:}}
 FM sketches initialize each register to zero in the beginning.
@@
 The vertices are hashed one by one, and the length of the longest all-zero prefix is stored in the register.
-Initialization for vertex $u$'s register can be formulated as following:
+Initialization for vertex $u$'s register can be formulated as follows:
 \begin{equation}
-    \label{eq:sketch-add}
+    \label{eq:sketch-init}
     M_u[j] = clz(h_j(u)),~1 \leq j \leq {\cal J}
@@
 
-\subsubsection{Adding Items}
-
+\item{{\bf Adding Items:}}
 In practice, multiple, ${\mathcal J}$, registers and hash values, $M[j]$ and $h_j$, $1 \leq j \leq {\cal J}$, are used to reduce the variance of the estimation.
@@
 
-\subsubsection{Union}
+\item{{\bf Union:}}
 Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers. Formally; 
@@
 \end{equation} 
-In our implementation, the merge operations are performed if and only if there is a sampled edge between the vertices.
-The union operation requires constant number($\mathcal{O}(J)$ operations for any size set.
-
-\subsubsection{Cardinality Estimation}
+In our implementation, the merge operations are performed if and only if there is a sampled edge between the vertices. The union operation requires a constant number ($\mathcal{O}(J)$) of operations.
+
+\item{\bf{Cardinality Estimation:}}
 With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register and applying a correction factor.
@@
 where $\bar{M} = {\tt{avg}}_j\{M[j]\}$ is the mean of the register values.
+\end{itemize}
 
@@
 
-\acro{} uses {\em directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy.
-An IM tool leveraging fusing is~{\sc InFuseR}~\cite{infuser} which employs {\emph {undirected}} hash-based fused sampling and CELF optimizations~\cite{CELF} for seed selection to find the best seed set.
+\acro{} uses {\em directed} fused sampling, which is originally proposed in~\cite{infuser}, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy.
+%An IM tool leveraging fusing is~{\sc InFuseR}~\cite{infuser} which employs {\emph {undirected}} hash-based fused sampling and CELF optimizations~\cite{CELF} for seed selection to find the best seed set.
 Unlike {\sc InFuseR}, \acro{} follows a completely different approach and only estimates the cardinalities of the reachability sets and do not compute them.
-
-Most IM algorithms have the same few steps to find the best seed vertex set; sampling, building the influence oracle, verifying the impact of new candidates, and removing the latent seed set's residual reachability set.
-Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.
-
-% \begin{wrapfigure}{l}{0.45\linewidth}
-%     \begin{center}
-%       \includegraphics[width=1\linewidth]{images/fminit.pdf}
-%     \end{center}
-%     \caption{Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.}
-%   \end{wrapfigure}
-
-% The method first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
-Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
-The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.
-
-% \begin{wrapfigure}{l}{0.35\linewidth}
-%     \begin{center}
-%       \includegraphics[width=1\linewidth]{images/fmmerge.pdf}
-%     \end{center}
-%     \caption{\label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers.}
-%   \end{wrapfigure}
-
-%At each iteration, the sketches of the existing reachable vertices are modified.
-\kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
-%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.
-
-% \begin{wrapfigure}{l}{0.35\linewidth}
-%     \begin{center}
-%       \includegraphics[width=1\linewidth]{images/fmwrite.pdf}
-%     \end{center}
-%     \caption{Example of writing merged sketch $M_{xy}$ in fig.\ref{fmmerge} back to $M_x$ w.r.t diffusion process.}
-%   \end{wrapfigure}
-
-\acro performs $K$ iterations to find $K$ vertices.
+To find the best seed vertex set, most IM algorithms perform (1) sampling, (2) building the influence oracle, (3) verifying the impact of new candidates, and (4) removing the latent seed set's residual reachability set.
+%Following the idea proposed in~\cite{infuser}, \acro fuses the sampling step with other steps to avoid reading the graph multiple times.
+Similar to these algorithms, \acro performs $K$ iterations to find $K$ vertices but implements each step differently due to leveraging sketches.
+
 Each iteration starts by estimating the reachability set cardinalities for all the vertices and keeping this information within sketches.
@@
 Hence, finally, the algorithm checks if sketch rebuilding is necessary based on the difference between the sketch estimate and Monte-Carlo estimate.
-The proposed approach and the algorithm is described here in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
+The proposed approach and the algorithm are described here in more detail.% starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok.
 $u \notin R_S$ şeklinde.}
+
+% \begin{wrapfigure}{l}{0.45\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fminit.pdf}
+%     \end{center}
+%     \caption{Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions.}
+%   \end{wrapfigure}
+
+% The method first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself).
+Then, for all the (sampled) edges ($u, v$), i.e., for the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge.
+The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.
+
+% \begin{wrapfigure}{l}{0.35\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fmmerge.pdf}
+%     \end{center}
+%     \caption{\label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers.}
+%   \end{wrapfigure}
+
+%At each iteration, the sketches of the existing reachable vertices are modified.
+\kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
+%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.
+
+% \begin{wrapfigure}{l}{0.35\linewidth}
+%     \begin{center}
+%       \includegraphics[width=1\linewidth]{images/fmwrite.pdf}
+%     \end{center}
+%     \caption{Example of writing merged sketch $M_{xy}$ in fig.\ref{fmmerge} back to $M_x$ w.r.t diffusion process.}
+%   \end{wrapfigure}
 
@@
 The probabilistic nature of cascade models \fixme{requires} sampling \fixme{subgraphs from $G = (V, E)$ to simulate the diffusion process}.
-If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel.
-That is first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size.
+Sampling can be an expensive stage if each sample is generated and processed individually, which is what the literature traditionally does.
+%If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel. 
+First, sampling multiple sub-graphs requires multiple passes on the graph, which can be very large. 
+%and expensive to stream to the computational cores, and 
+Second, if samples are generated in a single pass and memoized, the memory requirement can be a multiple of the graph size. 
 In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
@@
 
-\begin{figure}[!ht] 
-    \centering
-    %\subfloat[\label{fig:toy}]{%
-    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
-    \subfloat[\label{fig:sims}]{%
-        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
-    } 
-    \subfloat[\label{fig:fused}]{%
-     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
-  \caption{\small{
-  %\protect\subref{fig:toy} The toy graph 
-  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
-  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
-  }}
-  \label{fig:traversal} 
-\end{figure}
-
-In \acro, when an edge of the original graph is being processed, it is processed for all possible samples.
+%In \acro, when an edge of the original graph is being processed, it is processed for all possible samples.
 Then, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value for each sample.
@@
 % \end{equation} %FIXME: does this mean this value be negative?
-
-\begin{equation}
-    \label{eq:hash}
-    h(u,v) = \mbox{{\sc Hash}}(u||v)~mod~2^{31}  
-\end{equation} %FIXME: does this mean this value be negative?
-where $||$ is the concatenation operator. 
+%\begin{equation}
+%    \label{eq:hash}
+%    h(u,v) = \mbox{{\sc Hash}}(u||v)~mod~2^{31}  
+%\end{equation} %FIXME: does this mean this value be negative?
+%where $||$ is the concatenation operator. 
 % In our preliminary experiments, we have tried a set of hash algorithms and found that {\sc Crc32}~\cite{koopman200232} and {{\sc Murmur3}} are good candidates for {\sc Hash}.
@@
 
-Besides Sketching and Error-Adaptive Rebuilding, one of the many differences between {\sc InFuseR}~\cite{infuser} and \acro is that {\sc InFuseR} only works on undirected graphs and uses a symmetric hash function, i.e.
+%Besides Sketching and Error-Adaptive Rebuilding, one of the many differences between {\sc InFuseR}~\cite{infuser} and \acro is that {\sc InFuseR} only works on undirected graphs and uses a symmetric hash function, i.e.
 $h(u,v) = \mbox{{\sc Hash}}(min(u,v)||max(u,v))~mod~2^{31}$, to produce the same sampling random value for both ends of the edge (u,v).
@@
 
-An important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory.
+%An important bottleneck of hash-based fused sampling is the need of the hash value for an edge whenever it is read from the memory.
 To mitigate its overhead, using $\Theta(|E|)$ more memory, we precompute and memoize the hash values (and read them when we need them).
@@
 
-A set of uniformly \fixme{ randomly chosen numbers $X_r \in_R [0, h_{max}]$ } associated with each sample $r$ are generated for each edge to generate a unique sampling probabilities for all samples.
+To sample subgraphs in the fused setting, a set of uniformly \fixme{ randomly chosen numbers $X_r \in_R [0, h_{max}]$ } associated with each sample $r$ are generated for each edge to generate unique sampling probabilities for all samples.
 Then, the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$.
@@
     \label{eq:hash_prob}
-    P(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
+    P(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}
 \end{equation}
+where
+\begin{equation}
+    \label{eq:hash}
+    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}. 
+\end{equation} 
+Above, {\sc Murmur3} is a fast hash function with a good avalanche behavior and a maximum bias $0.5\%$~\cite{MurmurHash3Performance}.
 
 The edge $(u,v)$ exists \fixme{in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$.} One of this approach's benefits is that an edge can be sampled using \fixme{a single XOR and compare-greater-than operation} which is crucial since \acro{} recomputes this probability value each time the corresponding edge is read from the memory.
-In practice, we do not apply the division operation since $h_{max}$ is a constant value and the same for every edge and simulation.
+%In practice, we do not apply the division operation since $h_{max}$ is a constant value and the same for every edge and simulation.
 Moreover, the corresponding control flow branch overhead can be \fixme{removed} using {\em conditional move} \fixme{instructions}.
+For more implementation details, we refer the reader to \cite{infuser}.
 
@@
 In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers.
-In Fig.~\ref{fig:fmops}(b), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets.
+In Fig.~\ref{fig:fmops}(b), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes the element-wise maximum of registers to find the union of two reachability sets.
 All these operations are performed using vectorized instructions.
 
- To vectorize the rest of the process, we leverage conditional move operations.
+ To vectorize the rest of the process, we leverage {\em conditional move} operations.
 Although an edge ($u, v$) is inside the graph, it may not be in all the samples.
-In the toy example of Fig.~\ref{fig:fmops}, we assume that ($u, v$) only exists in the first and the last sample.
+In the toy example of Fig.~\ref{fig:fmops}, we assume that ($u, v$) only exists in the first and the last sample (see the checkmarks in (c)).
  Fig.~\ref{fig:fmops}(c) writes the merged reachability sets back to $u$'s registers.
@@
 sampled subgraph.
+The {\tt 0b} prefix on (a) denotes binary representation.
      }\label{fig:fmops} 
@@
 To summarize, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
-This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
+This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the reachability set cardinalities for all vertices very fast.
 
 \subsection{Finding the Seed Set}
-A greedy solution to IM requires finding a vertex with a maximum marginal influence at each step until the seed set size reaches $K$.
+A greedy solution to IM requires finding a vertex with a maximum marginal influence, i.e., the average number of {\em new} vertices in the reachability sets over multiple samples/subgraphs.
+This step is repeated until the seed set size reaches $K$.
 An exact computation of marginal influences, i.e., the additional influence when a vertex $v$ is added to the seed set, requires the computation of all candidate vertices' reachability sets within all the samples.
@@
 Hence,
-In this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
+As mentioned before, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores.
 Here we propose an efficient and effective IM algorithm, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs.
@@
  Then at each step, the incoming edges of the live vertices are processed. 
- For a vertex $u$, its sketch, $M_u$, is updated by merging the sketches $M_v$ of all live outgoing neighbors vertices $v \in {L} \cap \Gamma^+_{G}(u)$.
+ For a vertex $u$, its sketch, $M_u$, is updated by merging the sketches $M_v$ of all live outgoing neighbor vertices $v \in {L} \cap \Gamma^+_{G}(u)$.
 For each such vertex $v$ and simulation $j$, the operation $M_u[j] = max(M_u[j], M_v[j])$ is performed.
-This approach can be seen as a bottom-up, i.e., reversed,  diffusion process where at each iteration, the cardinality information is pulled from vertices neighbors.
+This approach can be seen as a bottom-up, i.e., reversed,  diffusion process where at each iteration, the cardinality information is pulled from vertices' neighbors.
 
@@
 The process initializes sketches using respective hashes' number of leading zeros.
-Then larger numbers are started to be pulled from all recently changed neighbors.
+Then larger numbers are pulled from all recently changed neighbors.
 The same process is repeated for multiple vertices until the new seed vertex is found.
 To understand the benefits of estimating (instead of counting), we present Fig.~\ref{fig:infuserdiff} which shows an example in the same settings as Fig.~\ref{fig:hyperdiff}.
-One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas {\sc InFuseR}, or another counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example).
+One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas the counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example).
 Doing otherwise, i.e., computing the reachability set cardinalities for all the vertices at once for a given sample, may require $\mathcal{O}(n^2)$ memory and union operations with $\mathcal{O}(n)$ complexity.
-Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
+%Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
 %This is why although the reachability sets in Fig.~\ref{fig:infuserdiff} are shown for all vertices with dense vectors, the ones except that of vertex 1 are greyed out since they are not manipulated.
@@
     \begin{center}
-    \includegraphics[width=0.85\linewidth]{images/sketchdiff.pdf}
+    \includegraphics[width=0.72\linewidth]{images/sketchdiff.pdf}
     \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph.
@@
     \begin{center}
-    \includegraphics[width=0.85\linewidth]{images/infuserdiff.pdf}
-    \caption{{\sc InFuseR} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.
-(a) \label{fig:infuserinit} Toy graph InFuseR initialization.
+    \includegraphics[width=0.77\linewidth]{images/infuserdiff.pdf}
+    \caption{{\sc Counting-based} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.
+(a) \label{fig:infuserinit} Toy graph initialization.
 (b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$.
@@
     \begin{center}
-    \includegraphics[width=\linewidth]{images/sketch-saturation.pdf}
+    \includegraphics[width=0.7\linewidth]{images/sketch-saturation.pdf}
     \caption{ Effect of register saturation on {\tt Amazon0302} dataset using \acro(${\cal J}=256$) without rebuilding against Greedy($\mathcal{R}=20000$) method\cite{kempe2003maximizing}.
@@
 Let $\sigma$ be the real influence for the seed set $S$ including the selected vertex.
-We first compute the marginal influence gain $\delta = \sigma - \varsigma$, which is the additional influence obtained since the last sketch rebuilt.
+We first compute the marginal influence gain $\delta = \sigma - \varsigma$, which is the additional influence obtained since the last sketch was rebuilt.
 Note that $e$, computed at line~\ref{line:e} is the sketch estimate for this value.
@@
 For a single iteration, we have multiple steps each processing a single depth of information, e.g., neighborhood.
-The propagation process is actually a reverse influence process that starts with whole graph as frontier and diffuses register values with respect to the sample graphs.
+The propagation process is actually a reverse influence process that starts with the whole graph as frontier and diffuses register values with respect to the sample graphs.
 In the worst case, i.e., assuming all edges are processed and all the sketch registers are updated at each step, each iteration of the seed-set construction has ${\mathcal O}(d \times (|V|\times \mathcal{J} + |E|))$ time complexity where $d$ is the diameter of $G$ which is the number of steps at each iteration.
@@
 
-These analysis and observations tell us that when the probability of being influenced, i.e., the average probability of an edge being in a sampled subgraph, is high, the samples will be denser and hence, the actual number of steps \acro performs will be smaller.
+These analyses and observations tell us that when the probability of being influenced, i.e., the average probability of an edge being in a sampled subgraph, is high, the samples will be denser and hence, the actual number of steps \acro performs will be smaller.
 Furthermore, depending on the topology of $G$, the marginal influence scores of the first few vertices can be much higher with larger probability values and adding these vertices to the seed set will leave less number of vertices to be processed for later iterations.
-On the other hand, increasing the influence probabilities also increase the number of edges to be processed on the samples.
-Note that other factors that has an impact on the overall performance exist such as the number of iterations skipping the sketch rebuilding.
+On the other hand, increasing the influence probabilities also increases the number of edges to be processed on the samples.
+Note that other factors that have an impact on the overall performance exist such as the number of iterations skipping the sketch rebuilding.
 This also depends on $G$'s structure as well as the influence probabilities.
@@
 This being said, based on the average approximation performance of the sketches, we can argue the following.
-\acro is a greedy algorithm; vertices with a maximum reachability which is estimated via sketches.
+
+\acro is a greedy algorithm; vertices with maximum reachability, which is estimated via sketches, are added to the seed set one after another.
 At each iteration, \acro can choose a vertex worse than the local optimum due to its estimation errors.
-Since the standard error for the FM sketch is $~1.30/\sqrt{\mathcal{J}}$~\cite{durand2003loglog}, we can expect $(1-1.3/\sqrt{256}) \times (1-(1-1/50)^{50}) \approx 58.4\%$ of the optimal solution for $K = 50$ and $\mathcal{J} = 256$.
-However, as the greedy algorithm, the practical performance is better.
-Furthermore, the mistakes in previous iterations can be rectified in later iterations due to submodularity.
+The standard error for the FM sketch is $~1.30/\sqrt{\mathcal{J}}$~\cite{durand2003loglog}.
+Hence, \acro is expected to contain at least $(1-1.3/\sqrt{256})$ of the marginal influence scores at each iteration.
+That is
+it is expected that $(1-1.3/\sqrt{256}) \times (1-(1-1/50)^{50}) \approx 58.4\%$ of the optimal solution will be obtained for $K = 50$ and $\mathcal{J} = 256$. 
+However, as that of the greedy algorithm, \acro's practical performance seems to be better. Furthermore, the mistakes in previous iterations can be rectified in later iterations due to submodularity.
 
@@
 
-The traditional two-step (sample-then-diffuse) computation model stores the (graph) data in a loosely coupled fashion.
+%The traditional two-step (sample-then-diffuse) computation model stores the (graph) data in a loosely coupled fashion.
 % That is the data is clustered w.r.t. their simulation IDs. 
-While designing \acro, we fine-tuned it to be vectorization friendly, including its data layout and computation patterns.
+%While designing \acro, we fine-tuned it to be vectorization friendly, including its data layout and computation patterns.
 These design choices allow us to perform multiple operations, i.e., the same operations but on different data, at once.
@@
 
-We allow a single easy-to-predict branch after the sample edges are generated to exit early without merging the registers.
+%We allow a single easy-to-predict branch after the sample edges are generated to exit early without merging the registers.
 In our experiments, sorting random values $X_r$ significantly increases the performance by clustering similar simulations together while preserving branch locality.
@@
 % Up to 20\% speed-up can be achieved by an early exit at line \ref{ln:early_exit} using sorted random values.   
-Multi-thread parallelization is achieved using OpenMP pragmas; the sketch computation and Monte-Carlo simulations are performed in per-vertex tasks.
-This approach allow us to preserve both temporal and spatial locality.
+Parallelization is achieved using OpenMP pragmas; the sketch computation and Monte-Carlo simulations are performed in per-vertex tasks.
+This approach allows us to preserve both temporal and spatial locality.
 The OpenMP tasks are distributed to the threads via dynamic scheduling with large enough chunks~(8192) to mitigate scheduling costs.
-Even though dynamic scheduling has a higher cost than the static scheduling, it is preferable due to uneven edge distribution among the vertices of $G$ (as well as of the sampled subgraphs).
+Even though dynamic scheduling has a higher cost than static scheduling, it is preferable due to uneven edge distribution among the vertices of $G$ (as well as of the sampled subgraphs).
 
@@
 The algorithms are implemented using {\tt C++20}, and compiled with {\tt GCC 9.3.0} with {\tt "-Ofast"} and {\tt "-march=native"} optimization flags.
-Multi-thread parallelization was achieved with {\tt OpenMP} pragmas.
+Multi-threading was achieved with {\tt OpenMP} pragmas.
 {\tt AVX2} instructions are utilized by handcrafted code with vector intrinsics.
@@
 % \scalebox{0.95}{
-\resizebox{1\columnwidth}{!}{
+\resizebox{0.75\columnwidth}{!}{
 \begin{tabular}{ll||r|r|r|r}
@@
 For comparability, graphs that have been frequently used within the Influence Maximization literature are selected.
-The properties of these graphs are given in Table~\ref{tab:NetProps}:  {\tt Amazon0302} is an Amazon co-purchase network, {\tt DBLP} is DBLP collaboration network, {\tt Orkut} is an online social network where users form friendship,  {\tt Youtube} is a video social video sharing platform that allows friendship relations, {\tt Epinions} is a consumer review trust network, {\tt Friendster} is a social gaming website where users can form friendship edge each other, {\tt LiveJournal} is a blogging site that allows users to add friends, {\tt Pokec} is the Slovakian poker game site friend network, and {\tt Slashdot} networks are friend-foe networks~(08-11, 09-11).
+The properties of these graphs are given in Table~\ref{tab:NetProps}:  {\tt Amazon0302} is an Amazon co-purchase network, {\tt DBLP} is DBLP collaboration network, {\tt Orkut} is an online social network where users form a friendship,  {\tt Youtube} is a video social video sharing platform that allows friendship relations, {\tt Epinions} is a consumer review trust network, {\tt Friendster} is a social gaming website where users can form friendship edge each other, {\tt LiveJournal} is a blogging site that allows users to add friends, {\tt Pokec} is the Slovakian poker game site friend network, and {\tt Slashdot} networks are friend-foe networks~(08-11, 09-11).
 
@@
 The later two settings, i.e., $w = 0.01$  and $w = 0.1$, are selected to emulate the experiments of~\cite{kempe2003maximizing} and~\cite{MixGreedy}.
-In addition to constant edge weights, we performed experiments on two different statistical distributed edge weights to test how algorithms behave on mixed (large and small edge weights together) edge weights.
-The normal distribution setting incurs a small number of extreme sketch values and uniform distribution setting incurs a large number of large sketch values.
+In addition to constant edge weights, we performed experiments with two different statistical distributions over edge weights to test how algorithms behave on mixed (large and small edge weights together) edge weights.
+The normal distribution setting incurs a small number of extreme sketch values and the uniform distribution setting incurs a large number of large sketch values.
 
@@
 In our experiments, we set  $\epsilon=0.2$ to have a high-quality influence maximization baseline as suggested by the software.
-We also experimented with $\epsilon = 1.0$ as authors' suggested, which gives around $8\times$ speedup on average but a reduction on the influence score up to $9\%$.
+We also experimented with $\epsilon = 1.0$ as the authors' suggested, which gives around $8\times$ speedup on average but a reduction on the influence score up to $9\%$.
 
@@
 The approach employs a novel Stop-and-Stare strategy.
-It stops at exponential checkpoints to verify (stare) if there is adequate statistical evidence on the solution quality.
+It stops at exponential checkpoints to verify (stare) if there is adequate statistical evidence of the solution quality.
 We used {\sc Ssa} for our benchmarks since our networks are static.
@@
 
-    \setlength{\tabcolsep}{1.5pt}
+    \setlength{\tabcolsep}{1.0pt}
         \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds,  $\tau=16$ threads, and $w=0.005$.
 Influence scores are given relative to \acro{}.
-The runs that did not finish in 5 hours or due to high memory use shown as "-".
+The runs that did not finish in 5 hours or due to high memory use are shown as "-".
         }
@@
         \centering
-        \resizebox{0.75\linewidth}{!}{
-
-\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+        \resizebox{\tablewidth\linewidth}{!}{
+
+\begin{tabular}{l|r|rrrr|r|rrrr|r|rrrr}
 \toprule
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & {\sc Hyp.} &   {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  {\sc Hyp.}   &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & {\sc Hyp.}  &  {\sc Tim+} &  {\sc Ripples} &   {\sc Skim} &  {\sc Ssa} \\
+Method & {\sc Hyp.} &   {\sc Tim+} &    {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} &  {\sc Hyp.}   &    {\sc Tim+} &     {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} & {\sc Hyp.}  &  {\sc Tim+} &  {\sc Ripp.} &   {\sc Skim} &  {\sc Ssa} \\
 Dataset                 &   {\sc Fus.}         &        &        &         &         & {\sc Fus.}           &         &         &         &      &      {\sc Fus.}         &       &      &        &      \\
@@
 Influence scores are given relative to \acro{}.
-The runs that did not finish in 5 hours or due to high memory use shown as "-".
+The runs that did not finish in 5 hours or due to high memory use are shown as "-".
         }
@@
         \centering
-        \resizebox{0.75\linewidth}{!}{
-
-\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+        \resizebox{\tablewidth\linewidth}{!}{
+
+\begin{tabular}{l|r|rrrr|r|rrrr|r|rrrr}
 \toprule
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & \acrotwo &    {\sc Tim+} &    {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
+Method & \acrotwo &    {\sc Tim+} &    {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripp.} &  {\sc Skim} &   {\sc Ssa} \\
 Dataset                 &            &         &        &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
         \centering
-        \resizebox{0.75\linewidth}{!}{
-
-\begin{tabular}{l|rrrrr|rrrrr|rrrrr}
+        \resizebox{\tablewidth\linewidth}{!}{
+
+\begin{tabular}{l|r|rrrr|r|rrrr|r|rrrr}
 \toprule
 {} & \multicolumn{5}{c|}{Time} & \multicolumn{5}{c|}{Score} & \multicolumn{5}{c}{Memory} \\
-Method & \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &  {\sc Skim} &   {\sc Ssa} \\
+Method & \acrotwo &    {\sc Tim+} &     {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripp.} &    {\sc Skim} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripp.} &  {\sc Skim} &   {\sc Ssa} \\
 Dataset                 &            &         &         &         &         &             &         &         &         &         &            &       &       &       &       \\
@@
 \begin{table*}
-    \setlength{\tabcolsep}{1.2pt}
+    \setlength{\tabcolsep}{1.8pt}
         \caption{Execution times~(in secs), inf.
@@
         \centering
-        \resizebox{0.75\linewidth}{!}{
-
-\begin{tabular}{l|rrrr|rrrr|rrrr}
+        \resizebox{\tablewidth\linewidth}{!}{
+
+\begin{tabular}{l|r|rrr|r|rrr|r|rrr}
 \toprule
 {} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
-Method & \acrotwo &   {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripples} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripples} &   {\sc Ssa} \\
+Method & \acrotwo &   {\sc Tim+} &     {\sc Ripp.} &     {\sc Ssa} &  \acrotwo &    {\sc Tim+} &     {\sc Ripp.} &     {\sc Ssa} & \acrotwo &  {\sc Tim+} &   {\sc Ripp.} &   {\sc Ssa} \\
 Dataset                 &            &        &         &         &             &         &         &         &            &       &       &       \\
@@
 \begin{table*}
-    \setlength{\tabcolsep}{1.2pt}
+    \setlength{\tabcolsep}{1.6pt}
         \caption{Execution times~(in secs), influence scores, and memory use~(in GBs) with $K = 50$ seeds, $\tau=16$ threads and $w \in U(0,0.1)$.
 Influence scores are given relative to \acro{}.
-The runs that did not finish in 5 hours or due to high memory use shown as "-".
+The runs that did not finish in 5 hours or due to high memory use are shown as "-".
         }
@@
 This is partly due to fused sampling; the memory consumption is linearly dependent only on the number of vertices in $G$.
-Both sketch-registers and {\em visited} information are stored per vertex.
+Both sketch registers and {\em visited} information are stored per vertex.
 Hence, \acro's memory consumption stays constant for any simulation parameters or any number of edges.
 That is given ${\cal J}$, \acro's memory use is predictable for any graph.
-On the other hand, the other methods' memory consumption tend to increase with $w$, and their behaviours change with different parameters and graphs.
+On the other hand, baseline methods' memory consumptions tend to increase with $w$, and their behaviours change with different parameters and graphs.
 
@@
 %Indeed, we observe highly varying performance speed-up results in the Tables \ref{tab:timings005}-\ref{tab:timings1}.
-For instance, for {\tt Pokec} with $w = 0.01$, the average diameter of the samples is 43, which makes \acro to lose its edge against its fastest competitor.
+For instance, for {\tt Pokec} with $w = 0.01$, the average diameter of the samples is 43, which makes \acro lose its edge against its fastest competitor.
 On the other hand, with $w = 0.1$, the average diameter is only around 17, and \acro is six times faster than its nearest competitor.
@@
      \centering
-     \includegraphics[width=1\linewidth]{images/speedup-imm}
+     \includegraphics[width=0.86\linewidth]{images/speedup-imm}
    \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Ripples}~($\epsilon\myeq 0.5$) using $\tau=16$ threads.
@@
 The uniform and normal distribution with mean $w_{mean} = 0.05$ also generate influence values in between the ones generated for $w = 0.01$ and $w = 0.1$.
-On the other hand, the changes on the influence vary for different graph; for instance, when $w$ is increased from $0.01$ to $0.1$, for {\tt Slashdot} graphs, the influence increases from around $1200$ to $24000$, whereas it increases from around 1850 to 775000 for {\tt Pokec}.
+On the other hand, the changes in the influence vary for different graphs; for instance, when $w$ is increased from $0.01$ to $0.1$, for {\tt Slashdot} graphs, the influence increases from around $1200$ to $24000$, whereas it increases from around 1850 to 775000 for {\tt Pokec}.
 
@@
      \centering
-     \includegraphics[width=1\linewidth]{images/speedup-skim}
+     \includegraphics[width=0.83\linewidth]{images/speedup-skim}
    \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Skim}~($r\myeq 64,l\myeq 64$) using $\tau=16$ threads.
@@
      \centering
-     \includegraphics[width=1\linewidth]{images/speedup-ssa}
+     \includegraphics[width=0.86\linewidth]{images/speedup-ssa}
    \centering \caption{Speed-up achieved by \acro{}~(${\cal J} = 256$) over {\sc Ssa}~($\epsilon=0.2$) using $\tau=16$ threads.
@@
 % \fixme{Techniques such as using GPUs~\cite{IMGPU,curipples}, sketches for finding set intersections~\cite{cohen2014sketch,IPA}, reverse sampling to estimate the influence~\cite{borgs2014maximizing,minutoli2019fast}, and estimating the necessary number of simulations/samples required for each step~\cite{leskovec2009community} greatly reduces} the execution times.
-\acro borrows much from {\sc InFuseR}~\cite{infuser}, including hash-based fused sampling.
+\acro borrows hash-based fused sampling from {\sc InFuseR}~\cite{infuser}.
+%including hash-based fused sampling.
 {\sc InFuseR} computes influence by memoizing connected components for all vertices and only can work on {\em undirected} datasets.
 It also employs CELF optimization to reduce cardinality computations.
-On the other hand, \acro can process both directed and undirected graphs and uses the Flajolet–Martin sketches in a novel way to estimate cardinality and choose seed candidates.
+On the other hand,
+However, unlike {\sc InFuseR}, \acro can process both directed and undirected graphs and uses the Flajolet–Martin sketches in a novel way to estimate cardinality and choose seed candidates.
 
@@
 It is parallel in the sense that it uses {\tt OpenMP} parallelization during sketch utilization.
-However, the sketch building step is single-threaded.
+However, the sketch-building step is single-threaded.
 In this work, we choose Flajolet-Martin sketches~\cite{flajolet1985probabilistic} for their simplicity, suitability for vectorization and fused sampling, and hence, execution-time performance.
@@
 In addition, \acro does not require removing the reachable vertices from the samples.
-Instead, it uses a rebuilding strategy to improve the result quality.
+Instead, it uses a rebuilding strategy to improve the final seed set's quality.
 
@@
 
-Two-phased Influence Maximization~({\sc Tim+}) borrows ideas from RIS but overcomes its limitations with a novel algorithm~\cite{tim}.
+Two-phased Influence Maximization~({\sc Tim+}) borrows ideas from RIS but overcomes its limitations~\cite{tim}.
 Its first phase computes a lower bound of the maximum expected influence over all size-$K$ node sets.
@@
 
-This work was supported by Scientific and Technological Research Council of Turkey (TÜBİTAK) and EuroHPC Joint Undertaking through grant agreement No 220N254 and grant agreement No 956213 (SparCity), respectively.
+This work was supported by the Scientific and Technological Research Council of Turkey (TÜBİTAK) and EuroHPC Joint Undertaking through grant agreement No 220N254 and grant agreement No 956213 (SparCity), respectively.
 The numerical calculations reported in this paper were partially performed at T{\"{U}}B\.{I}TAK ULAKB\.{I}M, High Performance and Grid Computing Center (TRUBA resources).
